### 2015-02-23 article.tex
rename things for wsc article and add beginning of bib

%        File: 20150216ModelDescription.tex
%     Created: lun. févr. 16 11:00  2015 C
% Last Change: lun. févr. 16 11:00  2015 C
%
\documentclass[a4paper]{article}

%%%%lualatex on
%\usepackage{fontspec}

\usepackage{natbib}

\title{Draft Model}
\author{Simon}
\begin{document}
\maketitle

\section{Introduction}
In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire. Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi1957tradeandmarketintheearlyempireseconomiesinhistoryandtheory}). Following \cite{epstein1996growingartificialsocietiessocialsciencefromthebottomup,
lake_trends_2014,
kohler2000dynamicsinhumanandprimatesocietiesagentbasedmodelingofsocialandspatialprocesses,
tesfatsion2003agentbasedcomputationaleconomicsmodelingeconomiesascomplexadaptivesystems} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.

Here we present such a model, showing that it reproduces well known economical and cultural mechanism and that, given the appropriate archaeological and historical data, it can be used to test hypothesis on those mechanisms.

\section{General Description} 
\begin{itemize}
	\item Resources :\\
		There is $n$ kind of resources, each one is produced by one or more Agents. Agents can exchange those resources and consume it following their need.
	\item  Agents :\\
		M agents with properties:
		\begin{itemize}
			\item Price $(p_1,\cdots,p_n)$ : an amount of money that could be use when in exchange of a good.
			\item Quantity $(q_1,\cdots,q_n)$ : the quantity of each food owned by each agent.
			\item Subjective value $(u_1,\cdots,u_n)$ : the values that each agent associates with each resource.
			\item Need $(b_1, \cdots, b_n)$ :  the quantity of each resource that each agent need to ``survive''. In the first experiments it only says the amount of resource that the agent will consume. It can be seen as the ``intrinsic'' value of the good.
		\end{itemize}
\end{itemize}
\section{Good Production}
%%%%%
%%TODO: Find refs
%%
\label{production}

In the simulation agents produce goods that they will barter (cf section \ref{trade}) and consume (cf section \ref{consumption}). This goods production should reflect the historical good production of the period studied and agent could produce various good in order to barter or sell them using the trade network.

Those production could change during the simulation based on meteorological data or historical knowledge and reflect some complex economical specialisation mechanisms \cite{bentley_specialisation_2005}.

But before integrating historical and meteorological data, and in order to validate the accuracy of the model, we will follow \cite{gintis_emergence_2006}. In its model each agent produces one kind of good in a given and finished quantity which is $n$, the number of different resource available in a simulation, thus allowing him to be able to trade every other goods that it does not produce.

\section{Good Consumption}
\label{consumption}

%%%%%
%%TODO: Find refs
%%

During the simulation the agents ``consume'' the good. This consumption could be vital (if agent do consume certain good they die) or not (as in \cite{macmillan_agent-based_2008}), it could be set as fixed, environmental constraint shared by everyone (the ``intrinsic'' value of things) or could be subject to historical or geographical cultural ``taste'' and variations. Depending on the kind of good agents consume (if they are ``vital'' or not\ldots) it allow us to test a wide range of hypothesis, from purely economical one to cultural consumption assumptions.  In an evolutionary perspective this consumption function could change trough time and is a good way to score the agent fitness and to know which strategies (the list of prices) are the best.

In the current version of the model, and following
\cite{gintis_emergence_2006} to be sure that we could reproduce the expected mechanism, all the goods are consumed in the same proportion by all the agents during all the simulation. A fixed-for-everyone proportion $b_1,\cdots,b_n$ of each resource $(1, \cdots, n)$ is given at the beginning of the simulation.

\section{Cultural Evolution}
In our model the ``cultural change'' is seen as the variation during time of the space of belief of all the agents. Pragmatically it's represented by variation in distribution of subjective value vector.

This subjective value is the value that agents ``put'' on each resources. It could be learn using any mechanism of ``social learning'' (as defined by \cite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \cite{lycett_cultural_2015} for some kind of bias that could be implemented).

In the first experiment we will try simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009} to show the usefulness of the method to study cultural change.

\section{Economical Trading}
\label{trade}

Using the network, the agents are able to barter/trade/exchange resources altogether. Here again, the idea is to propose a model in which several different bargaining/trading mechanisms can be tested. But to begin, we will implement a bargain mechanism already implemented in an Agent Based Model which is the one done by
\cite{gintis_emergence_2006} in order to be quickly able to compare our results and validate ability of the model to recreate economical behaviors.

Later it could be used to study other model such as those developed by 
\cite{rubinstein1985equilibriuminamarketwithsequentialbargaining} and to test more general proposal, as those done by \cite{polanyi1957tradeandmarketintheearlyempireseconomiesinhistoryandtheory,
polanyi1977thelivelihoodofman} about the early economical mechanisms.

Moreover, and in order to be more realistic, and consistently with the cognitive and agent based approach of the project, we will also test assumptions made by people from \emph{Prospect Theory} as proposed by 
\cite{kahneman_prospect_1979}, see also
\cite{camerer_prospect_2004}. The idea here is that traditional economical studies use formal mathematical models that suppose people acting as rational agent, which is a presumption that is far from being valid  in every day life.

Top palliate this problem, Prospect Theory put the focus on the study of the human cognitive abilities and the impact those abilities brings on economics issues. Among various aspect on which prospect theory shed light one can look at how cognitive abilities modify the decisions-making process of human under risk
\cite{weber_disposition_1998}.

Moreover, we think that this approach fit perfectly with our agent based modeling approach (also called Agent based Computational Economy, ACE, when dealing with economical problems, see
\cite{tesfatsion_introduction_2001}).

In the Ginti's model that we are following here, the goal is only to see if a market equilibrium can be reach in a bartering decentralized economy model. So the cognitive trading abilities of the agents are set at their minimum.

During the barter process, all agents meet all the producers of all goods and choose to exchange a certain amount of the good it produce with a certain amount of the other good depending on their own stock and the value they assign respectively to the resource it produce and the resources needed, in a totally rational way, without any cognitive bias.

\bibliographystyle{apalike}
\bibliography{wsc.bib}  
\end{document}

### 2015-02-23 article.tex
change style to wsc. update bib. still some problems in bib to correct (journal and date missing)

@@
-%        File: 20150216ModelDescription.tex
-%     Created: lun. févr. 16 11:00  2015 C
-% Last Change: lun. févr. 16 11:00  2015 C
-%
-\documentclass[a4paper]{article}
+\input{wsc15style.tex}     % download from author kit.  Style files for wsc formatting. Don't remove this line - required for generating the final paper!
 
-%%%%lualatex on
-%\usepackage{fontspec}
+\documentclass{wscpaperproc}
+\usepackage{latexsym}
+\usepackage{caption}
+\usepackage{graphicx}
+\usepackage{mathptmx}
 
-\usepackage{natbib}
+%****************************************************************************
+%% AUTHOR: You may want to use some of these packages. (Optional)
+%\usepackage{amsmath}
+%\usepackage{amsfonts}
+%\usepackage{amssymb}
+%\usepackage{amsbsy}
+%\usepackage{amsthm}
 
-\title{Draft Model}
-\author{Simon}
+\usepackage{xcolor}
+
+\newcommand{\memo}[2]{\textcolor{#1}{#2}}
+\newcommand{\added}[2]{\textcolor{#1}{#2}}
+%\renewcommand{\memo}[2]{} % uncomment in the final version
+%\renewcommand{\added}[2]{#2} % uncomment in the final version
+\newcommand{\todo}[1]{\memo{red}{TODO: #1\\}}
+\newcommand{\simon}[1]{\memo{green}{Simon: #1\\}}
+\newcommand{\jm}[1]{\memo{blue}{JM: #1\\}}
+\newcommand{\new}[1]{\added{orange}{#1}}
+
 \begin{document}
+
+\WSCpagesetup{Montanier, Carrignon, and Zerr}
+
+\title{Model to study co-evolution of trade an culture}
+
+\author{Jean-Marc Montanier\\ [12pt]
+Barcelona Supercomputing Center\\
+Carrer de Jordi Girona, 29, \\
+08034 Barcelona, Spain\\
+\and
+Simon Carrignon\\ [12pt]
+Barcelona Supercomputing Center\\
+Carrer de Jordi Girona, 29, \\
+08034 Barcelona, Spain\\
+\and
+Fabien Zerr\\ [12pt]
+Alsace, Represent
+}
+
 \maketitle
+
+\section*{ABSTRACT}
+\todo{write an abstract}
+
+In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire.
+Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire.
+We think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
+
+Here we present such a model, showing that it reproduces well known economical and cultural mechanism and that, given the appropriate archaeological and historical data, it can be used to test hypothesis on those mechanisms.
 
@@
 In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire.
-Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi1957tradeandmarketintheearlyempireseconomiesinhistoryandtheory}).
-Following \cite{epstein1996growingartificialsocietiessocialsciencefromthebottomup,
+Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi_trade_1957}).
+Following \cite{epstein_growing_1996,
 lake_trends_2014,
-kohler2000dynamicsinhumanandprimatesocietiesagentbasedmodelingofsocialandspatialprocesses,
-tesfatsion2003agentbasedcomputationaleconomicsmodelingeconomiesascomplexadaptivesystems} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
+kohler_dynamics_2000,
+tesfatsion_agent-based_2003} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
 
@@
 Later it could be used to study other model such as those developed by 
-\cite{rubinstein1985equilibriuminamarketwithsequentialbargaining} and to test more general proposal, as those done by \cite{polanyi1957tradeandmarketintheearlyempireseconomiesinhistoryandtheory,
-polanyi1977thelivelihoodofman} about the early economical mechanisms.
+\cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,
+polanyi_livelihood_1977} about the early economical mechanisms.
 
@@
 
-\bibliographystyle{apalike}
+\bibliographystyle{wsc}
 \bibliography{wsc.bib}  

### 2015-02-24 article.tex
fix bib stuff

@@
 Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi_trade_1957}).
-Following \cite{epstein_growing_1996,
-lake_trends_2014,
-kohler_dynamics_2000,
-tesfatsion_agent-based_2003} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
+Following \cite{epstein_growing_1996,lake_trends_2014,kohler_dynamics_2000,tesfatsion_agent-based_2003} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
 
@@
 Later it could be used to study other model such as those developed by 
-\cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,
-polanyi_livelihood_1977} about the early economical mechanisms.
+\cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,polanyi_livelihood_1977} about the early economical mechanisms.
 

### 2015-02-25 article.tex
write intro and start to prepare thing for state of the art

@@
 \section*{ABSTRACT}
-\todo{write an abstract}
 
-In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire.
-Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire.
-We think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
+In this article our aim is to present a model suitable to test various hypothesis on economic and cultural co-evolution during the Roman Empire.
+The ultimate goal is to address debates from history of economy such as the type of economical market found in early empires.
+Agent based modelling is a good way to understand social self-organisation resulting from a large number of interactions.
+It is used in a wide range of fields of research, from economical market mechanisms to social dynamics.
+We therefore apply this type of framework to our study.
 
-Here we present such a model, showing that it reproduces well known economical and cultural mechanism and that, given the appropriate archaeological and historical data, it can be used to test hypothesis on those mechanisms.
+Here we present a model able it reproduces well known economical and cultural mechanism.
+Moreover this model can be envisioned to test hypothesis on those mechanisms.
+Given the appropriate match between the simulations and archaeological and historical data, the results of the model can be validated.
 
-\section{Introduction}
-In this article our aim is to present a model suitable to test various hypothesis on economic and cultural exchange networks during the Roman Empire.
-Among the question we want to address is the traditional debate in history of economy on the type of economic market in early empire (a detailed resume can be found in the first article of \cite{polanyi_trade_1957}).
-Following \cite{epstein_growing_1996,lake_trends_2014,kohler_dynamics_2000,tesfatsion_agent-based_2003} we think that agent based modeling is one of the best way to understand complex social mechanism in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
+\section{INTRODUCTION}
 
-Here we present such a model, showing that it reproduces well known economical and cultural mechanism and that, given the appropriate archaeological and historical data, it can be used to test hypothesis on those mechanisms.
+%Roman empire and need of clean tool
+The trade system of the Roman empire is generally considered to be the first complex European trade network.
+A variety of theories have been proposed to explain the organization and rise of this powerful trade network.
+However, without the appropriate sources and tools these theories are hard to falsify (garnsey et al 1983, lo cascio 2000).
 
-\section{General Description} 
+%type of question we want to answer to and why we need trade an culture
+Among the question we would like to address is the on-going debate on the type of economic market in early empire~\cite{polanyi_trade_1957}.
+Two main view can be found in this debate.
+The first view state that the economical network of the Roman empire has evolve in a very different manner than our current trade network.
+The trade network is then perceived as qualitatively and quantitatively different.
+The second view state that the economical network of the Roman empire constitute a proto-version of our current trade network.
+The difference is then only quantitative but certainly not qualitative.
+We are specifically interested in the changes occurring in the production, trade and consumption of food.
+This can reflect the organization of the trade and cultural network.
+Moreover, this aspect has produced numerous historical records that we can now analyse.
+
+%What is agent-based modeling and what can it do
+Within the EPNet project~\cite{remesal_epnet_2014} we aim to create tools so that theories on the evolution of the trade network of the Roman empire can falsified .
+To do so we need tools that allow us to obtain the qualitative result of a specific theory.
+This qualitative result can then be compared to historical data and help to move forward.
+Following~\cite{epstein_growing_1996,lake_trends_2014,kohler_dynamics_2000,tesfatsion_agent-based_2003,epstein_why_2008} we consider Agent Based Modelling (ABM) to be a good way to test express theories in a falsifiable form.
+Within these models the social self-organisation of a society results from the interactions of a large number of agents.
+The behaviour of these agents is encoded so as to reflect the theory under test.
+It has been already used in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
+
+%What we want to bring to ABM with our work
+The aim of this paper is to use ABM to model the evolution of culture and trade under a unique framework.
+Importantly we aim to create a framework with a low number of parameters in order to ensure that the dynamics observed are simple to analyse.
+In order to assess the quality of this framework we attempt to reproduce results previous obtained in other works study either economy or culture.
+We will then show the capacities of our framework to study the interaction between culture and trade.
+
+%Organisation of the paper
+\todo{write once we are more sure of what we put}
+The paper is organised as follow
+
+\section{PREVIOUS MODELISATIONS OF TRADE AND CULTURE}
+
+This paper will provide a general view to the previous works done on the modelisation of trade, the modelisation of culture and the frameworks attempting to model both.
+While non-exhaustive this review aim to present the main trends on the previous work done on modelisation.
+
+\subsection{Modelisation of Trade}
+%expected utility: 
+%	Shoemaker:
+%prospective theory:
+%	Camerer : explain 10 economical trends that expected utility can not explain without making special cases.
+These are explained thanks to 3 effects from prospective theory: loss-aversion, reflection effects, non-linear weightening of probabilities
+%	: loss aversion
+%	: reflection effects
+%	: non-linear weightening of probabilities
+%	Barberis : 
+%ACE: 
+%	tesfatsion: base of ACE -> goal is to simulate complex interactions from large number of agents in decentralised markets.
+and observe the macroeconomic regularities resulting from that.
+and feedback look.
+notably interested in the formation of economic network (extract cites) and the evolution of behavioural norms (extract cites)
+%	gintis: particular work on pair exchage. Observe convergence to clearing prices and "optimal" utility.
+
+\subsection{Modelisation of Culture}
+%Review in Henrich "evolution of cultural evolution";  Lycett 2015
+%random copy
+%frequency dependent
+%influence of political structure
+
+\subsection{Modelisation of Trade and Culture}
+%stuff with both in it
+%macmillan et l'autre
+
+\section{MODEL DESCRIPTION}
+
+\subsection{Agent-based consumers and traders}
+%tell the story of what is happening
+
+%%%%%
+%%TODO: Find refs
+%%
+In the simulation agents produce goods that they will barter (cf section \ref{trade}) and consume (cf section \ref{consumption}).
+This goods production should reflect the historical good production of the period studied and agent could produce various good in order to barter or sell them using the trade network.
+
+%%%%%
+%%TODO: Find refs
+%%
+During the simulation the agents ``consume'' the good.
+This consumption could be vital (if agent do consume certain good they die) or not (as in \cite{macmillan_agent-based_2008}), it could be set as fixed, environmental constraint shared by everyone (the ``intrinsic'' value of things) or could be subject to historical or geographical cultural ``taste'' and variations.
+
+Using the network, the agents are able to barter/trade/exchange resources altogether.
+
+\subsection{Model structure} 
 \begin{itemize}
 	\item Resources :\\
-		There is $n$ kind of resources, each one is produced by one or more Agents. Agents can exchange those resources and consume it following their need.
+		There are $n$ kind of resources, each one is produced by one or more Agents. Agents can exchange those resources and consume it following their need.
 	\item  Agents :\\
-		M agents with properties:
+		The whole population is defined by a vector of $m$ agents: 
+		$$ population= (a_i, \cdots ,a_m) $$
+		Each agent $i$ is defined by the following vectors:
 		\begin{itemize}
-			\item Price $(p_1,\cdots,p_n)$ : an amount of money that could be use when in exchange of a good.
-			\item Quantity $(q_1,\cdots,q_n)$ : the quantity of each food owned by each agent.
-			\item Subjective value $(u_1,\cdots,u_n)$ : the values that each agent associates with each resource.
-			\item Need $(b_1, \cdots, b_n)$ :  the quantity of each resource that each agent need to ``survive''.
+			\item Price $(p^i_1,\cdots,p^i_n)$ : an amount of money that could be use when in exchange of a good.
+			\item Quantity $(q^i_1,\cdots,q^i_n)$ : the quantity of each food owned by each agent.
+			\item Subjective value $(u^i_1,\cdots,u^i_n)$ : the values that each agent associates with each resource.
+			\item Need $(b^i_1, \cdots, b^i_n)$ :  the quantity of each resource that each agent need to ``survive''.
 In the first experiments it only says the amount of resource that the agent will consume.
@@
 \end{itemize}
-\section{Good Production}
-%%%%%
-%%TODO: Find refs
-%%
-\label{production}
 
-In the simulation agents produce goods that they will barter (cf section \ref{trade}) and consume (cf section \ref{consumption}).
-This goods production should reflect the historical good production of the period studied and agent could produce various good in order to barter or sell them using the trade network.
+\todo{find another title}
+\subsection{Effects tested}
 
-Those production could change during the simulation based on meteorological data or historical knowledge and reflect some complex economical specialisation mechanisms \cite{bentley_specialisation_2005}.
-
-But before integrating historical and meteorological data, and in order to validate the accuracy of the model, we will follow \cite{gintis_emergence_2006}.
+\subsubsection{Good Production}\label{production}
+The production methods can vary depending of geographical or historical factors.
+In order to validate the relevance of the model, we will follow \cite{gintis_emergence_2006}.
 In its model each agent produces one kind of good in a given and finished quantity which is $n$, the number of different resource available in a simulation, thus allowing him to be able to trade every other goods that it does not produce.
 
-\section{Good Consumption}
-\label{consumption}
-
-%%%%%
-%%TODO: Find refs
-%%
-
-During the simulation the agents ``consume'' the good.
-This consumption could be vital (if agent do consume certain good they die) or not (as in \cite{macmillan_agent-based_2008}), it could be set as fixed, environmental constraint shared by everyone (the ``intrinsic'' value of things) or could be subject to historical or geographical cultural ``taste'' and variations.
+\subsubsection{Good Consumption}\label{consumption}
 Depending on the kind of good agents consume (if they are ``vital'' or not\ldots) it allow us to test a wide range of hypothesis, from purely economical one to cultural consumption assumptions.
@@
 
-\section{Cultural Evolution}
+\subsubsection{Cultural Evolution}
 In our model the ``cultural change'' is seen as the variation during time of the space of belief of all the agents.
@@
 
+In the first experiment we will try simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009} to show the usefulness of the method to study cultural change.
+
+\subsubsection{Economical Trading}\label{trade}
+Here again, the idea is to propose a model in which several different bargaining/trading mechanisms can be tested.
+
+But to begin, we will implement a bargain mechanism already implemented in an Agent Based Model which is the one done by
+\cite{gintis_emergence_2006} in order to be quickly able to compare our results and validate ability of the model to recreate economical behaviors.
+
+In the Ginti's model that we are following here, the goal is only to see if a market equilibrium can be reach in a bartering decentralized economy model.
+So the cognitive trading abilities of the agents are set at their minimum.
+
+During the barter process, all agents meet all the producers of all goods and choose to exchange a certain amount of the good it produce with a certain amount of the other good depending on their own stock and the value they assign respectively to the resource it produce and the resources needed, in a totally rational way, without any cognitive bias.
+
+\section{EXPERIMENTAL SETUP}
+
+\section{RESULTS}
+
+\section{FUTURE WORK}
+\subsection{Good Production}
+Those production could change during the simulation based on meteorological data or historical knowledge and reflect some complex economical specialisation mechanisms \cite{bentley_specialisation_2005}.
+
+\subsection{Cultural Evolution}
 This subjective value is the value that agents ``put'' on each resources.
@@
 
-In the first experiment we will try simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009} to show the usefulness of the method to study cultural change.
-
-\section{Economical Trading}
-\label{trade}
-
-Using the network, the agents are able to barter/trade/exchange resources altogether.
-Here again, the idea is to propose a model in which several different bargaining/trading mechanisms can be tested.
-But to begin, we will implement a bargain mechanism already implemented in an Agent Based Model which is the one done by
-\cite{gintis_emergence_2006} in order to be quickly able to compare our results and validate ability of the model to recreate economical behaviors.
-
+\subsection{Good Consumption and economical trading}
+%ACE and prospective trading
+%\subsection{Economical Trading}
 Later it could be used to study other model such as those developed by 
@@
 
-In the Ginti's model that we are following here, the goal is only to see if a market equilibrium can be reach in a bartering decentralized economy model.
-So the cognitive trading abilities of the agents are set at their minimum.
-
-During the barter process, all agents meet all the producers of all goods and choose to exchange a certain amount of the good it produce with a certain amount of the other good depending on their own stock and the value they assign respectively to the resource it produce and the resources needed, in a totally rational way, without any cognitive bias.
+\section{CONCLUSION}
 

### 2015-03-02 article.tex
add in comment stuff about economics
ajout de texte brouillon pour l'etat de l'art et des refs qui correspondent dans le bib. reste a ecrire pour de vrai toute la section
update intro and state of the art. first version for these parts. send to xavi

@@
 
+\todo{Rewrite later}
 In this article our aim is to present a model suitable to test various hypothesis on economic and cultural co-evolution during the Roman Empire.
@@
 %Roman empire and need of clean tool
+\todo{don't we have a more recent and better ref for that ?}
 The trade system of the Roman empire is generally considered to be the first complex European trade network.
-A variety of theories have been proposed to explain the organization and rise of this powerful trade network.
-However, without the appropriate sources and tools these theories are hard to falsify (garnsey et al 1983, lo cascio 2000).
+A variety of theories have been proposed to explain the development of this network as well as its organization.
+However, the appropriate tools are currently missing to falsify these theories  \cite{garnsey_trade_1983}.
 
 %type of question we want to answer to and why we need trade an culture
-Among the question we would like to address is the on-going debate on the type of economic market in early empire~\cite{polanyi_trade_1957}.
-Two main view can be found in this debate.
-The first view state that the economical network of the Roman empire has evolve in a very different manner than our current trade network.
-The trade network is then perceived as qualitatively and quantitatively different.
-The second view state that the economical network of the Roman empire constitute a proto-version of our current trade network.
-The difference is then only quantitative but certainly not qualitative.
-We are specifically interested in the changes occurring in the production, trade and consumption of food.
-This can reflect the organization of the trade and cultural network.
-Moreover, this aspect has produced numerous historical records that we can now analyse.
+We want notably to address the on-going debate about the characteristics of the economic market in Roman empire~\cite{polanyi_trade_1957}.
+Two main views are found on this debate.
+The first view states that the economical network of the Roman empire had characteristics very different than our modern trade network.
+The trade network of the Roman empire is then perceived to be qualitatively and quantitatively different than our modern trade network.
+The second view state that the economical network of the Roman empire constitutes a proto-version of our modern trade network.
+The difference between the two networks is then only quantitative and not qualitative.
+\jm{not sure that food item is the right word}
+Among all the goods transiting on the Roman network, we will focus on the food items. 
+\jm{i find the justification weak. any ideas ?}
+These are interesting as they reflect the organization of both the trade network and the cultural network.
+Moreover, the food items were circulating in amphorae which arrived up to us.
+As a consequence it will be possible to compare the qualitative output of a simulation with the qualitative structure of the historical data.
 
 %What is agent-based modeling and what can it do
-Within the EPNet project~\cite{remesal_epnet_2014} we aim to create tools so that theories on the evolution of the trade network of the Roman empire can falsified .
-To do so we need tools that allow us to obtain the qualitative result of a specific theory.
-This qualitative result can then be compared to historical data and help to move forward.
-Following~\cite{epstein_growing_1996,lake_trends_2014,kohler_dynamics_2000,tesfatsion_agent-based_2003,epstein_why_2008} we consider Agent Based Modelling (ABM) to be a good way to test express theories in a falsifiable form.
+\jm{maybe this paragraph should go before ?}
+Within the EPNet project~\cite{remesal_epnet_2014} we aim to create tools able to falsify theories on the characteristics of the trade network of the Roman empire.
+These tools have to produce the qualitative characteristics resulting from a specific theory.
+This qualitative result can then be compared to historical data and highlight the differences between the reality and the simulations.
+Following~\cite{epstein_growing_1996,lake_trends_2014,kohler_dynamics_2000,tesfatsion_agent-based_2003,epstein_why_2008} we consider Agent Based Modelling (ABM) is a good framework to express theories in a falsifiable form.
 Within these models the social self-organisation of a society results from the interactions of a large number of agents.
@@
 %What we want to bring to ABM with our work
-The aim of this paper is to use ABM to model the evolution of culture and trade under a unique framework.
-Importantly we aim to create a framework with a low number of parameters in order to ensure that the dynamics observed are simple to analyse.
-In order to assess the quality of this framework we attempt to reproduce results previous obtained in other works study either economy or culture.
-We will then show the capacities of our framework to study the interaction between culture and trade.
+\todo{the justification of reproducing previous works should be stronger}
+The aim of this paper is to develop an ABM to model the evolution of culture and trade.
+Importantly we aim to create a model with a low number of parameters in order to ensure that the dynamics observed are simple to analyse.
+In order to assess the quality of this model we use it to reproduce qualitatively certain dynamics observed in either economy or culture.
+We will then show the capacities of our model to study the interaction between culture and trade.
 
@@
 
-This paper will provide a general view to the previous works done on the modelisation of trade, the modelisation of culture and the frameworks attempting to model both.
-While non-exhaustive this review aim to present the main trends on the previous work done on modelisation.
+\todo{and/or is ugly, look for another way}
+This section will provide a brief review of the previous approaches to model trade and/or culture. While non-exhaustive, this review presents the mains trends of the previous work done.
 
 \subsection{Modelisation of Trade}
-%expected utility: 
-%	Shoemaker:
-%prospective theory:
-%	Camerer : explain 10 economical trends that expected utility can not explain without making special cases.
-These are explained thanks to 3 effects from prospective theory: loss-aversion, reflection effects, non-linear weightening of probabilities
-%	: loss aversion
-%	: reflection effects
-%	: non-linear weightening of probabilities
-%	Barberis : 
-%ACE: 
-%	tesfatsion: base of ACE -> goal is to simulate complex interactions from large number of agents in decentralised markets.
-and observe the macroeconomic regularities resulting from that.
-and feedback look.
-notably interested in the formation of economic network (extract cites) and the evolution of behavioural norms (extract cites)
-%	gintis: particular work on pair exchage. Observe convergence to clearing prices and "optimal" utility.
+
+Multiple approaches have been proposed to model the economical interactions between humans.
+Among them, this section will review three which constitute major trends and are the most relevant to our study.
+The approaches are presented in chronological order.
+
+The first approach to be reviewed is the Expected Utility (EU) which became a main trend after the second world war~\cite{schoemaker_expected_1982}.
+The goal of this model was to propose a first explanation to the economical actions of humans along the following axes: descriptive, predictive, postdictive and prescriptive.
+More precisely this approach model individuals as agents facing a choice among risky options.
+Each agent is aware of the probability that an event will happen and the utility (economical reward) associated to that event.
+Each agent can then maximise its expected utility by choosing the proper actions.
+By applying this methodology to various economical problems it became clear that humans do not see problems as probabilities and do not directly reason on them.
+From the perspective of this theory, humans show a collection of irrational behaviours, notably a strong aversion to risk.
+
+In an attempt to overcome the shortcomings of the EU models a new theory was introduced, the prospective theory.
+This theory conserve an approach close to the EU: individuals are modelled as agents facing risky actions each with a certain probability and utility.
+However, the agents do not face these problems by maximising the expected utility.
+They are rather endowed with behaviours composed of three key elements~\cite{camerer_prospect_2004}.
+First, the ``loss aversion'' element models the fact that individuals are much more sensitive to loss than to gains of the same magnitude.
+Second, the ``reference dependence'' models the fact that individuals measure their losses and gains with regards to their current possessions.
+Finally, individuals do not weight linearly the probabilities e.g.
+an individual will perceive a higher gain between 100 and 200 than between 1000 and 1100.
+Multiple difficulties have been encountered in applying this approach to practical problems of the real life.
+These are attributed to the lack of definition of certain elements of the theory and therefore the near impossibility to measure them~\cite{barberis_thirty_2012}.
+
+The two previous approaches address an economical problem as a block which all agents face in a similar fashion.
+As a consequence, the emerging properties due to the interaction of numerous agents can not be studied.
+Moreover, these approaches are not suitable to model systems composed of individuals with various characteristics and interests.
+The Agent-based Computational Economics (ACE) fields propose specifically to model the complex outcomes raising from a large number of interactions in a decentralized market~\cite{tesfatsion_agent-based_2003}.
+Naturally this approach is interesting for our project based on multi-agent methodology and it constitutes a source of hypothesis to test to characterise the economical network of the Roman empire.
+More specifically, multiple hypothesis are proposed on the formation of different types of economical networks depending on the economical rules between the agents~\cite{kirman_evolving_2001,tesfatsion_structure_2001}.
+Another interesting track is the study of the evolution of behavioural norms in an economical network~\cite{epstein_learning_2001,axelrod_complexity_1997}.
+Finally~\cite{gintis_emergence_2006} has proposed a specific analysis on the emergence of price structure when only pair exchanges are considered.
+\todo{put the section}
+This latest work constitutes naturally a strong reference and will be explained in further details in section XXX.
 
 \subsection{Modelisation of Culture}
-%Review in Henrich "evolution of cultural evolution";  Lycett 2015
-%random copy
-%frequency dependent
-%influence of political structure
+
+The second aspect we wish to model is the evolution of the culture in the Roman empire.
+The evolutionary framework (generally used in Biology) has been proposed to study the changes of culture and found to be suitable,  particularly in the case of historical and archaeological studies~\cite{lycett_cultural_2015,henrich_evolution_2003}.
+
+Within this framework, the individual preferences for cultural traits (such as music taste or shapes of pottery) are copied from one individual to the other.
+Each individual is then adding some small variations to this cultural trait she just acquired.
+The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
+Studies are then performed on the three key steps of the framework: the transmission, the variation and the differential replication.
+Interestingly the study of these elements is not only done thanks to humans but also thanks to other animals.
+
+The transmission mechanisms are the means used to transfer cultural traits from one individuals to another.
+A large number of social learning schemes can be envisioned~\cite{heyes_social_1994}.
+Notably, the mechanisms do not necessarily have to be as complex as teaching, since emulation and imitation can be sufficient to pass on certain cultural traits.
+
+The variation mechanisms are at the heart of the creation of the creation of new cultural elements~\cite{obrien_variation_1990}.
+These may happen due to some errors during the copy process~\cite{schillinger_copying_2014}.
+In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}.
+
+The last element is the one that will interest us the most in this study: the differential replication between different cultural traits.
+If a cultural trait is found more often than the others in the population it means that something modified the rate at which it is adopted by each agent.
+%The reproduction rate of ideas in a population can be characterise by different rates: directional, disruptive or stabilisation~\cite{rendell_cognitive_2011}. 
+Multiple processes can be at play behind the reproduction of cultural traits.
+Among them the three following will interest us due to their simplicity to test in an agent-based modelisation.
+First is the random copy of one trait from an agent to another agent.
+\todo{get a ref on that}
+This type of mechanism reproduces well the changes in musical preferences.
+Second are the the copy based on the frequency at which a cultural trait is observed.
+If a common trait is reproduced more often then we speak about ``conformity.'' If on the contrary the less common trait is preferred for reproduction we speak of ``rarity''.
+Finally a trait can be preferred depending on whom is carrying it.
+Among these preferences the prestige of the individual carrying it can constitute an explanation for the adoption foreign cultural traits in the Roman empire.
 
 \subsection{Modelisation of Trade and Culture}
-%stuff with both in it
-%macmillan et l'autre
+
+To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture.
+The model in~\cite{bentley_specialisation_2005} is proposed to study the wealth inequalities in a dynamic network.
+In this model the agents are in a virtual environment and can produce, consume and trade two products.
+This model has two major constraints which makes it unfit for the study presented here.
+First, the products are only for trade purposes and are not used as cultural factors, i.e.
+some goods can not be accumulated so that the agent show them to others.
+The cultural aspects appear only through the price associated to each product.
+Second, only two goods are considered and the system can not scale up to an undetermined number of products without major modifications.
+% Agents can negotiate the rate at which the two products will be traded.
+The agents have a will (hard-coded in their behaviour) to keep their wealth and number of agents within their trading network above a threshold.
+
+The model proposed in~\cite{macmillan_agent-based_2008} studies the settlement of primitive agricultural societies.
+In this model agents produce, trade and consume 2 essentials goods and 2 non-essentials goods.
+This model is interesting since it introduce the notion of non-essential goods which can be used to reflect the culture of a society.
+However, this framework is constrained as it does not allow the evolution of the trading network.
+Moreover the behaviour chosen for the agents is rather complex and not justified by observations made in economy or evolution of culture.
+
+The model presented in this work proposes to integrate the most interesting features from~\cite{bentley_specialisation_2005} and~\cite{macmillan_agent-based_2008}.
 

### 2015-03-03 article.tex
put the story of the model in place

@@
 
+\todo{find another title}
 \subsection{Agent-based consumers and traders}
@@
 
-%%%%%
-%%TODO: Find refs
-%%
-In the simulation agents produce goods that they will barter (cf section \ref{trade}) and consume (cf section \ref{consumption}).
+This model is composed of multiple agents producing goods of a fixed number of types.
+The agents are endowed with storage abilities for each good that can be produced.
+On top of	producing the agents have the ability to exchange and consume the goods.
+The specific rules for production, consumption and trading will vary depending on the hypothesis tested.
+Nevertheless the structure of the environment and the proceeding of a simulation will be the same for all hypothesis tested in this model.
+
+One time step of the simulation is divided in three phases.
+In the first phase all agents produce goods.
+Each agent is assigned one type of good, and it will produce only this type of good at each first phase.
+In the second phase all agents enter trade with other agents according to their own interest.
+Each agent has the possibility to choose with which other agent it will trade products.
+Once two agents agree to trade, the agents decide which products will be exchanged and in which quantities.
+When an agreement is found, the trade occur and the agents look for other potential partners.
+Within one trading phase, an agent can meet only one time each other agents.
+In the third phase all agent consume goods according to their own rules.
+A unit of a good consumed disappears from the stock of the agent.
+
+%In the simulation agents produce goods that they will barter (cf section \ref{trade}) and consume (cf section \ref{consumption}).
 This goods production should reflect the historical good production of the period studied and agent could produce various good in order to barter or sell them using the trade network.
 
-%%%%%
-%%TODO: Find refs
-%%
-During the simulation the agents ``consume'' the good.
-This consumption could be vital (if agent do consume certain good they die) or not (as in \cite{macmillan_agent-based_2008}), it could be set as fixed, environmental constraint shared by everyone (the ``intrinsic'' value of things) or could be subject to historical or geographical cultural ``taste'' and variations.
+More formally the model is composed of the following elements
 
-Using the network, the agents are able to barter/trade/exchange resources altogether.
-
-\subsection{Model structure} 
 \begin{itemize}
@@
 \subsection{Good Production}
+
+\todo{speak about good collection from the environment}
+
 Those production could change during the simulation based on meteorological data or historical knowledge and reflect some complex economical specialisation mechanisms \cite{bentley_specialisation_2005}.
@@
 \subsection{Good Consumption and economical trading}
+
+\todo{speak about death of the agents}
+
 %ACE and prospective trading

### 2015-03-04 article.tex
kinda draft of everything but the exp setup and results

@@
 
+\todo{speak about the fact that economy looks at convergence and culture looks before}
+
 To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture.
@@
 
-More formally the model is composed of the following elements
+More formally the model is composed as follow. $r$ is the number of ressources present in the environment. The whole population is defined by a vector of $m$ agents: 
+		$$ population = (a_i, \cdots ,a_m) $$
 
-\begin{itemize}
-	\item Resources :\\
-		There are $n$ kind of resources, each one is produced by one or more Agents. Agents can exchange those resources and consume it following their need.
-	\item  Agents :\\
-		The whole population is defined by a vector of $m$ agents: 
-		$$ population= (a_i, \cdots ,a_m) $$
-		Each agent $i$ is defined by the following vectors:
-		\begin{itemize}
-			\item Price $(p^i_1,\cdots,p^i_n)$ : an amount of money that could be use when in exchange of a good.
-			\item Quantity $(q^i_1,\cdots,q^i_n)$ : the quantity of each food owned by each agent.
-			\item Subjective value $(u^i_1,\cdots,u^i_n)$ : the values that each agent associates with each resource.
-			\item Need $(b^i_1, \cdots, b^i_n)$ :  the quantity of each resource that each agent need to ``survive''.
-In the first experiments it only says the amount of resource that the agent will consume.
-It can be seen as the ``intrinsic'' value of the good.
-		\end{itemize}
-\end{itemize}
+Each agent $i$ is defined by 4 vectors each of size $r$. The first correspond to the quantity of each good that the agent possesses: $$ quantity = (q^i_1,\cdots,q^i_n) $$
 
-\todo{find another title}
-\subsection{Effects tested}
+Each agent makes its own estimate on the price to attribute to a certain good. This price estimate is used for both selling and buying goods :
+$$ price = (p^i_1,\cdots,p^i_n) $$
 
-\subsubsection{Good Production}\label{production}
+Finally, as mentioned before, each agent will consume a certain quantity of each good. This quantity can be a property of the agent, i.e. each agent consumes a different quantity of each product :
+$$ consumption = (c^i_1, \cdots, c^i_n) $$
+
+The elments listed above constitute the basic structure of the model.
+Different behaviours can be used for the agents and world depending on the assumption to test.
+This scheme allow us to have a model ahieving the two main goals listed in section~\ref{}.
+First, this model has a simple behaviour and few parameters to analyse.
+Second, this  model is flexible enough to allow the study of multiple hypothesis while conserving the same units that can therefore be compared between simulations.
+
+\subsection{Validation}
+
+In order to validate our model mulitple experiments from the litterature in economy or evolution of culture have been selected to be reproduced.
+The basis of selection of these experiments is two fold.
+First, the experiment selected has to be simple and highlight clearly one effect.
+This restriction is to maintain the clarity of the paper.
+Second, these effects should consist the basis of our further studies toward understanding the principles of the roman economics.
+As a consequence the hypothesis tested will constitute valid hypothesis for the study of the economics and culture of the roman empire.
+
+\subsubsection{Economical Trading}\label{trade}
+
 The production methods can vary depending of geographical or historical factors.
 In order to validate the relevance of the model, we will follow \cite{gintis_emergence_2006}.
-In its model each agent produces one kind of good in a given and finished quantity which is $n$, the number of different resource available in a simulation, thus allowing him to be able to trade every other goods that it does not produce.
+In this model, the goal is to observe the convergence of price to a market equilibrium in a bartering decentralized economy model.
+In the orignal model it is shown that the prices can converge to the market clearing price.
 
-\subsubsection{Good Consumption}\label{consumption}
-Depending on the kind of good agents consume (if they are ``vital'' or not\ldots) it allow us to test a wide range of hypothesis, from purely economical one to cultural consumption assumptions.
-In an evolutionary perspective this consumption function could change trough time and is a good way to score the agent fitness and to know which strategies (the list of prices) are the best.
+In this economical model the agents are ranked with regards to the value of their stock. This value is computed as follow ...
+\todo{find the computation}
 
-In the current version of the model, and following
-\cite{gintis_emergence_2006} to be sure that we could reproduce the expected mechanism, all the goods are consumed in the same proportion by all the agents during all the simulation.
+In this model each agent produces only one type of good.
+During the trading process, all agents meet each other.
+Since one agent is producing only one good it will only trade with the agents not producing this good.
+The procedure to choose the trading partners is detailed in algorithm XXXX.
+\todo{do the algorithm}
+Briefly summarised, for each good that it does not produced, an agent will look for the parter that offer the best trade, i.e.
+the agent that proposes to exchange the most of the other product for the fewest of the product produced by the agent.
+
+All agents of the simulation have the same constant consumption vector.
 A fixed-for-everyone proportion $b_1,\cdots,b_n$ of each resource $(1, \cdots, n)$ is given at the beginning of the simulation.
+At the end of the consumption phase all remaining products are removed from the agents.
+
+At the end of a time step, each agent has the opportunity to update its prices .
+Following the strategy proposed in the original model the XXX\% agents with the worst economical results adopt the strategy of the XXX\% best agents.
 
 \subsubsection{Cultural Evolution}
-In our model the ``cultural change'' is seen as the variation during time of the space of belief of all the agents.
-Pragmatically it's represented by variation in distribution of subjective value vector.
 
-In the first experiment we will try simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009} to show the usefulness of the method to study cultural change.
+In our model the ``cultural change'' is represented by the variations in the distribution of prices for each good.
+In order to validate our model we will try two simple biases: simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009}.
+The aim is to show that these simple modifications can allow us to obvserve the emergence of different cultures, each modifying the price structure obtained.
+The price structure obtained will be also compare to the obtained by the the economical model explained at the previous section.
 
-\subsubsection{Economical Trading}\label{trade}
-Here again, the idea is to propose a model in which several different bargaining/trading mechanisms can be tested.
-
-But to begin, we will implement a bargain mechanism already implemented in an Agent Based Model which is the one done by
-\cite{gintis_emergence_2006} in order to be quickly able to compare our results and validate ability of the model to recreate economical behaviors.
-
-In the Ginti's model that we are following here, the goal is only to see if a market equilibrium can be reach in a bartering decentralized economy model.
-So the cognitive trading abilities of the agents are set at their minimum.
-
-During the barter process, all agents meet all the producers of all goods and choose to exchange a certain amount of the good it produce with a certain amount of the other good depending on their own stock and the value they assign respectively to the resource it produce and the resources needed, in a totally rational way, without any cognitive bias.
+The production, consumption and trade phases described are not modified.
+However the price update phase is modified as follow.
+When the random copy behaviour is used each agent has a XXX\% chance to copy a new price from one agent selected randomly.
+Two frequency dependent behaviour are proposed.
+The first to be tested is the conformist behaviour with which each agent at each agent will have a XXXX\% chance to select the most common price for each good.
+The second to be tested is the rarity behaviour with which each agent at each iteration will have a XXX\% chance to select the least common beahviour.
 
@@
 
-\section{FUTURE WORK}
-\subsection{Good Production}
+\section{CONCLUSION}
 
-\todo{speak about good collection from the environment}
+\section{DISCUSSION}
 
-Those production could change during the simulation based on meteorological data or historical knowledge and reflect some complex economical specialisation mechanisms \cite{bentley_specialisation_2005}.
+In future works numerous, more realistic and complex dynamics can be studied in the same model.
+First the constraints on the production could be relaxed so that each agent can choose the products it wishes to produce at the current time step.
+Moreover meterological factors can modify the quality of the production (noisy outcome of the proces) thus making the process more realistic and more complex~\cite{bentley_specialisation_2005}.
 
-\subsection{Cultural Evolution}
-This subjective value is the value that agents ``put'' on each resources.
-It could be learn using any mechanism of ``social learning'' (as defined by \cite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \cite{lycett_cultural_2015} for some kind of bias that could be implemented).
-
-\subsection{Good Consumption and economical trading}
-
-\todo{speak about death of the agents}
+The goods themselves can be of different type: ``vital'' or ``common''.
+The absence of a ``vital'' good would then lead to the death of the agent.
+Thus making the need to trade at the best price even stronger for the agent.
+The ``common'' goods on the other sides would be interesting to observe the evolution of a culture out of the necessity of survival.
+The mechanisms behind the strong use of a non-essential product can then be studied.
+Naturally in the study of these questions the consumption function would change trough time for the agent.
 
 %ACE and prospective trading
-%\subsection{Economical Trading}
-Later it could be used to study other model such as those developed by 
+More complex models can also be envisionned such as those developed by 
 \cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,polanyi_livelihood_1977} about the early economical mechanisms.
-
 Moreover, and in order to be more realistic, and consistently with the cognitive and agent based approach of the project, we will also test assumptions made by people from \emph{Prospect Theory} as proposed by
@@
 
-\section{CONCLUSION}
+This subjective value is the value that agents ``put'' on each resources.
+It could be learn using any mechanism of ``social learning'' (as defined by \cite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \cite{lycett_cultural_2015} for some kind of bias that could be implemented).
+
+In order to test these hypohtesis more advanced agents are naturally envisionned.
+One possible tracks of investigation is agents endowed with self-adaptation abilities as proposed in Reinforcement Learning or Developmental Learning.
+Another possibility is to follow the cognitive approaches that propose to model the complexity of the human behaviour in general representations such as BDI and XXXX.
 

### 2015-03-09 article.tex
added some references and structure suggestions

@@
 \usepackage{mathptmx}
+\usepackage[utf8]{inputenc}
 
@@
 \newcommand{\jm}[1]{\memo{blue}{JM: #1\\}}
+\newcommand{\xrc}[1]{\memo{orange}{XRC: #1\\}}
 \newcommand{\new}[1]{\added{orange}{#1}}
@@
 \todo{Rewrite later}
-In this article our aim is to present a model suitable to test various hypothesis on economic and cultural co-evolution during the Roman Empire.
+In this article our aim is to present a model suitable to test various hypotheses on economic and cultural co-evolution during the Roman Empire.
 The ultimate goal is to address debates from history of economy such as the type of economical market found in early empires.
@@
 \todo{don't we have a more recent and better ref for that ?}
+\xrc{There is plenty of evidence of previous trade networks (e.g. Sahoglu, 2005 for Bronze Age, Malkin, 2003 for greek identity). Is Rome different than the rest of the Mediterranean...? How?}
 The trade system of the Roman empire is generally considered to be the first complex European trade network.
 A variety of theories have been proposed to explain the development of this network as well as its organization.
-However, the appropriate tools are currently missing to falsify these theories  \cite{garnsey_trade_1983}.
+However, the appropriate tools are currently missing to falsify these theories \cite{garnsey_trade_1983} \xrc{what theories?
+why the tools?}.
 
@@
 The difference between the two networks is then only quantitative and not qualitative.
+\\
+\xrc{this needs further discussion: at what level they are different, etc. it is mainly defining what is a market economy, and the question is: was the roman trade network a market economy?}
 \jm{not sure that food item is the right word}
+\\
 Among all the goods transiting on the Roman network, we will focus on the food items. 
 \jm{i find the justification weak. any ideas ?}
+\xrc{justification is based on the existence of evidence: the shipment of containers such as amphorae, which are used to transport selected items (olive oil, salsamenta, etc) is one of the best datasets in terms of the archaeological record \cite{bevan_2014}.}
 These are interesting as they reflect the organization of both the trade network and the cultural network.
@@
 As a consequence it will be possible to compare the qualitative output of a simulation with the qualitative structure of the historical data.
+
+\xrc{I would switch the line of thought: a) we have hypotheses, b) we need evidence to evaluate them and c) containers are the best existing datasets to do that}
 
@@
 
+\xrc{A potential reviewer would say that you need to specify your research question and needs before justifying the tool}
+
+\xrc{I would propose a different structure for the intro:}
+\begin{enumerate}
+    \item \emph{trade networks are increasingly being recognised as a key process in ancient Mediterranean}
+    \item \emph{this process played a role in the trajectories of cultural change of the different regions, which were interconnected by trade}
+    \item \emph{these two elements (cultural transmission and trade networks) are traditionally been studied as isolated systems}
+    \item \emph{this is wrong because blablabla...}
+    \item \emph{we propose a model of coevolution to explore the deep links between trade and cultural transmission in the ancient Mediterranean}
+\end{enumerate}
+
 %Organisation of the paper
@@
 
+\xrc{I would suggest to use modelling instead of modelisation}
 \subsection{Modelisation of Trade}
@@
 The approaches are presented in chronological order.
+
+\xrc{I'm not sure if it would be wiser to limit this section to models of ancient trade...otherwise a proper lit. review becomes huge.}
 
@@
 
+\xrc{models of cultural change, not culture in general?}
+
+\xrc{what is exactly the definition of culture used in the paper?
+I would suggest this one: \emph{Culture is socially learned information capable of affecting  individual phenotypes.
+People acquire culture from other  individuals, via teaching or imitation} \cite{richerson1996}}
+
 The second aspect we wish to model is the evolution of the culture in the Roman empire.
-The evolutionary framework (generally used in Biology) has been proposed to study the changes of culture and found to be suitable,  particularly in the case of historical and archaeological studies~\cite{lycett_cultural_2015,henrich_evolution_2003}.
+The evolutionary framework (generally used in Biology) has been proposed to study the changes of culture and found to be suitable,  particularly in the case of historical and archaeological studies~\cite{lycett_cultural_2015,henrich_evolution_2003}\xrc{henrich's paper is not on archaeology or history, better reference \cite{shennan_2008}}.
 
@@
 
+\xrc{I would use social learning instead of cultural transmission}
+
 The transmission mechanisms are the means used to transfer cultural traits from one individuals to another.
-A large number of social learning schemes can be envisioned~\cite{heyes_social_1994}.
+A large number of social learning schemes can be envisioned~\cite{heyes_social_1994} \xrc{a better reference would be \cite{henrich_evolution_2003}}.
 Notably, the mechanisms do not necessarily have to be as complex as teaching, since emulation and imitation can be sufficient to pass on certain cultural traits.
@@
 These may happen due to some errors during the copy process~\cite{schillinger_copying_2014}.
-In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}.
+In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}\xrc{see also recombination \cite{sole_2013}}.
 
+\xrc{Instead of differential replication I would use \emph{biased selection}}
 The last element is the one that will interest us the most in this study: the differential replication between different cultural traits.
-If a cultural trait is found more often than the others in the population it means that something modified the rate at which it is adopted by each agent.
+If a cultural trait is found more often than the others in the population it means that something modified the rate at which it is adopted by each agent \xrc{beyond drift effects produced by random copy of neutral traits \cite{bentley_2004}}.
 %The reproduction rate of ideas in a population can be characterise by different rates: directional, disruptive or stabilisation~\cite{rendell_cognitive_2011}. 
-Multiple processes can be at play behind the reproduction of cultural traits.
+Multiple processes can be at play behind the reproduction \xrc{selection?
+transmission?
+reproduction is too biological} of cultural traits.
 Among them the three following will interest us due to their simplicity to test in an agent-based modelisation.
 First is the random copy of one trait from an agent to another agent.
-\todo{get a ref on that}
-This type of mechanism reproduces well the changes in musical preferences.
+\todo{get a ref on that} \xrc{you can use \cite{bentley_2004}}
+This type of mechanism reproduces well the changes in musical preferences \xrc{music here is odd; if an example is used it should be related to the topic of the paper}.
 Second are the the copy based on the frequency at which a cultural trait is observed.
-If a common trait is reproduced more often then we speak about ``conformity.'' If on the contrary the less common trait is preferred for reproduction we speak of ``rarity''.
+If a common trait is reproduced more often then we speak about ``conformity.'' If on the contrary the less common trait is preferred for reproduction we speak of ``rarity'' \xrc{nope, we speak of anti-conformism}.
 Finally a trait can be preferred depending on whom is carrying it.
-Among these preferences the prestige of the individual carrying it can constitute an explanation for the adoption foreign cultural traits in the Roman empire.
+Among these preferences the prestige of the individual carrying it can constitute an explanation for the adoption foreign cultural traits in the Roman empire \xrc{this is known as model biased transmission}.
+
+\xrc{Again, I should focus the lit.review on models of cultural change in at least ancient societies, this is too broad.}
 
@@
 The model presented in this work proposes to integrate the most interesting features from~\cite{bentley_specialisation_2005} and~\cite{macmillan_agent-based_2008}.
+
+\xrc{here a research question should be defined, and some hypotheses, e.g.: \emph{Did trade networks between regions bias cultural change towards anti-conformism?} or \emph{What is the relation between shipment time and cultural change?}}
+
+\xrc{A co-evolutionary model is really difficult to study, so a careful justification needs to be done on why this is here needed}
 
@@
 \subsection{Validation}
+\xrc{Validation is impossible for a theoretical model.
+Either you use verification if the goal is to check that implementation is correct, or design experiment for defining the experimens that will be used to explore the model.}
 

### 2015-03-11 article.tex
start to address comments of xavi on introduction. miss key examples and refs

@@
 
-\author{Jean-Marc Montanier\\ [12pt]
+\begin{figure*}[htb]
+{
+\centering
+Jean-Marc Montanier\\
+Simon Carrignon\\ 
+Xavier Rubio\\
+\vspace{12pt}
 Barcelona Supercomputing Center\\
@@
 08034 Barcelona, Spain\\
-\and
-Simon Carrignon\\ [12pt]
-Barcelona Supercomputing Center\\
-Carrer de Jordi Girona, 29, \\
-08034 Barcelona, Spain\\
-\and
-Fabien Zerr\\ [12pt]
-Alsace, Represent
 }
+\end{figure*}
 
@@
 
-%Roman empire and need of clean tool
-\todo{don't we have a more recent and better ref for that ?}
-\xrc{There is plenty of evidence of previous trade networks (e.g. Sahoglu, 2005 for Bronze Age, Malkin, 2003 for greek identity). Is Rome different than the rest of the Mediterranean...? How?}
-The trade system of the Roman empire is generally considered to be the first complex European trade network.
-A variety of theories have been proposed to explain the development of this network as well as its organization.
-However, the appropriate tools are currently missing to falsify these theories \cite{garnsey_trade_1983} \xrc{what theories?
-why the tools?}.
+%XRC trade networks are increasingly being recognised as a key process in ancient Mediterranean
+The trade networks are being increasingly recognised as a key process in the structure of ancient Mediterranean societies.
+Among the recent works studying these networks, brugmans 2010 shows the relation between trade network and the use of table ware in the roman empire.
+In another example Malkin 2003 show the influence of these trade networks on the emergence of the greek identity between XXX and XXX.
+%An objective of the research undertaken is to compare these networks between each other and understand their specificities.
+On top of these comparisons we would also like to determine if these trade networks are comparable to a market economy.
+The work presented in this paper takes place within the EPNET project~\cite{remesal_epnet_2014} which aims at studying the properties of the trade network of the roman empire.
 
-%type of question we want to answer to and why we need trade an culture
-We want notably to address the on-going debate about the characteristics of the economic market in Roman empire~\cite{polanyi_trade_1957}.
-Two main views are found on this debate.
-The first view states that the economical network of the Roman empire had characteristics very different than our modern trade network.
-The trade network of the Roman empire is then perceived to be qualitatively and quantitatively different than our modern trade network.
-The second view state that the economical network of the Roman empire constitutes a proto-version of our modern trade network.
-The difference between the two networks is then only quantitative and not qualitative.
-\\
-\xrc{this needs further discussion: at what level they are different, etc. it is mainly defining what is a market economy, and the question is: was the roman trade network a market economy?}
-\jm{not sure that food item is the right word}
-\\
-Among all the goods transiting on the Roman network, we will focus on the food items. 
-\jm{i find the justification weak. any ideas ?}
-\xrc{justification is based on the existence of evidence: the shipment of containers such as amphorae, which are used to transport selected items (olive oil, salsamenta, etc) is one of the best datasets in terms of the archaeological record \cite{bevan_2014}.}
-These are interesting as they reflect the organization of both the trade network and the cultural network.
-Moreover, the food items were circulating in amphorae which arrived up to us.
-As a consequence it will be possible to compare the qualitative output of a simulation with the qualitative structure of the historical data.
+%XRC this process played a role in the trajectories of cultural change of the different regions, which were interconnected by trade
+The trade possibilities between different regions will play a role in changes in their cultures.
+The influence can comes from two main sources.
+First, with each trade connection new good can arrive in a province.
+The arrival of these new goods will change the rate of adoption of other goods CITE.
+Moreover the arrival of new products can lead to their recombination with previous products and therefore the creation of an new item.
+Persons are also travelling on these trade networks, each carrying its own culture.
+Large movements of populations may lead to changes in the cultures.
+For example, when Roman troops were travelling to a new region, traditional roman products were delivered to that regions such as oil CITE ROMAN DELIVERING OIL.
 
-\xrc{I would switch the line of thought: a) we have hypotheses, b) we need evidence to evaluate them and c) containers are the best existing datasets to do that}
+%XRC these two elements (cultural transmission and trade networks) are traditionally been studied as isolated systems.
+Traditionally cultural transmission and trade are studied distinctively.
+On the one hand, the transmission of culture is studied purely as learning and transmitting information between persons or animals.
+The focus is then for example to understand the different transmission, selection and transformation mechanism.
+This does not take into account the economical constraints of certain behaviours in human societies.
+On the other hand, the economical behaviours of persons are studied solely with regards to economical values.
+The questions traditionally answered are relative to the convergence of prices to an optimal value or the possibility for a person to maximise the economical value of its possessions.
+The influence of the culture surrounding the person and the bias that may result from it are not taken into account.
+
+%XRC this is wrong because blablabla...
+As has been stated before the trade of goods is influence the culture by modifying both the goods present in a region and the people consuming these goods.
+Moreover we can also expect that the different cultures present in a region will influence the trades this region has with others.
+\jm{include trade pottery} Focusing on either trade or cultural transmission allows to formalize their inner mechanisms and understand their respective dynamics.
+However, in order to understand the analyse the trading system of a region one must take into account both trading strategy and culture.
+\jm{find a problem that we can study thanks to that}
+%XRC A potential reviewer would say that you need to specify your research question and needs before justifying the tool
+%Jm   -> take care that it is well justified
+%XRC we propose a model of coevolution to explore the deep links between trade and cultural transmission in the ancient Mediterranean
+%JM we think that agent stuff is a good tool because blah blah
+We propose in this article a framework to study the interaction between cultural transmission and trade.
+This framework should be able first to reproduce well known dynamics of both cultural transmission and trading.
+Moreover, to be useful, this framework should be able to show the result of the interaction of these dynamics.
 
 %What is agent-based modeling and what can it do
-\jm{maybe this paragraph should go before ?}
-Within the EPNet project~\cite{remesal_epnet_2014} we aim to create tools able to falsify theories on the characteristics of the trade network of the Roman empire.
-These tools have to produce the qualitative characteristics resulting from a specific theory.
-This qualitative result can then be compared to historical data and highlight the differences between the reality and the simulations.
-Following~\cite{epstein_growing_1996,lake_trends_2014,kohler_dynamics_2000,tesfatsion_agent-based_2003,epstein_why_2008} we consider Agent Based Modelling (ABM) is a good framework to express theories in a falsifiable form.
+The Agent Based Modeling (ABM) methodology~\cite{} has been applied to both the study of cultural transmission and the study of trading~\cite{}.
+\jm{achievement on each aspect} ABM is therefore a good candidate to produce a framework able to express theories on trade and cultural transmission.
 Within these models the social self-organisation of a society results from the interactions of a large number of agents.
 The behaviour of these agents is encoded so as to reflect the theory under test.
-It has been already used in a wide range of fields of research, from economical market mechanisms to the understanding of cultural goods production and exchange.
-
 %What we want to bring to ABM with our work
-\todo{the justification of reproducing previous works should be stronger}
 The aim of this paper is to develop an ABM to model the evolution of culture and trade.
@@
 We will then show the capacities of our model to study the interaction between culture and trade.
-
-\xrc{A potential reviewer would say that you need to specify your research question and needs before justifying the tool}
-
-\xrc{I would propose a different structure for the intro:}
-\begin{enumerate}
-    \item \emph{trade networks are increasingly being recognised as a key process in ancient Mediterranean}
-    \item \emph{this process played a role in the trajectories of cultural change of the different regions, which were interconnected by trade}
-    \item \emph{these two elements (cultural transmission and trade networks) are traditionally been studied as isolated systems}
-    \item \emph{this is wrong because blablabla...}
-    \item \emph{we propose a model of coevolution to explore the deep links between trade and cultural transmission in the ancient Mediterranean}
-\end{enumerate}
 
@@
 
+%The questions we would like to ultimately study are for example: how does the hierarchical structure changes the adoption of a new product ?
+How delays and interruptions in the trade network change the culture of a society ?
+
 In future works numerous, more realistic and complex dynamics can be studied in the same model.

### 2015-03-12 notes.tex
last version of the notes

\documentclass[a4paper]{article}
\usepackage{fontspec}
\usepackage{amsmath}
\usepackage{amssymb}

%%%%lualatex on
%\usepackage{luatextra}
%Ligatures={Contextual, Common, Historical, Rare, Discretionary}
%\setmainfont[Mapping=tex-text]{Linux Libertine O}

\usepackage{natbib}

\title{Note about WSC}
\author{Simon}
\begin{document}
\maketitle
\section{Cultural Evolution}

We run a first set of experiment where all agents interact with everyone. The only evolutionary mechanism are .Following \cite{bentley2004randomdriftandculturechange}

\subsection{One trait}

The Finite Innovation Effect (ie : $n$ variant  $| n\in\{0,\cdots,100\}$) :
\begin{figure}[h]
	\begin{center}
		\includegraphics[width=7cm]{../../epnet-dev/analtest/allmu.png}
	\end{center}
	\caption{rand()\%100}
	\label{fig:finitEffect}
\end{figure}

With infinite innovation possibilities(ie : $n$ variant $| n\in\mathbb{A} $):
\begin{figure}[hbp]
	\begin{center}
		\includegraphics[width=7cm]{../../epnet-dev/analtest/allmuRandMax.png}
	\end{center}
	\caption{rand()\%RAND\_MAX}
	\label{fig:allMutation}
\end{figure}

\section{Multiple Traits (all varying on $\mathbb{N}$)}
In that case individual owns a vector of $n$ traits. One a cultural exchange occurs the whole vector is exchanged.

In the case individual carries multiples traits (ie price in our experiment), we check that it does not change the result of the algorithm in the long terms, each traits will evolve following the same curves than when juste one traits is evolving and exchange.
\begin{figure}[h]
	\begin{center}
		\includegraphics[width=6cm]{../../epnet-dev/analtest/10resources.png}
	\end{center}
	\caption{$\mu=\{.08,.098\}$ for 10 resources}
	\label{fig:10resources}
\end{figure}

\begin{figure}[h]
	\begin{center}
		\includegraphics[width=6cm]{../../epnet-dev/analtest/OneVsTenMu098.png}
		\includegraphics[width=6cm]{../../epnet-dev/analtest/OneVsTenMu008.png}
	\end{center}
	\caption{$\mu=\{.08,.098\}$ for one of the 10 resources VS one only}
	\label{fig:OneVsTen}
\end{figure}

\bibliographystyle{apalike}
\bibliography{/home/scarrign/Documents/biblio/bib/phd.bib}  
\end{document}

### 2015-03-12 notes.tex
images

@@
 
-We run a first set of experiment where all agents interact with everyone. The only evolutionary mechanism are .Following \cite{bentley2004randomdriftandculturechange}
+We run a first set of experiment where all agents interact with everyone. The only evolutionary mechanism are. Following \cite{bentley2004randomdriftandculturechange}
+
+The cultural evolution's literature gives us a way to interpret evolution of cultural artifact such as those produce in economical field.
+We want to confront well know cultural evolution's mechanism to well known economical evolution's mechanism and see and show their differences.
+
+To do so we cross those different mechanisms following the table \ref{tab:exp}.
+\begin{table}
+	\centering
+	\begin{tabular}{l|c|c}
+		& Eco\footnote{a} & Rand \\\hline
+		$\mu$ &A & B \\
+		$\alpha$ & B & C \\
+	\end{tabular}
+	\caption{Experimental Setup}
+	\label{tab:exp}
+\end{table}
 
@@
 
-The Finite Innovation Effect (ie : $n$ variant  $| n\in\{0,\cdots,100\}$) :
+The Finite Innovation Effect (ie : $n$ variant  $| n\in\{0,\cdots,100\}$).
+If choose a innovation mechanism such as the number of possible new variant is finite, we see a strange ``anticonformist-like'' effect such the one shown by \cite{mesoudi2009randomcopyingfrequencydependencopyingandulturechange}.
+This effect is visible in the figure \ref{fig:finitEffect}.
 \begin{figure}[h]
 	\begin{center}
-		\includegraphics[width=7cm]{../../epnet-dev/analtest/allmu.png}
+		\includegraphics[width=7cm]{img/allmu.png}
 	\end{center}
@@
 
-With infinite innovation possibilities(ie : $n$ variant $| n\in\mathbb{A} $):
+With infinite innovation possibilities(ie : $n$ variant $| n\in\mathbb{A} $) the results, showed in the figure \ref{fig:allMutation} are the same that those from \cite{bentley2004randomdriftandculturechange}.
 \begin{figure}[hbp]
 	\begin{center}
-		\includegraphics[width=7cm]{../../epnet-dev/analtest/allmuRandMax.png}
+		\includegraphics[width=7cm]{img/allmuRandMax.png}
 	\end{center}
@@
 
-In the case individual carries multiples traits (ie price in our experiment), we check that it does not change the result of the algorithm in the long terms, each traits will evolve following the same curves than when juste one traits is evolving and exchange.
+In the case individual carries multiples traits (ie price in our experiment), we check that it does not change the result of the algorithm in the long terms, each traits will evolve following the same curves than when just one trait is evolving.
+The results are shown in figures \ref{fig:10resources}.
+Those results are statistically the same than those from the previous experiments.
 \begin{figure}[h]
 	\begin{center}
-		\includegraphics[width=6cm]{../../epnet-dev/analtest/10resources.png}
+		\includegraphics[width=6cm]{img/10resources.png}
 	\end{center}
@@
 	\begin{center}
-		\includegraphics[width=6cm]{../../epnet-dev/analtest/OneVsTenMu098.png}
-		\includegraphics[width=6cm]{../../epnet-dev/analtest/OneVsTenMu008.png}
+		\includegraphics[width=6cm]{img/OneVsTenMu098.png}
+		\includegraphics[width=6cm]{img/OneVsTenMu008.png}
 	\end{center}

### 2015-03-12 article.tex
finish first round of correction on intro

@@
 
-\WSCpagesetup{Montanier, Carrignon, and Zerr}
+\WSCpagesetup{Montanier, Carrignon, Rubio and Zerr}
 
@@
 %XRC trade networks are increasingly being recognised as a key process in ancient Mediterranean
-The trade networks are being increasingly recognised as a key process in the structure of ancient Mediterranean societies.
-Among the recent works studying these networks, brugmans 2010 shows the relation between trade network and the use of table ware in the roman empire.
-In another example Malkin 2003 show the influence of these trade networks on the emergence of the greek identity between XXX and XXX.
-%An objective of the research undertaken is to compare these networks between each other and understand their specificities.
-On top of these comparisons we would also like to determine if these trade networks are comparable to a market economy.
-The work presented in this paper takes place within the EPNET project~\cite{remesal_epnet_2014} which aims at studying the properties of the trade network of the roman empire.
+Trades are being increasingly recognised as a key process in the structure of ancient Mediterranean societies.
+For example, the use of table ware in the Roman empire  has been linked to the trade network~\cite{brughmans_connecting_2010}.
+Interestingly this trade network has been shown to be a market economy~\cite{temin_market_2001}.
+The work presented in this paper proposes a framework to further study the relation between trade and culture within the roman empire.
+This work takes place within the EPNET project~\cite{remesal_epnet_2014}.
 
 %XRC this process played a role in the trajectories of cultural change of the different regions, which were interconnected by trade
-The trade possibilities between different regions will play a role in changes in their cultures.
+The trade possibilities between provinces modify the transmission of culture within each province and between them.
 The influence can comes from two main sources.
-First, with each trade connection new good can arrive in a province.
-The arrival of these new goods will change the rate of adoption of other goods CITE.
-Moreover the arrival of new products can lead to their recombination with previous products and therefore the creation of an new item.
-Persons are also travelling on these trade networks, each carrying its own culture.
+First, when a new connection is made between two provinces, new products can arrive in their respective markets.
+The arrival of new goods naturally changes the rate of adoption of every goods of the market CITE.
+Moreover, the arrival of new products can lead to their recombination with previous products and therefore the creation of an new item.
+This further modify the structure of the market of the province.
+Second, persons are also travelling on the roads of the trade network, each carrying its own culture.
 Large movements of populations may lead to changes in the cultures.
-For example, when Roman troops were travelling to a new region, traditional roman products were delivered to that regions such as oil CITE ROMAN DELIVERING OIL.
+For example, when Roman soldiers were stationing in a province, Roman products such as olive oil were delivered to that province CITE ROMAN DELIVERING OIL.
+This can lead to the adoption of olive oil in regions that were originally not using it.
 
@@
 Traditionally cultural transmission and trade are studied distinctively.
-On the one hand, the transmission of culture is studied purely as learning and transmitting information between persons or animals.
-The focus is then for example to understand the different transmission, selection and transformation mechanism.
-This does not take into account the economical constraints of certain behaviours in human societies.
-On the other hand, the economical behaviours of persons are studied solely with regards to economical values.
-The questions traditionally answered are relative to the convergence of prices to an optimal value or the possibility for a person to maximise the economical value of its possessions.
-The influence of the culture surrounding the person and the bias that may result from it are not taken into account.
+On the one hand, the cultural transmission mechanisms studied do not take economical consideration into accounts.
+The works done are interested in the adoption of various cultural trait without taking into consideration their economical value.
+On the other hand, trading behaviours are studied within their own framework which are designed to measure the amount of goods exchanged and the value at which they are exchanged.
+Within these frameworks the cultural transmission between persons is not present.
 
-%XRC this is wrong because blablabla...
-As has been stated before the trade of goods is influence the culture by modifying both the goods present in a region and the people consuming these goods.
-Moreover we can also expect that the different cultures present in a region will influence the trades this region has with others.
-\jm{include trade pottery} Focusing on either trade or cultural transmission allows to formalize their inner mechanisms and understand their respective dynamics.
-However, in order to understand the analyse the trading system of a region one must take into account both trading strategy and culture.
-\jm{find a problem that we can study thanks to that}
-%XRC A potential reviewer would say that you need to specify your research question and needs before justifying the tool
-%Jm   -> take care that it is well justified
+%XRC this is wrong because blablabla
+As it has been stated before, trades influence cultural transmission by modifying both the goods present in a region and the people consuming these goods.
+On the one side, analysing separately trade and cultural transmission allows to formalize their inner mechanisms and understand their respective dynamics.
+On the other hand, in order to analyse the adoption of goods within a province one must take into account both trading strategy and cultural transmission.
+For example, the modification of good's consumption after the rupture of a connection in the trade system is better explained by knowing the local adoption of this good (cultural transmission) and the prices of this good (trade).
+
 %XRC we propose a model of coevolution to explore the deep links between trade and cultural transmission in the ancient Mediterranean
-%JM we think that agent stuff is a good tool because blah blah
 We propose in this article a framework to study the interaction between cultural transmission and trade.
 This framework should be able first to reproduce well known dynamics of both cultural transmission and trading.
-Moreover, to be useful, this framework should be able to show the result of the interaction of these dynamics.
-
-%What is agent-based modeling and what can it do
-The Agent Based Modeling (ABM) methodology~\cite{} has been applied to both the study of cultural transmission and the study of trading~\cite{}.
-\jm{achievement on each aspect} ABM is therefore a good candidate to produce a framework able to express theories on trade and cultural transmission.
-Within these models the social self-organisation of a society results from the interactions of a large number of agents.
-The behaviour of these agents is encoded so as to reflect the theory under test.
-%What we want to bring to ABM with our work
-The aim of this paper is to develop an ABM to model the evolution of culture and trade.
-Importantly we aim to create a model with a low number of parameters in order to ensure that the dynamics observed are simple to analyse.
-In order to assess the quality of this model we use it to reproduce qualitatively certain dynamics observed in either economy or culture.
-We will then show the capacities of our model to study the interaction between culture and trade.
+Second, to be useful, this framework should be able to compare results obtained by taking cultural or trade into consideration.
+In order to build this framework we view trade events as part of the culture.
+The price of a good are then viewed as a cultural trait.
+This traits can be transmitted and modified along different rules.
+By this mean, traditional works previously expressed in a trading framework, can be expressed in a cultural evolution framework.
+Therefore, the dynamics observed on various cultural transmission mechanisms can be straightforwardly compared to dynamics obtained by trading mechanisms.
+In order to demonstrate the feasibility of this approach we propose a minimal implementation able to reproduce both cultural transmission dynamics and trade dynamics.
+Additionally we will analyse the results obtained with tools from both economy and cultural evolution.
 

### 2015-03-12 notes.tex

@@
 \maketitle
-\section{Cultural Evolution}
-
-We run a first set of experiment where all agents interact with everyone. The only evolutionary mechanism are. Following \cite{bentley2004randomdriftandculturechange}
+\section{Classic Cultural Evolution}
 
@@
 
-To do so we cross those different mechanisms following the table \ref{tab:exp}.
+\subsection{Verification}
+First we verify that our model implements well the already known cultural evolution mechanisms.
+
+Here we follow \cite{mesoudi2009randomcopyingfrequencydependencopyingandulturechange,bentley2004randomdriftandculturechange} and look for the evolution of a single traits depending on the innovation rate $\mu$ in a 250 agents population during 1000 steps.
+
+With infinite innovation possibilities(ie : $n$ variant $| n\in\mathbb{A} $) the results, showed in the figure \ref{fig:allMutation} are the same that those from \cite{bentley2004randomdriftandculturechange}.
+\begin{figure}[hbp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/allmuRandMax.png}
+	\end{center}
+	\caption{rand()\%RAND\_MAX}
+	\label{fig:allMutation}
+\end{figure}
+
+\subsection{generalisation: Multiple Traits (all varying on $\mathbb{N}$)}
+Once the results are verified, we generalized those result for $n$ possible traits.
+
+In that case individual owns a vector of $n$ traits. One a cultural exchange occurs the whole vector is exchanged.
+
+Individual carries multiples traits (ie price in our experiment), we check that it does not change the result of the algorithm in the long terms, each traits will evolve following the same curves than when just one trait is evolving.
+The results are shown in figures \ref{fig:10resources}.
+Those results are statistically the same than those from the previous experiments.
+\begin{figure}[h]
+	\begin{center}
+		\includegraphics[width=6cm]{img/10resources.png}
+	\end{center}
+	\caption{$\mu=\{.08,.098\}$ for 10 resources}
+	\label{fig:10resources}
+\end{figure}
+
+\section{Cultural Mechanisms Comparison}
+
+Now that we have shown our model reproduce well known cultural evolution mechansims we will compare the evolution of the system when it is submit to the previous mechanism studied to the evolution of the same system submitted to the mechanisms cultural transmission and innovation used by \cite{gintis2006theemergenceofapricesystemfromdecentralizedbilateralexchange}.
+
+\subsection{framework Adjustment}
+In order to allow such comparison we will do our simulation using the same parameters used by Gintis which are : a population with 100 agents per good assuming six good so 600 agents evolving during 1500 steps and with a innovation rate of .01.
+
+It worth to notice here than the way Gintis counts the steps is slightly different than the others article.
+Indeed in Gintis agents follow 10 Produce/Trade/Consume cycles before exchanging their cultural belief, which means than when in the previous runs we speak about 5 runs, it means in Gintis framework ``5 cycle of cultural exchange'' so 50 steps.
+
+The results are those expected : given the much higher number of agents and
+
+\subsection{Comparison}
+In order to compare the different mechanisms used in the different paper we will cross them  following the table \ref{tab:exp}.
 \begin{table}
@@
 		$\mu$ &A & B \\
-		$\alpha$ & B & C \\
+		$\mu +\alpha$ & B & C \\
 	\end{tabular}
@@
 
-\subsection{One trait}
-
+\section{Other reflexion}
+\subsection{Discrete and finite inovation space}
 The Finite Innovation Effect (ie : $n$ variant  $| n\in\{0,\cdots,100\}$).
@@
 
-With infinite innovation possibilities(ie : $n$ variant $| n\in\mathbb{A} $) the results, showed in the figure \ref{fig:allMutation} are the same that those from \cite{bentley2004randomdriftandculturechange}.
-\begin{figure}[hbp]
-	\begin{center}
-		\includegraphics[width=7cm]{img/allmuRandMax.png}
-	\end{center}
-	\caption{rand()\%RAND\_MAX}
-	\label{fig:allMutation}
-\end{figure}
-
-\section{Multiple Traits (all varying on $\mathbb{N}$)}
-In that case individual owns a vector of $n$ traits. One a cultural exchange occurs the whole vector is exchanged.
-
-In the case individual carries multiples traits (ie price in our experiment), we check that it does not change the result of the algorithm in the long terms, each traits will evolve following the same curves than when just one trait is evolving.
-The results are shown in figures \ref{fig:10resources}.
-Those results are statistically the same than those from the previous experiments.
-\begin{figure}[h]
-	\begin{center}
-		\includegraphics[width=6cm]{img/10resources.png}
-	\end{center}
-	\caption{$\mu=\{.08,.098\}$ for 10 resources}
-	\label{fig:10resources}
-\end{figure}
-
+\subsection{Validation of the curves similarities}
 \begin{figure}[h]
@@
 \end{figure}
-
 \bibliographystyle{apalike}

### 2015-03-13 notes.tex
standard deviation for exp C & power law curves for each exp

@@
 	\begin{tabular}{l|c|c}
-		& Eco\footnote{a} & Rand \\\hline
+		& Rand & Gintis \\\hline
 		$\mu$ &A & B \\
-		$\mu +\alpha$ & B & C \\
+		$\mu +\alpha$ & C & D \\
 	\end{tabular}
@@
 	\label{tab:exp}
+\end{table}
+
+First we check how those different mechanisms impact the power law distribution.
+
+\begin{figure}[hbp]
+	\begin{center}
+		\includegraphics[width=6cm]{img/powerABCD.png}
+	\end{center}
+	\caption{power law for each exp define in table \ref{tab:exp} after 2000 step}
+	\label{fig:powerABCD}
+\end{figure}
+
+As expected depending on the selection process the repartition follow a power law (random selection) or a exponential law).
+
+Next let's have a look which combination lead to the right economical processes.
+
+\begin{table}
+	\centering
+	\begin{tabular}{l c c}
+		& Random Transmission & Gintis Transmission \\
+		FRI & \raisebox{-.5\height}{\includegraphics[width=5cm]{img/sdEvolEXP2.png}}&\raisebox{-.5\height}{\includegraphics[width=5cm]{img/sdEvolEXP2.png}} \\
+		GRI & \raisebox{-.5\height}{\includegraphics[width=5cm]{img/sdEvolEXP3.png}}&\raisebox{-.5\height}{\includegraphics[width=5cm]{img/sdEvolEXP4.png}}
+
+	\end{tabular}
+	\caption{Evolution of SD. FRI : Fully Random Innovation, GRI: Gintis Random Innovation}
+	\label{tab:sdevol}
 \end{table}

### 2015-03-16 article.tex
start to modify everything for state of the art trade

@@
 
-\section{PREVIOUS MODELISATIONS OF TRADE AND CULTURE}
+\section{PREVIOUS MODELLINGS OF TRADE AND CULTURE}
 
@@
 
-\xrc{I would suggest to use modelling instead of modelisation}
-\subsection{Modelisation of Trade}
+\subsection{Modelling of Trade}
 
-Multiple approaches have been proposed to model the economical interactions between humans.
-Among them, this section will review three which constitute major trends and are the most relevant to our study.
-The approaches are presented in chronological order.
+Multiple approaches have been proposed to model the economical interactions in the ancient mediteranean culture.
+Among these we will focus on the formal models.
+These are close to our works, can be tested and compared.
 
-\xrc{I'm not sure if it would be wiser to limit this section to models of ancient trade...otherwise a proper lit. review becomes huge.}
+%Hopkins 1980: structure of tax system.
+two hypothesis.
+1)taxation increased volume of trade in the empire?
+2) tax-exporting province (recently integrated province) had to export to pay tax.
+roman supported by many small taxes.
+Not sure to cite it, goes to much more
+%Termin 2001: based on multiple consideration classify roman economy as market based with loose tie from things far appart. composed of local markets connected together
+%Terpstra 2011: micro economic model to explain possibility of trade in roman empire under uncertainty.
+based on reputation in the network and removal of bad from the network (personalized network based on geographical info).
+focus on a specific case (one city and its relations with others).
+threat of expulsion or loss of reputation as reinforcement <- not only economic.
 
-The first approach to be reviewed is the Expected Utility (EU) which became a main trend after the second world war~\cite{schoemaker_expected_1982}.
-The goal of this model was to propose a first explanation to the economical actions of humans along the following axes: descriptive, predictive, postdictive and prescriptive.
-More precisely this approach model individuals as agents facing a choice among risky options.
-Each agent is aware of the probability that an event will happen and the utility (economical reward) associated to that event.
-Each agent can then maximise its expected utility by choosing the proper actions.
-By applying this methodology to various economical problems it became clear that humans do not see problems as probabilities and do not directly reason on them.
-From the perspective of this theory, humans show a collection of irrational behaviours, notably a strong aversion to risk.
-
-In an attempt to overcome the shortcomings of the EU models a new theory was introduced, the prospective theory.
-This theory conserve an approach close to the EU: individuals are modelled as agents facing risky actions each with a certain probability and utility.
-However, the agents do not face these problems by maximising the expected utility.
-They are rather endowed with behaviours composed of three key elements~\cite{camerer_prospect_2004}.
-First, the ``loss aversion'' element models the fact that individuals are much more sensitive to loss than to gains of the same magnitude.
-Second, the ``reference dependence'' models the fact that individuals measure their losses and gains with regards to their current possessions.
-Finally, individuals do not weight linearly the probabilities e.g.
-an individual will perceive a higher gain between 100 and 200 than between 1000 and 1100.
-Multiple difficulties have been encountered in applying this approach to practical problems of the real life.
-These are attributed to the lack of definition of certain elements of the theory and therefore the near impossibility to measure them~\cite{barberis_thirty_2012}.
-
-The two previous approaches address an economical problem as a block which all agents face in a similar fashion.
-As a consequence, the emerging properties due to the interaction of numerous agents can not be studied.
-Moreover, these approaches are not suitable to model systems composed of individuals with various characteristics and interests.
-The Agent-based Computational Economics (ACE) fields propose specifically to model the complex outcomes raising from a large number of interactions in a decentralized market~\cite{tesfatsion_agent-based_2003}.
-Naturally this approach is interesting for our project based on multi-agent methodology and it constitutes a source of hypothesis to test to characterise the economical network of the Roman empire.
-More specifically, multiple hypothesis are proposed on the formation of different types of economical networks depending on the economical rules between the agents~\cite{kirman_evolving_2001,tesfatsion_structure_2001}.
-Another interesting track is the study of the evolution of behavioural norms in an economical network~\cite{epstein_learning_2001,axelrod_complexity_1997}.
-Finally~\cite{gintis_emergence_2006} has proposed a specific analysis on the emergence of price structure when only pair exchanges are considered.
-\todo{put the section}
-This latest work constitutes naturally a strong reference and will be explained in further details in section XXX.
+Finally we would like to add this additional work even if it has not been specifically designed for historical studies~\cite{gintis_emergence_2006}.
+This model proposes a specific analysis on the emergence of price structure when only pair exchanges are considered, thus observing the emergence of a market economy.
+This constitutes a relatively realistic model with simple assumptions and will be explained in further details in section XXX.
 

### 2015-03-18 notes.tex
alpha's data for each mu values

@@
 \documentclass[a4paper]{article}
-\usepackage{fontspec}
 \usepackage{amsmath}
 \usepackage{amssymb}
+\usepackage{graphicx}
 
@@
 
+\subsection{Statistical Analysis}
+In order to test if the data fit power law curve aand to know the parameters off such learning curve, we will used to R Cran Package poweRlaw \cite{gillespie2015fittingheavytaileddistributionsthepowerlawpackage} wich is based on \cite{clauset2009powerlawdistributionsinempiricaldat}.
+This package allow us to fit the datas with a power law and to know the parameters of this fitted power law ($\alpha$).
+Moreover, it allows use to test if the datas are actually following the fitted power law using a bootstrapping method that calcul kolmogorv smirnov coefficient.
+
 \subsection{Verification}
+
 First we verify that our model implements well the already known cultural evolution mechanisms.
@@
 
+And as them we find the same between $\alpha$ and $\mu$ (cf tab :\ref{tab:mualpha} \& tab \ref{tab:Bmualpha}).
+\begin{figure}[hbp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/alphawrtmu.png}
+	\end{center}
+	\caption{$\alpha$  wrt. $\mu$ }
+	\label{fig:alphamu}
+\end{figure}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l|cc}
+			$\mu$ & $\alpha$ & SD\\\hline
+			0.008&1.539122&0.010154623\\
+			0.018&1.550888&0.005487468\\
+			0.028&1.564014&0.004155942\\
+			0.038&1.572597&0.003297191\\
+			0.048&1.586550&0.003965373\\
+			0.058&1.593909&0.002497322\\
+			0.068&1.608492&0.003090030\\
+			0.078&1.617235&0.002188951\\
+			0.088&1.627801&0.003247013\\
+			0.098&1.637116&0.002900783\\
+	\end{tabular}
+	\caption{Mean \& SD are done with 10 run for each $\mu$}
+	\label{tab:mualpha}
+\end{table}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l|cc}
+$\mu$&$\alpha$&(SD)\\\hline
+0.004&1.50&(0.02) \\
+0.008&1.52&(0.02)\\
+0.016&1.55&(0.03)\\
+0.032&1.59&(0.06)\\
+0.064&1.78&(0.08)\\
+0.128&1.99&(0.04)\\
+	\end{tabular}
+	\caption{Mean \& SD from \cite{bentley2004randomdriftandculturechange} }
+	\label{tab:Bmualpha}
+\end{table}
+
 \subsection{generalisation: Multiple Traits (all varying on $\mathbb{N}$)}
@@
 
-In that case individual owns a vector of $n$ traits. One a cultural exchange occurs the whole vector is exchanged.
+In that case individual owns a vector of $n$ traits (price in our experiment). When a cultural exchange occurs the whole vector is exchanged and each traits  had a $\mu$ probability to mutate.
 
-Individual carries multiples traits (ie price in our experiment), we check that it does not change the result of the algorithm in the long terms, each traits will evolve following the same curves than when just one trait is evolving.
+Here we check that it does not change the result of the algorithm in the long terms and that each traits will evolve following the same curves than when just one trait is evolving.
 The results are shown in figures \ref{fig:10resources}.
 Those results are statistically the same than those from the previous experiments.
+
 \begin{figure}[h]
@@
 
-\section{Cultural Mechanisms Comparison}
+\section{Cultural Mechanisms Comparison with economical evolution}
 
-Now that we have shown our model reproduce well known cultural evolution mechansims we will compare the evolution of the system when it is submit to the previous mechanism studied to the evolution of the same system submitted to the mechanisms cultural transmission and innovation used by \cite{gintis2006theemergenceofapricesystemfromdecentralizedbilateralexchange}.
+Now that we have shown that our model reproduce well the well known cultural evolution mechanisms, and that even when multiple price are simultaneously evolved, we will compare the evolution of the system when it is submit to different mechanisms of transmission and innovation.
+The one we will use and compare with those used previously are those used by \cite{gintis2006theemergenceofapricesystemfromdecentralizedbilateralexchange}.
 
-\subsection{framework Adjustment}
+\subsection{Framework Adjustment}
 In order to allow such comparison we will do our simulation using the same parameters used by Gintis which are : a population with 100 agents per good assuming six good so 600 agents evolving during 1500 steps and with a innovation rate of .01.
@@
 The results are those expected : given the much higher number of agents and
+
+\subsection{Gintis' imitation mechanism}
+The imitation mechanism is ``score biased'', meaning that people tends to copy the price vector of other that exhibits a high score.
+This score is computed using the utility function and is summed for every 10 step during a evaluation periode.
+After those 10 step of evaluation the exchange is done between agents
+
+In its new paper agents adapt themselves using learning simple rules that could be useful to have quicker improvement (and a more cognitively accurate model):
+
+\begin{quotation}
+	After each trading period, agents consume their consumption inventories provided they have a positive amount of each consumption good, and agents replenish their inventories of their production goods.
+Moreover, each trader updates his private price vector on the basis of his trading experience over the period, raising the price of a consumption or production good by 0.02\% if his inventory is empty (i.e.,if he failed to purchase any of the consumption good or sell all of his production good), and lowering price by 0.02\% otherwise (i.e., if he succeeded in obtaining his consumption good or sold all his production inventory).In general, it would be desirable to allow this adjustment strategy to evolve endogenously according to learning or imitation processes, but I have not investigated this possibility.
+	\\\cite[p. 7]{gintis2010thedynamicsofgeneralizedmarketexchange}
+\end{quotation}
+
+\subsubsection{The utility function \& Barter Process}
+The utility function is computed depending on the quantity that agent had collected during the trade.
+Those quantities are themselves defined by the Barter Process in order to maximise this utility function and depend on the private price of both trader.
+
+\subsection{Gintis' innovation mechanism}
 
@@
 	\begin{center}
-		\includegraphics[width=6cm]{img/powerABCD.png}
+%		\includegraphics[width=6cm]{img/powerABCD.png}
 	\end{center}

### 2015-03-23 article.tex
notes on article read from economics of ancient cultures
start to rewrite state of the art trade

@@
 \title{Model to study co-evolution of trade an culture}
+\maketitle
 
@@
 \end{figure*}
-
-\maketitle
 
@@
 
-Multiple approaches have been proposed to model the economical interactions in the ancient mediteranean culture.
+Multiple approaches have been proposed to model the economical interactions in the ancient Mediterranean culture.
 Among these we will focus on the formal models.
 These are close to our works, can be tested and compared.
+
+Hola chicos, our goal is to understand the interaction between trade exchange and cultural evolution in the mediteranean societies.
+Therefore we start by looking at the work studying the economy in the mediteraneean word
+\todo{list of works and that none of them generate stuff}
 
@@
 Not sure to cite it, goes to much more
+
 %Termin 2001: based on multiple consideration classify roman economy as market based with loose tie from things far appart. composed of local markets connected together
+
 %Terpstra 2011: micro economic model to explain possibility of trade in roman empire under uncertainty.
@@
 threat of expulsion or loss of reputation as reinforcement <- not only economic.
+
+%quantifying roman economy 2009: collections of work on roman economy.
+Study of the integratedness of the roman economy.
+How the enforcement and so on were working ?
+Hard to find global vision <- maybe because there was none.
+More inter-connected stuffs
+%  even pattern of currency is complex. diff between west and east
+%  Approaches to Quantifying Roman Trade: try different stuff on different goods. 
+%    little prospect of quantifying vague notions of ‘trade’. need to brake the question in sub questions. in all data some biases that have to be cleared
+%  Response to Andrew Wilson: need to put findings in context. look from the point of view of the costumer
+
+%A Model of Real Income Growth in Roman Italy, scheidel, 2007 : constraint on pop growth from different factors.
+massive redistribution that raised household wealth.
+raising income of sub-elite in italia.
+%  model: well just with words and a table listing the different factors on income and their effect varying with time
+
+%The organization of the grain trade in the early Roman Empire, 2007: problem of importation of grain to roman cities. use of variety of mechanisms to deal with problems of long-distance trade
+
+%In Search of Roman Economic Growth, 2008: relate proxy indice to economic performance <- maybe read
+
+%The economy of the early roman empire, 2006: market perspective on roman history.
+
+%Monitoring regional market systems in prehistory: Models, methods, and metrics, 2005
+%  claim that model produced is testable. model of distribution of commodity distribution under different market system organisaton. To check in details. 
+%  argue that markets have a central role on the organisation of ancient societes and that they have been rarely studied.
+need measure to model and monitor regional organisation.
+here measure distribution of goods on the market.
+case study on aztec.
+
+% Central place theory <- prediction of working of settlements. link to dynamic version and Spatial Interactions Models
+
+Therefore another way to tackle the review is to know if someone appears to have studied the use of MAS to create models of early economies.
+The stuff on anasazi is a famous modelisation of early cultures but they don't study the trading part.
+However in the Pueblo project they look at the modelisation of an early society from various angle including trade and cultural transmission.
+They are for example interested in the competition between various trade mechanisms and the emergence of inequalities However there are two limitations on the works done: they consider a pre-market society which clearly doesn't exhibit the same dynamics.
+The study also takes place in the village framework which makes it hard to extract the conclusions reached on the economy from the global framework.
+
+%lake 2014:
+%  take the third paragraph of lake 2014 for the description of MAS for archaeology
+%  we are not interested in the end result but how certain process works and what sort of change could have happen.
+
+%Dean 2000: famous anasazi model. in sugarscape, no trading.
+
+%Kohler 2012: travail sur pueblo societies, and some stuff on trading. Stuff on trading are actually super close to us. They look also at political hierarchy
+%Cockburn :
+% operate in proto-market economy while we aim to test market.
+% they look at specialization
+
+%kobti 2012 la meme que kobti 2006 ?
+%	pour 2006: etude de l'apparition d'inegalite
+
+%cockburn: specialisation avec une machine a gaz
+
+% smith and choi 2007 (pas sur de citer)
+%  model of inequalities
+%	start with two models of interaction mostly mutualistic and end up with inequalities
 

### 2015-03-24 article.tex
fixed references

@@
 Simon Carrignon\\ 
-Xavier Rubio\\
+Xavier Rubio-Campillo\\
 \vspace{12pt}
@@
 I would suggest this one: \emph{Culture is socially learned information capable of affecting  individual phenotypes.
-People acquire culture from other  individuals, via teaching or imitation} \cite{richerson1996}}
+People acquire culture from other individuals, via teaching or imitation} \cite{richerson_1996}}
 
@@
 These may happen due to some errors during the copy process~\cite{schillinger_copying_2014}.
-In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}\xrc{see also recombination \cite{sole_2013}}.
+In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_2003}\xrc{see also recombination \cite{sole_2013}}.
 

### 2015-03-25 notes.tex
results with simple trade 2 goods 600 agents

@@
 
+The Gintis' innovation mechanism differ from those used in cultural evolution literature (such as mechanism used by \cite{bentley2004randomdriftandculturechange,mesoudi2009randomcopyingfrequencydependencopyingandulturechange}).
+In the literature, when people ``innovate'', they could set the cultural traits anywhere in it's \emph{space state}\footnote{The differents form that the given traits could talk}, whereas in Gintis the trait mutate in a fixed proportion depending on its previous value.
+
 \subsection{Comparison}
@@
 
-As expected depending on the selection process the repartition follow a power law (random selection) or a exponential law).
+As expected depending on the selection process the repartition follow a power law (random selection) or a exponential law.
 

### 2015-03-25 article.tex
integrate corrections of bib to zotero, add new articles from zotero to bib, update economy state of the art

--- 2015-03-16 article.tex
@@
 \usepackage{xcolor}
+    \usepackage{cite}
 
@@
 
-Multiple approaches have been proposed to model the economical interactions in the ancient mediteranean culture.
-Among these we will focus on the formal models.
-These are close to our works, can be tested and compared.
-
 %Hopkins 1980: structure of tax system.
@@
 roman supported by many small taxes.
-Not sure to cite it, goes to much more
-%Termin 2001: based on multiple consideration classify roman economy as market based with loose tie from things far appart. composed of local markets connected together
-%Terpstra 2011: micro economic model to explain possibility of trade in roman empire under uncertainty.
-based on reputation in the network and removal of bad from the network (personalized network based on geographical info).
-focus on a specific case (one city and its relations with others).
-threat of expulsion or loss of reputation as reinforcement <- not only economic.
+Not sure to cite it
 
-Finally we would like to add this additional work even if it has not been specifically designed for historical studies~\cite{gintis_emergence_2006}.
-This model proposes a specific analysis on the emergence of price structure when only pair exchanges are considered, thus observing the emergence of a market economy.
-This constitutes a relatively realistic model with simple assumptions and will be explained in further details in section XXX.
+Within the archaeological field a large number of works have been proposed to quantify the properties of the economical interactions in the ancient Mediterranean societies~\cite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,minc_monitoring_2006,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
+In the works of~\cite{temin_market_2001,temin_economy_2006,wilson_approaches_2009}, based on the analysis of archaeological evidence, the Roman economy has been classified as a type of market economy where a variety of small tightly connected markets had loose connections between them.
+This view of a market system in ancient societies has been further expended in~\cite{minc_monitoring_2006} by a model applicable to various cases and studied in a test case of the aztec economical structure.
+The reaming works attempted at defining more exactly which type market economy it was, i.e.
+was it close to ours or remote ?
+
+The work of~\cite{scheidel_model_2007} proposes to analyse the factors affecting the growth of income and population in the Roman Italy.
+The analysis of historical evidence and historical documents lead the author to propose a model highlighting the key factors in the economical growth.
+More in link with the work conducted in this article~\cite{terpstra_trade_2011,kessler_organization_2007} have analysed the interactions between economy and culture transmission in roman empire.
+An analysis based on historical documents in~\cite{kessler_organization_2007} highlights the importance of economical and social institutions in order to perform an efficient trade of trains in the early Roman Empire.
+More precisely, the work conducted in~\cite{terpstra_trade_2011} proposes a micro-economic model analysing the possibility of trade under uncertainty in the roman empire.
+This work highlight the importance of reputation and the threat of expulsion from a trade network as mechanisms the overall efficiency of the trade network.
+
+A limitation of the works cited above is the impossibility to test the conclusions reached by the authors.
+The models proposed reflects only the view of the authors on the data they have analyse.
+A new type of model would be necessary to go beyond the interpretation, and allow the verification of the conclusions reached.
+These models should be able to generate data which is then qualitatively compared to the real historical data.
+By this mean, if a factor is really important in the economical network, its removal from the model will lead to data qualitatively different from the historical data.
+The Multi-Agent Simulations (MAS) offer a way to produce this kind of model~\cite{lake_trends_2014}.
+
+Based on this tool a relatively complex and exact modelisation of the prehispanic Pueblo societies has been proposed~\cite{kohler_modelling_2012}.
+This work offer a relatively exact MAS integrating notable the effects food consumption, production and landscape.
+The questions studied are  numerous and some works are performed on the economical system and its ties with social transmissions~\cite{kobti_emergence_2006,cockburn_simulating_2013}.
+However the work done in this project consider a pre-market society in a specific village which makes it difficult to reach more general conclusions, notably applicable to the Roman Empire.
+
+%kobti 2012 la meme que kobti 2006 ?
+%	pour 2006: etude de l'apparition d'inegalite
 
@@
 I would suggest this one: \emph{Culture is socially learned information capable of affecting  individual phenotypes.
-People acquire culture from other  individuals, via teaching or imitation} \cite{richerson1996}}
+People acquire culture from other individuals, via teaching or imitation} \cite{richerson_principles_1996}}
 
 The second aspect we wish to model is the evolution of the culture in the Roman empire.
-The evolutionary framework (generally used in Biology) has been proposed to study the changes of culture and found to be suitable,  particularly in the case of historical and archaeological studies~\cite{lycett_cultural_2015,henrich_evolution_2003}\xrc{henrich's paper is not on archaeology or history, better reference \cite{shennan_2008}}.
+The evolutionary framework (generally used in Biology) has been proposed to study the changes of culture and found to be suitable,  particularly in the case of historical and archaeological studies~\cite{lycett_cultural_2015,henrich_evolution_2003}\xrc{henrich's paper is not on archaeology or history, better reference \cite{shennan_evolution_2008}}.
 
@@
 These may happen due to some errors during the copy process~\cite{schillinger_copying_2014}.
-In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}\xrc{see also recombination \cite{sole_2013}}.
+In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}\xrc{see also recombination \cite{sole_evolutionary_2013}}.
 
@@
 The last element is the one that will interest us the most in this study: the differential replication between different cultural traits.
-If a cultural trait is found more often than the others in the population it means that something modified the rate at which it is adopted by each agent \xrc{beyond drift effects produced by random copy of neutral traits \cite{bentley_2004}}.
+If a cultural trait is found more often than the others in the population it means that something modified the rate at which it is adopted by each agent \xrc{beyond drift effects produced by random copy of neutral traits \cite{bentley_random_2004}}.
 %The reproduction rate of ideas in a population can be characterise by different rates: directional, disruptive or stabilisation~\cite{rendell_cognitive_2011}. 
@@
 First is the random copy of one trait from an agent to another agent.
-\todo{get a ref on that} \xrc{you can use \cite{bentley_2004}}
+\todo{get a ref on that} \xrc{you can use \cite{bentley_random_2004}}
 This type of mechanism reproduces well the changes in musical preferences \xrc{music here is odd; if an example is used it should be related to the topic of the paper}.
@@
 
-This model is composed of multiple agents producing goods of a fixed number of types.
-The agents are endowed with storage abilities for each good that can be produced.
+The only mandatory elements are a set of agents each possessing a fixed number of goods and associate a value to each of these goods.
+The value can be for example either an interest in the good or the price associated to this good.
+The agents are also endowed with limited storage abilities for each good that can be produced.
+
+More formally the model is composed as follow. $r$ is the number of resources present in the environment. The whole population is defined by a vector of $m$ agents: 
+$$ population = (a_i, \cdots ,a_m) $$
+
+Each agent $i$ is defined by 4 vectors each of size $r$. The first correspond to the quantity of each good that the agent possesses: $$ quantity = (q^i_1,\cdots,q^i_n) $$
+
+Each agent makes its own estimate on the price to attribute to a certain good. This price estimate is used for both selling and buying goods :
+$$ values = (v^i_1,\cdots,p^i_n) $$
+
 On top of producing the agents have the ability to exchange and consume the goods. 
-The specific rules for production, consumption and trading will vary depending on the hypothesis tested.
-Nevertheless the structure of the environment and the proceeding of a simulation will be the same for all hypothesis tested in this model.
+On the one side, the structure of the environment and the proceeding of a simulation will be the same for all hypothesis tested in this model.
+The specific rules for production, consumption and trading vary depending on the hypothesis tested.
+Nevertheless
 
@@
 
-More formally the model is composed as follow. $r$ is the number of ressources present in the environment. The whole population is defined by a vector of $m$ agents: 
-		$$ population = (a_i, \cdots ,a_m) $$
-
-Each agent $i$ is defined by 4 vectors each of size $r$. The first correspond to the quantity of each good that the agent possesses: $$ quantity = (q^i_1,\cdots,q^i_n) $$
-
-Each agent makes its own estimate on the price to attribute to a certain good. This price estimate is used for both selling and buying goods :
-$$ price = (p^i_1,\cdots,p^i_n) $$
-
 Finally, as mentioned before, each agent will consume a certain quantity of each good. This quantity can be a property of the agent, i.e. each agent consumes a different quantity of each product :
@@
 
-The elments listed above constitute the basic structure of the model.
+The elements listed above constitute the basic structure of the model.
 Different behaviours can be used for the agents and world depending on the assumption to test.
-This scheme allow us to have a model ahieving the two main goals listed in section~\ref{}.
+This scheme allow us to have a model achieving the two main goals listed in section~\ref{}.
 First, this model has a simple behaviour and few parameters to analyse.
@@
 \xrc{Validation is impossible for a theoretical model.
-Either you use verification if the goal is to check that implementation is correct, or design experiment for defining the experimens that will be used to explore the model.}
+Either you use verification if the goal is to check that implementation is correct, or design experiment for defining the experiments that will be used to explore the model.}
 

### 2015-03-25 article.tex
start to reorganise setup section

@@
 
-Each agent $i$ is defined by 4 vectors each of size $r$. The first correspond to the quantity of each good that the agent possesses: $$ quantity = (q^i_1,\cdots,q^i_n) $$
+Each agent $i$ is defined by 2 vectors each of size $r$. The first correspond to the quantity of each good that the agent possesses: $$ quantity = (q^i_1,\cdots,q^i_r) $$
 
 Each agent makes its own estimate on the price to attribute to a certain good. This price estimate is used for both selling and buying goods :
-$$ values = (v^i_1,\cdots,p^i_n) $$
+$$ values = (v^i_1,\cdots,p^i_r) $$
+
+This scheme allow us to have a model achieving the two main goals listed in section~\ref{}.
+First, this model is flexible enough to allow the study of multiple hypothesis while conserving the same units that can therefore be compared between simulations.
+Second, few parameters are present in the model which makes it easier to analyse and reuse by other researchers.
+
+\subsection{Experiment design}
+
+In order to validate our model a first result from the literature on the evolutionary transmission is reproduced.
+We then tackle the inclusion of simple trade mechanisms in order to show the possibility to implement them and the possibility to compare the results obtained in both economy and cultural transmission.
+
+\subsubsection{Cultural Evolution}
+
+In our model the ``cultural change'' is represented by the variations in the distribution of prices for each good.
+In order to validate our model we will try two simple biases: simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009}.
+The aim is to show that these simple modifications can allow us to observe the emergence of different cultures, each modifying the price structure obtained.
+The price structure obtained will be also compare to the obtained by the the economical model explained at the previous section.
+
+The production, consumption and trade phases described are not modified.
+However the price update phase is modified as follow.
+When the random copy behaviour is used each agent has a XXX\% chance to copy a new price from one agent selected randomly.
+Two frequency dependent behaviour are proposed.
+The first to be tested is the conformist behaviour with which each agent at each agent will have a XXXX\% chance to select the most common price for each good.
+The second to be tested is the rarity behaviour with which each agent at each iteration will have a XXX\% chance to select the least common beahviour.
+
+\subsubsection{Economical Trading}\label{trade}
 
@@
 
-The elements listed above constitute the basic structure of the model.
-Different behaviours can be used for the agents and world depending on the assumption to test.
-This scheme allow us to have a model achieving the two main goals listed in section~\ref{}.
-First, this model has a simple behaviour and few parameters to analyse.
-Second, this model is flexible enough to allow the study of multiple hypothesis while conserving the same units that can therefore be compared between simulations.
-
-\subsection{Validation}
-\xrc{Validation is impossible for a theoretical model.
-Either you use verification if the goal is to check that implementation is correct, or design experiment for defining the experiments that will be used to explore the model.}
-
-In order to validate our model mulitple experiments from the litterature in economy or evolution of culture have been selected to be reproduced.
-The basis of selection of these experiments is two fold.
-First, the experiment selected has to be simple and highlight clearly one effect.
-This restriction is to maintain the clarity of the paper.
-Second, these effects should consist the basis of our further studies toward understanding the principles of the roman economics.
-As a consequence the hypothesis tested will constitute valid hypothesis for the study of the economics and culture of the roman empire.
-
-\subsubsection{Economical Trading}\label{trade}
-
 The production methods can vary depending of geographical or historical factors.
@@
 Following the strategy proposed in the original model the XXX\% agents with the worst economical results adopt the strategy of the XXX\% best agents.
-
-\subsubsection{Cultural Evolution}
-
-In our model the ``cultural change'' is represented by the variations in the distribution of prices for each good.
-In order to validate our model we will try two simple biases: simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009}.
-The aim is to show that these simple modifications can allow us to obvserve the emergence of different cultures, each modifying the price structure obtained.
-The price structure obtained will be also compare to the obtained by the the economical model explained at the previous section.
-
-The production, consumption and trade phases described are not modified.
-However the price update phase is modified as follow.
-When the random copy behaviour is used each agent has a XXX\% chance to copy a new price from one agent selected randomly.
-Two frequency dependent behaviour are proposed.
-The first to be tested is the conformist behaviour with which each agent at each agent will have a XXXX\% chance to select the most common price for each good.
-The second to be tested is the rarity behaviour with which each agent at each iteration will have a XXX\% chance to select the least common beahviour.
 

### 2015-03-25 article.tex
working on cultural evolution section

--- 2015-03-25 article.tex
@@
 
-\subsection{Modelisation of Culture}
+\subsection{Neutral models of cultural change}
 
-\xrc{models of cultural change, not culture in general?}
+% 1. the second aspect is cultural change
+% 2. an evolutionary framework has explored this
+% 3. a large percentage of cultural products exchanged in an economic basis are neutral
+% 4. explain neutrality, model of random copy.
+% 5. from this perspective the interest of a product for an individual is directly related to its frequency
+% 6. this can potentially affect the product as part of a market because offer/demand is related to frequency
+% 7. at the same time, frequency will change depending on trade dynamics.
 
-\xrc{what is exactly the definition of culture used in the paper?
-I would suggest this one: \emph{Culture is socially learned information capable of affecting  individual phenotypes.
-People acquire culture from other individuals, via teaching or imitation} \cite{richerson_principles_1996}}
+The second component of our model is focused on the dynamics of cultural change.
+They comprise the collection of processes that promote or inhibit the spread of information by social interaction within a population \cite[3]{boyd_origin_2005}.
+This evolutionary framework is being used by an increasing number of social scientists, fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}.
+Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.
 
-The second aspect we wish to model is the evolution of the culture in the Roman empire.
-The evolutionary framework (generally used in Biology) has been proposed to study the changes of culture and found to be suitable,  particularly in the case of historical and archaeological studies~\cite{lycett_cultural_2015,henrich_evolution_2003}\xrc{henrich's paper is not on archaeology or history, better reference \cite{shennan_evolution_2008}}.
+Of particular interest to our study are the scenarios where cultural traits are copied by unbiased transmission (i.e.
+traits which do not have a intrinsic positive or negative value for the individuals adopting them).
+This situation is often analysed following the genetic theory of neutral evolution \cite{neiman_stylistic_1995}, where the variation of traits is strictly explained by their frequency distribution in the population.
+There exist a large number of works using this model as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 

### 2015-03-27 article.tex
cultural change section

@@
 
-% 1. the second aspect is cultural change
-% 2. an evolutionary framework has explored this
-% 3. a large percentage of cultural products exchanged in an economic basis are neutral
-% 4. explain neutrality, model of random copy.
-% 5. from this perspective the interest of a product for an individual is directly related to its frequency
-% 6. this can potentially affect the product as part of a market because offer/demand is related to frequency
-% 7. at the same time, frequency will change depending on trade dynamics.
-
 The second component of our model is focused on the dynamics of cultural change.
@@
 This evolutionary framework is being used by an increasing number of social scientists, fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}.
-Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.
+Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{obrien_cladistics_2001} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.
 
-Of particular interest to our study are the scenarios where cultural traits are copied by unbiased transmission (i.e.
-traits which do not have a intrinsic positive or negative value for the individuals adopting them).
-This situation is often analysed following the genetic theory of neutral evolution \cite{neiman_stylistic_1995}, where the variation of traits is strictly explained by their frequency distribution in the population.
+A large percentage of these studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependance (e.g.
+conformism and anti-conformism).
+These analysis are often based in the genetic theory of neutral evolution \cite{neiman_stylistic_1995} and they take neutrality as a null-hypotheses (i.e.
+variation of traits is strictly explained by its frequency distribution in the population).
 There exist a large number of works using this model as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
-Within this framework, the individual preferences for cultural traits (such as music taste or shapes of pottery) are copied from one individual to the other.
-Each individual is then adding some small variations to this cultural trait she just acquired.
+Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism \cite{bentley_random_2004}.
+Within this framework, an individual will copy the traits of a randomly chosen individual with a given probability.
+This copy can potentially introduce some errors in the acquired trait, which account for innovation processes.
 The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
-Studies are then performed on the three key steps of the framework: the transmission, the variation and the differential replication.
-Interestingly the study of these elements is not only done thanks to humans but also thanks to other animals.
+This basic model can be enriched by several additional processes both in the innovation \cite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission \cite{heyes_social_1994,henrich_evolution_2003}.
 
-\xrc{I would use social learning instead of cultural transmission}
-
-The transmission mechanisms are the means used to transfer cultural traits from one individuals to another.
-A large number of social learning schemes can be envisioned~\cite{heyes_social_1994} \xrc{a better reference would be \cite{henrich_evolution_2003}}.
-Notably, the mechanisms do not necessarily have to be as complex as teaching, since emulation and imitation can be sufficient to pass on certain cultural traits.
-
-The variation mechanisms are at the heart of the creation of the creation of new cultural elements~\cite{obrien_variation_1990}.
-These may happen due to some errors during the copy process~\cite{schillinger_copying_2014}.
-In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}\xrc{see also recombination \cite{sole_evolutionary_2013}}.
-
-\xrc{Instead of differential replication I would use \emph{biased selection}}
-The last element is the one that will interest us the most in this study: the differential replication between different cultural traits.
-If a cultural trait is found more often than the others in the population it means that something modified the rate at which it is adopted by each agent \xrc{beyond drift effects produced by random copy of neutral traits \cite{bentley_random_2004}}.
-%The reproduction rate of ideas in a population can be characterise by different rates: directional, disruptive or stabilisation~\cite{rendell_cognitive_2011}. 
-Multiple processes can be at play behind the reproduction \xrc{selection?
-transmission?
-reproduction is too biological} of cultural traits.
-Among them the three following will interest us due to their simplicity to test in an agent-based modelisation.
-First is the random copy of one trait from an agent to another agent.
-\todo{get a ref on that} \xrc{you can use \cite{bentley_random_2004}}
-This type of mechanism reproduces well the changes in musical preferences \xrc{music here is odd; if an example is used it should be related to the topic of the paper}.
-Second are the the copy based on the frequency at which a cultural trait is observed.
-If a common trait is reproduced more often then we speak about ``conformity.'' If on the contrary the less common trait is preferred for reproduction we speak of ``rarity'' \xrc{nope, we speak of anti-conformism}.
-Finally a trait can be preferred depending on whom is carrying it.
-Among these preferences the prestige of the individual carrying it can constitute an explanation for the adoption foreign cultural traits in the Roman empire \xrc{this is known as model biased transmission}.
-
-\xrc{Again, I should focus the lit.review on models of cultural change in at least ancient societies, this is too broad.}
+In particular, the trade of cultural products within a market system can potentially introduce a dynamics content-related bias linked to the price of the different products.
+This would also affect the frequency of the product within the population, which in turn would modify its price following a co-evolutionary dynamic.
 

### 2015-03-27 article.tex
work on the presentation of the setup

--- 2015-03-25 article.tex
@@
 %\usepackage{amsthm}
+
+\usepackage{mathtools}
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
+\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
+\makeatletter
+\let\oldabs\abs
+\def\abs{\@ifstar{\oldabs}{\oldabs*}}
+\let\oldnorm\norm
+\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
+\makeatother
 
@@
 
-\section{INTRODUCTION}
+\section{INTRODUCTION}\label{sec:intro}
 
@@
 
-\todo{find another title}
-\subsection{Agent-based consumers and traders}
-%tell the story of what is happening
-
-The only mandatory elements are a set of agents each possessing a fixed number of goods and associate a value to each of these goods.
-The value can be for example either an interest in the good or the price associated to this good.
+In the model presented a set of agents are each in possession of a fixed number of goods and associate a value to each of these goods.
+Depending on the question studied, the value can reflect the interest of the agent for the good or it can be the price at which the agent evaluate this good.
 The agents are also endowed with limited storage abilities for each good that can be produced.
@@
 
-This scheme allow us to have a model achieving the two main goals listed in section~\ref{}.
-First, this model is flexible enough to allow the study of multiple hypothesis while conserving the same units that can therefore be compared between simulations.
-Second, few parameters are present in the model which makes it easier to analyse and reuse by other researchers.
+On top of these elements two processes are included : imitation and innovation.
+The first one reflects the possibility for agents to imitate other agents.
+For this, an agent can copy the value vector of another agent.
+The second process reflects the possibility for an agent to associate new values for the goods.
+For this, an agent can select new elements for its value vector independently of the values of other agents.
 
-\subsection{Experiment design}
+This scheme allow us to have a model achieving the two main goals listed in section~\ref{sec:intro}.
+First, this model allows us to test various cultural transmission mechanisms as well as trade mechanisms.
+The experiments presented in this article show examples of implementations for both categories.
+Moreover, the fact that only two processes are modified allow comparisons between simulations with the same units.
+Second, few parameters are present in the default model which makes it easier to analyse and reuse by other researchers.
 
-In order to validate our model a first result from the literature on the evolutionary transmission is reproduced.
-We then tackle the inclusion of simple trade mechanisms in order to show the possibility to implement them and the possibility to compare the results obtained in both economy and cultural transmission.
+\section{EXPERIMENTAL SETUP}
 
-\subsubsection{Cultural Evolution}
+In order to validate our model a first result from the literature on the evolutionary transmission is reproduced. We then illustrate the possibility to implement a trade mechanisms.
 
-In our model the ``cultural change'' is represented by the variations in the distribution of prices for each good.
-In order to validate our model we will try two simple biases: simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009}.
-The aim is to show that these simple modifications can allow us to observe the emergence of different cultures, each modifying the price structure obtained.
-The price structure obtained will be also compare to the obtained by the the economical model explained at the previous section.
+\subsection{Cultural Transmission}
 
-The production, consumption and trade phases described are not modified.
-However the price update phase is modified as follow.
-When the random copy behaviour is used each agent has a XXX\% chance to copy a new price from one agent selected randomly.
-Two frequency dependent behaviour are proposed.
-The first to be tested is the conformist behaviour with which each agent at each agent will have a XXXX\% chance to select the most common price for each good.
-The second to be tested is the rarity behaviour with which each agent at each iteration will have a XXX\% chance to select the least common beahviour.
+In this article the cultural transmission tested is the ``random copy" such as presented in~\cite{mesoudi_random_2009}.
+The aim is to show that our model is indeed able to reproduce the main trends expected with such copy mechanism.
+Namely, we should observe a distribution known as the power law, displaying a line in the log-log graph of the proportion of variants with regards to the frequency of variant.
 
-\subsubsection{Economical Trading}\label{trade}
+The imitation process is a ``random copy" meaning that with a low probability each agent pick randomly one agent among all and copy it's vector of values.
+The innovation process is triggered with a low probability and select new elements for the vector of values.
+These new elements are drawn from a uniform distribution.
+The imitation and innovation probabilities are presented with other parameters in table~\ref{tab:parameters}
+
+\subsection{Trading Model}\label{sec:trade}
+
+\paragraph*{Imitation}
+To test a simple trading model, two notions are introduced in the imitation mechanism: need and score.
+The need is a quantity of product that each agent tries to obtain.
+This quantity is different for each product but the need for a product is the same for all agents:
+$$ need = (n_1, \cdots, n_r) $$
+
+The score reflects the ability for an agent to obtain the products it needs, it is formally computed as follow for agent $i$:
+
+$$ \abs{\dfrac{q^i_j - n_j}{ \sqrt{\abs{(q^i_j*q^i_j)-(n_j*n_j)}}}} $$
+
+\paragraph*{Trading}
 
@@
 Nevertheless
+
+\paragraph*{Innovation}
 
@@
 This goods production should reflect the historical good production of the period studied and agent could produce various good in order to barter or sell them using the trade network.
-
-Finally, as mentioned before, each agent will consume a certain quantity of each good. This quantity can be a property of the agent, i.e. each agent consumes a different quantity of each product :
-$$ consumption = (c^i_1, \cdots, c^i_n) $$
 
@@
 Following the strategy proposed in the original model the XXX\% agents with the worst economical results adopt the strategy of the XXX\% best agents.
-
-\section{EXPERIMENTAL SETUP}
 

### 2015-03-27 article.tex

@@
 
-\subsection{Modelisation of Culture}
+\subsection{Neutral models of cultural change}
 
-\xrc{models of cultural change, not culture in general?}
+The second component of our model is focused on the dynamics of cultural change.
+They comprise the collection of processes that promote or inhibit the spread of information by social interaction within a population \cite[3]{boyd_origin_2005}.
+This evolutionary framework is being used by an increasing number of social scientists, fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}.
+Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{obrien_cladistics_2001} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.
 
-\xrc{what is exactly the definition of culture used in the paper?
-I would suggest this one: \emph{Culture is socially learned information capable of affecting  individual phenotypes.
-People acquire culture from other individuals, via teaching or imitation} \cite{richerson_principles_1996}}
+A large percentage of these studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependance (e.g.
+conformism and anti-conformism).
+These analysis are often based in the genetic theory of neutral evolution \cite{neiman_stylistic_1995} and they take neutrality as a null-hypotheses (i.e.
+variation of traits is strictly explained by its frequency distribution in the population).
+There exist a large number of works using this model as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
-The second aspect we wish to model is the evolution of the culture in the Roman empire.
-The evolutionary framework (generally used in Biology) has been proposed to study the changes of culture and found to be suitable,  particularly in the case of historical and archaeological studies~\cite{lycett_cultural_2015,henrich_evolution_2003}\xrc{henrich's paper is not on archaeology or history, better reference \cite{shennan_evolution_2008}}.
+Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism \cite{bentley_random_2004}.
+Within this framework, an individual will copy the traits of a randomly chosen individual with a given probability.
+This copy can potentially introduce some errors in the acquired trait, which account for innovation processes.
+The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
+This basic model can be enriched by several additional processes both in the innovation \cite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission \cite{heyes_social_1994,henrich_evolution_2003}.
 
-Within this framework, the individual preferences for cultural traits (such as music taste or shapes of pottery) are copied from one individual to the other.
-Each individual is then adding some small variations to this cultural trait she just acquired.
-The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
-Studies are then performed on the three key steps of the framework: the transmission, the variation and the differential replication.
-Interestingly the study of these elements is not only done thanks to humans but also thanks to other animals.
-
-\xrc{I would use social learning instead of cultural transmission}
-
-The transmission mechanisms are the means used to transfer cultural traits from one individuals to another.
-A large number of social learning schemes can be envisioned~\cite{heyes_social_1994} \xrc{a better reference would be \cite{henrich_evolution_2003}}.
-Notably, the mechanisms do not necessarily have to be as complex as teaching, since emulation and imitation can be sufficient to pass on certain cultural traits.
-
-The variation mechanisms are at the heart of the creation of the creation of new cultural elements~\cite{obrien_variation_1990}.
-These may happen due to some errors during the copy process~\cite{schillinger_copying_2014}.
-In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}\xrc{see also recombination \cite{sole_evolutionary_2013}}.
-
-\xrc{Instead of differential replication I would use \emph{biased selection}}
-The last element is the one that will interest us the most in this study: the differential replication between different cultural traits.
-If a cultural trait is found more often than the others in the population it means that something modified the rate at which it is adopted by each agent \xrc{beyond drift effects produced by random copy of neutral traits \cite{bentley_random_2004}}.
-%The reproduction rate of ideas in a population can be characterise by different rates: directional, disruptive or stabilisation~\cite{rendell_cognitive_2011}. 
-Multiple processes can be at play behind the reproduction \xrc{selection?
-transmission?
-reproduction is too biological} of cultural traits.
-Among them the three following will interest us due to their simplicity to test in an agent-based modelisation.
-First is the random copy of one trait from an agent to another agent.
-\todo{get a ref on that} \xrc{you can use \cite{bentley_random_2004}}
-This type of mechanism reproduces well the changes in musical preferences \xrc{music here is odd; if an example is used it should be related to the topic of the paper}.
-Second are the the copy based on the frequency at which a cultural trait is observed.
-If a common trait is reproduced more often then we speak about ``conformity.'' If on the contrary the less common trait is preferred for reproduction we speak of ``rarity'' \xrc{nope, we speak of anti-conformism}.
-Finally a trait can be preferred depending on whom is carrying it.
-Among these preferences the prestige of the individual carrying it can constitute an explanation for the adoption foreign cultural traits in the Roman empire \xrc{this is known as model biased transmission}.
-
-\xrc{Again, I should focus the lit.review on models of cultural change in at least ancient societies, this is too broad.}
+In particular, the trade of cultural products within a market system can potentially introduce a dynamics content-related bias linked to the price of the different products.
+This would also affect the frequency of the product within the population, which in turn would modify its price following a co-evolutionary dynamic.
 

### 2015-03-27 article.tex
add the algorithms and stories in the setup

@@
 %\usepackage{amsthm}
+
+\usepackage{algorithm,algorithmicx,algpseudocode}
+\algnewcommand\And{\textbf{and}}
 
@@
 
-On top of these elements two processes are included : imitation and innovation.
-The first one reflects the possibility for agents to imitate other agents.
-For this, an agent can copy the value vector of another agent.
-The second process reflects the possibility for an agent to associate new values for the goods.
+On top of these elements three processes are included : production, imitation and innovation.
+The \textit{production} process describe the creation of goods by the agent.
+In this article each agent is producing only one type of good.
+The type good produced by an agent is assigned to it at the beginning of the simulation and does not change.
+Once a good is produced it is added to the quantity vector of the agent.
+Within the \textit{imitation} process an agent can copy the value vector of another agent.
+The \textit{innovation} process reflects the possibility for an agent to associate new values for the goods.
 For this, an agent can select new elements for its value vector independently of the values of other agents.
@@
 The experiments presented in this article show examples of implementations for both categories.
-Moreover, the fact that only two processes are modified allow comparisons between simulations with the same units.
+Moreover, the fact that only three processes are modified allow comparisons between simulations with the same units.
+In this article the \textit{production} process will remain the same and only the \textit{imitation} and \textit{innovation} processes are changed.
 Second, few parameters are present in the default model which makes it easier to analyse and reuse by other researchers.
@@
 
-\paragraph*{Imitation}
+\paragraph{Imitation}
 To test a simple trading model, two notions are introduced in the imitation mechanism: need and score.
@@
 
-\paragraph*{Trading}
+\paragraph{Trading}
+
+\todo{miss the formula for a possible trade}
 
 On top of producing the agents have the ability to exchange and consume the goods.
-On the one side, the structure of the environment and the proceeding of a simulation will be the same for all hypothesis tested in this model.
-The specific rules for production, consumption and trading vary depending on the hypothesis tested.
-Nevertheless
+During the trading phase the value associated to a good by an agent corresponds to the subjective price of the good for this agent.
+Briefly summarised, for each good that it does not produced, an agent will trade with the first parter that offer an acceptable trade, i.e.
+the agent that proposes a satisfiable ratio between the other product and the product produced by the agent.
+In more detail, the trading phase start by the agent looking at a first random agent producing another product.
+A trade is possible with the other agent if the following condition holds:
 
-\paragraph*{Innovation}
+$$ hey $$
 
-One time step of the simulation is divided in three phases.
-In the first phase all agents produce goods.
-Each agent is assigned one type of good, and it will produce only this type of good at each first phase.
-In the second phase all agents enter trade with other agents according to their own interest.
-Each agent has the possibility to choose with which other agent it will trade products.
-Once two agents agree to trade, the agents decide which products will be exchanged and in which quantities.
-When an agreement is found, the trade occur and the agents look for other potential partners.
-Within one trading phase, an agent can meet only one time each other agents.
-In the third phase all agent consume goods according to their own rules.
-A unit of a good consumed disappears from the stock of the agent.
+If a trade is possible the two agents will exchange the agreed quantities.
+If the trade is not possible, the agent will continue to look at random partners for this good until either a good is find or $TradeThreshold$ agents have been tried.
+At this point the agent will try to trade with agents producing another good.
+The process goes on until all goods have been tried.
+This trading process is described in algorithm~\ref{algo:trade}.
 
-%In the simulation agents produce goods that they will barter (cf section \ref{trade}) and consume (cf section \ref{consumption}).
-This goods production should reflect the historical good production of the period studied and agent could produce various good in order to barter or sell them using the trade network.
+\begin{algorithm}
+\caption{Trading Process}
+\label{algo:trade}
+	\begin{algorithmic}[1]
+	\scriptsize
+		\For{$Good_i \in Goods \And i \neq A_g $}
+			\State $tradeAttempt = 0$
+			\For{$A_i \in Good_i \And tradeAttempt < TradeThreshold $}
+				\If{$acceptableTrade(A_i)$}
+					\State $trade(A_i)$
+				\Else
+					\State $tradeAttempt = tradeAttempt + 1$					
+				\EndIf
+			\EndFor
+		\EndFor
+\end{algorithmic}
+\end{algorithm}
 
-The production methods can vary depending of geographical or historical factors.
-In order to validate the relevance of the model, we will follow \cite{gintis_emergence_2006}.
-In this model, the goal is to observe the convergence of price to a market equilibrium in a bartering decentralized economy model.
-In the orignal model it is shown that the prices can converge to the market clearing price.
+The trading process is performed at every iteration while the imitation and innovation processes are executed only every $CulturalStep$.
+The idea behind this is to perform the imitation based on a score that reflects the performance of the agent and not only one lucky or unlucky trading round.
 
-In this economical model the agents are ranked with regards to the value of their stock. This value is computed as follow ...
-\todo{find the computation}
+\paragraph{Innovation} The innovation process is triggered with a low probability and select new elements for the vector of values.
+These new elements are drawn from a uniform distribution centred on the current value of each product.
 
-In this model each agent produces only one type of good.
-During the trading process, all agents meet each other.
-Since one agent is producing only one good it will only trade with the agents not producing this good.
-The procedure to choose the trading partners is detailed in algorithm XXXX.
-\todo{do the algorithm}
-Briefly summarised, for each good that it does not produced, an agent will look for the parter that offer the best trade, i.e.
-the agent that proposes to exchange the most of the other product for the fewest of the product produced by the agent.
+\subsection{Complete model}
 
-All agents of the simulation have the same constant consumption vector.
-A fixed-for-everyone proportion $b_1,\cdots,b_n$ of each resource $(1, \cdots, n)$ is given at the beginning of the simulation.
-At the end of the consumption phase all remaining products are removed from the agents.
+The model used in these experiments, including the cultural transmission and trading mechanisms, is described in algorithms~\ref{algo:complete}
 
-At the end of a time step, each agent has the opportunity to update its prices .
-Following the strategy proposed in the original model the XXX\% agents with the worst economical results adopt the strategy of the XXX\% best agents.
+\begin{algorithm}
+\caption{Trading Process}
+\label{algo:complete}
+	\begin{algorithmic}[1]
+	\scriptsize
+	\State INITIALIZATION: 
+		\For{$Good_i \in Goods$}
+			\For{$Agents per Goods$}
+				\State $A_i = (g_i,p_i,n_i)$
+			\EndFor
+		\EndFor
+
+	\State SIMULATION:
+		\Loop{$step \in TimeSteps$}
+			\For{$A_i \in Pop$}
+				\State $Production$
+				\State $Trade$				
+				\If{$step CulturalStep$}	
+					\State $Imitation$
+					\State $Inovation$
+				\EndIf
+			\EndFor
+		\EndLoop
+\end{algorithmic}
+\end{algorithm}
 

### 2015-03-27 article.tex
results simon

--- 2015-03-27 article.tex
@@
 %\usepackage{amsthm}
-
-\usepackage{mathtools}
-\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
-\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
-
-\makeatletter
-\let\oldabs\abs
-\def\abs{\@ifstar{\oldabs}{\oldabs*}}
-\let\oldnorm\norm
-\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
-\makeatother
 
@@
 
-\section{INTRODUCTION}\label{sec:intro}
+\section{INTRODUCTION}
 
@@
 
-In the model presented a set of agents are each in possession of a fixed number of goods and associate a value to each of these goods.
-Depending on the question studied, the value can reflect the interest of the agent for the good or it can be the price at which the agent evaluate this good.
+\todo{find another title}
+\subsection{Agent-based consumers and traders}
+%tell the story of what is happening
+
+The only mandatory elements are a set of agents each possessing a fixed number of goods and associate a value to each of these goods.
+The value can be for example either an interest in the good or the price associated to this good.
 The agents are also endowed with limited storage abilities for each good that can be produced.
@@
 
-Each agent $i$ is defined by 2 vectors each of size $r$. The first correspond to the quantity of each good that the agent possesses: $$ quantity = (q^i_1,\cdots,q^i_r) $$
+Each agent $i$ is defined by 4 vectors each of size $r$. The first correspond to the quantity of each good that the agent possesses: $$ quantity = (q^i_1,\cdots,q^i_n) $$
 
 Each agent makes its own estimate on the price to attribute to a certain good. This price estimate is used for both selling and buying goods :
-$$ values = (v^i_1,\cdots,p^i_r) $$
-
-On top of these elements two processes are included : imitation and innovation.
-The first one reflects the possibility for agents to imitate other agents.
-For this, an agent can copy the value vector of another agent.
-The second process reflects the possibility for an agent to associate new values for the goods.
-For this, an agent can select new elements for its value vector independently of the values of other agents.
-
-This scheme allow us to have a model achieving the two main goals listed in section~\ref{sec:intro}.
-First, this model allows us to test various cultural transmission mechanisms as well as trade mechanisms.
-The experiments presented in this article show examples of implementations for both categories.
-Moreover, the fact that only two processes are modified allow comparisons between simulations with the same units.
-Second, few parameters are present in the default model which makes it easier to analyse and reuse by other researchers.
-
-\section{EXPERIMENTAL SETUP}
-
-In order to validate our model a first result from the literature on the evolutionary transmission is reproduced. We then illustrate the possibility to implement a trade mechanisms.
-
-\subsection{Cultural Transmission}
-
-In this article the cultural transmission tested is the ``random copy" such as presented in~\cite{mesoudi_random_2009}.
-The aim is to show that our model is indeed able to reproduce the main trends expected with such copy mechanism.
-Namely, we should observe a distribution known as the power law, displaying a line in the log-log graph of the proportion of variants with regards to the frequency of variant.
-
-The imitation process is a ``random copy" meaning that with a low probability each agent pick randomly one agent among all and copy it's vector of values.
-The innovation process is triggered with a low probability and select new elements for the vector of values.
-These new elements are drawn from a uniform distribution.
-The imitation and innovation probabilities are presented with other parameters in table~\ref{tab:parameters}
-
-\subsection{Trading Model}\label{sec:trade}
-
-\paragraph*{Imitation}
-To test a simple trading model, two notions are introduced in the imitation mechanism: need and score.
-The need is a quantity of product that each agent tries to obtain.
-This quantity is different for each product but the need for a product is the same for all agents:
-$$ need = (n_1, \cdots, n_r) $$
-
-The score reflects the ability for an agent to obtain the products it needs, it is formally computed as follow for agent $i$:
-
-$$ \abs{\dfrac{q^i_j - n_j}{ \sqrt{\abs{(q^i_j*q^i_j)-(n_j*n_j)}}}} $$
-
-\paragraph*{Trading}
+$$ values = (v^i_1,\cdots,p^i_n) $$
 
@@
 Nevertheless
-
-\paragraph*{Innovation}
 
@@
 This goods production should reflect the historical good production of the period studied and agent could produce various good in order to barter or sell them using the trade network.
+
+Finally, as mentioned before, each agent will consume a certain quantity of each good. This quantity can be a property of the agent, i.e. each agent consumes a different quantity of each product :
+$$ consumption = (c^i_1, \cdots, c^i_n) $$
+
+The elements listed above constitute the basic structure of the model.
+Different behaviours can be used for the agents and world depending on the assumption to test.
+This scheme allow us to have a model achieving the two main goals listed in section~XXX.
+First, this model has a simple behaviour and few parameters to analyse.
+Second, this model is flexible enough to allow the study of multiple hypothesis while conserving the same units that can therefore be compared between simulations.
+
+\subsection{Validation}
+\xrc{Validation is impossible for a theoretical model.
+Either you use verification if the goal is to check that implementation is correct, or design experiment for defining the experiments that will be used to explore the model.}
+
+In order to validate our model mulitple experiments from the litterature in economy or evolution of culture have been selected to be reproduced.
+The basis of selection of these experiments is two fold.
+First, the experiment selected has to be simple and highlight clearly one effect.
+This restriction is to maintain the clarity of the paper.
+Second, these effects should consist the basis of our further studies toward understanding the principles of the roman economics.
+As a consequence the hypothesis tested will constitute valid hypothesis for the study of the economics and culture of the roman empire.
+
+\subsubsection{Economical Trading}\label{trade}
 
@@
 
+\subsubsection{Cultural Evolution}
+
+In our model the ``cultural change'' is represented by the variations in the distribution of prices for each good.
+In order to validate our model we will try two simple biases: simple random copying and frequency-dependent copying as \cite{mesoudi_random_2009}.
+The aim is to show that these simple modifications can allow us to obvserve the emergence of different cultures, each modifying the price structure obtained.
+The price structure obtained will be also compare to the obtained by the the economical model explained at the previous section.
+
+The production, consumption and trade phases described are not modified.
+However the price update phase is modified as follow.
+When the random copy behaviour is used each agent has a XXX\% chance to copy a new price from one agent selected randomly.
+Two frequency dependent behaviour are proposed.
+The first to be tested is the conformist behaviour with which each agent at each agent will have a XXXX\% chance to select the most common price for each good.
+The second to be tested is the rarity behaviour with which each agent at each iteration will have a XXX\% chance to select the least common beahviour.
+
+\section{EXPERIMENTAL SETUP}
+
 \section{RESULTS}
+\subsection{Random cultural transmission and random innovation process}
+In our model, agent own a set of price they assign to a certain number of resources.
+Those prices could be seen as the importance, or the ``value''  that each agents believe each good bears.
+It could be seen as cultural traits that agents can modify or share with other agent.
+In the first experiment the value of those traits does not impact the agent  behavior neither the way they will modify and share it.
+\subsubsection{One trait}
+Knowing that and following \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}, we think that in our model those prices will behave exactly like any other cultural trait, and that the different version of prices for each good will be found in the population in proportion that follow a power law.
+
+It's indeed what we observe.
+In the first experiment, in order to compare our result with those of the literature, we use only one price.
+We check for some of the same $\mu$ value used in \cite{bentley_specialisation_2005,mesoudi_random_2009} that the distribution of the number of variants are the same.
+
+That is what we can see in the figure \ref{fig:allMutation}.
+
+Each curves on the figures show the mean for 100 runs.
+In our experiment one has to take in account that agents modifies their prices or exchange their price only every ten steps.
+Between, they exchange goods given their own prices.
+Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}, for $\mu$ the innovation rate $\in {.004,.008,.016,.064}$ and for 250 and 500 agents.
+
+\simon{reference to the R package and the theoreticla ref in the Rpackage?}
+Those distribution exhibit power law like attribute and we can fit them.
+The result of the alpha fitted with are in the table \ref{tab:mualpha}.
+The alpha values represent the mean of the fitted alpha for each run computed using RPACKAGE with the standard deviation associated with each mean.
+\begin{figure}[hbp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/allmuRandMaxBentleyValues.pdf}
+	\end{center}
+	\caption{rand()\%RAND\_MAX}
+	\label{fig:allMutation}
+\end{figure}
+
+\begin{table}
+	\centering
+	\begin{tabular}{cc}
+		\begin{tabular}{l|cc}
+			$\mu$ & $\alpha$ & SD\\\hline
+			0.004&1.541193&0.031384174\\
+			0.008&1.549726&0.021953251\\
+			0.016&1.568096&0.017025456\\
+			0.064&1.651690&0.006538209\\
+
+		\end{tabular}
+		&
+		\begin{tabular}{l|cc}
+			$\mu$ & $\alpha$ & SD\\\hline
+			0.004&1.539710&0.022515901\\
+			0.008&1.557460&0.017805810\\
+			0.016&1.570036&0.004412181\\
+			0.064&1.651521&0.009988488\\
+		\end{tabular}\\
+		(a) & (b)
+	\end{tabular}
+	\caption{Mean \& SD are done with 100 run for each with 250 agent for (a) and 500 for (b) }
+	\label{tab:mualpha}
+\end{table}
+
+\subsubsection{Multiple traits co-evolving randomly}
+\simon{ this part could be resumed to one phrase saying that nothing change and that we check it without showing any result moreover}
+As our aims is to study the evolution of an economy where people exchange different goods, we have checked if the previous results are the same when the agents own not just one price for one good but a vector of price associated to each good available in the environment.
+If the innovation process assure that all price could be modified in totally independent way, when a cultural transmission occur agents copy the whole vector of price from another agent.
+We show in the table~\ref{tab:alphagoods} the mean of $\alpha$ between each resource for different number of resource.
+
+\begin{table}
+	\centering
+		\begin{tabular}{l|cccc}
+			  & g=1  & g= 2 & g=3 & g=4 \\\hline
+			$\alpha$&\\
+			sd \\
+		\end{tabular}
+	\caption{alpha is the mean alpha between each good for 100 runs }
+	\label{tab:alphagoods}
+\end{table}
+
+\subsection{ Economical  process}
+
+In the previous experiment the estimate price of good have no impact on the agents choices and behaviors.
+In a real economical system it's not the case.
+In order to approximate such a process and to see how our framework could handle economical mechanism we introduce a new cultural transmission mechanism.
+
+This time agent will not copying randomly the vector of price from one random individual but they will choose among the agent that produce the same good those that seem the most successful.
+In practice, a fixed proportion of the less successful agents will copy the prices of the more successful agent.
+
+To express this idea of success we define a score that is maximum when you manage to have exactly the needed amount for each good.
+If you exchange too much or too few of one of the good your score will decreased.
+The score is computed in such a way that each good count for the same proportion in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value won't help you to increase your score).
+
+Meanwhile time the innovation mechanism used in the experiment  we follow in the previous section seems not  an adequate economical mechanism.
+While in a cultural point a view an innovation could be anything new in you space innovation, it's seem little probable than a price will be change to something totally new.
+
+That why we  introduce a new innovation mechanism which will also occur with a probability of $\mu$ but this time, instead of set a totally new price, it will modify the previous price by adding or subtract to it a small amount randomly choose between $0 ..
+\beta$.
+
+In order to study the impact of the introduction of those new mechanism  we summarize it in the table~\ref{tab:exp}. 
+\begin{table}
+	\centering
+	\begin{tabular}{l|c|c}
+		& Rand & Eco \\\hline
+		$\mu$ &A & B \\
+		$\mu +\alpha$ & C & D \\
+	\end{tabular}
+	\caption{Experimental Setup}
+	\label{tab:exp}
+\end{table}
+
+The following  experiments will last longer than the firsts one because this time the exchange mechanisms will have an impact on the evolution of prices in the population.
+All the next experiments are run during 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
 

### 2015-03-27 article.tex

--- 2015-03-27 article.tex
@@
 
+%%A integrer
+Knowing that and following \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}, we think that in our model those prices will behave exactly like any other cultural trait, and that the different version of prices for each good will be found in the population in proportion that follow a power law.
+
+It's indeed what we observe.
+In the first experiment, in order to compare our result with those of the literature, we use only one price.
+We check for some of the same $\mu$ value used in \cite{bentley_specialisation_2005,mesoudi_random_2009} that the distribution of the number of variants are the same.
+
 \subsection{Trading Model}\label{sec:trade}
+%%à integrer
+In the previous experiment the estimate price of good have no impact on the agents choices and behaviors.
+In a real economical system it's not the case.
+In order to approximate such a process and to see how our framework could handle economical mechanism we introduce a new cultural transmission mechanism.
+
+This time agent will not copying randomly the vector of price from one random individual but they will choose among the agent that produce the same good those that seem the most successful.
+In practice, a fixed proportion of the less successful agents will copy the prices of the more successful agent.
+
+Meanwhile time the innovation mechanism used in the experiment  we follow in the previous section seems not  an adequate economical mechanism.
+While in a cultural point a view an innovation could be anything new in you space innovation, it's seem little probable than a price will be change to something totally new.
+
+That why we  introduce a new innovation mechanism which will also occur with a probability of $\mu$ but this time, instead of set a totally new price, it will modify the previous price by adding or subtract to it a small amount randomly choose between $0 ..
+\beta$.
 
@@
 $$ \abs{\dfrac{q^i_j - n_j}{ \sqrt{\abs{(q^i_j*q^i_j)-(n_j*n_j)}}}} $$
+
+%%A integrer
+To express this idea of success we define a score that is maximum when you manage to have exactly the needed amount for each good.
+If you exchange too much or too few of one of the good your score will decreased.
+The score is computed in such a way that each good count for the same proportion in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value won't help you to increase your score).
 
@@
 \section{RESULTS}
+\subsection{Random cultural transmission and random innovation process}
+\subsubsection{One trait}
+
+That is what we can see in the figure \ref{fig:allMutation}.
+
+Each curves on the figures show the mean for 100 runs.
+In our experiment one has to take in account that agents modifies their prices or exchange their price only every ten steps.
+Between, they exchange goods given their own prices.
+Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}, for $\mu$ the innovation rate $\in {.004,.008,.016,.064}$ and for 250 and 500 agents.
+
+\simon{reference to the R package and the theoreticla ref in the Rpackage?}
+Those distribution exhibit power law like attribute and we can fit them.
+The result of the alpha fitted with are in the table \ref{tab:mualpha}.
+The alpha values represent the mean of the fitted alpha for each run computed using RPACKAGE with the standard deviation associated with each mean.
+\begin{figure}[hbp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/allmuRandMaxBentleyValues.pdf}
+	\end{center}
+	\caption{rand()\%RAND\_MAX}
+	\label{fig:allMutation}
+\end{figure}
+
+\begin{table}
+	\centering
+	\begin{tabular}{cc}
+		\begin{tabular}{l|cc}
+			$\mu$ & $\alpha$ & SD\\\hline
+			0.004&1.541193&0.031384174\\
+			0.008&1.549726&0.021953251\\
+			0.016&1.568096&0.017025456\\
+			0.064&1.651690&0.006538209\\
+
+		\end{tabular}
+		&
+		\begin{tabular}{l|cc}
+			$\mu$ & $\alpha$ & SD\\\hline
+			0.004&1.539710&0.022515901\\
+			0.008&1.557460&0.017805810\\
+			0.016&1.570036&0.004412181\\
+			0.064&1.651521&0.009988488\\
+		\end{tabular}\\
+		(a) & (b)
+	\end{tabular}
+	\caption{Mean \& SD are done with 100 run for each with 250 agent for (a) and 500 for (b) }
+	\label{tab:mualpha}
+\end{table}
+
+\subsubsection{Multiple traits co-evolving randomly}
+\simon{ this part could be resumed to one phrase saying that nothing change and that we check it without showing any result moreover}
+As our aims is to study the evolution of an economy where people exchange different goods, we have checked if the previous results are the same when the agents own not just one price for one good but a vector of price associated to each good available in the environment.
+And every thing is OKAY
+
+%\begin{table}
+%	\centering
+%		\begin{tabular}{l|cccc}
+%			  & g=1  & g= 2 & g=3 & g=4 \\\hline
+%			$\alpha$&\\
+%			sd \\
+%		\end{tabular}
+%	\caption{alpha is the mean alpha between each good for 100 runs }
+%	\label{tab:alphagoods}
+%\end{table}
+
+\subsection{ Economical  process}
+
+In order to study the impact of the introduction of those new mechanism  we summarize it in the table~\ref{tab:exp}. 
+\begin{table}
+	\centering
+	\begin{tabular}{l|c|c}
+		& Rand & Eco \\\hline
+		$\mu$ &A & B \\
+		$\mu +\alpha$ & C & D \\
+	\end{tabular}
+	\caption{Experimental Setup}
+	\label{tab:exp}
+\end{table}
+
+The following  experiments will last longer than the firsts one because this time the exchange mechanisms will have an impact on the evolution of prices in the population.
+All the next experiments are run during 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
 

### 2015-03-27 article.tex
integrate things of simon in setup and improve a bit algorithm

@@
 
-In order to validate our model a first result from the literature on the evolutionary transmission is reproduced. We then illustrate the possibility to implement a trade mechanisms.
+In order to validate our model a result from the literature on cultural transmission is reproduced. We then illustrate the possibility to implement a trade mechanisms.
 
@@
 
-In this article the cultural transmission tested is the ``random copy" such as presented in~\cite{mesoudi_random_2009}.
+In this article the neutral hypothesis is tested which implies that the cultural transmission mechanism is the ``random copy"~\cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
 The aim is to show that our model is indeed able to reproduce the main trends expected with such copy mechanism.
-Namely, we should observe a distribution known as the power law, displaying a line in the log-log graph of the proportion of variants with regards to the frequency of variant.
+Namely, we should observe a distribution known as the ``power law'', displaying a line in the log-log graph of the proportion of variants with regards to the frequency of variant.
 
-The imitation process is a ``random copy" meaning that with a low probability each agent pick randomly one agent among all and copy it's vector of values.
+The imitation process of ``random copy" is implemented by a low probability for each agent to pick randomly one agent among all and copy its vector of values.
 The innovation process is triggered with a low probability and select new elements for the vector of values.
 These new elements are drawn from a uniform distribution.
-The imitation and innovation probabilities are presented with other parameters in table~\ref{tab:parameters}
-
-%%A integrer
-Knowing that and following \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}, we think that in our model those prices will behave exactly like any other cultural trait, and that the different version of prices for each good will be found in the population in proportion that follow a power law.
-
-It's indeed what we observe.
-In the first experiment, in order to compare our result with those of the literature, we use only one price.
-We check for some of the same $\mu$ value used in \cite{bentley_specialisation_2005,mesoudi_random_2009} that the distribution of the number of variants are the same.
+The imitation and innovation probabilities are presented with other parameters in table~\ref{tab:parameters}.
 
 \subsection{Trading Model}\label{sec:trade}
-%%à integrer
-In the previous experiment the estimate price of good have no impact on the agents choices and behaviors.
-In a real economical system it's not the case.
-In order to approximate such a process and to see how our framework could handle economical mechanism we introduce a new cultural transmission mechanism.
-
-This time agent will not copying randomly the vector of price from one random individual but they will choose among the agent that produce the same good those that seem the most successful.
-In practice, a fixed proportion of the less successful agents will copy the prices of the more successful agent.
-
-Meanwhile time the innovation mechanism used in the experiment  we follow in the previous section seems not  an adequate economical mechanism.
-While in a cultural point a view an innovation could be anything new in you space innovation, it's seem little probable than a price will be change to something totally new.
-
-That why we  introduce a new innovation mechanism which will also occur with a probability of $\mu$ but this time, instead of set a totally new price, it will modify the previous price by adding or subtract to it a small amount randomly choose between $0 ..
-\beta$.
 
 \paragraph{Imitation}
-To test a simple trading model, two notions are introduced in the imitation mechanism: need and score.
-The need is a quantity of product that each agent tries to obtain.
-This quantity is different for each product but the need for a product is the same for all agents:
+In the cultural transmission model the value vector does not impact the imitation process.
+When trading is involved it is not not the case.
+In order to model such aspect we introduce a new cultural transmission mechanism taking into account the value vector.
+This mechanism is based on two new notions: need and score.
+
+The need is a quantity of product that each agent tries to obtain. This quantity is different for each product but the need for a product is the same for all agents:
 $$ need = (n_1, \cdots, n_r) $$
 
-The score reflects the ability for an agent to obtain the products it needs, it is formally computed as follow for agent $i$:
+The score reflects the ability for an agent to obtain the products it needs.
+It is maximum when the quantity vector of an agent is equal to its need vector and lower in proportion to the distance between the need vector and the quantity vector.
+It is formally computed as follow for agent $i$:
 
-$$ \abs{\dfrac{q^i_j - n_j}{ \sqrt{\abs{(q^i_j*q^i_j)-(n_j*n_j)}}}} $$
+$$ 1- \abs{\dfrac{q^i_j - n_j}{ \sqrt{\abs{(q^i_j*q^i_j)-(n_j*n_j)}}}} $$
 
-%%A integrer
-To express this idea of success we define a score that is maximum when you manage to have exactly the needed amount for each good.
-If you exchange too much or too few of one of the good your score will decreased.
-The score is computed in such a way that each good count for the same proportion in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value won't help you to increase your score).
+This function ensures that each good count for the same proportion in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
+
+The agents will choose the agent from whom the price vector should be copied among the agents that produce the same good and have the highest score.
+In practice, a fixed proportion of the less successful agents will copy the prices of the most successful agent.
 
@@
 If a trade is possible the two agents will exchange the agreed quantities.
-If the trade is not possible, the agent will continue to look at random partners for this good until either a good is find or $TradeThreshold$ agents have been tried.
+If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ agents have been tried.
 At this point the agent will try to trade with agents producing another good.
@@
 
-\paragraph{Innovation} The innovation process is triggered with a low probability and select new elements for the vector of values.
-These new elements are drawn from a uniform distribution centred on the current value of each product.
+\paragraph{Innovation} In a trading environment it seems unlikely that a price will change radically to a very different value.
+Therefore, a new and more realistic mechanism is proposed.
+The innovation process is still triggered with a probability $\mu$
+but modify the previous price by adding or subtracting a small amount taken randomly from a uniform  distribution between $0 .. \beta$.
+
+\paragraph{Expected outcome}
+
+\todo{complete the equation}
+
+With such a setup it is expected that the prices will converge to a ration allowing each agent to obtain a number of resources equivalent to the needs.
+There the price of a good should follow the following equation :
+
+$$ hey hey $$
+
+If such a price is reached to score of all agents should be equal to : $$ 10*1*(ngoods-1) $$
 
@@
 			\For{$Agents per Goods$}
-				\State $A_i = (g_i,p_i,n_i)$
+				\State $A_i = (g^i,p^i, N)$ \Comment{Initialize the agent for the good it has to produce, a random price and the needs}
 			\EndFor
@@
 				\State $Trade$				
-				\If{$step CulturalStep$}	
+				\If{$ (step \mod CulturalStep) = 0$}	
 					\State $Imitation$
-					\State $Inovation$
+					\State $Innovation$
 				\EndIf
@@
 	\begin{center}
-		\includegraphics[width=7cm]{img/allmuRandMaxBentleyValues.pdf}
+%		\includegraphics[width=7cm]{img/allmuRandMaxBentleyValues.pdf}
 	\end{center}

### 2015-03-27 article.tex
new results but **without** the marenostrum results

--- 2015-03-27 article.tex
@@
 
-\simon{reference to the R package and the theoreticla ref in the Rpackage?}
-Those distribution exhibit power law like attribute and we can fit them.
-The result of the alpha fitted with are in the table \ref{tab:mualpha}.
-The alpha values represent the mean of the fitted alpha for each run computed using RPACKAGE with the standard deviation associated with each mean.
+\simon{reference to the R package and the theoretical ref in the Rpackage?}
+Those distribution exhibit power law like distribution in such a way that we can find a power law $formul powerlaw$ that can fit it.
+The value of the $\alpha$ parameter of the fitted power law are in the table \ref{tab:mualpha}.
+Those $\alpha$ values are the mean of the $\alpha$ parameter of each power law fitted to each run and computed using with the standard deviation associated with each mean.PACKAGE.
+The SD are the SD associated each means .
 \begin{figure}[hbp]
@@
 	\end{center}
-	\caption{rand()\%RAND\_MAX}
+	\caption{Distribution of frequencies depending on the $\mu$ parameter}
 	\label{fig:allMutation}
@@
 
-In order to study the impact of the introduction of those new mechanism  we summarize it in the table~\ref{tab:exp}. 
+In order to study the impact of the introduction of the new mechanism  introduced in XXX we summarize it in the table~\ref{tab:exp}. 
 \begin{table}
@@
 All the next experiments are run during 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
+
+In the case A and S as no transmission is done using the score value this one change randomly.
+In the other cases, we can see that using the different innovation process help the system ton converge as no strange new price will emerge.
+
+all th result are resume in the figure~\ref{tab:scoreEvol}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l c c}
+		& Random Transmission & Eco Transmission \\
+		$\mu$ & \raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeA.png}}&\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeB.png}} \\
+		$\mu + \alpha$& \raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeC.png}}&\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeD.png}}
+
+	\end{tabular}
+	\caption{Evolution of the score in the different setup}
+	\label{tab:scoreEvol}
+\end{table}
+
+Distribution:
+
+In the figure~\ref{fig:4setDi} we look at how the different variants of price are adopted in population.
+As we can see the economical imitation operator transform the power law in a more exponential law.
+\begin{figure}[htpb]
+	\begin{center}
+		\includegraphics[width=7cm]{img/4SetupDistrib.png}
+	\end{center}
+	\caption{Frequency distribution for the 4 setup}
+	\label{fig:4setDi}
+\end{figure}
+
+Equilibrium:
+
+As told in the section XX we expect that with our slightly different imitation and innovation process that the agent will finish with a good set of price that will allow them to exchange optimally the good they produce with the other goods.
+
+To verify that this actually happen we look in the figure~\ref{fig:ratioEvol} at the deviation from optimal price (with is the ratio between the need of the needed good and the produced good).
+\begin{figure}[htp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/ratioEvol.png}
+	\end{center}
+	\caption{Evolution of the difference $\dfrac{p(g_w)}{p(g_p)}-n(g_p)$ where $p(x_i)$ is the price for a good $i$, $n(x_i)$ its need, $g$ the produced good and $w$ the wanted}
+	\label{fig:ratioEvol}
+\end{figure}
+
+One remarkable thing is that some suboptimal  market are sometimes found as we can see in the example in the figure~\ref{fig:suboptimal}, where we see that the product or of the good blue found a good price for him but price that block the other product or to do well .
+
+\begin{figure}[htp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/suboptimal.png}
+	\end{center}
+	\caption{Evolution of the Score for the three types of agents of the simulation}
+	\label{fig:suboptimal}
+\end{figure}
+
+\begin{figure}[htp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/fitness.png}
+	\end{center}
+	\caption{The fitness depending on price and needs}
+	\label{fig:fit}
+\end{figure}
 

### 2015-03-28 article.tex
few changes on the result part

@@
 
-\subsubsection{Multiple traits co-evolving randomly}
-\simon{ this part could be resumed to one phrase saying that nothing change and that we check it without showing any result moreover}
-As our aims is to study the evolution of an economy where people exchange different goods, we have checked if the previous results are the same when the agents own not just one price for one good but a vector of price associated to each good available in the environment.
-And every thing is OKAY
-
-%\begin{table}
-%	\centering
-%		\begin{tabular}{l|cccc}
-%			  & g=1  & g= 2 & g=3 & g=4 \\\hline
-%			$\alpha$&\\
-%			sd \\
-%		\end{tabular}
-%	\caption{alpha is the mean alpha between each good for 100 runs }
-%	\label{tab:alphagoods}
-%\end{table}
+As our aims is to study the evolution of an economy where people exchange different goods, we have checked if the previous results are the same when the agents own not just one price for one good but a vector of price associated to each good available in the environment and continue to copy and modify those price in the same random way.
+In this case the system behave similarly , in the random copy and random innovation,  the price for each good evolves as totally independent traits.
 
@@
 The following  experiments will last longer than the firsts one because this time the exchange mechanisms will have an impact on the evolution of prices in the population.
-All the next experiments are run during 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
+All the next experiments are done for 100000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
 
-In the case A and S as no transmission is done using the score value this one change randomly.
-In the other cases, we can see that using the different innovation process help the system ton converge as no strange new price will emerge.
-
-all th result are resume in the figure~\ref{tab:scoreEvol}
+We show  in the figure~\ref{tab:scoreEvol} how each setup is able, or not, to evolve in such a way that allow agents to find the good price to exchange with eachother.
+In the case A and S, as the score is not at all used in the transmission process, it evolves randomly.
+In the other cases where score is used to know which individuals will copy which other, the score goes better.
+Moreover, we can see that using the different innovation process help the system to converge as no strange new price will randomly appear.
 
@@
 
-In the figure~\ref{fig:4setDi} we look at how the different variants of price are adopted in population.
+In the figure~\ref{fig:4setDi} we look at how the different variants of price are distributed in population.
 As we can see the economical imitation operator transform the power law in a more exponential law.
@@
 
-As told in the section XX we expect that with our slightly different imitation and innovation process that the agent will finish with a good set of price that will allow them to exchange optimally the good they produce with the other goods.
+As told in the section XX we expect that with our slightly different imitation and innovation processes that the agent will finished with a set of price for each good that will allow them to exchange optimally the good they produce with the other goods.
 
@@
 
-One remarkable thing is that some suboptimal  market are sometimes found as we can see in the example in the figure~\ref{fig:suboptimal}, where we see that the product or of the good blue found a good price for him but price that block the other product or to do well .
+One remarkable thing is that some suboptimal  market are sometimes found, as we can see in the example in the figure~\ref{fig:suboptimal}, where we see that the product or of the good blue found a good price for him but price that block the other product or to do well .
 

### 2015-03-28 article.tex
work on result section, swap some text up to setup

--- 2015-03-27 article.tex
@@
 \usepackage{algorithm,algorithmicx,algpseudocode}
+\usepackage{float}
+
 \algnewcommand\And{\textbf{and}}
@@
 \DeclarePairedDelimiter\norm{\lVert}{\rVert}%
+
+\newcommand{\specialcell}[2][c]{%
+  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
 
@@
 
+\todo{to integrate}
+All experiments are performed with Pandora. The code is available at XXXX.
+
+In our experiment one has to take in account that agents modifies their prices or exchange their price only every ten steps.
+Between, they exchange goods given their own prices.
+Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}.
+
+With trade, experiments will last longer than the firsts one because this time the exchange mechanisms will have an impact on the evolution of prices in the population.
+
 \section{RESULTS}
 \subsection{Random cultural transmission and random innovation process}
-\subsubsection{One trait}
 
-That is what we can see in the figure \ref{fig:allMutation}.
+We first analyse the result obtained in the ``neutral model" as presented in section~\ref{sec:}.
+The figure~\ref{fig:} presents an analysis of the value vectors obtained across the 100 runs performed with a $\mu$ value equal to XXXX.
+In this graph it is not the exact values that are analysed but their relative frequencies.
+The y-axis of the graph shows the frequencies of the variants of the vector values, the x-axis shows how many variant achieves such frequencies and the line represents the average of the frequencies obtained across all runs.
+Both axes are in a logarithmic scale
 
-Each curves on the figures show the mean for 100 runs.
-In our experiment one has to take in account that agents modifies their prices or exchange their price only every ten steps.
-Between, they exchange goods given their own prices.
-Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}, for $\mu$ the innovation rate $\in {.004,.008,.016,.064}$ and for 250 and 500 agents.
+On this graphic one can observe a straight line which shows that a few of the variants are very frequent and a majority of them are not.
+Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
+This line corresponds to the ``power law" distribution mentioned in section~\ref{sec:} and is typical of the result obtained under the ``neutral model".
 
-\simon{reference to the R package and the theoretical ref in the Rpackage?}
-Those distribution exhibit power law like distribution in such a way that we can find a power law $formul powerlaw$ that can fit it.
-The value of the $\alpha$ parameter of the fitted power law are in the table \ref{tab:mualpha}.
-Those $\alpha$ values are the mean of the $\alpha$ parameter of each power law fitted to each run and computed using with the standard deviation associated with each mean.PACKAGE.
-The SD are the SD associated each means .
+In order to further validate our model, we perform such study under various $\mu$ values as it has been done in previous works.
+The $\mu$ innovation rates studied vary $\in {.004,.008,.016,.064}$ and two population sizes are studied: 250 and 500 agents.
+The distribution of variants obtained is shown in figure~\ref{fig:allMutation}.
+
 \begin{figure}[hbp]
@@
 
-\begin{table}
+\jm{yes say the R package}
+Under all parameters tested the value vectors exhibit power law like distribution.
+It would then be interesting to analyse the shape of such distribution.
+In order to perform this study a linear regression is used to fit the curve obtained to a function of the form $formul powerlaw$.
+The mean value of the $\alpha$ parameters obtained and their standard deviation is presented in table~\ref{tab:mualpha}.
+The computations of the linear regression is done thanks to PACKAGE
+
+\begin{table}[h]
 	\centering
@@
 
-\subsubsection{Multiple traits co-evolving randomly}
-\simon{ this part could be resumed to one phrase saying that nothing change and that we check it without showing any result moreover}
-As our aims is to study the evolution of an economy where people exchange different goods, we have checked if the previous results are the same when the agents own not just one price for one good but a vector of price associated to each good available in the environment.
-And every thing is OKAY
-
-%\begin{table}
-%	\centering
-%		\begin{tabular}{l|cccc}
-%			  & g=1  & g= 2 & g=3 & g=4 \\\hline
-%			$\alpha$&\\
-%			sd \\
-%		\end{tabular}
-%	\caption{alpha is the mean alpha between each good for 100 runs }
-%	\label{tab:alphagoods}
-%\end{table}
+\jm{Simon, do you have a comment on the table ? Like does it fit what is found in other articles ?}
 
@@
 
-In order to study the impact of the introduction of the new mechanism  introduced in XXX we summarize it in the table~\ref{tab:exp}. 
-\begin{table}
+In order to study a trading model two new innovation and imitation mechanisms have been introduced as explained in section~\ref{sec:}.
+These mechanisms are summarized in the table~\ref{tab:exp}.
+Each couple of innovation/imitation mechanism form one setup that is labelled with one later.
+Note that the ``neutral model" studied in the previous section corresponds to the setup A.
+All the runs presented in this section are done for 100000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
+
+\todo{add innovation and imitation}
+\begin{table}[h]
 	\centering
@@
 
-The following  experiments will last longer than the firsts one because this time the exchange mechanisms will have an impact on the evolution of prices in the population.
-All the next experiments are run during 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
+\subsubsection{Distribution}
 
-In the case A and S as no transmission is done using the score value this one change randomly.
-In the other cases, we can see that using the different innovation process help the system ton converge as no strange new price will emerge.
+Our first step is to study the distribution of values in order to compare them to the distribution previous obtained.
+The distribution of values in the 4 setups is presented in figure~\ref{fig:4setDi}.
 
-all th result are resume in the figure~\ref{tab:scoreEvol}
-
-\begin{table}
-	\centering
-	\begin{tabular}{l c c}
-		& Random Transmission & Eco Transmission \\
-		$\mu$ & \raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeA.png}}&\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeB.png}} \\
-		$\mu + \alpha$& \raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeC.png}}&\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeD.png}}
-
-	\end{tabular}
-	\caption{Evolution of the score in the different setup}
-	\label{tab:scoreEvol}
-\end{table}
-
-Distribution:
-
-In the figure~\ref{fig:4setDi} we look at how the different variants of price are adopted in population.
-As we can see the economical imitation operator transform the power law in a more exponential law.
-\begin{figure}[htpb]
+\begin{figure}[H]
 	\begin{center}
@@
 
-Equilibrium:
+\todo{update once all graphs are there}
+\jm{is exponential law characteristic of prestige bias ?}
 
-As told in the section XX we expect that with our slightly different imitation and innovation process that the agent will finish with a good set of price that will allow them to exchange optimally the good they produce with the other goods.
+The results studied in the previous section is reproduce here in the by the setup A, it is therefore no surprise that this setup follow a power law.
+We observe that the setup D is also following a power law.
+However, setups B and C are following an exponential law.
+We therefore observe that the innovation process has a negligeable influence on the shape distribution.
+However, the use of a biased imitation process has a major effect on the shape of the distribution.
 
-To verify that this actually happen we look in the figure~\ref{fig:ratioEvol} at the deviation from optimal price (with is the ratio between the need of the needed good and the produced good).
-\begin{figure}[htp]
+\subsubsection{Score}
+
+We now study the setup in more detail by investigating the ability of the population of agents to find the good price to perform exchanges between each other.
+This is done by observing the score of all agents in each of the 4 setups.
+The results obtained are presented in figure~\ref{tab:scoreEvol}.
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{l c c}
+		& Random Transmission & Eco Transmission \\
+		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeA.png}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeB.png}} \\ Setup B} \\
+		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeC.png}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeD.png}} \\ Setup D}
+
+	\end{tabular}
+	\caption{Evolution of the score in the different setup}
+	\label{tab:scoreEvol}
+\end{table}
+
+\todo{simon you have put A and S, I guess it's C and D ?}
+\todo{update explanation with new graphs}
+\todo{get clear names for innovation and imitaiton mechanisms}
+
+In the setups A and D, the score evolves randomly.
+In the two other setups however the score is increasing.
+Moreover, we observe that the XXXX innovation process used in the setups A and B leads to higher convergences.
+Since only the ``prestige imitation" takes the score into account it is normal that only this mechanism leads higher scores.
+The XXXX innovation mechanism leads to lower convergences as it select prices randomly in the complete range available.
+
+\subsubsection{Prices}
+
+We pursue the analysis of the economical aspect by observing the prices reached in setup D.
+As explained in the section~\ref{sec:} we expect that the trade imitation and innovation processes will produce a convergence toward a set of price for each good that will allow agents to exchange optimally the good they produce with the other goods.
+To verify this assumption we analyse the prices reached.
+These are presented in figure~\ref{fig:ratioEvol} as a deviation from the optimal price.
+Record that the optimal price is the ratio between the need of the needed good and the produced good.
+
+\begin{figure}[H]
 	\begin{center}
@@
 
-One remarkable thing is that some suboptimal  market are sometimes found as we can see in the example in the figure~\ref{fig:suboptimal}, where we see that the product or of the good blue found a good price for him but price that block the other product or to do well .
+We observe that prices are indeed converging to the optimal prices which means that our innovation and imitation process are valid trade mechanisms.
+Notably, they produce results similar to the ones obtained in~\cite{gintis_emergence_2006}.
+
+\subsubsection{Suboptimal markets}
+
+Finally, a more careful analysis of the price structure reveals the presence of suboptimal markets.
+In figure~\ref{fig:suboptimal} the price structure of one run of setup C is presented.
+The x-axis represents the number of iteration, the y-axis the prices.
+The green boxplot represents the price of good X for an agent producing Y.
+And the blue boxplot represents the price of good X for agent producince Y
 
@@
 \end{figure}
+
+\jm{stop for this evening}
+where we see that the product or of the good blue found a good price for him but price that block the other product or to do well .
 

### 2015-03-29 article.tex
finish result

@@
 
+\begin{figure}[htp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/fitness.png}
+	\end{center}
+	\caption{The fitness depending on price and needs}
+	\label{fig:fit}
+\end{figure}
+
 The agents will choose the agent from whom the price vector should be copied among the agents that produce the same good and have the highest score.
@@
 
-\jm{stop for this evening}
-where we see that the product or of the good blue found a good price for him but price that block the other product or to do well .
-
-\begin{figure}[htp]
-	\begin{center}
-		\includegraphics[width=7cm]{img/fitness.png}
-	\end{center}
-	\caption{The fitness depending on price and needs}
-	\label{fig:fit}
-\end{figure}
+In this graphic we can observe that the product displayed in green is blocked to a non-optimal value until iteration XXXX, and decreasing after.
+The prices for the blue product, on the other side, decrease steadily until the median reaches the uptimum at iteration XXXX.
+This illustrate the complexity of finding the right prices in the market.
+Indeed all prices are strongly linked together and until one has reach its optimum value, the other price can not evolve.
 

### 2015-03-29 article.tex
done ccl and update discussion

@@
 
+This article has propose a framework to study both cultural transmission mechanisms and trade mechanisms.
+Our framework is based on a central element, the value vector, which is interpreted differently depending on the mechanisms studied.
+We have shown the validity of this approach by reproducing expected results on both the cultural and trade side.
+On the cultural transmission side we have shown that the implementation of the ``neutral model" leads to the expected observations on the variants of the vector value: a power law.
+When implementing trading mechanisms we observe the convergence of prices to the expected values and the improvement of the scores of the agents.
+
+On top of these results, by the implementation of trade mechanisms as cultural mechanisms, we show that trade is plainly a cultural factor.
+The modifications needed in our framework where relative to the proposition of new imitation and innovation mechanisms which are typical of the study of the cultural transmission.
+This proximity between trade mechanisms and cultural transmission allows for the comparisons of the results obtained.
+For example, it has been possible here to compare the distribution of values obtained and highlight that the divergence from a power law actually is coming mainly from the imitation mechanism used in trade.
+Moreover this imitation mechanism can further be interpreted as a ``prestige bias" imitation already studied in cultural transmission.
+
 \section{DISCUSSION}
@@
 First the constraints on the production could be relaxed so that each agent can choose the products it wishes to produce at the current time step.
-Moreover meterological factors can modify the quality of the production (noisy outcome of the proces) thus making the process more realistic and more complex~\cite{bentley_specialisation_2005}.
+Moreover, meterological factors can modify the quality of the production (noisy outcome of the process) thus making the process more realistic and more complex~\cite{bentley_specialisation_2005}.
 
@@
 
-%ACE and prospective trading
-More complex models can also be envisionned such as those developed by 
-\cite{rubinstein_equilibrium_1985} and to test more general proposal, as those done by \cite{polanyi_trade_1957,polanyi_livelihood_1977} about the early economical mechanisms.
-Moreover, and in order to be more realistic, and consistently with the cognitive and agent based approach of the project, we will also test assumptions made by people from \emph{Prospect Theory} as proposed by
-\cite{kahneman_prospect_1979}, see also
-\cite{camerer_prospect_2004}.
-The idea here is that traditional economical studies use formal mathematical models that suppose people acting as rational agent, which is a presumption that is far from being valid  in every day life.
+The trading theories studied also can be extended to the \emph{Prospect Theory}~\cite{kahneman_prospect_1979} which proposes to study more realistic trade mechanisms taking into account the biases of humans.
+Another economical framework we envision is the Agent based Computational Economy, ACE, which is  addressing economical problems raising from the interactions of a large number of agents~\cite{tesfatsion_introduction_2001}.
+On top of these trading theories the influence of the network of trades by itself can be studied.
+Various networks can be envisioned ranging from fully connected to small world, and taking into account possible delays or the sudden rupture of a link.
 
-Top palliate this problem, Prospect Theory put the focus on the study of the human cognitive abilities and the impact those abilities brings on economics issues.
-Among various aspect on which prospect theory shed light one can look at how cognitive abilities modify the decisions-making process of human under risk
-\cite{weber_disposition_1998}.
-
-Moreover, we think that this approach fit perfectly with our agent based modeling approach (also called Agent based Computational Economy, ACE, when dealing with economical problems, see
-\cite{tesfatsion_introduction_2001}).
-
-This subjective value is the value that agents ``put'' on each resources.
-It could be learn using any mechanism of ``social learning'' (as defined by \cite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \cite{lycett_cultural_2015} for some kind of bias that could be implemented).
-
-In order to test these hypohtesis more advanced agents are naturally envisionned.
-One possible tracks of investigation is agents endowed with self-adaptation abilities as proposed in Reinforcement Learning or Developmental Learning.
-Another possibility is to follow the cognitive approaches that propose to model the complexity of the human behaviour in general representations such as BDI and XXXX.
+On the cultural transmission side, the vector value could be learned using any mechanism of ``social learning'' (as defined by \cite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \cite{lycett_cultural_2015} for some kind of bias that could be implemented).
+Agents could be also endowed with self-adaptation abilities implemented thanks to Reinforcement Learning or Developmental Learning.
+Another possible track to implement the self-adaptation abilities is to rely on the cognitive approaches that propose to model the complexity of the human behaviour in general representations such as BDI.
 

### 2015-03-29 article.tex
swap the two first state of the art sections and simplify the last one

@@
 
+\subsection{Neutral models of cultural change}
+
+The first aspect of our model is focused on the dynamics of cultural change.
+They comprise the collection of processes that promote or inhibit the spread of information by social interaction within a population \cite[3]{boyd_origin_2005}.
+This evolutionary framework is being used by an increasing number of social scientists, fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}.
+Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{obrien_cladistics_2001} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.
+
+A large percentage of these studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependance (e.g.
+conformism and anti-conformism).
+These analysis are often based in the genetic theory of neutral evolution \cite{neiman_stylistic_1995} and they take neutrality as a null-hypotheses (i.e.
+variation of traits is strictly explained by its frequency distribution in the population).
+There exist a large number of works using this model as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
+
+Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism \cite{bentley_random_2004}.
+Within this framework, an individual will copy the traits of a randomly chosen individual with a given probability.
+This copy can potentially introduce some errors in the acquired trait, which account for innovation processes.
+The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
+This basic model can be enriched by several additional processes both in the innovation \cite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission \cite{heyes_social_1994,henrich_evolution_2003}.
+
+In particular, the trade of cultural products within a market system can potentially introduce a dynamics content-related bias linked to the price of the different products.
+This would also affect the frequency of the product within the population, which in turn would modify its price following a co-evolutionary dynamic.
+
 \subsection{Modelling of Trade}
@@
 
+The second aspect of our model is focused on the dynamics produced by trade in ancient Mediterranean societes.
 Within the archaeological field a large number of works have been proposed to quantify the properties of the economical interactions in the ancient Mediterranean societies~\cite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,minc_monitoring_2006,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
@@
 
-\subsection{Neutral models of cultural change}
-
-The second component of our model is focused on the dynamics of cultural change.
-They comprise the collection of processes that promote or inhibit the spread of information by social interaction within a population \cite[3]{boyd_origin_2005}.
-This evolutionary framework is being used by an increasing number of social scientists, fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}.
-Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{obrien_cladistics_2001} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.
-
-A large percentage of these studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependance (e.g.
-conformism and anti-conformism).
-These analysis are often based in the genetic theory of neutral evolution \cite{neiman_stylistic_1995} and they take neutrality as a null-hypotheses (i.e.
-variation of traits is strictly explained by its frequency distribution in the population).
-There exist a large number of works using this model as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
-
-Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism \cite{bentley_random_2004}.
-Within this framework, an individual will copy the traits of a randomly chosen individual with a given probability.
-This copy can potentially introduce some errors in the acquired trait, which account for innovation processes.
-The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
-This basic model can be enriched by several additional processes both in the innovation \cite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission \cite{heyes_social_1994,henrich_evolution_2003}.
-
-In particular, the trade of cultural products within a market system can potentially introduce a dynamics content-related bias linked to the price of the different products.
-This would also affect the frequency of the product within the population, which in turn would modify its price following a co-evolutionary dynamic.
-
 \subsection{Modelisation of Trade and Culture}
 
-\todo{speak about the fact that economy looks at convergence and culture looks before}
+\jm{tried a justification of co-evolutionary framework but I find it too light. ideas ?}
 
-To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture.
-The model in~\cite{bentley_specialisation_2005} is proposed to study the wealth inequalities in a dynamic network.
-In this model the agents are in a virtual environment and can produce, consume and trade two products.
-This model has two major constraints which makes it unfit for the study presented here.
-First, the products are only for trade purposes and are not used as cultural factors, i.e.
-some goods can not be accumulated so that the agent show them to others.
-The cultural aspects appear only through the price associated to each product.
-Second, only two goods are considered and the system can not scale up to an undetermined number of products without major modifications.
-% Agents can negotiate the rate at which the two products will be traded.
-The agents have a will (hard-coded in their behaviour) to keep their wealth and number of agents within their trading network above a threshold.
+Ultimately we aim to study the relation between cultural change and trade networks within the Roman Empire.
+Examples of questions that should be answered by our model are: What is the relation between distances in the trade network and cultural changes ?
+Did anti-conformism promote the adaptation of new products coming from remote provinces ?
+In order to answer these questions the model used has to take into account both cultural effects and trade influence.
+More precisely, the variations in these two aspects should be modelled and should influence each other.
+Therefore, in order to answer the questions targeted we need a co-evolutionary model able to take into account both trade and cultural changes.
 
-The model proposed in~\cite{macmillan_agent-based_2008} studies the settlement of primitive agricultural societies.
-In this model agents produce, trade and consume 2 essentials goods and 2 non-essentials goods.
-This model is interesting since it introduce the notion of non-essential goods which can be used to reflect the culture of a society.
-However, this framework is constrained as it does not allow the evolution of the trading network.
-Moreover the behaviour chosen for the agents is rather complex and not justified by observations made in economy or evolution of culture.
+To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture~\cite{bentley_specialisation_2005,macmillan_agent-based_2008}.
+The first proposes a relatively simple model which is limited by 2 products, a fixed behaviour of the agents and a limited variation of cultural mechanisms.
+The second proposes a more complete model including a large number of goods (certain being essential and the others non-essential), but suffer from a greater complexity and the absence of the notion of trade networks.
+Moreover, both models propose new dynamics but these dynamics are not compared to the state of the art on the models for cultural change and trade.
 
-The model presented in this work proposes to integrate the most interesting features from~\cite{bentley_specialisation_2005} and~\cite{macmillan_agent-based_2008}.
-
-\xrc{here a research question should be defined, and some hypotheses, e.g.: \emph{Did trade networks between regions bias cultural change towards anti-conformism?} or \emph{What is the relation between shipment time and cultural change?}}
-
-\xrc{A co-evolutionary model is really difficult to study, so a careful justification needs to be done on why this is here needed}
+The model presented in this work aims to offer a framework for the co-evolution of trades and culture which relies on a low number of parameters.
+In order to assess its validity we will reproduce results obtained in the literature and verify that the results obtained are conform to what is expected.
 

### 2015-03-29 article.tex
last little edit for sunday

@@
 
-$$ 1- \abs{\dfrac{q^i_j - n_j}{ \sqrt{\abs{(q^i_j*q^i_j)-(n_j*n_j)}}}} $$
+$$ 1- \dfrac{\abs{q^i_j - n_j}}{ \sqrt{\abs{(q^i_j)^2-(n_j)^2}}} $$
 
@@
 
+\begin{itemize}
+	\item Both agents have enough good in their inventory
+	\item The quantitie of each good  fit the will of both agents.
+\end{itemize}
+
 $$ hey $$
@@
 If a trade is possible the two agents will exchange the agreed quantities.
-If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ agents have been tried.
+If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ ($\frac{Number of agent}{2}$ agents have been tried.
 At this point the agent will try to trade with agents producing another good.
@@
 
-With such a setup it is expected that the prices will converge to a ration allowing each agent to obtain a number of resources equivalent to the needs.
-There the price of a good should follow the following equation :
+With such a setup it is expected that the prices will converge to a ratio allowing each agent to obtain a number of resources equivalent to the needs.
+Knowing that,  the best possible price of a good should follow the equation :
 
-$$ hey hey $$
+$$\frac{V^j_i}{V^j_g} = N_i   $$
+with g the produced good of the agent j and i another good which is not the one which is produced.
 
-If such a price is reached to score of all agents should be equal to : $$ 10*1*(ngoods-1) $$
+If such a price is reached to score of all agents should be equal to : $$ 10\times1\times(ngoods-1) $$
 
@@
 
+\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below}
+
+\begin{table}
+	\centering
+	\begin{tabular}{l|cc}
+N=250\\\hline
+$\mu$&$\alpha$&(SD)\\\hline
+0.004&1.50&(0.02) \\
+0.008&1.52&(0.02)\\
+0.016&1.55&(0.03)\\
+0.032&1.59&(0.06)\\
+0.064&1.78&(0.08)\\
+0.128&1.99&(0.04)\\
+	\end{tabular}
+	\begin{tabular}{l|cc}
+N=500\\\hline
+$\mu$&$\alpha$&(SD)\\\hline
+0.004&1.53&(0.03)
+0.008&1.57&(0.01)
+0.016&1.61&(0.04)
+0.032&1.70&(0.05)
+0.064&1.81&(0.10)
+0.128&1.98&(0.02)
+	\end{tabular}
+	\caption{Mean \& SD from \cite{bentley_random_2004} }
+	\label{tab:Bmualpha}
+\end{table}
+
 \subsection{ Economical  process}
@@
 	\begin{tabular}{l|c|c}
-		& Rand & Eco \\\hline
+	 Imitation  Process :& Rand & Eco \\
+	 Mutation Process& & \\\hline
 		$\mu$ &A & B \\
@@
 		& Random Transmission & Eco Transmission \\
-		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeA.png}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeB.png}} \\ Setup B} \\
-		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeC.png}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeD.png}} \\ Setup D}
+		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeA.png}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeC.png}} \\ Setup B} \\
+		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeB.png}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeD.png}} \\ Setup D}
 
@@
 \todo{simon you have put A and S, I guess it's C and D ?}
+\simon{It's A and C, the setup where their is no selection. But those two graph (A and B) are not good, don't take them in account. }
 \todo{update explanation with new graphs}
@@
 
-In the setups A and D, the score evolves randomly.
+In the setups A and C, the score evolves randomly.
 In the two other setups however the score is increasing.

### 2015-03-31 article.tex
minor modifications
correct compile mistake
corrections from me on state of the art and model desctiption

@@
 
-\todo{and/or is ugly, look for another way}
-This section will provide a brief review of the previous approaches to model trade and/or culture. While non-exhaustive, this review presents the mains trends of the previous work done.
+This section will provide a brief review of the previous approaches to model trade and culture. While non-exhaustive, this review presents the mains trends of the previous work done.
 
@@
 The first aspect of our model is focused on the dynamics of cultural change.
-They comprise the collection of processes that promote or inhibit the spread of information by social interaction within a population \cite[3]{boyd_origin_2005}.
-This evolutionary framework is being used by an increasing number of social scientists, fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}.
+They comprise the collection of processes that promotes or inhibits the spread of information by social interaction within a population \cite[3]{boyd_origin_2005}.
+An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}.
 Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{obrien_cladistics_2001} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.
 
-A large percentage of these studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependance (e.g.
+A large percentage of these studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependence (e.g.
 conformism and anti-conformism).
-These analysis are often based in the genetic theory of neutral evolution \cite{neiman_stylistic_1995} and they take neutrality as a null-hypotheses (i.e.
-variation of traits is strictly explained by its frequency distribution in the population).
+\jm{to keep it simple, can we say ``evolutionary theory" instead of ``genetic theory" ?}
+These analysis are often based on the genetic theory of neutral evolution \cite{neiman_stylistic_1995} and they take neutrality as a null-hypotheses, i.e.
+variations of traits are strictly explained by their frequency distribution in the population.
 There exist a large number of works using this model as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
@@
 
-The second aspect of our model is focused on the dynamics produced by trade in ancient Mediterranean societes.
-Within the archaeological field a large number of works have been proposed to quantify the properties of the economical interactions in the ancient Mediterranean societies~\cite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,minc_monitoring_2006,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
-In the works of~\cite{temin_market_2001,temin_economy_2006,wilson_approaches_2009}, based on the analysis of archaeological evidence, the Roman economy has been classified as a type of market economy where a variety of small tightly connected markets had loose connections between them.
-This view of a market system in ancient societies has been further expended in~\cite{minc_monitoring_2006} by a model applicable to various cases and studied in a test case of the aztec economical structure.
-The reaming works attempted at defining more exactly which type market economy it was, i.e.
-was it close to ours or remote ?
+Previous historical and archaeological studies to model trade in the ancient Mediterranean societies have focus on descriptive approaches ~\cite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
+These works have conclude that the Roman economy was a type of market economy where a variety of small tightly connected markets had loose connections between them~\cite{temin_market_2001,temin_economy_2006,wilson_approaches_2009}.
+Based on these conclusions, further works have attempt to define more exactly which type market economy was in use, i.e. was it close to our market economy or remote ?
 
-The work of~\cite{scheidel_model_2007} proposes to analyse the factors affecting the growth of income and population in the Roman Italy.
-The analysis of historical evidence and historical documents lead the author to propose a model highlighting the key factors in the economical growth.
-More in link with the work conducted in this article~\cite{terpstra_trade_2011,kessler_organization_2007} have analysed the interactions between economy and culture transmission in roman empire.
-An analysis based on historical documents in~\cite{kessler_organization_2007} highlights the importance of economical and social institutions in order to perform an efficient trade of trains in the early Roman Empire.
-More precisely, the work conducted in~\cite{terpstra_trade_2011} proposes a micro-economic model analysing the possibility of trade under uncertainty in the roman empire.
-This work highlight the importance of reputation and the threat of expulsion from a trade network as mechanisms the overall efficiency of the trade network.
+Among the various works done with this objective, few are studying the interactions between economy and cultural change in Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
+An analysis based on historical documents has revealed the importance of economical and social institutions for the efficiency of trades of grains in the early Roman Empire~\cite{kessler_organization_2007}.
+The same type of analysis has also revealed the importance of a number of key factors () for the growth of income and population in the Roman Italy~\cite{scheidel_model_2007}.
+Finally, a micro-economic model has determined the importance of reputation and threat of expulsion from a trade network as mechanisms to maintain the overall efficiency of the trade network~\cite{terpstra_trade_2011}.
+These works therefore reveal the strong relation between trade and cultural change in the Roman empire.
 
-A limitation of the works cited above is the impossibility to test the conclusions reached by the authors.
+However, a limitation of the previous works is the impossibility to test the conclusions reached by the authors.
 The models proposed reflects only the view of the authors on the data they have analyse.
@@
 
-Ultimately we aim to study the relation between cultural change and trade networks within the Roman Empire.
-Examples of questions that should be answered by our model are: What is the relation between distances in the trade network and cultural changes ?
+Ultimately, we aim to create a model to study the relation between cultural change and trade networks within the Roman Empire.
+Examples of questions that could be asked to our model are: What is the relation between distances in the trade network and cultural changes ?
 Did anti-conformism promote the adaptation of new products coming from remote provinces ?
@@
 The second proposes a more complete model including a large number of goods (certain being essential and the others non-essential), but suffer from a greater complexity and the absence of the notion of trade networks.
-Moreover, both models propose new dynamics but these dynamics are not compared to the state of the art on the models for cultural change and trade.
+Moreover, both models propose new dynamics but these dynamics are not compared to previous results obtained in the study of cultural evolution and the study of trading mechanisms.
 
 The model presented in this work aims to offer a framework for the co-evolution of trades and culture which relies on a low number of parameters.
-In order to assess its validity we will reproduce results obtained in the literature and verify that the results obtained are conform to what is expected.
+It is not within the scope of this article to answer the questions asked at the beginning of this section as they require specific implementations of the model proposed.
+However, the article will focus on the presentation of the framework, its justification and more importantly its validation by reproducing previous results obtained on cultural change and trade mechanisms.
 
@@
 
-In the model presented a set of agents are each in possession of a fixed number of goods and associate a value to each of these goods.
+The model proposed is a Multi-Agent Based model including agents and products.
+It revolves around the value that agents associate to products through cultural change mechanisms, trade mechanisms or both.
 Depending on the question studied, the value can reflect the interest of the agent for the good or it can be the price at which the agent evaluate this good.
@@
 
-More formally the model is composed as follow. $r$ is the number of resources present in the environment. The whole population is defined by a vector of $m$ agents: 
-$$ population = (a_i, \cdots ,a_m) $$
+More formally the model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $r$.
+The first corresponds to the quantity of each good that the agent $i$ possesses: $$ Q^i = (q^i_1,\cdots,q^i_r) $$
 
-Each agent $i$ is defined by 2 vectors each of size $r$. The first correspond to the quantity of each good that the agent possesses: $$ quantity = (q^i_1,\cdots,q^i_r) $$
+where $Q^i$ is the total list of possessions of agent $i$, and $q^i_j$ is the number of goods of type $j$ that agent $i$ posses.
 
-Each agent makes its own estimate on the price to attribute to a certain good. This price estimate is used for both selling and buying goods :
-$$ values = (v^i_1,\cdots,p^i_r) $$
+The second vector reflects the estimation of the value of a product that an agent $i$ makes.
+$$ V^i = (v^i_1,\cdots,v^i_r) $$
+where $V^i$ is the total list of estimated values of agent $i$, and $v^i_j$ is the value that agent $i$ associates to the goods of type $j$.
 
-On top of these elements three processes are included : production, imitation and innovation.
+On top of these elements three processes are included : \textit{production}, \textit{imitation} and \textit{innovation}.
 The \textit{production} process describe the creation of goods by the agent.
-In this article each agent is producing only one type of good.
-The type good produced by an agent is assigned to it at the beginning of the simulation and does not change.
 Once a good is produced it is added to the quantity vector of the agent.
@@
 This scheme allow us to have a model achieving the two main goals listed in section~\ref{sec:intro}.
-First, this model allows us to test various cultural transmission mechanisms as well as trade mechanisms.
-The experiments presented in this article show examples of implementations for both categories.
-Moreover, the fact that only three processes are modified allow comparisons between simulations with the same units.
-In this article the \textit{production} process will remain the same and only the \textit{imitation} and \textit{innovation} processes are changed.
-Second, few parameters are present in the default model which makes it easier to analyse and reuse by other researchers.
+The first goal is to be able to implement and compare various cultural transmission mechanisms as well as trade mechanisms within the same framework.
+We argue that this is possible in our framework by modifying only the three key processes i.e.
+production, imitation and innovation.
+Moreover, thanks to the use of a unique $V^i$ vector, it is possible to compare the outcomes of different combinations of production, imitation and innovation mechanisms.
+The second goal is to produce a model composed of a low number of parameter.
+Our model is composed of only three processes and two vectors which is significantly less complex than previous models.
+
+\todo{check that it's integrated later: In this article each agent is producing only one type of good.
+The type good produced by an agent is assigned to it at the beginning of the simulation and does not change.}
+
+\todo{check that it's integrated later: 
+In this article the \textit{production} process will remain the same and only the \textit{imitation} and \textit{innovation} processes are changed.}
 
@@
 $\mu$&$\alpha$&(SD)\\\hline
-0.004&1.53&(0.03)
-0.008&1.57&(0.01)
-0.016&1.61&(0.04)
-0.032&1.70&(0.05)
-0.064&1.81&(0.10)
-0.128&1.98&(0.02)
+0.004&1.53&(0.03)\\
+0.008&1.57&(0.01)\\
+0.016&1.61&(0.04)\\
+0.032&1.70&(0.05)\\
+0.064&1.81&(0.10)\\
+0.128&1.98&(0.02)\\
 	\end{tabular}
-	\caption{Mean \& SD from \cite{bentley_random_2004} }
+	\caption{Mean \& SD of $\alpha$ parameter }
 	\label{tab:Bmualpha}

### 2015-03-31 article.tex
new result and Trade Model

--- 2015-03-29 article.tex
@@
 
-In order to validate our model a result from the literature on cultural transmission is reproduced. We then illustrate the possibility to implement a trade mechanisms.
+In order to validate our model we first reproduced traditional  result often seen in the literature on cultural transmission.
+After that we show that doing small modification we can transform our model to make it fit processes that are more economically consistent.
 
@@
 In this article the neutral hypothesis is tested which implies that the cultural transmission mechanism is the ``random copy"~\cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
-The aim is to show that our model is indeed able to reproduce the main trends expected with such copy mechanism.
-Namely, we should observe a distribution known as the ``power law'', displaying a line in the log-log graph of the proportion of variants with regards to the frequency of variant.
+In the literature, people have shown that a lot of cultural phenomene where people copy randomly the cultural traits of other exhibit a particular pattern.
+
+With this mechanism of copy and given enough time  we will find in a fixed size population always the same repartition of the cultural variants.
+A few that are very frequent and an always bigger number of variant that are always less frequent.
+This is traduced by a ``power law'' distribution, following the equation $P(v)=C/v^\alpha $ that one could display as a line with a slope $-\alpha$ in the log-log graph of the proportion of variants with regards to the frequency of variant.
 
@@
 
-The score reflects the ability for an agent to obtain the products it needs.
+The score $S^i$ of agent $i$ reflects the ability for an agent to obtain the products it needs.
 It is maximum when the quantity vector of an agent is equal to its need vector and lower in proportion to the distance between the need vector and the quantity vector.
@@
 
-$$ 1- \dfrac{\abs{q^i_j - n_j}}{ \sqrt{\abs{(q^i_j)^2-(n_j)^2}}} $$
+$$ S^i=1- \dfrac{\abs{q^i_j - n_j}}{ \sqrt{\abs{(q^i_j)^2-(n_j)^2}}} $$
 
 This function ensures that each good count for the same proportion in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
+This can be seen in the figure~\ref{fig:fit}.
 
@@
 
-\todo{miss the formula for a possible trade}
-
 On top of producing the agents have the ability to exchange and consume the goods.
@@
 
-$$ hey $$
+Let be : $o$ the agent ``offerer'', and $r$ the agent that receive the offer.
+Both have an inventory $x_i$ of every good where $x_i^o$ is the quantity of good $i$ owned by $o$.
+$o$ produce the good $g$ and want to trade it in a quantity $q_g^o$ for a quantity $q_k^o$ of the good $k$ produced by $r$.
+In its side $r$ own also a quantity $q_k^r$ of the good $g$ that it want to trade with quantity $q_k^r$ of its own produced goods.
+
+The exchange take place only if :
+$$ x_g^o >= q_g^o $$
+$$ x_g^r <= q_g^o $$
+$$ x_k^r >= q_k^o $$
+$$q_g^o>=(x_g^r+q_g^r)$$
+$$q_k^o<=q_k^r$$
+$$q_g^o<=q_g^r$$
+
+The given quantity of the produced good ($g$ for $o$) is the estimate value of it ( its price).
+The requested quantity of the non produced value is simply the ratio between the estimated value of the good requested and the given quantity of the produced good.
+
+In our case, for $o$ : $q_g^o = v_g^o$ and $q_k^o= \frac{v_k^o}{v_g^o} $ and for $r$  : $q_k^o = v_k^o$ and $q_g^o= \frac{v_g^o}{v_k^o} $.
 
@@
 With such a setup it is expected that the prices will converge to a ratio allowing each agent to obtain a number of resources equivalent to the needs.
-Knowing that,  the best possible price of a good should follow the equation :
+Knowing that,  the best possible price of a good should satisfy the equations :
 
-$$\frac{V^j_i}{V^j_g} = N_i   $$
+$$\frac{v^o_k}{v^o_g} = n_k $$
+$$\frac{v^r_g}{v^r_k} = n_g $$
+$$v^r_k = \frac{1}{n_k} $$
+$$v^r_g = \frac{1}{n_g} $$
 with g the produced good of the agent j and i another good which is not the one which is produced.
 
-If such a price is reached to score of all agents should be equal to : $$ 10\times1\times(ngoods-1) $$
+If such a price is reached to score of all agents should be equal to : $$ CulturalStep\times1\times ngoods $$
 
@@
 	\begin{center}
-%		\includegraphics[width=7cm]{img/allmuRandMaxBentleyValues.pdf}
+		\includegraphics[width=7cm]{img/allmuRandMaxN250.pdf}
+		\includegraphics[width=7cm]{img/allmuRandMaxN500.pdf}
 	\end{center}
-	\caption{Distribution of frequencies depending on the $\mu$ parameter}
-	\label{fig:allMutation}
+	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right)}
+	\label{fig:allMutation }
 \end{figure}
@@
 	\centering
-	\begin{tabular}{cc}
+	\begin{tabular}{l|cc}
+		Agents Number & Our result & Bentley et al 2004\\\hline
+		N = 250 &
 		\begin{tabular}{l|cc}
 			$\mu$ & $\alpha$ & SD\\\hline
-			0.004&1.541193&0.031384174\\
-			0.008&1.549726&0.021953251\\
-			0.016&1.568096&0.017025456\\
-			0.064&1.651690&0.006538209\\
-
+			0.004&1.53&0.03\\
+			0.008&1.55&0.03\\
+			0.016&1.57&0.02\\
+			0.064&1.66&0.01\\
 		\end{tabular}
 		&
+		\begin{tabular}{cc}
+		$\alpha$&SD\\\hline
+		1.50&0.02 \\
+		1.52&0.02\\
+		1.55&0.03\\
+		1.78&0.08\\
+		\end{tabular} \\
+		N= 500&
 		\begin{tabular}{l|cc}
 			$\mu$ & $\alpha$ & SD\\\hline
-			0.004&1.539710&0.022515901\\
-			0.008&1.557460&0.017805810\\
-			0.016&1.570036&0.004412181\\
-			0.064&1.651521&0.009988488\\
-		\end{tabular}\\
-		(a) & (b)
+			0.004&1.54&0.02\\
+			0.008&1.55&0.01\\
+			0.016&1.57&0.01\\
+			0.064&1.67&0.01\\
 		\end{tabular}
-	\caption{Mean \& SD are done with 100 run for each with 250 agent for (a) and 500 for (b) }
+		&
+		\begin{tabular}{cc}
+			$\alpha$&(SD)\\\hline
+			1.53&0.03\\
+			1.57&0.01\\
+			1.61&0.04\\
+			1.81&0.10\\
+		\end{tabular}
+	\end{tabular}
+	\caption{Mean \& SD are calculate on 100 run.}
 	\label{tab:mualpha}
@@
 
-\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below}
-
-\begin{table}
-	\centering
-	\begin{tabular}{l|cc}
-N=250\\\hline
-$\mu$&$\alpha$&(SD)\\\hline
-0.004&1.50&(0.02) \\
-0.008&1.52&(0.02)\\
-0.016&1.55&(0.03)\\
-0.032&1.59&(0.06)\\
-0.064&1.78&(0.08)\\
-0.128&1.99&(0.04)\\
-	\end{tabular}
-	\begin{tabular}{l|cc}
-N=500\\\hline
-$\mu$&$\alpha$&(SD)\\\hline
-0.004&1.53&(0.03)
-0.008&1.57&(0.01)
-0.016&1.61&(0.04)
-0.032&1.70&(0.05)
-0.064&1.81&(0.10)
-0.128&1.98&(0.02)
-	\end{tabular}
-	\caption{Mean \& SD from \cite{bentley_random_2004} }
-	\label{tab:Bmualpha}
-\end{table}
+\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below?\\ 
+By the way, doing t.test on the different value of alpha I have gives me statistically differences between 250 and 500 agents ONLY for $\mu=.064$  }
 
@@
 	\centering
-	\begin{tabular}{l|c|c}
-	 Imitation  Process :& Rand & Eco \\
-	 Mutation Process& & \\\hline
-		$\mu$ &A & B \\
-		$\mu +\alpha$ & C & D \\
+	\begin{tabular}{l|cc}
+					&Imitation  Process \\
+		Inovation Mechanism	& Rand & Success \\\hline  
+		Unbounded 		&A & B \\
+		Local Modification	& C & D \\
 	\end{tabular}
@@
 	\begin{center}
-		\includegraphics[width=7cm]{img/4SetupDistrib.png}
+		\includegraphics[width=7cm]{img/frequenciesABCD.pdf}
 	\end{center}
@@
 \end{figure}
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{lcccc}
+		& A & B & C & D\\
+A & X& \includegraphics[width=5cm]{img/A-B.pdf}&\includegraphics[width=5cm]{img/A-C.pdf}&\includegraphics[width=5cm]{img/A-D.pdf}\\
+B & X& X &\includegraphics[width=5cm]{img/B-C.pdf}&\includegraphics[width=5cm]{img/B-D.pdf}\\
+C & X& X & X &\includegraphics[width=5cm]{img/C-D.pdf}\\
+	\end{tabular}
+	\caption{Experimental Setup}
+	\label{tab:allRes}
+\end{table}
 
@@
 		& Random Transmission & Eco Transmission \\
-		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeA.png}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeC.png}} \\ Setup B} \\
-		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeB.png}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/scoreWrtTimeD.png}} \\ Setup D}
+		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForA-G2N250.pdf}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForB-G2N250.pdf}} \\ Setup B} \\
+		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForC-G2N250.pdf}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForD-G2N250.pdf}} \\ Setup D}
 
 	\end{tabular}
-	\caption{Evolution of the score in the different setup}
+	\caption{Evolution of the score in the different setup for typical run of each setup.}%%
 	\label{tab:scoreEvol}

### 2015-03-31 article.tex

--- 2015-03-31 article.tex
@@
 
-\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below}
-
-\begin{table}
-	\centering
-	\begin{tabular}{l|cc}
-N=250\\\hline
-$\mu$&$\alpha$&(SD)\\\hline
-0.004&1.50&(0.02) \\
-0.008&1.52&(0.02)\\
-0.016&1.55&(0.03)\\
-0.032&1.59&(0.06)\\
-0.064&1.78&(0.08)\\
-0.128&1.99&(0.04)\\
-	\end{tabular}
-	\begin{tabular}{l|cc}
-N=500\\\hline
-$\mu$&$\alpha$&(SD)\\\hline
-0.004&1.53&(0.03)\\
-0.008&1.57&(0.01)\\
-0.016&1.61&(0.04)\\
-0.032&1.70&(0.05)\\
-0.064&1.81&(0.10)\\
-0.128&1.98&(0.02)\\
-	\end{tabular}
-	\caption{Mean \& SD of $\alpha$ parameter }
-	\label{tab:Bmualpha}
-\end{table}
+\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below?\\ 
+By the way, doing t.test on the different value of alpha I have gives me statistically differences between 250 and 500 agents ONLY for $\mu=.064$  }
 

### 2015-03-31 article.tex
review with jm and few other modification

@@
 
-More formally the model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $r$.
-The first corresponds to the quantity of each good that the agent $i$ possesses: $$ Q^i = (q^i_1,\cdots,q^i_r) $$
+More formally the model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$.
+The first corresponds to the quantity of each good that the agent $i$ possesses: $$ Q^i = (q^i_1,\cdots,q^i_n) $$
 
@@
 The second vector reflects the estimation of the value of a product that an agent $i$ makes.
-$$ V^i = (v^i_1,\cdots,v^i_r) $$
+$$ V^i = (v^i_1,\cdots,v^i_n) $$
 where $V^i$ is the total list of estimated values of agent $i$, and $v^i_j$ is the value that agent $i$ associates to the goods of type $j$.
@@
 
+\section{EXPERIMENTAL SETUP}
+
+In order to validate our model we first reproduce traditional results often seen in the literature on cultural transmission.
+We then show that it is possible to transform it to fit processes that are economically sound.
+
+\subsection{Cultural Transmission}
+
+In this article, the cultural transmission mechanism tested is the neutral hypothesis, which has been shown to be followed by multiple cultural phenomenons~\cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
+Under this hypothesis, the \emph{imitation} process used is  ``random copy'', which has been implemented as follow: each agent has a low probability to pick randomly one agent among all and copy its vector of values.
+The \emph{innovation} process, termed ``unbounded'', is triggered with a low probability and draw a new random value to replace an element $v^i_j$.
+The imitation and innovation probabilities are presented with other parameters in table~\ref{tab:parameters}.
+
+The neutral hypothesis states that the random copy and the unbounded innovation process used under a fixed population size, leads to a repartition of cultural variants termed ``power law''.
+This distribution is characterized by a small number of very frequent traits and a large number of very rare traits.
+This distribution is formalized as: $$P(v)=C/v^\alpha $$
+
+\subsection{Trading Model}\label{sec:trade}
+\paragraph{Production}
 \todo{check that it's integrated later: In this article each agent is producing only one type of good.
@@
 In this article the \textit{production} process will remain the same and only the \textit{imitation} and \textit{innovation} processes are changed.}
-
-\section{EXPERIMENTAL SETUP}
-
-In order to validate our model we first reproduced traditional  result often seen in the literature on cultural transmission.
-After that we show that doing small modification we can transform our model to make it fit processes that are more economically consistent.
-
-\subsection{Cultural Transmission}
-
-In this article the neutral hypothesis is tested which implies that the cultural transmission mechanism is the ``random copy"~\cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
-In the literature, people have shown that a lot of cultural phenomene where people copy randomly the cultural traits of other exhibit a particular pattern.
-
-With this mechanism of copy and given enough time  we will find in a fixed size population always the same repartition of the cultural variants.
-A few that are very frequent and an always bigger number of variant that are always less frequent.
-This is traduced by a ``power law'' distribution, following the equation $P(v)=C/v^\alpha $ that one could display as a line with a slope $-\alpha$ in the log-log graph of the proportion of variants with regards to the frequency of variant.
-
-The imitation process of ``random copy" is implemented by a low probability for each agent to pick randomly one agent among all and copy its vector of values.
-The innovation process is triggered with a low probability and select new elements for the vector of values.
-These new elements are drawn from a uniform distribution.
-The imitation and innovation probabilities are presented with other parameters in table~\ref{tab:parameters}.
-
-\subsection{Trading Model}\label{sec:trade}
 
@@
 
+$$ S^{max}=1 \text{ if } q^i_j = n_j \text{ else}$$
 $$ S^i=1- \dfrac{\abs{q^i_j - n_j}}{ \sqrt{\abs{(q^i_j)^2-(n_j)^2}}} $$
@@
 
-On top of producing the agents have the ability to exchange and consume the goods.
+On top of producing goods, the agents have the ability to exchange them.
 During the trading phase the value associated to a good by an agent corresponds to the subjective price of the good for this agent.
@@
 the agent that proposes a satisfiable ratio between the other product and the product produced by the agent.
-In more detail, the trading phase start by the agent looking at a first random agent producing another product.
-A trade is possible with the other agent if the following condition holds:
+In more detail, the trading phase starts by the agent looking at a first random agent producing another product.
 
-\begin{itemize}
-	\item Both agents have enough good in their inventory
-	\item The quantitie of each good  fit the will of both agents.
-\end{itemize}
+Let $o$ be an agent producing $g$ that proposes a trade and $r$ an agent producing $k$ that receives the offer.
+As explained earlier, each has a quantity of good $Q^o$ and $Q^r$.
+On the one side, $o$ wants to exchange a quantity $w_g^o$ of the good $g$ for a quantity $w_k^o$ of the good $k$.
+On the other side, $r$ wants to exchange a quantity $w_g^r$ of the good $g$ for a quantity $w_k^r$.
+The quantities $W^o$ and $W^r$ are defined by :
 
-Let be : $o$ the agent ``offerer'', and $r$ the agent that receive the offer.
-Both have an inventory $x_i$ of every good where $x_i^o$ is the quantity of good $i$ owned by $o$.
-$o$ produce the good $g$ and want to trade it in a quantity $q_g^o$ for a quantity $q_k^o$ of the good $k$ produced by $r$.
-In its side $r$ own also a quantity $q_k^r$ of the good $g$ that it want to trade with quantity $q_k^r$ of its own produced goods.
+ $$ W^o=(w_g^o = v_g^o,w_k^o= \frac{v_k^o}{v_g^o}) $$ 
+ $$ W^r=(w_k^r = v_k^r,w_g^r= \frac{v_g^r}{v_k^r}) $$
 
-The exchange take place only if :
-$$ x_g^o >= q_g^o $$
-$$ x_g^r <= q_g^o $$
-$$ x_k^r >= q_k^o $$
-$$q_g^o>=(x_g^r+q_g^r)$$
-$$q_k^o<=q_k^r$$
-$$q_g^o<=q_g^r$$
+ Where $v_j^i$ are the estimated value of the good $j$ by the agente $i$ as defined earlier. 
+The requested quantity of the non produced good is simply the ratio between the estimated value of the good requested and the estimated value of the produced good.
 
-The given quantity of the produced good ($g$ for $o$) is the estimate value of it ( its price).
-The requested quantity of the non produced value is simply the ratio between the estimated value of the good requested and the given quantity of the produced good.
+Once de quantities are defined, the agents declare that the trade is possible if :
+\begin{enumerate}
+	\item  $$ q_g^o >= w_g^o $$
+	\item  $$ q_g^r <= w_g^o $$
+	\item  $$ q_k^r >= w_k^o $$
+	\item  $$w_g^o>=(q_g^r+w_g^r)$$
+	\item  $$w_k^o<=w_k^r$$
+	\item  $$w_g^o<=w_g^r$$
+\end{enumerate}
 
-In our case, for $o$ : $q_g^o = v_g^o$ and $q_k^o= \frac{v_k^o}{v_g^o} $ and for $r$  : $q_k^o = v_k^o$ and $q_g^o= \frac{v_g^o}{v_k^o} $.
+The conditions 1-3 insure that both agents have enough goods in their inventory and the conditions 4-5 insure that the quantities of each good fit the will of both agents.
 
 If a trade is possible the two agents will exchange the agreed quantities.
-If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ ($\frac{Number of agent}{2}$ agents have been tried.
+If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ ($\frac{Number of agent}{2}$) agents have been tried.
 At this point the agent will try to trade with agents producing another good.
@@
 This trading process is described in algorithm~\ref{algo:trade}.
+%faire tableau parametre et y integrer Tradethreshold
 
@@
 
+%%deplacer et integrer dans 4.3
 The trading process is performed at every iteration while the imitation and innovation processes are executed only every $CulturalStep$.
@@
 Therefore, a new and more realistic mechanism is proposed.
-The innovation process is still triggered with a probability $\mu$
+The innovation process, termed ``self referenced'', is still triggered with a probability $\mu$
 but modify the previous price by adding or subtracting a small amount taken randomly from a uniform  distribution between $0 .. \beta$.
@@
 With such a setup it is expected that the prices will converge to a ratio allowing each agent to obtain a number of resources equivalent to the needs.
-Knowing that,  the best possible price of a good should satisfy the equations :
+The best possible price of a good satisfies the equations :
 
@@
 $$\frac{v^r_g}{v^r_k} = n_g $$
-$$v^r_k = \frac{1}{n_k} $$
-$$v^r_g = \frac{1}{n_g} $$
-with g the produced good of the agent j and i another good which is not the one which is produced.
+$$v^r_k = n_k $$
+$$v^o_g = n_g $$
+$$=>v^r_g = v^o_k = n_k * n_g$$
 
-If such a price is reached to score of all agents should be equal to : $$ CulturalStep\times1\times ngoods $$
+With as earlier, $o$ and $r$ the agents that respectively produces $g$ and $k$, $v_j^i$ the estimated value of the good $j$ for the agent $i$ and $n_j$ the needed value of the good $j$ for all agents.
+
+If such prices are reached, all exchange can be done leading to a score of each agent of the population : $$ CulturalStep\times S^i(\tilde{Q}^i) \times ngoods $$ with $S^i(\tilde{Q}^i) = S_{max}$, the score for the optimal inventory $\tilde{Q}^i$ for the agent $i$ which is $S_{max}=1$.
 
@@
 We first analyse the result obtained in the ``neutral model" as presented in section~\ref{sec:}.
-The figure~\ref{fig:} presents an analysis of the value vectors obtained across the 100 runs performed with a $\mu$ value equal to XXXX.
+The figure~\ref{fig:allMutation} presents an analysis of the value vectors obtained across the 100 runs performed with a $\mu$ value equal to XXXX.
 In this graph it is not the exact values that are analysed but their relative frequencies.
@@
 
-\begin{figure}[hbp]
+\begin{figure}[!hbp]
 	\begin{center}
-		\includegraphics[width=7cm]{img/allmuRandMaxN250.pdf}
-		\includegraphics[width=7cm]{img/allmuRandMaxN500.pdf}
+		\includegraphics[width=6cm]{img/allmuRandMaxN250.pdf}
+		\includegraphics[width=6cm]{img/allmuRandMaxN500.pdf}
 	\end{center}
@@
 	\centering
-	\begin{tabular}{l|cc}
-		Agents Number & Our result & Bentley et al 2004\\\hline
-		N = 250 &
-		\begin{tabular}{l|cc}
-			$\mu$ & $\alpha$ & SD\\\hline
-			0.004&1.53&0.03\\
-			0.008&1.55&0.03\\
-			0.016&1.57&0.02\\
-			0.064&1.66&0.01\\
-		\end{tabular}
-		&
-		\begin{tabular}{cc}
-		$\alpha$&SD\\\hline
-		1.50&0.02 \\
-		1.52&0.02\\
-		1.55&0.03\\
-		1.78&0.08\\
-		\end{tabular} \\
-		N= 500&
-		\begin{tabular}{l|cc}
-			$\mu$ & $\alpha$ & SD\\\hline
-			0.004&1.54&0.02\\
-			0.008&1.55&0.01\\
-			0.016&1.57&0.01\\
-			0.064&1.67&0.01\\
-		\end{tabular}
-		&
-		\begin{tabular}{cc}
-			$\alpha$&(SD)\\\hline
-			1.53&0.03\\
-			1.57&0.01\\
-			1.61&0.04\\
-			1.81&0.10\\
-		\end{tabular}
+	\begin{tabular}{ll|lllll}
+		Agents Number & & Our result& & Bentley et al 2004\\
+			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
+
+		N = 250 
+			&0.004&1.53&0.03&1.54&0.02\\
+			&0.008&1.55&0.03&1.55&0.01\\
+			&0.016&1.57&0.02&1.57&0.01\\
+			&0.064&1.66&0.01&1.67&0.01\\\hline
+		N= 500
+		&0.004&1.50&0.02&1.53&0.03\\
+		&0.008&1.52&0.02&1.57&0.01\\
+		&0.016&1.55&0.03&1.61&0.04\\
+		&0.064&1.78&0.08&1.81&0.10\\
 	\end{tabular}
@@
 \jm{Simon, do you have a comment on the table ? Like does it fit what is found in other articles ?}
-
-\simon{What do you think about puting  the bentley et al resutlts cf table~\ref{tab:Bmualpha} below?\\ 
-By the way, doing t.test on the different value of alpha I have gives me statistically differences between 250 and 500 agents ONLY for $\mu=.064$  }
 
@@
 					&Imitation  Process \\
-		Inovation Mechanism	& Rand & Success \\\hline  
+		Innovation Mechanism	& Rand & Success \\\hline  
 		Unbounded 		&A & B \\
-		Local Modification	& C & D \\
+		Self Referenced	& C & D \\
 	\end{tabular}

### 2015-04-01 article.tex
minor modifications

@@
 
-\subsection{Modelling of Trade}
+\subsection{Models of Trade}
 
@@
 
-Among the various works done with this objective, few are studying the interactions between economy and cultural change in Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
+Among the various works done with this objective, few are studying the interactions between economy and cultural change in the Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
 An analysis based on historical documents has revealed the importance of economical and social institutions for the efficiency of trades of grains in the early Roman Empire~\cite{kessler_organization_2007}.
-The same type of analysis has also revealed the importance of a number of key factors () for the growth of income and population in the Roman Italy~\cite{scheidel_model_2007}.
+The same type of analysis has also revealed the importance of a number of key factors (such as commercial development, population growth and geographical mobility) for the growth of income and population in the Roman Italy~\cite{scheidel_model_2007}.
 Finally, a micro-economic model has determined the importance of reputation and threat of expulsion from a trade network as mechanisms to maintain the overall efficiency of the trade network~\cite{terpstra_trade_2011}.
@@
 However, a limitation of the previous works is the impossibility to test the conclusions reached by the authors.
-The models proposed reflects only the view of the authors on the data they have analyse.
+The models proposed reflects only the view of the authors on the data analysed.
 A new type of model would be necessary to go beyond the interpretation, and allow the verification of the conclusions reached.
@@
 By this mean, if a factor is really important in the economical network, its removal from the model will lead to data qualitatively different from the historical data.
-The Multi-Agent Simulations (MAS) offer a way to produce this kind of model~\cite{lake_trends_2014}.
+The Agent Based Models (ABM) methodology offers a way to produce this kind of model~\cite{lake_trends_2014}.
 

### 2015-04-02 article.tex
modifications of state of the art and setup

@@
 \usepackage{float}
+\usepackage{booktabs}
 
@@
 Based on this tool a relatively complex and exact modelisation of the prehispanic Pueblo societies has been proposed~\cite{kohler_modelling_2012}.
-This work offer a relatively exact MAS integrating notable the effects food consumption, production and landscape.
+This work offers an ABM integrating numerous effects such as food consumption, production and landscape.
 The questions studied are  numerous and some works are performed on the economical system and its ties with social transmissions~\cite{kobti_emergence_2006,cockburn_simulating_2013}.
@@
 
-\subsection{Modelisation of Trade and Culture}
+\subsection{Models of Trade and Culture}
 
@@
 The second proposes a more complete model including a large number of goods (certain being essential and the others non-essential), but suffer from a greater complexity and the absence of the notion of trade networks.
-Moreover, both models propose new dynamics but these dynamics are not compared to previous results obtained in the study of cultural evolution and the study of trading mechanisms.
+Moreover, these works do not compare the dynamics obtained to the previous studies on cultural change and trading mechanisms.
 
-The model presented in this work aims to offer a framework for the co-evolution of trades and culture which relies on a low number of parameters.
+The model presented in this work aims to offer a framework for the co-evolution of culture and trades which relies on a low number of parameters.
 It is not within the scope of this article to answer the questions asked at the beginning of this section as they require specific implementations of the model proposed.
@@
 
-More formally the model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$.
-The first corresponds to the quantity of each good that the agent $i$ possesses: $$ Q^i = (q^i_1,\cdots,q^i_n) $$
+More formally the model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$. The first corresponds to the quantity of each good that the agent $i$ possesses: 
+$$\forall i \in Pop, \quad Q^i = (q^i_1,\cdots,q^i_n) $$
 
@@
 The second vector reflects the estimation of the value of a product that an agent $i$ makes.
-$$ V^i = (v^i_1,\cdots,v^i_n) $$
+$$\forall i \in Pop, \quad V^i = (v^i_1,\cdots,v^i_n) $$
 where $V^i$ is the total list of estimated values of agent $i$, and $v^i_j$ is the value that agent $i$ associates to the goods of type $j$.
@@
 The \textit{production} process describe the creation of goods by the agent.
-Once a good is produced it is added to the quantity vector of the agent.
-Within the \textit{imitation} process an agent can copy the value vector of another agent.
-The \textit{innovation} process reflects the possibility for an agent to associate new values for the goods.
-For this, an agent can select new elements for its value vector independently of the values of other agents.
+Once a good is produced by an agent $i$ it is added its quantity vector ($Q^i$).
+Within the \textit{imitation} process an agent $i$ can copy the value vector ($V^j$) of an agent $j$, where $j \neq i$.
+Finally, the \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{imitation} process in that the modification is done without reference to the other agents.
 
@@
 
-In order to validate our model we first reproduce traditional results often seen in the literature on cultural transmission.
-We then show that it is possible to transform it to fit processes that are economically sound.
+In order to validate our model we first reproduce common results from the literature on cultural transmission.
+We then show that it is possible to transform our model to fit processes that are economically sound.
+In the following, we present the two set of implementations of the three core processes (production, imitation and innovation) that were used in our experiments.
 
@@
 
-In this article, the cultural transmission mechanism tested is the neutral hypothesis, which has been shown to be followed by multiple cultural phenomenons~\cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
-Under this hypothesis, the \emph{imitation} process used is  ``random copy'', which has been implemented as follow: each agent has a low probability to pick randomly one agent among all and copy its vector of values.
+The first set of implementations of the core processes aims at reproducing a common result from the literature on cultural change.
+In this article, the cultural change hypothesis tested is the neutral hypothesis, which has been shown to be followed by multiple cultural phenomenons~\cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
+Under this hypothesis, the production of goods is not tested, as a consequence, in this set of implementation, the \emph{production} process does not modify the content of the quantity vector of the agents.
+The \emph{imitation} process used is  ``random copy'', which has been implemented as follow: each agent has a low probability to pick randomly one agent among all and copy its vector of values.
 The \emph{innovation} process, termed ``unbounded'', is triggered with a low probability and draw a new random value to replace an element $v^i_j$.
@@
 
-The neutral hypothesis states that the random copy and the unbounded innovation process used under a fixed population size, leads to a repartition of cultural variants termed ``power law''.
+The neutral hypothesis states that the ``random copy'' and the ``unbounded'' innovation process used under a fixed population size, leads to a repartition of cultural variants termed ``power law''.
 This distribution is characterized by a small number of very frequent traits and a large number of very rare traits.
-This distribution is formalized as: $$P(v)=C/v^\alpha $$
+Since this hypothesis has been verified in previous works implementing similar \emph{imitation} and \emph{innovation} mechanisms, we expect in this work the observation of a similar ``power law' distribution.
+More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$, where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable.
 
 \subsection{Trading Model}\label{sec:trade}
+
+The second set of implementations of the core processes aims at producing economical dynamics.
+We are interested in the exchange of products between agents when they can modify the prices at which they sell and buy products.
+We want to implement simple processes leading to the convergence of prices to values acceptable by all agents.
+
 \paragraph{Production}
-\todo{check that it's integrated later: In this article each agent is producing only one type of good.
-The type good produced by an agent is assigned to it at the beginning of the simulation and does not change.}
-
-\todo{check that it's integrated later: 
-In this article the \textit{production} process will remain the same and only the \textit{imitation} and \textit{innovation} processes are changed.}
+In this set of implementations, each agent is producing only one type of good. The type good produced by an agent is assigned to it at the beginning of the simulation and does not change.
 
 \paragraph{Imitation}
-In the cultural transmission model the value vector does not impact the imitation process.
-When trading is involved it is not not the case.
-In order to model such aspect we introduce a new cultural transmission mechanism taking into account the value vector.
-This mechanism is based on two new notions: need and score.
+Within this set of implementations, the key ideas behind the imitation mechanism is to copy the agents which are the best at trading.
+To do so, the imitation mechanism used takes into account the value vector of the other agents and relies on two new notions: \emph{need} and \emph{score}.
 
-The need is a quantity of product that each agent tries to obtain. This quantity is different for each product but the need for a product is the same for all agents:
-$$ need = (n_1, \cdots, n_r) $$
+The \emph{need} is a quantity of product that each agent tries to obtain. This quantity is different for each product but the need for a product is the same for all agents:
+$$ N = (n_1, \cdots, n_r) $$
 
-The score $S^i$ of agent $i$ reflects the ability for an agent to obtain the products it needs.
-It is maximum when the quantity vector of an agent is equal to its need vector and lower in proportion to the distance between the need vector and the quantity vector.
+The \emph{score} $s^i$ of an agent $i$ reflects the ability of this agent to obtain the products it needs.
+It is maximum when the quantity vector of an agent is equal to its need vector and lower proportionally to the distance between the need vector and the quantity vector.
 It is formally computed as follow for agent $i$:
 
-$$ S^{max}=1 \text{ if } q^i_j = n_j \text{ else}$$
-$$ S^i=1- \dfrac{\abs{q^i_j - n_j}}{ \sqrt{\abs{(q^i_j)^2-(n_j)^2}}} $$
+\begin{equation}\label{eq:score}
+s^i = \begin{cases}
+ s_{max}=1 & \text{if $q^i_j = n_j$}\\
+1 -\dfrac{\abs{q^i_j - n_j}}{ \sqrt{\abs{(q^i_j)^2-(n_j)^2}}} & \text{if $q^i_j \neq n_j$}
+\end{cases}
+\end{equation}
 
 This function ensures that each good count for the same proportion in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
-This can be seen in the figure~\ref{fig:fit}.
+The values of $s^i$ obtained for different need values are depicted in figure~\ref{fig:fit}.
 
@@
 
+\todo{put a little description of what is in the figure}
 The agents will choose the agent from whom the price vector should be copied among the agents that produce the same good and have the highest score.
@@
 During the trading phase the value associated to a good by an agent corresponds to the subjective price of the good for this agent.
-Briefly summarised, for each good that it does not produced, an agent will trade with the first parter that offer an acceptable trade, i.e.
+Briefly summarised, for each good that it does not produce, an agent will trade with the first parter that offer an acceptable trade, i.e.
 the agent that proposes a satisfiable ratio between the other product and the product produced by the agent.
-In more detail, the trading phase starts by the agent looking at a first random agent producing another product.
 
-Let $o$ be an agent producing $g$ that proposes a trade and $r$ an agent producing $k$ that receives the offer.
+In more details, the trading phase starts by the agent looking at a first random agent producing another product. 
+Let $o$ be an agent producing $g$ that proposes a trade and $r$ an agent producing $k$ that receives the proposition.
 As explained earlier, each has a quantity of good $Q^o$ and $Q^r$.
@@
 On the other side, $r$ wants to exchange a quantity $w_g^r$ of the good $g$ for a quantity $w_k^r$.
-The quantities $W^o$ and $W^r$ are defined by :
+The tuples $W^o$ and $W^r$ describe the quantities of goods wanted by agent $o$ and $r$ for one trade proposition and are defined by:
 
@@
 
- Where $v_j^i$ are the estimated value of the good $j$ by the agente $i$ as defined earlier. 
+ Where $v_j^i$ are the estimated value of the good $j$ by the agent $i$ as defined earlier. 
 The requested quantity of the non produced good is simply the ratio between the estimated value of the good requested and the estimated value of the produced good.
@@
 Once de quantities are defined, the agents declare that the trade is possible if :
-\begin{enumerate}
-	\item  $$ q_g^o >= w_g^o $$
-	\item  $$ q_g^r <= w_g^o $$
-	\item  $$ q_k^r >= w_k^o $$
-	\item  $$w_g^o>=(q_g^r+w_g^r)$$
-	\item  $$w_k^o<=w_k^r$$
-	\item  $$w_g^o<=w_g^r$$
-\end{enumerate}
+\begin{align}
+q_g^o >= w_g^o \\
+q_g^r <= w_g^o \\
+q_k^r >= w_k^o \\
+w_g^o>=(q_g^r+w_g^r) \\
+w_k^o<=w_k^r \\
+w_g^o<=w_g^r
+\end{align}
 
-The conditions 1-3 insure that both agents have enough goods in their inventory and the conditions 4-5 insure that the quantities of each good fit the will of both agents.
+The conditions 2-4 insure that both agents have enough goods in their inventory to realise the trade and the conditions 5-7 insure that the quantities of each good fit the will of both agents.
 
 If a trade is possible the two agents will exchange the agreed quantities.
-If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ ($\frac{Number of agent}{2}$) agents have been tried.
+If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ agents have been tried.
 At this point the agent will try to trade with agents producing another good.
@@
 \begin{algorithm}
-\caption{Trading Process}
+\caption{Trading Process for agent $o$}
 \label{algo:trade}
@@
 	\scriptsize
-		\For{$Good_i \in Goods \And i \neq A_g $}
+		\For{$j \in Goods \And j \neq produced^i $}
 			\State $tradeAttempt = 0$
-			\For{$A_i \in Good_i \And tradeAttempt < TradeThreshold $}
-				\If{$acceptableTrade(A_i)$}
-					\State $trade(A_i)$
+			\For{$r \in Pop \And produced^r = j \And tradeAttempt < TradeThreshold $}
+				\If{$acceptableTrade(W_o,W_r)$}
+					\State $trade(W_o,W_r)$
 				\Else
@@
 The best possible price of a good satisfies the equations :
-
-$$\frac{v^o_k}{v^o_g} = n_k $$
-$$\frac{v^r_g}{v^r_k} = n_g $$
-$$v^r_k = n_k $$
-$$v^o_g = n_g $$
-$$=>v^r_g = v^o_k = n_k * n_g$$
+\begin{align}
+\frac{v^o_k}{v^o_g} = n_k \\
+\frac{v^r_g}{v^r_k} = n_g \\
+v^r_k = n_k \\
+v^o_g = n_g \\
+=>v^r_g = v^o_k = n_k * n_g \\
+\end{align}
 
@@
 
-If such prices are reached, all exchange can be done leading to a score of each agent of the population : $$ CulturalStep\times S^i(\tilde{Q}^i) \times ngoods $$ with $S^i(\tilde{Q}^i) = S_{max}$, the score for the optimal inventory $\tilde{Q}^i$ for the agent $i$ which is $S_{max}=1$.
+If such prices are reached, all exchange can be done leading to a total score $S$ for each agent of the population : 
+$$ S = \sum_{i=0}^{CulturalStep}  s^i(\tilde{Q}^i) \times ngoods $$ 
+where $\tilde{Q}^i$ is the optimal quantity vector, i.e. the one for which $s^i(\tilde{Q}^i) = s_{max}$. Remember that from equation~\ref{eq:score}, $s_{max}=1$.
 
@@
 \begin{algorithm}
-\caption{Trading Process}
+\caption{Model}
 \label{algo:complete}
@@
 	\State INITIALIZATION: 
-		\For{$Good_i \in Goods$}
-			\For{$Agents per Goods$}
-				\State $A_i = (g^i,p^i, N)$ \Comment{Initialize the agent for the good it has to produce, a random price and the needs}
+		\For{$j \in Goods$}
+			\For{$i \in \#Pop/\#Goods$} \Comment{Initialize the agent for the good it has to produce and a random value vector}
+				\State $produced^i = j$
+				\State $Q^i = (0, \cdots, 0)$
+				\State $V^i = (v^i_0, \cdots, v^i_n)$ \Comment{The values of $v^i_j$ are selected randomly}
 			\EndFor
@@
 	\State SIMULATION:
-		\Loop{$step \in TimeSteps$}
-			\For{$A_i \in Pop$}
-				\State $Production$
-				\State $Trade$				
+		\Loop{$~step \in TimeSteps$}
+			\For{$i \in Pop$}
+				\State $Production()$
+				\For{$j \in Pop$}
+					\State $TradeProcess(i,j)$
+				\EndFor				
 				\If{$ (step \mod CulturalStep) = 0$}	
-					\State $Imitation$
-					\State $Innovation$
+					\State $Imitation()$
+					\State $Innovation()$
 				\EndIf
@@
 
-\todo{to integrate}
-All experiments are performed with Pandora. The code is available at XXXX.
+\todo{upload and put an url, complete cite mare nostrum, put nb of hours per run (or the total)}
+All experiments are performed with the simulator pandora~\cite{wittek_scalable_2012}.
+We have make the source code of our project available online~\footnote{put ulr}.
+All simulations presented are performed in the MareNostrumIII super computer~\cite{}, and took XXXh per run.
 
-In our experiment one has to take in account that agents modifies their prices or exchange their price only every ten steps.
-Between, they exchange goods given their own prices.
+\jm{what about saying that we just count the iterations at the ``imitation, innovation step" ?}
+In our experiment one has to take in account that agents modifies their prices or exchange their price only every $culturalStep$ steps.
+Between, twos such steps, the agent exchange goods given their own prices.
 Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}.
 
-With trade, experiments will last longer than the firsts one because this time the exchange mechanisms will have an impact on the evolution of prices in the population.
+\todo{put the values in the table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{@{}ll@{}}
+\toprule
+Parameter & Value \\
+\midrule
+Mutation probability & \\
+Innovation probability & \\
+CulturalStep &  10 \\
+TradeThreshold & $\frac{Number of agent}{2}$ \\
+TimeSteps & \\
+\bottomrule
+\end{tabular}
+\caption{Table of parameters}\label{tab:parameters}
+\end{center}
+\end{table}
 

### 2015-04-02 article.tex
multicol

--- 2015-03-31 article.tex
@@
 	\centering
-	\begin{tabular}{ll|lllll}
-		Agents Number & & Our result& & Bentley et al 2004\\
+	\begin{tabular}{ll|llll}
+		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et al 2004}\\
 			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
-
-		N = 250 
-			&0.004&1.53&0.03&1.54&0.02\\
+		N = 250	&0.004&1.53&0.03&1.54&0.02\\
 			&0.008&1.55&0.03&1.55&0.01\\
@@
 			&0.064&1.66&0.01&1.67&0.01\\\hline
-		N= 500
-		&0.004&1.50&0.02&1.53&0.03\\
+		N= 500	&0.004&1.50&0.02&1.53&0.03\\
 			&0.008&1.52&0.02&1.57&0.01\\

### 2015-04-02 article.tex
todo

@@
 \midrule
-Mutation probability & \\
-Innovation probability & \\
+Mutation probability & .004 \\
+Innovation probability & .001\\
 CulturalStep &  10 \\
-TradeThreshold & $\frac{Number of agent}{2}$ \\
-TimeSteps & \\
+TradeThreshold & 100  \\
+TimeSteps & 200000 \\
 \bottomrule
@@
 These mechanisms are summarized in the table~\ref{tab:exp}.
-Each couple of innovation/imitation mechanism form one setup that is labelled with one later.
+Each couple of innovation/imitation mechanism form one setup that is labelled with one letter.
 Note that the ``neutral model" studied in the previous section corresponds to the setup A.
-All the runs presented in this section are done for 100000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
+All the runs presented in this section are done for 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
 
@@
 		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForA-G2N250.pdf}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForB-G2N250.pdf}} \\ Setup B} \\
-		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForC-G2N250.pdf}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForD-G2N250.pdf}} \\ Setup D}
+		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForC-G2N250.pdf}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForD-G3N500.pdf}} \\ Setup D}
 
@@
 	\begin{center}
-		\includegraphics[width=7cm]{img/ratioEvol.png}
+		\includegraphics[width=7cm]{img/ClearingPriceDistanceEvolutionForD-G3N500.pdf}
 	\end{center}

### 2015-04-02 article.tex
comments and fixes

--- 2015-04-02 article.tex
@@
 conformism and anti-conformism).
-\jm{to keep it simple, can we say ``evolutionary theory" instead of ``genetic theory" ?}
-These analysis are often based on the genetic theory of neutral evolution \cite{neiman_stylistic_1995} and they take neutrality as a null-hypotheses, i.e.
-variations of traits are strictly explained by their frequency distribution in the population.
-There exist a large number of works using this model as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
+These analysis are often based on the theory of neutral evolution \cite{neiman_stylistic_1995}, which explains variation in the distribution of traits as a function of their frequency distribution in the population.
+Thus, a trait is assumed to lack any selective bias and its transmission will depend on its popularity amongst the rest of individuals.
+The comparison of a given frequency distribution found in data against this unbiased transmission model is traditionally used as a null-hypothesis testing for selection.
+There exist a large number of works using this approach as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
@@
 
-In particular, the trade of cultural products within a market system can potentially introduce a dynamics content-related bias linked to the price of the different products.
+In particular, trade within a market system can potentially introduce a complex dynamic bias to the neutral model.
+Trasmission will be linked to the price of the different products.
 This would also affect the frequency of the product within the population, which in turn would modify its price following a co-evolutionary dynamic.
@@
 
+\xrc{close or remote in terms of what?}
+
 Among the various works done with this objective, few are studying the interactions between economy and cultural change in the Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
@@
 
+\xrc{I would move this discussion to the coevolution section?
+Besides, I would ass something such as "a large percentage of datasets used for this purpose are material objects found in archaeological contexts (i.e.
+pottery).
+Most of them are usually represented following a neutral model, but how this affects its weight inside the market system?"}
+
 However, a limitation of the previous works is the impossibility to test the conclusions reached by the authors.
@@
 These models should be able to generate data which is then qualitatively compared to the real historical data.
+
+\xrc{what data is being used?}
+
 By this mean, if a factor is really important in the economical network, its removal from the model will lead to data qualitatively different from the historical data.
 The Agent Based Models (ABM) methodology offers a way to produce this kind of model~\cite{lake_trends_2014}.
+
+\xrc{I would add a paragraph briefly explaining what is an ABM}
 
@@
 However the work done in this project consider a pre-market society in a specific village which makes it difficult to reach more general conclusions, notably applicable to the Roman Empire.
+
+\xrc{The Pueblo model is an example, but there are tons of other ones...why is this chosen?
+After the paragraph explaining ABM I would say "As an example of its potential, a detailed model of the prehispanic blablabla..."}
+
+\xrc{Didn't Brughmans have a model of roman trade?}
 
@@
 \jm{tried a justification of co-evolutionary framework but I find it too light. ideas ?}
+
+\xrc{What if we move the text to the intro and remove this subsection?}
 
@@
 
+\xrc{This first paragraph should briefly explain the trade component?}
+
 More formally the model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$. The first corresponds to the quantity of each good that the agent $i$ possesses: 
@@
 
+\xrc{I would use cultural transmission instead of imitation?}
+
 This scheme allow us to have a model achieving the two main goals listed in section~\ref{sec:intro}.
@@
 
+\xrc{how do agents trade?}
+
 \section{EXPERIMENTAL SETUP}
+
+\xrc{Not sure about the name...the sections below are describing the model so why are they in different section?}
 
@@
 
-The first set of implementations of the core processes aims at reproducing a common result from the literature on cultural change.
-In this article, the cultural change hypothesis tested is the neutral hypothesis, which has been shown to be followed by multiple cultural phenomenons~\cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
-Under this hypothesis, the production of goods is not tested, as a consequence, in this set of implementation, the \emph{production} process does not modify the content of the quantity vector of the agents.
-The \emph{imitation} process used is  ``random copy'', which has been implemented as follow: each agent has a low probability to pick randomly one agent among all and copy its vector of values.
+The first mechanism of the model aims at reproducing a scenario of unbiased transmission, where each product is a cultural trait without intrinsic positive or negative weight \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
+Under this hypothesis, the process of \emph{production} is not relevant, and as a consequence, it does not modify the content of the quantity vector of the agents.
+
+Unbiased transmission is implemented using ``random copy'': each agent has a low probability to pick randomly one agent among all and copy its vector of values.
 The \emph{innovation} process, termed ``unbounded'', is triggered with a low probability and draw a new random value to replace an element $v^i_j$.
@@
 
-The neutral hypothesis states that the ``random copy'' and the ``unbounded'' innovation process used under a fixed population size, leads to a repartition of cultural variants termed ``power law''.
+The neutral hypothesis states that the ``random copy'' transmission and the ``unbounded'' innovation process used under a fixed population size leads to a \emph{power law} distribution of the frequency for the different cultural variants.
 This distribution is characterized by a small number of very frequent traits and a large number of very rare traits.
 Since this hypothesis has been verified in previous works implementing similar \emph{imitation} and \emph{innovation} mechanisms, we expect in this work the observation of a similar ``power law' distribution.
+
+\xrc{I would remove the previous sentence: it is obvious that it works right?}
+
 More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$, where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable.
@@
 We want to implement simple processes leading to the convergence of prices to values acceptable by all agents.
+
+\xrc{What do you mean by convergence? Equilibrium?}
 
@@
 
+\xrc{score is fitness? Not sure if we should use fitness here, as we are already using an evolutionary framework. Also, we could use payoff.}
 The \emph{score} $s^i$ of an agent $i$ reflects the ability of this agent to obtain the products it needs.
@@
 
-This function ensures that each good count for the same proportion in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
+This function ensures that each good count for the same proportion \xrc{weight?} in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
 The values of $s^i$ obtained for different need values are depicted in figure~\ref{fig:fit}.
@@
 
+\xrc{so no random copy? It should be clear that agents copy values based on random copy, and copy strategy based on payoff biased transmission (if i'm not mistaken).}
+
 \paragraph{Trading}
@@
 On top of producing goods, the agents have the ability to exchange them.
-During the trading phase the value associated to a good by an agent corresponds to the subjective price of the good for this agent.
+During the trading phase \xrc{we should explain the phases of the model before mentioning the trading phase} the value associated to a good by an agent corresponds to the subjective price of the good for this agent.
 Briefly summarised, for each good that it does not produce, an agent will trade with the first parter that offer an acceptable trade, i.e.
@@
 The idea behind this is to perform the imitation based on a score that reflects the performance of the agent and not only one lucky or unlucky trading round.
+
+\xrc{Add some 'scheduling' definition where this is shown. Also it should be justified (market is faster than cultural change?)}
 
@@
 \todo{upload and put an url, complete cite mare nostrum, put nb of hours per run (or the total)}
-All experiments are performed with the simulator pandora~\cite{wittek_scalable_2012}.
+All experiments are performed with the Pandora open source framework ~\cite{rubiocampillo_2014}.
 We have make the source code of our project available online~\footnote{put ulr}.
+\xrc{I always put this in the acknowledgements to avoid the technical details while describing the experiments}
+
 All simulations presented are performed in the MareNostrumIII super computer~\cite{}, and took XXXh per run.
@@
 	\centering
-	\begin{tabular}{ll|llll}
-		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et al 2004}\\
+	\begin{tabular}{ll|lllll}
+		Agents Number & & Our result& & Bentley et al 2004\\
 			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
-		N = 250	&0.004&1.53&0.03&1.54&0.02\\
+
+		N = 250 
+			&0.004&1.53&0.03&1.54&0.02\\
 			&0.008&1.55&0.03&1.55&0.01\\
@@
 			&0.064&1.66&0.01&1.67&0.01\\\hline
-		N= 500	&0.004&1.50&0.02&1.53&0.03\\
+		N= 500
+		&0.004&1.50&0.02&1.53&0.03\\
 		&0.008&1.52&0.02&1.57&0.01\\
@@
 \end{table}
+
+\xrc{ok but this is the experiment design right??}
 
@@
 
+\xrc{these boxplots are confusing because they are small and contain a huge amount of information.
+What if we do a scatterplot with a given alpha, and on top of this a loess regression?
+It always works better to me when you have this kind of data; also, I would provide a figure for each type of score.}
+
 In this graphic we can observe that the product displayed in green is blocked to a non-optimal value until iteration XXXX, and decreasing after.
@@
 
+\xrc{discussion should go before conclusion.
+Also, this is not a disucussion but some comments on future stuff that could be done: what is the model explaining in terms of what was mentioned in the intro?}
 %The questions we would like to ultimately study are for example: how does the hierarchical structure changes the adoption of a new product ?
@@
 
+\section{Acknowledgements}
+
+Funding for this work was provided by the ERC Advanced Grant EPNet (\todo{look for code}) and the SimulPast Consolider Ingenio project (CSD2010-00034) of the former Ministry for Science and Innovation of the Spanish Government.
+
+The model was created using Pandora \cite{rubiocampillo_2014}.
+R was used for figures and statistical analysis \cite{rdev_2012}.
+The source code of the model is licensed under a GNU General Public License and will be available for download at publication.
+
 \bibliographystyle{wsc}

### 2015-04-03 article.tex
scatter graph, new equilibrum equations

@@
 \end{figure}
+We can see in the figure~\ref{fig:fit} the score with regards to the quantity of one good traded by an agent and that given different value for the need of its good.
+We can see that even if the need for a good is small (for instance when $need = .01$) one can have a high score as soon as he manage to get a quantity closed to the needed quantity.
+It insure that one need to have all of each good in the good proportion and that none could reach a better score just managing to get the right amount of a good with a high need.
 
-\todo{put a little description of what is in the figure}
 The agents will choose the agent from whom the price vector should be copied among the agents that produce the same good and have the highest score.
@@
 
- $$ W^o=(w_g^o = v_g^o,w_k^o= \frac{v_k^o}{v_g^o}) $$ 
- $$ W^r=(w_k^r = v_k^r,w_g^r= \frac{v_g^r}{v_k^r}) $$
+\begin{equation}
+	 W^o=(w_g^o = v_g^o,w_k^o= \frac{v_k^o}{v_g^o}) 
+	 W^r=(w_k^r = v_k^r,w_g^r= \frac{v_g^r}{v_k^r}) 
+	 \label{eq:trade}
+\end{equation}
 
@@
 \begin{align}
-q_g^o >= w_g^o \\
+q_g^o >= w_g^o \label{eq:constraintFirst}\\
 q_g^r <= w_g^o \\
-q_k^r >= w_k^o \\
-w_g^o>=(q_g^r+w_g^r) \\
+q_k^r >= w_k^o \label{eq:constraintLastInv}\\
+w_g^o>=(q_g^r+w_g^r)\label{eq:constraintFirstWill} \\
 w_k^o<=w_k^r \\
 w_g^o<=w_g^r
+\label{eq:constraintLast}
 \end{align}
 
-The conditions 2-4 insure that both agents have enough goods in their inventory to realise the trade and the conditions 5-7 insure that the quantities of each good fit the will of both agents.
+The conditions \ref{eq:constraintFirst}-\ref{eq:constraintLastInv} insure that both agents have enough goods in their inventory to realise the trade and the conditions \ref{eq:constraintFirstWill}-\ref{eq:constraintLast} insure that the quantities of each good fit the will of both agents.
 
@@
 This trading process is described in algorithm~\ref{algo:trade}.
-%faire tableau parametre et y integrer Tradethreshold
 
@@
 
-%%deplacer et integrer dans 4.3
 The trading process is performed at every iteration while the imitation and innovation processes are executed only every $CulturalStep$.
@@
 
-With such a setup it is expected that the prices will converge to a ratio allowing each agent to obtain a number of resources equivalent to the needs.
-The best possible price of a good satisfies the equations :
-\begin{align}
+With such a setup and given (\ref{eq:score}) and (\ref{eq:trade}), it is expected that the prices will converge to value allowing each agent to obtain quantities of resources exactly equivalent to the needs.
+The best possible price of all good satisfies the equations :
+\begin{equation}
+	\begin{cases}
 		\frac{v^o_k}{v^o_g} = n_k \\
-\frac{v^r_g}{v^r_k} = n_g \\
-v^r_k = n_k \\
-v^o_g = n_g \\
-=>v^r_g = v^o_k = n_k * n_g \\
-\end{align}
+		v^o_g = n_g 
+	\end{cases} =>v^o_k = n_k \times n_g, \quad \forall k \in Goods, \forall o \in Pop, g = produced^o, k \not= g 
+\end{equation}
 
-With as earlier, $o$ and $r$ the agents that respectively produces $g$ and $k$, $v_j^i$ the estimated value of the good $j$ for the agent $i$ and $n_j$ the needed value of the good $j$ for all agents.
+Which mean that
 
-If such prices are reached, all exchange can be done leading to a total score $S$ for each agent of the population : 
+\begin{equation}
+	\quad \forall j \in Goods, \forall i \in Pop \quad \tilde{V}^i = 
+	\begin{cases}
+		\tilde{v}^i_j = n_j & \text{if $ j=produced^i$}\\
+		 \tilde{v}^i_j = n_j \times n_{produced^i} & \text{else}
+	\end{cases}\label{eq:optimum}
+\end{equation}
+
+If such prices are reached, given the exchange rules defined in (\ref{eq:trade}) and the exchange constraints (\ref{eq:constraintFirst}) to (\ref{eq:constraintLast}) all exchanges will be optimally achieved, leading to a total score $S$ for each agent of the population :
 $$ S = \sum_{i=0}^{CulturalStep}  s^i(\tilde{Q}^i) \times ngoods $$ 
@@
 	\end{center}
-	\caption{Evolution of the difference $\dfrac{p(g_w)}{p(g_p)}-n(g_p)$ where $p(x_i)$ is the price for a good $i$, $n(x_i)$ its need, $g$ the produced good and $w$ the wanted}
+	\caption{Evolution of the mean difference for each good of the estimated value $v_g$ and its optimal value as given by \ref{eq:optimum}. Means computed for 100 run adn 2 goods. }
 	\label{fig:ratioEvol}
@@
 	\begin{center}
-		\includegraphics[width=7cm]{img/suboptimal.png}
+		\includegraphics[width=7cm]{img/evolutionGlobalScoreG4N800.pdf}
 	\end{center}
-	\caption{Evolution of the Score for the three types of agents of the simulation}
+	\caption{Evolution of global score for a run with 800 agents and 4 goods.}
+	\label{fig:G4N500}
+\end{figure}
+
+\begin{figure}[htp]
+	\begin{center}
+		\includegraphics[width=7cm]{img/scatterPlotGood1.pdf}
+		\includegraphics[width=7cm]{img/scatterPlotGood2.pdf}
+		\includegraphics[width=7cm]{img/scatterPlotGood3.pdf}
+		\includegraphics[width=7cm]{img/scatterPlotGood4.pdf}
+	\end{center}
+	\caption{Evolution of the Score for the four types of agents of a simulation with 4 differents good and 800 agents}
 	\label{fig:suboptimal}
@@
 It always works better to me when you have this kind of data; also, I would provide a figure for each type of score.}
+\simon{What do you mean by ``a given alpha''? does something like those new ones is better?}
 

### 2015-04-04 article.tex
update some graph
reorganise following comments of xavi. correct text in model, experimental setup, most of results and a bit in ccl/discussion. Left mainly the correction in state of the art on models trade

@@
 \usepackage{booktabs}
+ \usepackage{multirow}
 
@@
 
+\jm{to integrate}
+Ultimately, we aim to create a model to study the relation between cultural change and trade networks within the Roman Empire.
+Examples of questions that could be asked to our model are: What is the relation between distances in the trade network and cultural changes ?
+Did anti-conformism promote the adaptation of new products coming from remote provinces ?
+In order to answer these questions the model used has to take into account both cultural effects and trade influence.
+More precisely, the variations in these two aspects should be modelled and should influence each other.
+Therefore, in order to answer the questions targeted we need a co-evolutionary model able to take into account both trade and cultural changes.
+
+To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture~\cite{bentley_specialisation_2005,macmillan_agent-based_2008}.
+The first proposes a relatively simple model which is limited by 2 products, a fixed behaviour of the agents and a limited variation of cultural mechanisms.
+The second proposes a more complete model including a large number of goods (certain being essential and the others non-essential), but suffer from a greater complexity and the absence of the notion of trade networks.
+Moreover, these works do not compare the dynamics obtained to the previous studies on cultural change and trading mechanisms.
+
+The model presented in this work aims to offer a framework for the co-evolution of culture and trades which relies on a low number of parameters.
+It is not within the scope of this article to answer the questions asked at the beginning of this section as they require specific implementations of the model proposed.
+However, the article will focus on the presentation of the framework, its justification and more importantly its validation by reproducing previous results obtained on cultural change and trade mechanisms.
+
 %Organisation of the paper
@@
 
-Among the various works done with this objective, few are studying the interactions between economy and cultural change in the Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
-An analysis based on historical documents has revealed the importance of economical and social institutions for the efficiency of trades of grains in the early Roman Empire~\cite{kessler_organization_2007}.
-The same type of analysis has also revealed the importance of a number of key factors (such as commercial development, population growth and geographical mobility) for the growth of income and population in the Roman Italy~\cite{scheidel_model_2007}.
-Finally, a micro-economic model has determined the importance of reputation and threat of expulsion from a trade network as mechanisms to maintain the overall efficiency of the trade network~\cite{terpstra_trade_2011}.
-These works therefore reveal the strong relation between trade and cultural change in the Roman empire.
-
-\xrc{I would move this discussion to the coevolution section?
-Besides, I would ass something such as "a large percentage of datasets used for this purpose are material objects found in archaeological contexts (i.e.
-pottery).
-Most of them are usually represented following a neutral model, but how this affects its weight inside the market system?"}
-
 However, a limitation of the previous works is the impossibility to test the conclusions reached by the authors.
@@
 
+\jm{to integrate}
+Among the various works done with this objective, few are studying the interactions between economy and cultural change in the Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
+An analysis based on historical documents has revealed the importance of economical and social institutions for the efficiency of trades of grains in the early Roman Empire~\cite{kessler_organization_2007}.
+The same type of analysis has also revealed the importance of a number of key factors (such as commercial development, population growth and geographical mobility) for the growth of income and population in the Roman Italy~\cite{scheidel_model_2007}.
+Finally, a micro-economic model has determined the importance of reputation and threat of expulsion from a trade network as mechanisms to maintain the overall efficiency of the trade network~\cite{terpstra_trade_2011}.
+These works therefore reveal the strong relation between trade and cultural change in the Roman empire.
+\xrc{I would move this discussion to the coevolution section?
+Besides, I would ask something such as "a large percentage of datasets used for this purpose are material objects found in archaeological contexts (i.e.
+pottery).
+Most of them are usually represented following a neutral model, but how this affects its weight inside the market system?"}
+
 %kobti 2012 la meme que kobti 2006 ?
@@
 
-\subsection{Models of Trade and Culture}
-
-\jm{tried a justification of co-evolutionary framework but I find it too light. ideas ?}
-
-\xrc{What if we move the text to the intro and remove this subsection?}
-
-Ultimately, we aim to create a model to study the relation between cultural change and trade networks within the Roman Empire.
-Examples of questions that could be asked to our model are: What is the relation between distances in the trade network and cultural changes ?
-Did anti-conformism promote the adaptation of new products coming from remote provinces ?
-In order to answer these questions the model used has to take into account both cultural effects and trade influence.
-More precisely, the variations in these two aspects should be modelled and should influence each other.
-Therefore, in order to answer the questions targeted we need a co-evolutionary model able to take into account both trade and cultural changes.
-
-To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture~\cite{bentley_specialisation_2005,macmillan_agent-based_2008}.
-The first proposes a relatively simple model which is limited by 2 products, a fixed behaviour of the agents and a limited variation of cultural mechanisms.
-The second proposes a more complete model including a large number of goods (certain being essential and the others non-essential), but suffer from a greater complexity and the absence of the notion of trade networks.
-Moreover, these works do not compare the dynamics obtained to the previous studies on cultural change and trading mechanisms.
-
-The model presented in this work aims to offer a framework for the co-evolution of culture and trades which relies on a low number of parameters.
-It is not within the scope of this article to answer the questions asked at the beginning of this section as they require specific implementations of the model proposed.
-However, the article will focus on the presentation of the framework, its justification and more importantly its validation by reproducing previous results obtained on cultural change and trade mechanisms.
-
 \section{MODEL DESCRIPTION}
 
-The model proposed is a Multi-Agent Based model including agents and products.
-It revolves around the value that agents associate to products through cultural change mechanisms, trade mechanisms or both.
+The model proposed is a Multi-Agent Based model based on agents and goods.
+The interactions between agents and goods are modelled thanks to the four processes (production, cultural transmission, innovation and trade) which will be explained in further details later.
+The flexibility of the models comes from the possibility to implement these processes differently depending on the hypothesis tested.
+However, since all experiments are performed with the same four processes, the effect of the various implementations of one process can be studied easily.
+Moreover, the operating of the model revolves around the value that agents associate to products.
 Depending on the question studied, the value can reflect the interest of the agent for the good or it can be the price at which the agent evaluate this good.
-The agents are also endowed with limited storage abilities for each good that can be produced.
+Since this vector is common to all experiments performed with this model, it is extremely useful for the comparisons of results obtained with different implementation of the key processes.
 
 \xrc{This first paragraph should briefly explain the trade component?}
+
+\subsection{Overview of the model}
 
@@
 
-On top of these elements three processes are included : \textit{production}, \textit{imitation} and \textit{innovation}.
-The \textit{production} process describe the creation of goods by the agent.
+On top of these elements four processes are used: \emph{production}, \emph{cultural transmission}, \emph{innovation} and \emph{trade}.
+The \textit{production} process describes the creation of goods by the agent.
 Once a good is produced by an agent $i$ it is added its quantity vector ($Q^i$).
-Within the \textit{imitation} process an agent $i$ can copy the value vector ($V^j$) of an agent $j$, where $j \neq i$.
-Finally, the \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{imitation} process in that the modification is done without reference to the other agents.
-
-\xrc{I would use cultural transmission instead of imitation?}
+The \emph{trade} process models the exchange of goods between the agents which results in a modification of the quantity vectors ($Q^i$).
+The amount of goods exchanged is computed by the agents concerned by the trade, within the \emph{trade} process, based on their value vectors ($V^i$).
+Within the \textit{cultural transmission} process an agent $i$ can copy the value vector ($V^j$) of an agent $j$, where $j \neq i$.
+The \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{cultrual transmission} process in that the modification is done without reference to the other agents.
+Finally, .
 
@@
 The first goal is to be able to implement and compare various cultural transmission mechanisms as well as trade mechanisms within the same framework.
-We argue that this is possible in our framework by modifying only the three key processes i.e.
-production, imitation and innovation.
+We argue that this is possible in our framework by modifying only these four key processes i.e.
+production, trade, imitation and innovation.
 Moreover, thanks to the use of a unique $V^i$ vector, it is possible to compare the outcomes of different combinations of production, imitation and innovation mechanisms.
 The second goal is to produce a model composed of a low number of parameter.
-Our model is composed of only three processes and two vectors which is significantly less complex than previous models.
+Our model is composed of only four processes and two vectors which is significantly less complex than previous models.
 
-\xrc{how do agents trade?}
+The scheduling of the four processes (production, trade, cultural transmission and innovation) is described in algorithm~\ref{algo:complete} along with the vectors modified by each of these processes.
+Between line 2 and 7 all agents of the population are initialised with empty quantity vectors and random values.
+Between the lines 11 and 19 is presented the part of the pseudo-code describing the instructions that will be repeated for each iteration of the simulation.
+\jm{what about saying that we just count the iterations at the ``imitation, innovation step" ?}
+\xrc{It should be justified (market is faster than cultural change?)}
+One can note that the trading process is performed at every iteration while the imitation and innovation processes are executed only every $CulturalStep$.
+The idea behind this is to perform the imitation based on a score that reflects the performance of the agent and not only one lucky or unlucky trading round.
 
-\section{EXPERIMENTAL SETUP}
+\begin{algorithm}
+\caption{Model}
+\label{algo:complete}
+	\begin{algorithmic}[1]
+	\scriptsize
+	\State INITIALIZATION: 
+		\For{$j \in Goods$}
+			\For{$i \in \#Pop/\#Goods$} \Comment{Initialize the agent with no products and a random value vector}
+				\State $Q^i = (0, \cdots, 0)$
+				\State $V^i = (v^i_0, \cdots, v^i_n)$ \Comment{The values of $v^i_j$ are selected randomly}
+			\EndFor
+		\EndFor
 
-\xrc{Not sure about the name...the sections below are describing the model so why are they in different section?}
+	\State SIMULATION:
+		\Loop{$~step \in TimeSteps$}
+			\For{$i \in Pop$}
+				\State $Production(Q^i)$
+				\For{$j \in Pop$}
+					\State $TradeProcess(V^i,Q^i,V^j,Q^j)$
+				\EndFor				
+				\If{$ (step \mod CulturalStep) = 0$}	
+					\State $CulturalTransmission(V)$
+					\State $Innovation(V^i)$
+				\EndIf
+			\EndFor
+		\EndLoop
+\end{algorithmic}
+\end{algorithm}
 
@@
 We then show that it is possible to transform our model to fit processes that are economically sound.
-In the following, we present the two set of implementations of the three core processes (production, imitation and innovation) that were used in our experiments.
+To achieve these two goals, we have design for each one specific set of implementations of the four core processes (production, imitation and innovation).
 
-\subsection{Cultural Transmission}
+\subsection{Cultural Transmission}\label{sec:culturalTrans}
 
-The first mechanism of the model aims at reproducing a scenario of unbiased transmission, where each product is a cultural trait without intrinsic positive or negative weight \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
-Under this hypothesis, the process of \emph{production} is not relevant, and as a consequence, it does not modify the content of the quantity vector of the agents.
+The first set of implementations is designed to reproduce a scenario of unbiased transmission, where each product is a cultural trait without intrinsic positive or negative weight \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
+Under this hypothesis, the processes of \emph{production} and \emph{trade} are not relevant, and as a consequence, they do not modify the content of the quantity vectors of the agents.
 
@@
 This distribution is characterized by a small number of very frequent traits and a large number of very rare traits.
-Since this hypothesis has been verified in previous works implementing similar \emph{imitation} and \emph{innovation} mechanisms, we expect in this work the observation of a similar ``power law' distribution.
-
-\xrc{I would remove the previous sentence: it is obvious that it works right?}
-
-More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$, where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable.
+%Since this hypothesis has been verified in previous works implementing similar \emph{imitation} and \emph{innovation} mechanisms, we expect in this work the observation of a similar ``power law' distribution.
+More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$, where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
 
@@
 We are interested in the exchange of products between agents when they can modify the prices at which they sell and buy products.
-We want to implement simple processes leading to the convergence of prices to values acceptable by all agents.
-
-\xrc{What do you mean by convergence? Equilibrium?}
+We want to implement simple processes leading to the convergence of all prices to values acceptable by all agents, i.e.
+we would like to observe, at the end of an experiment, all the agents using the same set of prices which allow them to trade efficiently.
 
 \paragraph{Production}
-In this set of implementations, each agent is producing only one type of good. The type good produced by an agent is assigned to it at the beginning of the simulation and does not change.
+In this set of implementations, each agent is producing only one type of good.
+The type good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
 
-\paragraph{Imitation}
-Within this set of implementations, the key ideas behind the imitation mechanism is to copy the agents which are the best at trading.
-To do so, the imitation mechanism used takes into account the value vector of the other agents and relies on two new notions: \emph{need} and \emph{score}.
+\paragraph{Cultural transmission}
+Within this set of implementations, the cultural transmission process is not random but biased toward the agents which are the best at trading, and is therefore termed ``success bias''.
+To achieve this bias, the cultural transmission mechanism used takes into account the value vector of the other agents and relies on two new notions: \emph{need} and \emph{score}.
 
@@
 
-This function ensures that each good count for the same proportion \xrc{weight?} in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
-The values of $s^i$ obtained for different need values are depicted in figure~\ref{fig:fit}.
+This function ensures that each good has the same weight in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
 
@@
 \end{figure}
-We can see in the figure~\ref{fig:fit} the score with regards to the quantity of one good traded by an agent and that given different value for the need of its good.
-We can see that even if the need for a good is small (for instance when $need = .01$) one can have a high score as soon as he manage to get a quantity closed to the needed quantity.
-It insure that one need to have all of each good in the good proportion and that none could reach a better score just managing to get the right amount of a good with a high need.
+The figure~\ref{fig:fit} depicts the score of an agent, for different need value of one good, with regards to the quantity of the good possessed by the agent.
+We can see that even if the need for a good is small (for instance when $need(x) = .01$) an agent can have a high score as soon as it manages to get a quantity close to the need.
+This insures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.
 
@@
 
-\xrc{so no random copy? It should be clear that agents copy values based on random copy, and copy strategy based on payoff biased transmission (if i'm not mistaken).}
-
 \paragraph{Trading} 
-
-On top of producing goods, the agents have the ability to exchange them.
-During the trading phase \xrc{we should explain the phases of the model before mentioning the trading phase} the value associated to a good by an agent corresponds to the subjective price of the good for this agent.
+During the trading phase the value associated to a good by an agent corresponds to the subjective price of the good for this agent.
 Briefly summarised, for each good that it does not produce, an agent will trade with the first parter that offer an acceptable trade, i.e.
@@
 
-The trading process is performed at every iteration while the imitation and innovation processes are executed only every $CulturalStep$.
-The idea behind this is to perform the imitation based on a score that reflects the performance of the agent and not only one lucky or unlucky trading round.
-
-\xrc{Add some 'scheduling' definition where this is shown. Also it should be justified (market is faster than cultural change?)}
-
 \paragraph{Innovation} In a trading environment it seems unlikely that a price will change radically to a very different value.
@@
 
-\todo{complete the equation}
-
-With such a setup and given (\ref{eq:score}) and (\ref{eq:trade}), it is expected that the prices will converge to value allowing each agent to obtain quantities of resources exactly equivalent to the needs.
+Based on the set of implementations presented and given the equations (\ref{eq:score}) and (\ref{eq:trade}), it is expected that the prices will converge to value allowing each agent to obtain quantities of resources exactly equivalent to the needs.
 The best possible price of all good satisfies the equations :
@@
 
-Which mean that
+Which means that
 
@@
 
-\subsection{Complete model}
+\section{Experimental setup}
+In order to study the cultural transmission and the trading model two sets of implementation of the four processes of our model have been presented.
+Remember that during the definition of these two sets of implementation, two cultural transmission mechanisms have been defined () along with two innovation mechanisms ().
+Therefore, on top of exploring the results offered by the two set of implementations, it would be also interesting to understand which of the process is responsible for the variation in results.
+The four implementations proposed are summarized in the table~\ref{tab:exp}.
+Each couple of innovation/imitation mechanism form one setup that is labelled with one letter.
+Note that the ``neutral model" presented in section~\ref{sec:culturalTrans} corresponds to the setup A, and the trading model presented in section~\ref{sec:trade} corresponds to the setup D.
 
-The model used in these experiments, including the cultural transmission and trading mechanisms, is described in algorithms~\ref{algo:complete}
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ll|cc}
+				&	&\multicolumn{2}{c}{\textbf{Cultural transmission}} \\
+		\multirow{2}[20]{*}{\rotatebox[origin=c]{90}{\textbf{Innovation}}}&  & Random & Success biased \\\hline  
+		& \rule[-0.45cm]{0pt}{1cm} Unbounded 		&A & B \\
+		& \rule[-0.45cm]{0pt}{1cm} Self Referenced	& C & D \\
+	\end{tabular}
+	\caption{Experimental Setup}
+	\label{tab:exp}
+\end{table}
 
-\begin{algorithm}
-\caption{Model}
-\label{algo:complete}
-	\begin{algorithmic}[1]
-	\scriptsize
-	\State INITIALIZATION: 
-		\For{$j \in Goods$}
-			\For{$i \in \#Pop/\#Goods$} \Comment{Initialize the agent for the good it has to produce and a random value vector}
-				\State $produced^i = j$
-				\State $Q^i = (0, \cdots, 0)$
-				\State $V^i = (v^i_0, \cdots, v^i_n)$ \Comment{The values of $v^i_j$ are selected randomly}
-			\EndFor
-		\EndFor
-
-	\State SIMULATION:
-		\Loop{$~step \in TimeSteps$}
-			\For{$i \in Pop$}
-				\State $Production()$
-				\For{$j \in Pop$}
-					\State $TradeProcess(i,j)$
-				\EndFor				
-				\If{$ (step \mod CulturalStep) = 0$}	
-					\State $Imitation()$
-					\State $Innovation()$
-				\EndIf
-			\EndFor
-		\EndLoop
-\end{algorithmic}
-\end{algorithm}
-
-\todo{upload and put an url, complete cite mare nostrum, put nb of hours per run (or the total)}
-All experiments are performed with the Pandora open source framework ~\cite{rubiocampillo_2014}.
-We have make the source code of our project available online~\footnote{put ulr}.
-\xrc{I always put this in the acknowledgements to avoid the technical details while describing the experiments}
-
-All simulations presented are performed in the MareNostrumIII super computer~\cite{}, and took XXXh per run.
-
-\jm{what about saying that we just count the iterations at the ``imitation, innovation step" ?}
-In our experiment one has to take in account that agents modifies their prices or exchange their price only every $culturalStep$ steps.
+For each of the setup 100 runs of 200000 timestep is performed.
+The parameters used are presented in table~\ref{tab:parameters}.
+Finally, remember that in our experiment one has to take in account that agents modifies their prices or exchange their price only every $culturalStep$ steps.
 Between, twos such steps, the agent exchange goods given their own prices.
 Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}.
-
-\todo{put the values in the table}
 
@@
 \midrule
+Number of goods & 4 \\
+Number of agents & 800 \\
 Mutation probability & .004 \\
@@
 
-We first analyse the result obtained in the ``neutral model" as presented in section~\ref{sec:}.
-The figure~\ref{fig:allMutation} presents an analysis of the value vectors obtained across the 100 runs performed with a $\mu$ value equal to XXXX.
-In this graph it is not the exact values that are analysed but their relative frequencies.
+We first analyse the result obtained in the ``neutral model" as presented in section~\ref{sec:culturalTrans} and labelled as setup A in table~\ref{tab:exp}.
+The figure~\ref{fig:allMutation} present the results obtained with $\mu$ varying $\in {.004,.008,.016,.064}$ and two population sizes: 250 and 500 agents.
+The distribution of variants obtained is shown in figure~\ref{fig:allMutation}.
+In this graph the relative frequencies of the values obtained is analysed.
 The y-axis of the graph shows the frequencies of the variants of the vector values, the x-axis shows how many variant achieves such frequencies and the line represents the average of the frequencies obtained across all runs.
-Both axes are in a logarithmic scale
-
-On this graphic one can observe a straight line which shows that a few of the variants are very frequent and a majority of them are not.
-Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
-This line corresponds to the ``power law" distribution mentioned in section~\ref{sec:} and is typical of the result obtained under the ``neutral model".
-
-In order to further validate our model, we perform such study under various $\mu$ values as it has been done in previous works.
-The $\mu$ innovation rates studied vary $\in {.004,.008,.016,.064}$ and two population sizes are studied: 250 and 500 agents.
-The distribution of variants obtained is shown in figure~\ref{fig:allMutation}.
+Both axes are in a logarithmic scale.
 
@@
 	\end{center}
-	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right)}
-	\label{fig:allMutation }
+	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right)\label{fig:allMutation}}
 \end{figure}
 
-\jm{yes say the R package}
+In the figure~\ref{fig:allMutation} one can observe that the lower the mutation rate, the closer from a line the result is.
+This line corresponds to the ``power law" distribution explained in section~\ref{sec:culturalTrans} and is typical of the result obtained under the ``neutral model".
+Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
+
 Under all parameters tested the value vectors exhibit power law like distribution.
 It would then be interesting to analyse the shape of such distribution.
-In order to perform this study a linear regression is used to fit the curve obtained to a function of the form $formul powerlaw$.
+In order to perform this study a linear regression is used to fit the curve obtained to a function of the form $P(v)=C/v^\alpha $.
 The mean value of the $\alpha$ parameters obtained and their standard deviation is presented in table~\ref{tab:mualpha}.
-The computations of the linear regression is done thanks to PACKAGE
 
@@
 
-\subsection{ Economical  process}
+\subsection{Distribution}
 
-In order to study a trading model two new innovation and imitation mechanisms have been introduced as explained in section~\ref{sec:}.
-These mechanisms are summarized in the table~\ref{tab:exp}.
-Each couple of innovation/imitation mechanism form one setup that is labelled with one letter.
-Note that the ``neutral model" studied in the previous section corresponds to the setup A.
-All the runs presented in this section are done for 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.
-
-\todo{add innovation and imitation}
-\begin{table}[h]
-	\centering
-	\begin{tabular}{l|cc}
-					&Imitation  Process \\
-		Innovation Mechanism	& Rand & Success \\\hline  
-		Unbounded 		&A & B \\
-		Self Referenced	& C & D \\
-	\end{tabular}
-	\caption{Experimental Setup}
-	\label{tab:exp}
-\end{table}
-
-\xrc{ok but this is the experiment design right??}
-
-\subsubsection{Distribution}
-
-Our first step is to study the distribution of values in order to compare them to the distribution previous obtained.
-The distribution of values in the 4 setups is presented in figure~\ref{fig:4setDi}.
+In order to understand the effect of the other cultural transmission and innovation mechanisms, we study first the distribution of values obtained in the different setups.
+The distribution of values in the four setups is presented in figure~\ref{fig:4setDi}.
 
@@
 
-\todo{update once all graphs are there}
-\jm{is exponential law characteristic of prestige bias ?}
-
-The results studied in the previous section is reproduce here in the by the setup A, it is therefore no surprise that this setup follow a power law.
+The results studied in the previous section is reproduced here by the line labelled ``setup A''. 
+\jm{this sounds wrong what would be a valid analysis ?}
 We observe that the setup D is also following a power law.
@@
 
-\subsubsection{Score}
+\subsection{Values}
 
-We now study the setup in more detail by investigating the ability of the population of agents to find the good price to perform exchanges between each other.
-This is done by observing the score of all agents in each of the 4 setups.
+We now study the results obtained in more detail by investigating the ability of the population of agents to find the good price to perform exchanges between each other.
+This is done by observing the score of all agents in each of the four setups.
 The results obtained are presented in figure~\ref{tab:scoreEvol}.
@@
 	\begin{tabular}{l c c}
-		& Random Transmission & Eco Transmission \\
-		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForA-G2N250.pdf}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForB-G2N250.pdf}} \\ Setup B} \\
-		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForC-G2N250.pdf}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForD-G3N500.pdf}} \\ Setup D}
+		& Random Transmission & Biased Transmission \\
+		Unbounded & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForA-G2N250.pdf}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForB-G2N250.pdf}} \\ Setup B} \\
+		Self-referenced & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForC-G2N250.pdf}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForD-G3N500.pdf}} \\ Setup D}
 
@@
 
-\todo{simon you have put A and S, I guess it's C and D ?}
-\simon{It's A and C, the setup where their is no selection. But those two graph (A and B) are not good, don't take them in account. }
-\todo{update explanation with new graphs}
-\todo{get clear names for innovation and imitaiton mechanisms}
-
+\todo{redo the explanations nicer} 
 In the setups A and C, the score evolves randomly.
 In the two other setups however the score is increasing.
-Moreover, we observe that the XXXX innovation process used in the setups A and B leads to higher convergences.
-Since only the ``prestige imitation" takes the score into account it is normal that only this mechanism leads higher scores.
-The XXXX innovation mechanism leads to lower convergences as it select prices randomly in the complete range available.
+Moreover, we observe that the Self-referenced innovation process used in the setups C and D leads to higher convergences.
+Since only the ``biased transmission" takes the score into account it is normal that only this mechanism leads higher scores.
+The ``unbounded'' mechanism leads to lower convergences as it select prices randomly in the complete range available.
 
-\subsubsection{Prices}
+\subsection{Prices}
 
 We pursue the analysis of the economical aspect by observing the prices reached in setup D.
-As explained in the section~\ref{sec:} we expect that the trade imitation and innovation processes will produce a convergence toward a set of price for each good that will allow agents to exchange optimally the good they produce with the other goods.
+As explained in the section~\ref{sec:trade} we expect that the trade imitation and innovation processes will produce a convergence toward a set of price for each good that will allow agents to exchange optimally the good they produce with the other goods.
 To verify this assumption we analyse the prices reached.
@@
 
-\subsubsection{Suboptimal markets}
+\subsection{Suboptimal markets}
 
 Finally, a more careful analysis of the price structure reveals the presence of suboptimal markets. 
-In figure~\ref{fig:suboptimal} the price structure of one run of setup C is presented.
+\jm{it was written setup C, it's not setup D?}
+\jm{is it the mean in blue ?}
+In figure~\ref{fig:suboptimal} the price structure of one run of setup D is presented.
 The x-axis represents the number of iteration, the y-axis the prices.
-The green boxplot represents the price of good X for an agent producing Y.
-And the blue boxplot represents the price of good X for agent producince Y
+Each of the four figures represents the score of all agents producing one of the four goods used.
+In blue is presented the mean of the score of the figures.
 
-\begin{figure}[htp]
-	\begin{center}
-		\includegraphics[width=7cm]{img/evolutionGlobalScoreG4N800.pdf}
-	\end{center}
-	\caption{Evolution of global score for a run with 800 agents and 4 goods.}
-	\label{fig:G4N500}
-\end{figure}
+%\begin{figure}[htp]
+%	\begin{center}
+%		\includegraphics[width=7cm]{img/evolutionGlobalScoreG4N800.pdf}
+%	\end{center}
+%	\caption{Evolution of global score for a run with 800 agents and 4 goods.}
+%	\label{fig:G4N500}
+%\end{figure}
+%\begin{figure}[htp]
+%	\begin{center}
+%		\includegraphics[width=7cm]{img/evolutionToClearningPricesG4N800.pdf}
+%	\end{center}
+%	\caption{Evolution of prices for a run with 800 agents and 4 goods.}
+%	\label{fig:G4N500Clearing}
+%\end{figure}
 
@@
 	\end{center}
-	\caption{Evolution of the Score for the four types of agents of a simulation with 4 differents good and 800 agents}
+	\caption{Evolution of the Score for the four types of agents of a simulation with four differents good and 800 agents}
 	\label{fig:suboptimal}
@@
 
-In this graphic we can observe that the product displayed in green is blocked to a non-optimal value until iteration XXXX, and decreasing after.
-The prices for the blue product, on the other side, decrease steadily until the median reaches the uptimum at iteration XXXX.
-This illustrate the complexity of finding the right prices in the market.
-Indeed all prices are strongly linked together and until one has reach its optimum value, the other price can not evolve.
+For the agents producing the goods 1,2 and 3 we observe a long stagnation of the mean score until timestep 750,000.
+Further investigations have revealed that during this period a few of the prices used by the agents are far from the optimal.
+After a relatively long search, the correct prices are finally found and the score of all agents improve.
+This example illustrates well the complexity of finding the right prices in the market.
+This situation is due to the fact that all prices are strongly linked together and until one has reach its optimum value, the other price can not evolve.
+
+\section{DISCUSSION}
+\xrc{what is the model explaining in terms of what was mentioned in the intro?}
+
+\todo{write better}
+In the experiments conducted multiple implementations of the cultural transmission and innovation mechanisms have been proposed.
+Notably, one set of implementation aimed at reproducing trade mechanisms.
+The sections XXXX have shown that this set of implementation is producing results expected from a trade mechanism and therefore that trade is plainly a cultural factor.
+The modifications needed in our framework were relative to the proposition of new imitation and innovation mechanisms which are typical of the study of the cultural transmission.
+This proximity between trade mechanisms and cultural transmission allows for the comparisons of the results obtained.
+For example, it has been possible here to compare the distribution of values obtained and highlight that the divergence from a power law actually is coming mainly from the imitation mechanism used in trade.
+Moreover this imitation mechanism can further be interpreted as a ``prestige bias" imitation already studied in cultural transmission.
 
@@
 When implementing trading mechanisms we observe the convergence of prices to the expected values and the improvement of the scores of the agents.
-
-On top of these results, by the implementation of trade mechanisms as cultural mechanisms, we show that trade is plainly a cultural factor.
-The modifications needed in our framework where relative to the proposition of new imitation and innovation mechanisms which are typical of the study of the cultural transmission.
-This proximity between trade mechanisms and cultural transmission allows for the comparisons of the results obtained.
-For example, it has been possible here to compare the distribution of values obtained and highlight that the divergence from a power law actually is coming mainly from the imitation mechanism used in trade.
-Moreover this imitation mechanism can further be interpreted as a ``prestige bias" imitation already studied in cultural transmission.
-
-\section{DISCUSSION}
-
-\xrc{discussion should go before conclusion.
-Also, this is not a disucussion but some comments on future stuff that could be done: what is the model explaining in terms of what was mentioned in the intro?}
-%The questions we would like to ultimately study are for example: how does the hierarchical structure changes the adoption of a new product ?
-How delays and interruptions in the trade network change the culture of a society ?
 
@@
 
+\todo{upload and put an url, complete cite mare nostrum, put nb of hours per run (or the total)}
+
 Funding for this work was provided by the ERC Advanced Grant EPNet (\todo{look for code}) and the SimulPast Consolider Ingenio project (CSD2010-00034) of the former Ministry for Science and Innovation of the Spanish Government.

### 2015-04-05 article.tex
correction on introduction and state of the art on models. Left discussion and ccl

@@
 As it has been stated before, trades influence cultural transmission by modifying both the goods present in a region and the people consuming these goods.
-On the one side, analysing separately trade and cultural transmission allows to formalize their inner mechanisms and understand their respective dynamics.
-On the other hand, in order to analyse the adoption of goods within a province one must take into account both trading strategy and cultural transmission.
+Certainly, analysing separately trade and cultural transmission allows to formalize their inner mechanisms and understand their respective dynamics.
+However, in order to analyse the adoption of goods within a province one must take into account both trading strategy and cultural transmission.
 For example, the modification of good's consumption after the rupture of a connection in the trade system is better explained by knowing the local adoption of this good (cultural transmission) and the prices of this good (trade).
@@
 %XRC we propose a model of coevolution to explore the deep links between trade and cultural transmission in the ancient Mediterranean
-We propose in this article a framework to study the interaction between cultural transmission and trade.
-This framework should be able first to reproduce well known dynamics of both cultural transmission and trading.
-Second, to be useful, this framework should be able to compare results obtained by taking cultural or trade into consideration.
-In order to build this framework we view trade events as part of the culture.
-The price of a good are then viewed as a cultural trait.
-This traits can be transmitted and modified along different rules.
-By this mean, traditional works previously expressed in a trading framework, can be expressed in a cultural evolution framework.
-Therefore, the dynamics observed on various cultural transmission mechanisms can be straightforwardly compared to dynamics obtained by trading mechanisms.
-In order to demonstrate the feasibility of this approach we propose a minimal implementation able to reproduce both cultural transmission dynamics and trade dynamics.
-Additionally we will analyse the results obtained with tools from both economy and cultural evolution.
-
-\jm{to integrate}
 Ultimately, we aim to create a model to study the relation between cultural change and trade networks within the Roman Empire.
@@
 The model presented in this work aims to offer a framework for the co-evolution of culture and trades which relies on a low number of parameters.
-It is not within the scope of this article to answer the questions asked at the beginning of this section as they require specific implementations of the model proposed.
-However, the article will focus on the presentation of the framework, its justification and more importantly its validation by reproducing previous results obtained on cultural change and trade mechanisms.
+Moreover, to be useful, the framework is developed with the aim to ease the comparison of results obtained when taking cultural or trade into consideration.
+This article will focus on the presentation of the framework, its justification and more importantly its validation by reproducing previous results obtained on cultural change, and the ability to produce trade dynamics.
+The results obtained when studying trade and cultural change are compared with each other.
 
@@
 
-\subsection{Models of Trade}
+\subsection{Models including Trade}
 
@@
 Previous historical and archaeological studies to model trade in the ancient Mediterranean societies have focus on descriptive approaches ~\cite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
-These works have conclude that the Roman economy was a type of market economy where a variety of small tightly connected markets had loose connections between them~\cite{temin_market_2001,temin_economy_2006,wilson_approaches_2009}.
-Based on these conclusions, further works have attempt to define more exactly which type market economy was in use, i.e. was it close to our market economy or remote ?
+These works have conclude that the Roman economy was a type of market economy where a variety of small tightly connected markets had loose connections between them~\cite{temin_market_2001,temin_economy_2006}.
+Based on these conclusions, further works have attempt to define more exactly the characteristics of this market such, e.g.
+level of intervention of the state and its impact, or the relation-ship between local and long-distance trade~\cite{wilson_approaches_2009}.
 
-\xrc{close or remote in terms of what?}
-
-However, a limitation of the previous works is the impossibility to test the conclusions reached by the authors.
-The models proposed reflects only the view of the authors on the data analysed.
-A new type of model would be necessary to go beyond the interpretation, and allow the verification of the conclusions reached.
-These models should be able to generate data which is then qualitatively compared to the real historical data.
-
-\xrc{what data is being used?}
-
-By this mean, if a factor is really important in the economical network, its removal from the model will lead to data qualitatively different from the historical data.
-The Agent Based Models (ABM) methodology offers a way to produce this kind of model~\cite{lake_trends_2014}.
-
-\xrc{I would add a paragraph briefly explaining what is an ABM}
-
-Based on this tool a relatively complex and exact modelisation of the prehispanic Pueblo societies has been proposed~\cite{kohler_modelling_2012}.
-This work offers an ABM integrating numerous effects such as food consumption, production and landscape.
-The questions studied are  numerous and some works are performed on the economical system and its ties with social transmissions~\cite{kobti_emergence_2006,cockburn_simulating_2013}.
-However the work done in this project consider a pre-market society in a specific village which makes it difficult to reach more general conclusions, notably applicable to the Roman Empire.
-
-\xrc{The Pueblo model is an example, but there are tons of other ones...why is this chosen?
-After the paragraph explaining ABM I would say "As an example of its potential, a detailed model of the prehispanic blablabla..."}
-
-\xrc{Didn't Brughmans have a model of roman trade?}
-
-\jm{to integrate}
-Among the various works done with this objective, few are studying the interactions between economy and cultural change in the Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
+Few works have attempt to model the interactions between economy and cultural change in the Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
 An analysis based on historical documents has revealed the importance of economical and social institutions for the efficiency of trades of grains in the early Roman Empire~\cite{kessler_organization_2007}.
@@
 These works therefore reveal the strong relation between trade and cultural change in the Roman empire.
-\xrc{I would move this discussion to the coevolution section?
-Besides, I would ask something such as "a large percentage of datasets used for this purpose are material objects found in archaeological contexts (i.e.
-pottery).
-Most of them are usually represented following a neutral model, but how this affects its weight inside the market system?"}
+However a large percentage of the datasets used for these studies are based on material objects found in archaeological contexts such as pottery.
+Most of these objects are usually represented following a neutral model, but the weight of this model within a market system is not studied.
+
+An additional limitation of the previous works is the impossibility to test the conclusions reached by the authors.
+The models proposed reflects only the view of the authors on the historical and archaeological data analysed.
+A new type of model would be necessary to go beyond the interpretation, and allow the verification of the conclusions reached.
+These models should be able to generate data relative to trade which are then qualitatively compared to results of analysis of archaeological data such as amphorae or other container used to carry goods.
+By this mean, if a factor is really important in the economical network, its removal from the model will lead to data qualitatively different from the historical data.
+
+\todo{check that paragraph}
+The Agent Based Models (ABM) methodology offers a way to produce this kind of model within a computer~\cite{lake_trends_2014}.
+An ABM is composed of a group of agents performing actions within a virtual environment.
+The environment and the behaviour of the agents, despite being an simpler than the real world, are designed to be analogous to their real-world counterpart.
+The experimenter hand designs the agents, the environment and their interaction, and observes the outcome of all interactions through time in order to compare it to the archaelogical data obtained from the real world.
+The goal of the experimenter is therefore to find a plausible set of assumptions used during the creation of the ABM produce results close to what is observed in reality.
+
+A first example of its potential is given through a model of the trade network of tableware in the roman east~\cite{brughmans_roman_2014}.
+Among the parameters tested, preliminary results of this model show that number of links between production site has a strong influence on the results obtained.
+A second more complete example proposes a detailed model of the prehispanic Pueblo societies~\cite{kohler_modelling_2012}.
+This work offers an ABM integrating numerous effects such as food consumption, production and landscape.
+The questions studied are  numerous and some works are performed on the economical system and its ties with social transmissions~\cite{kobti_emergence_2006,cockburn_simulating_2013}.
+However the work done in this project consider a pre-market society in a specific village which makes it difficult to reach more general conclusions, notably applicable to the Roman Empire.
 
@@
 
-The model proposed is a Multi-Agent Based model based on agents and goods.
+The model proposed is an ABM based on agents and goods.
 The interactions between agents and goods are modelled thanks to the four processes (production, cultural transmission, innovation and trade) which will be explained in further details later.

### 2015-04-05 article.tex
check discussion and ccl

@@
 
-\todo{check that paragraph}
 The Agent Based Models (ABM) methodology offers a way to produce this kind of model within a computer~\cite{lake_trends_2014}.
@@
 The experimenter hand designs the agents, the environment and their interaction, and observes the outcome of all interactions through time in order to compare it to the archaelogical data obtained from the real world.
-The goal of the experimenter is therefore to find a plausible set of assumptions used during the creation of the ABM produce results close to what is observed in reality.
+The goal of the experimenter is therefore to find a plausible set of assumptions used during the creation of the ABM to produce results close to what is observed in reality.
 
 A first example of its potential is given through a model of the trade network of tableware in the roman east~\cite{brughmans_roman_2014}.
-Among the parameters tested, preliminary results of this model show that number of links between production site has a strong influence on the results obtained.
+Among the parameters tested, preliminary results of this model, show that the number of links between production site has a strong influence on the results obtained.
 A second more complete example proposes a detailed model of the prehispanic Pueblo societies~\cite{kohler_modelling_2012}.
-This work offers an ABM integrating numerous effects such as food consumption, production and landscape.
+This project proposes an ABM integrating numerous effects such as food consumption, production and landscape.
 The questions studied are  numerous and some works are performed on the economical system and its ties with social transmissions~\cite{kobti_emergence_2006,cockburn_simulating_2013}.
@@
 
-\begin{table}[h]
-	\centering
-	\begin{tabular}{lcccc}
-		& A & B & C & D\\
-A & X& \includegraphics[width=5cm]{img/A-B.pdf}&\includegraphics[width=5cm]{img/A-C.pdf}&\includegraphics[width=5cm]{img/A-D.pdf}\\
-B & X& X &\includegraphics[width=5cm]{img/B-C.pdf}&\includegraphics[width=5cm]{img/B-D.pdf}\\
-C & X& X & X &\includegraphics[width=5cm]{img/C-D.pdf}\\
-	\end{tabular}
-	\caption{Experimental Setup}
-	\label{tab:allRes}
-\end{table}
+%\begin{table}[h]
+%	\centering
+%	\begin{tabular}{lcccc}
+%		& A & B & C & D\\
+%A & X& \includegraphics[width=5cm]{img/A-B.pdf}&\includegraphics[width=5cm]{img/A-C.pdf}&\includegraphics[width=5cm]{img/A-D.pdf}\\
+%B & X& X &\includegraphics[width=5cm]{img/B-C.pdf}&\includegraphics[width=5cm]{img/B-D.pdf}\\
+%C & X& X & X &\includegraphics[width=5cm]{img/C-D.pdf}\\
+%	\end{tabular}
+%	\caption{Experimental Setup}
+%	\label{tab:allRes}
+%\end{table}
 
@@
 \section{DISCUSSION}
-\xrc{what is the model explaining in terms of what was mentioned in the intro?}
 
-\todo{write better}
-In the experiments conducted multiple implementations of the cultural transmission and innovation mechanisms have been proposed.
-Notably, one set of implementation aimed at reproducing trade mechanisms.
-The sections XXXX have shown that this set of implementation is producing results expected from a trade mechanism and therefore that trade is plainly a cultural factor.
-The modifications needed in our framework were relative to the proposition of new imitation and innovation mechanisms which are typical of the study of the cultural transmission.
-This proximity between trade mechanisms and cultural transmission allows for the comparisons of the results obtained.
-For example, it has been possible here to compare the distribution of values obtained and highlight that the divergence from a power law actually is coming mainly from the imitation mechanism used in trade.
-Moreover this imitation mechanism can further be interpreted as a ``prestige bias" imitation already studied in cultural transmission.
+In this paper, and thanks to the model developed, we have shown that it is the possible to implement trade mechanisms within a cultural evolutionary framework.
+In the end, it appears that the key aspects of trade are just different implementations of the key elements of cultural evolutionary framework, i.e.
+cultural transmission and innovation.
+Moreover, we have ensure that such an implementation is valid in the sense that it leads the prices of goods to converges to the values expected under economical theories.
+This aspect which has not been studied before, opens a new line of thinking on the weight of trade mechanisms within cultural change.
+
+Within this line of thought, we have shown that the implementation of trade mechanisms as cultural transmission and innovation mechanisms leads to results departing from the neutral hypothesis largely studied to understand cultural changes.
+Interesting additional work could be, for example, the comparison between trade mechanisms and prestige biased cultural transmission.
 

### 2015-04-06 article.tex
minor modifications to intro and ccl

@@
 %XRC this process played a role in the trajectories of cultural change of the different regions, which were interconnected by trade
-The trade possibilities between provinces modify the transmission of culture within each province and between them.
-The influence can comes from two main sources.
-First, when a new connection is made between two provinces, new products can arrive in their respective markets.
-The arrival of new goods naturally changes the rate of adoption of every goods of the market CITE.
-Moreover, the arrival of new products can lead to their recombination with previous products and therefore the creation of an new item.
-This further modify the structure of the market of the province.
-Second, persons are also travelling on the roads of the trade network, each carrying its own culture.
+Trade roads between provinces generates cultural changes due to two main effects.
+First, when a new connection is made between two provinces, new goods can arrive in their respective markets.
+The arrival of new goods naturally changes the rate of adoption of all the goods of the market CITE.
+Moreover, a good recently introduced in a province can be recombined with previous goods in order to create yet a new type of good, which further modify the structure of the market of the province.
+The second element affecting the change of culture within a province is due to the persons travelling on the roads of the trade network, each carrying its own culture.
 Large movements of populations may lead to changes in the cultures.
-For example, when Roman soldiers were stationing in a province, Roman products such as olive oil were delivered to that province CITE ROMAN DELIVERING OIL.
-This can lead to the adoption of olive oil in regions that were originally not using it.
+For example, when Roman soldiers were stationing in a province, Roman products such as olive oil were delivered to that province CITE ROMAN DELIVERING OIL, which may have lead to the adoption of olive oil in regions that were originally not using it.
 
 %XRC these two elements (cultural transmission and trade networks) are traditionally been studied as isolated systems.
-Traditionally cultural transmission and trade are studied distinctively.
-On the one hand, the cultural transmission mechanisms studied do not take economical consideration into accounts.
-The works done are interested in the adoption of various cultural trait without taking into consideration their economical value.
-On the other hand, trading behaviours are studied within their own framework which are designed to measure the amount of goods exchanged and the value at which they are exchanged.
-Within these frameworks the cultural transmission between persons is not present.
-
+Usually, the studies on cultural change mechanisms focus on the adoption of cultural goods such as pottery by a population.
+However, these studies do not take into account economical factors, such as the cost of production or acquisition of the goods.
+Moreover, the effect that trade may have on the frequency of goods in the population or in neighbourhood populations is not analysed.
+A dedicated research field studies the effect of trade mechanisms on the change of prices and the modification of goods repartition in the population.
+This field relies on a specific set of framework which do not take into account the results obtained on the study of cultural change mechanisms.
+Certainly, this division in the analysis of cultural change and trade and cultural transmission allows for a precise formalization of their inner mechanisms and therefore a good understanding of their respective dynamics.
 %XRC this is wrong because blablabla
-As it has been stated before, trades influence cultural transmission by modifying both the goods present in a region and the people consuming these goods.
-Certainly, analysing separately trade and cultural transmission allows to formalize their inner mechanisms and understand their respective dynamics.
-However, in order to analyse the adoption of goods within a province one must take into account both trading strategy and cultural transmission.
-For example, the modification of good's consumption after the rupture of a connection in the trade system is better explained by knowing the local adoption of this good (cultural transmission) and the prices of this good (trade).
+However, as it has been shown before, trades influence cultural change by modifying both the goods present in a region and the people consuming these goods.
+Therefore, in order to analyse the adoption of goods within a province one must take into account both trading strategy and cultural transmission.
+For example, the modification of good's consumption after the rupture of a connection in the trade system is better explained by knowing the local adoption of this good (cultural change) and the prices of this good (trade).
 
@@
 Did anti-conformism promote the adaptation of new products coming from remote provinces ?
-In order to answer these questions the model used has to take into account both cultural effects and trade influence.
+In order to answer these questions the model developed has to take into account both cultural effects and trade influence.
 More precisely, the variations in these two aspects should be modelled and should influence each other.
@@
 
-The model presented in this work aims to offer a framework for the co-evolution of culture and trades which relies on a low number of parameters.
-Moreover, to be useful, the framework is developed with the aim to ease the comparison of results obtained when taking cultural or trade into consideration.
+Therefore, in this work, we aim for the development of a framework to study the co-evolution of culture and trades which relies on a low number of parameters.
+The idea behind the development of such framework is to ease the comparison of different cultural change and trade mechanisms, which means that the framework should be flexible enough to allow for the implementation of both type of mechanisms and with enough structural elements to allow the comparison of various implementations.
 This article will focus on the presentation of the framework, its justification and more importantly its validation by reproducing previous results obtained on cultural change, and the ability to produce trade dynamics.
@@
 
-This article has propose a framework to study both cultural transmission mechanisms and trade mechanisms.
-Our framework is based on a central element, the value vector, which is interpreted differently depending on the mechanisms studied.
+This article has proposed a framework to study both cultural change mechanisms and trade mechanisms.
+The development of our framework was first aimed at simplicity which is achieved by the use of two vectors (quantity and value) and four processes (production, trade, cultural transmission and innovation).
+The second aim of the work conducted was to obtain a flexible framework which is possible since each of the processes can be implemented accordingly to the question studied.
 We have shown the validity of this approach by reproducing expected results on both the cultural and trade side.
-On the cultural transmission side we have shown that the implementation of the ``neutral model" leads to the expected observations on the variants of the vector value: a power law.
+On the cultural transmission side we have shown that the implementation of a ``neutral model" leads to the expected observations on the variants of the vector value: a power law.
 When implementing trading mechanisms we observe the convergence of prices to the expected values and the improvement of the scores of the agents.

### 2015-04-06 article.tex
small fixes

@@
 The first aspect of our model is focused on the dynamics of cultural change.
-They comprise the collection of processes that promotes or inhibits the spread of information by social interaction within a population \cite[3]{boyd_origin_2005}.
-An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution \cite{henrich_evolution_2003}.
-Archaeology has a rich tradition of evolutionary studies \cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution \cite{burger_absence_2007}, diffusion processes \cite{fort_synthesis_2012}, phylogenetic analysis of material culture \cite{obrien_cladistics_2001} or detection of rates of change in the archaeological record \cite{premo_cultural_2014}.
+They comprise the collection of processes that promotes or inhibits the spread of information by social interaction within a population~\cite[3]{boyd_origin_2005}.
+An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution~\cite{henrich_evolution_2003}.
+Archaeology has a rich tradition of evolutionary studies~\cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution~\cite{burger_absence_2007}, diffusion processes~\cite{fort_synthesis_2012}, phylogenetic analysis of material culture~\cite{obrien_cladistics_2001} or detection of rates of change in the archaeological record~\cite{premo_cultural_2014}.
 
@@
 conformism and anti-conformism).
-These analysis are often based on the theory of neutral evolution \cite{neiman_stylistic_1995}, which explains variation in the distribution of traits as a function of their frequency distribution in the population.
+These analysis are often based on the theory of neutral evolution~\cite{neiman_stylistic_1995}, which explains variation in the distribution of traits as a function of their frequency distribution in the population.
 Thus, a trait is assumed to lack any selective bias and its transmission will depend on its popularity amongst the rest of individuals.
 The comparison of a given frequency distribution found in data against this unbiased transmission model is traditionally used as a null-hypothesis testing for selection.
-There exist a large number of works using this approach as the starting point to analyse patterns of cultural change in past societies \cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
+There exist a large number of works using this approach as the starting point to analyse patterns of cultural change in past societies~\cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
-Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism \cite{bentley_random_2004}.
+Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism~\cite{bentley_random_2004}.
 Within this framework, an individual will copy the traits of a randomly chosen individual with a given probability.
@@
 The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
-This basic model can be enriched by several additional processes both in the innovation \cite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission \cite{heyes_social_1994,henrich_evolution_2003}.
+This basic model can be enriched by several additional processes both in the innovation~\cite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmissio~\cite{heyes_social_1994,henrich_evolution_2003}.
 
@@
 
-Previous historical and archaeological studies to model trade in the ancient Mediterranean societies have focus on descriptive approaches ~\cite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
+Previous historical and archaeological studies to model trade in the ancient Mediterranean societies have focus on descriptive approaches~\cite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
 These works have conclude that the Roman economy was a type of market economy where a variety of small tightly connected markets had loose connections between them~\cite{temin_market_2001,temin_economy_2006}.
@@
 
-The model proposed is an ABM based on agents and goods.
-The interactions between agents and goods are modelled thanks to the four processes (production, cultural transmission, innovation and trade) which will be explained in further details later.
+To explore this coevolution between trade and cultural change we have developed an ABM where the different agents trade goods with variable prices.
+
+\xrc{we can totally remove this paragraph and move the entire next subsection here:\\
+These dynamics are modelled after processes (production, cultural transmission, innovation and trade) which will be explained in further details later.
 The flexibility of the models comes from the possibility to implement these processes differently depending on the hypothesis tested.
@@
 Depending on the question studied, the value can reflect the interest of the agent for the good or it can be the price at which the agent evaluate this good.
-Since this vector is common to all experiments performed with this model, it is extremely useful for the comparisons of results obtained with different implementation of the key processes.
+Since this vector is common to all experiments performed with this model, it is extremely useful for the comparisons of results obtained with different implementation of the key processes.}
 
@@
 
-More formally the model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$. The first corresponds to the quantity of each good that the agent $i$ possesses: 
+The model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$. The first corresponds to the quantity of each good that the agent $i$ possesses: 
 $$\forall i \in Pop, \quad Q^i = (q^i_1,\cdots,q^i_n) $$
@@
 
-This scheme allow us to have a model achieving the two main goals listed in section~\ref{sec:intro}.
+This scheme achieves the two main goals listed in section~\ref{sec:intro}.
 The first goal is to be able to implement and compare various cultural transmission mechanisms as well as trade mechanisms within the same framework.
@@
 Our model is composed of only four processes and two vectors which is significantly less complex than previous models.
+
+\xrc{I would remove the previous paragraph, because it is implied that we want few parameters and compare mechanisms}
 
@@
 The figure~\ref{fig:fit} depicts the score of an agent, for different need value of one good, with regards to the quantity of the good possessed by the agent.
-We can see that even if the need for a good is small (for instance when $need(x) = .01$) an agent can have a high score as soon as it manages to get a quantity close to the need.
+We can see that even if the need for a good is small (for instance when $need(x) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need.
 This insures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.
@@
 
-Once de quantities are defined, the agents declare that the trade is possible if :
+Once the quantities are defined, the agents declare that the trade is possible if :
 \begin{align}
@@
 
-The conditions \ref{eq:constraintFirst}-\ref{eq:constraintLastInv} insure that both agents have enough goods in their inventory to realise the trade and the conditions \ref{eq:constraintFirstWill}-\ref{eq:constraintLast} insure that the quantities of each good fit the will of both agents.
+The conditions \ref{eq:constraintFirst}-\ref{eq:constraintLastInv} insure that both agents have enough goods in their inventory to realise the trade while the conditions \ref{eq:constraintFirstWill}-\ref{eq:constraintLast} insure that the quantities of each good fit the will of both agents.
 
@@
 
-Funding for this work was provided by the ERC Advanced Grant EPNet (\todo{look for code}) and the SimulPast Consolider Ingenio project (CSD2010-00034) of the former Ministry for Science and Innovation of the Spanish Government.
+Funding for this work was provided by the ERC Advanced Grant EPNet (340828) and the SimulPast Consolider Ingenio project (CSD2010-00034) of the former Ministry for Science and Innovation of the Spanish Government.
 

### 2015-04-06 article.tex
added et al.

@@
 Trades are being increasingly recognised as a key process in the structure of ancient Mediterranean societies.
-For example, the use of table ware in the Roman empire  has been linked to the trade network~\cite{brughmans_connecting_2010}.
-Interestingly this trade network has been shown to be a market economy~\cite{temin_market_2001}.
+For example, the use of table ware in the Roman empire  has been linked to the trade network~\shortcite{brughmans_connecting_2010}.
+Interestingly this trade network has been shown to be a market economy~\shortcite{temin_market_2001}.
 The work presented in this paper proposes a framework to further study the relation between trade and culture within the roman empire.
-This work takes place within the EPNET project~\cite{remesal_epnet_2014}.
+This work takes place within the EPNET project~\shortcite{remesal_epnet_2014}.
 
@@
 
-To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture~\cite{bentley_specialisation_2005,macmillan_agent-based_2008}.
+To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture~\shortcite{bentley_specialisation_2005,macmillan_agent-based_2008}.
 The first proposes a relatively simple model which is limited by 2 products, a fixed behaviour of the agents and a limited variation of cultural mechanisms.
@@
 The first aspect of our model is focused on the dynamics of cultural change.
-They comprise the collection of processes that promotes or inhibits the spread of information by social interaction within a population~\cite[3]{boyd_origin_2005}.
-An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution~\cite{henrich_evolution_2003}.
-Archaeology has a rich tradition of evolutionary studies~\cite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution~\cite{burger_absence_2007}, diffusion processes~\cite{fort_synthesis_2012}, phylogenetic analysis of material culture~\cite{obrien_cladistics_2001} or detection of rates of change in the archaeological record~\cite{premo_cultural_2014}.
+They comprise the collection of processes that promotes or inhibits the spread of information by social interaction within a population~\shortcite[3]{boyd_origin_2005}.
+An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution~\shortcite{henrich_evolution_2003}.
+Archaeology has a rich tradition of evolutionary studies~\shortcite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution~\shortcite{burger_absence_2007}, diffusion processes~\shortcite{fort_synthesis_2012}, phylogenetic analysis of material culture~\shortcite{obrien_cladistics_2001} or detection of rates of change in the archaeological record~\shortcite{premo_cultural_2014}.
 
@@
 conformism and anti-conformism).
-These analysis are often based on the theory of neutral evolution~\cite{neiman_stylistic_1995}, which explains variation in the distribution of traits as a function of their frequency distribution in the population.
+These analysis are often based on the theory of neutral evolution~\shortcite{neiman_stylistic_1995}, which explains variation in the distribution of traits as a function of their frequency distribution in the population.
 Thus, a trait is assumed to lack any selective bias and its transmission will depend on its popularity amongst the rest of individuals.
 The comparison of a given frequency distribution found in data against this unbiased transmission model is traditionally used as a null-hypothesis testing for selection.
-There exist a large number of works using this approach as the starting point to analyse patterns of cultural change in past societies~\cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
+There exist a large number of works using this approach as the starting point to analyse patterns of cultural change in past societies~\shortcite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
-Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism~\cite{bentley_random_2004}.
+Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism~\shortcite{bentley_random_2004}.
 Within this framework, an individual will copy the traits of a randomly chosen individual with a given probability.
@@
 The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
-This basic model can be enriched by several additional processes both in the innovation~\cite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmissio~\cite{heyes_social_1994,henrich_evolution_2003}.
+This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmissio~\shortcite{heyes_social_1994,henrich_evolution_2003}.
 
@@
 
-Previous historical and archaeological studies to model trade in the ancient Mediterranean societies have focus on descriptive approaches~\cite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
-These works have conclude that the Roman economy was a type of market economy where a variety of small tightly connected markets had loose connections between them~\cite{temin_market_2001,temin_economy_2006}.
+Previous historical and archaeological studies to model trade in the ancient Mediterranean societies have focus on descriptive approaches~\shortcite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
+These works have conclude that the Roman economy was a type of market economy where a variety of small tightly connected markets had loose connections between them~\shortcite{temin_market_2001,temin_economy_2006}.
 Based on these conclusions, further works have attempt to define more exactly the characteristics of this market such, e.g.
-level of intervention of the state and its impact, or the relation-ship between local and long-distance trade~\cite{wilson_approaches_2009}.
+level of intervention of the state and its impact, or the relation-ship between local and long-distance trade~\shortcite{wilson_approaches_2009}.
 
-Few works have attempt to model the interactions between economy and cultural change in the Roman empire~\cite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
-An analysis based on historical documents has revealed the importance of economical and social institutions for the efficiency of trades of grains in the early Roman Empire~\cite{kessler_organization_2007}.
-The same type of analysis has also revealed the importance of a number of key factors (such as commercial development, population growth and geographical mobility) for the growth of income and population in the Roman Italy~\cite{scheidel_model_2007}.
-Finally, a micro-economic model has determined the importance of reputation and threat of expulsion from a trade network as mechanisms to maintain the overall efficiency of the trade network~\cite{terpstra_trade_2011}.
+Few works have attempt to model the interactions between economy and cultural change in the Roman empire~\shortcite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
+An analysis based on historical documents has revealed the importance of economical and social institutions for the efficiency of trades of grains in the early Roman Empire~\shortcite{kessler_organization_2007}.
+The same type of analysis has also revealed the importance of a number of key factors (such as commercial development, population growth and geographical mobility) for the growth of income and population in the Roman Italy~\shortcite{scheidel_model_2007}.
+Finally, a micro-economic model has determined the importance of reputation and threat of expulsion from a trade network as mechanisms to maintain the overall efficiency of the trade network~\shortcite{terpstra_trade_2011}.
 These works therefore reveal the strong relation between trade and cultural change in the Roman empire.
@@
 
-The Agent Based Models (ABM) methodology offers a way to produce this kind of model within a computer~\cite{lake_trends_2014}.
+The Agent Based Models (ABM) methodology offers a way to produce this kind of model within a computer~\shortcite{lake_trends_2014}.
 An ABM is composed of a group of agents performing actions within a virtual environment.
@@
 
-A first example of its potential is given through a model of the trade network of tableware in the roman east~\cite{brughmans_roman_2014}.
+A first example of its potential is given through a model of the trade network of tableware in the roman east~\shortcite{brughmans_roman_2014}.
 Among the parameters tested, preliminary results of this model, show that the number of links between production site has a strong influence on the results obtained.
-A second more complete example proposes a detailed model of the prehispanic Pueblo societies~\cite{kohler_modelling_2012}.
+A second more complete example proposes a detailed model of the prehispanic Pueblo societies~\shortcite{kohler_modelling_2012}.
 This project proposes an ABM integrating numerous effects such as food consumption, production and landscape.
-The questions studied are  numerous and some works are performed on the economical system and its ties with social transmissions~\cite{kobti_emergence_2006,cockburn_simulating_2013}.
+The questions studied are  numerous and some works are performed on the economical system and its ties with social transmissions~\shortcite{kobti_emergence_2006,cockburn_simulating_2013}.
 However the work done in this project consider a pre-market society in a specific village which makes it difficult to reach more general conclusions, notably applicable to the Roman Empire.
@@
 
-The first set of implementations is designed to reproduce a scenario of unbiased transmission, where each product is a cultural trait without intrinsic positive or negative weight \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
+The first set of implementations is designed to reproduce a scenario of unbiased transmission, where each product is a cultural trait without intrinsic positive or negative weight \shortcite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
 Under this hypothesis, the processes of \emph{production} and \emph{trade} are not relevant, and as a consequence, they do not modify the content of the quantity vectors of the agents.
@@
 Between, twos such steps, the agent exchange goods given their own prices.
-Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}.
+Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \shortcite{bentley_random_2004,mesoudi_random_2009}.
 
@@
 We observe that prices are indeed converging to the optimal prices which means that our innovation and imitation process are valid trade mechanisms.
-Notably, they produce results similar to the ones obtained in~\cite{gintis_emergence_2006}.
+Notably, they produce results similar to the ones obtained in~\shortcite{gintis_emergence_2006}.
 
@@
 First the constraints on the production could be relaxed so that each agent can choose the products it wishes to produce at the current time step.
-Moreover, meterological factors can modify the quality of the production (noisy outcome of the process) thus making the process more realistic and more complex~\cite{bentley_specialisation_2005}.
+Moreover, meterological factors can modify the quality of the production (noisy outcome of the process) thus making the process more realistic and more complex~\shortcite{bentley_specialisation_2005}.
 
@@
 
-The trading theories studied also can be extended to the \emph{Prospect Theory}~\cite{kahneman_prospect_1979} which proposes to study more realistic trade mechanisms taking into account the biases of humans.
-Another economical framework we envision is the Agent based Computational Economy, ACE, which is  addressing economical problems raising from the interactions of a large number of agents~\cite{tesfatsion_introduction_2001}.
+The trading theories studied also can be extended to the \emph{Prospect Theory}~\shortcite{kahneman_prospect_1979} which proposes to study more realistic trade mechanisms taking into account the biases of humans.
+Another economical framework we envision is the Agent based Computational Economy, ACE, which is  addressing economical problems raising from the interactions of a large number of agents~\shortcite{tesfatsion_introduction_2001}.
 On top of these trading theories the influence of the network of trades by itself can be studied.
@@
 
-On the cultural transmission side, the vector value could be learned using any mechanism of ``social learning'' (as defined by \cite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \cite{lycett_cultural_2015} for some kind of bias that could be implemented).
+On the cultural transmission side, the vector value could be learned using any mechanism of ``social learning'' (as defined by \shortcite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \shortcite{lycett_cultural_2015} for some kind of bias that could be implemented).
 Agents could be also endowed with self-adaptation abilities implemented thanks to Reinforcement Learning or Developmental Learning.
@@
 
-The model was created using Pandora \cite{rubiocampillo_2014}.
-R was used for figures and statistical analysis \cite{rdev_2012}.
+The model was created using Pandora \shortcite{rubiocampillo_2014}.
+R was used for figures and statistical analysis \shortcite{rdev_2012}.
 The source code of the model is licensed under a GNU General Public License and will be available for download at publication.

### 2015-04-07 article.tex
merge of sections

@@
 
-\title{Model to study co-evolution of trade an culture}
+\title{Modelling the co-evolution of trade and culture in the Roman market}
+
 \maketitle
@@
 
-%XRC trade networks are increasingly being recognised as a key process in ancient Mediterranean
-Trades are being increasingly recognised as a key process in the structure of ancient Mediterranean societies.
-For example, the use of table ware in the Roman empire  has been linked to the trade network~\shortcite{brughmans_connecting_2010}.
-Interestingly this trade network has been shown to be a market economy~\shortcite{temin_market_2001}.
-The work presented in this paper proposes a framework to further study the relation between trade and culture within the roman empire.
-This work takes place within the EPNET project~\shortcite{remesal_epnet_2014}.
+% the spread of cultural traits is often modelled following neutral theory
 
-%XRC this process played a role in the trajectories of cultural change of the different regions, which were interconnected by trade
-Trade roads between provinces generates cultural changes due to two main effects.
-First, when a new connection is made between two provinces, new goods can arrive in their respective markets.
-The arrival of new goods naturally changes the rate of adoption of all the goods of the market CITE.
-Moreover, a good recently introduced in a province can be recombined with previous goods in order to create yet a new type of good, which further modify the structure of the market of the province.
-The second element affecting the change of culture within a province is due to the persons travelling on the roads of the trade network, each carrying its own culture.
-Large movements of populations may lead to changes in the cultures.
-For example, when Roman soldiers were stationing in a province, Roman products such as olive oil were delivered to that province CITE ROMAN DELIVERING OIL, which may have lead to the adoption of olive oil in regions that were originally not using it.
+Cultural change comprise the collection of processes that promotes or inhibits the spread of information by social interaction within a population~\shortcite[3]{boyd_origin_2005}.
+An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution~\shortcite{henrich_evolution_2003}.
 
-%XRC these two elements (cultural transmission and trade networks) are traditionally been studied as isolated systems.
-Usually, the studies on cultural change mechanisms focus on the adoption of cultural goods such as pottery by a population.
-However, these studies do not take into account economical factors, such as the cost of production or acquisition of the goods.
-Moreover, the effect that trade may have on the frequency of goods in the population or in neighbourhood populations is not analysed.
-A dedicated research field studies the effect of trade mechanisms on the change of prices and the modification of goods repartition in the population.
-This field relies on a specific set of framework which do not take into account the results obtained on the study of cultural change mechanisms.
-Certainly, this division in the analysis of cultural change and trade and cultural transmission allows for a precise formalization of their inner mechanisms and therefore a good understanding of their respective dynamics.
-%XRC this is wrong because blablabla
-However, as it has been shown before, trades influence cultural change by modifying both the goods present in a region and the people consuming these goods.
-Therefore, in order to analyse the adoption of goods within a province one must take into account both trading strategy and cultural transmission.
-For example, the modification of good's consumption after the rupture of a connection in the trade system is better explained by knowing the local adoption of this good (cultural change) and the prices of this good (trade).
-
-%XRC we propose a model of coevolution to explore the deep links between trade and cultural transmission in the ancient Mediterranean
-Ultimately, we aim to create a model to study the relation between cultural change and trade networks within the Roman Empire.
-Examples of questions that could be asked to our model are: What is the relation between distances in the trade network and cultural changes ?
-Did anti-conformism promote the adaptation of new products coming from remote provinces ?
-In order to answer these questions the model developed has to take into account both cultural effects and trade influence.
-More precisely, the variations in these two aspects should be modelled and should influence each other.
-Therefore, in order to answer the questions targeted we need a co-evolutionary model able to take into account both trade and cultural changes.
-
-To the best of our knowledge two works have previously proposed frameworks that could be used to model the co-evolution of trade and culture~\shortcite{bentley_specialisation_2005,macmillan_agent-based_2008}.
-The first proposes a relatively simple model which is limited by 2 products, a fixed behaviour of the agents and a limited variation of cultural mechanisms.
-The second proposes a more complete model including a large number of goods (certain being essential and the others non-essential), but suffer from a greater complexity and the absence of the notion of trade networks.
-Moreover, these works do not compare the dynamics obtained to the previous studies on cultural change and trading mechanisms.
-
-Therefore, in this work, we aim for the development of a framework to study the co-evolution of culture and trades which relies on a low number of parameters.
-The idea behind the development of such framework is to ease the comparison of different cultural change and trade mechanisms, which means that the framework should be flexible enough to allow for the implementation of both type of mechanisms and with enough structural elements to allow the comparison of various implementations.
-This article will focus on the presentation of the framework, its justification and more importantly its validation by reproducing previous results obtained on cultural change, and the ability to produce trade dynamics.
-The results obtained when studying trade and cultural change are compared with each other.
-
-%Organisation of the paper
-\todo{write once we are more sure of what we put}
-The paper is organised as follow
-
-\section{PREVIOUS MODELLINGS OF TRADE AND CULTURE}
-
-This section will provide a brief review of the previous approaches to model trade and culture. While non-exhaustive, this review presents the mains trends of the previous work done.
-
-\subsection{Neutral models of cultural change}
-
-The first aspect of our model is focused on the dynamics of cultural change.
-They comprise the collection of processes that promotes or inhibits the spread of information by social interaction within a population~\shortcite[3]{boyd_origin_2005}.
-An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution~\shortcite{henrich_evolution_2003}.
-Archaeology has a rich tradition of evolutionary studies~\shortcite{lycett_cultural_2015}, exploring concepts such as gene-culture coevolution~\shortcite{burger_absence_2007}, diffusion processes~\shortcite{fort_synthesis_2012}, phylogenetic analysis of material culture~\shortcite{obrien_cladistics_2001} or detection of rates of change in the archaeological record~\shortcite{premo_cultural_2014}.
-
-A large percentage of these studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependence (e.g.
-conformism and anti-conformism).
-These analysis are often based on the theory of neutral evolution~\shortcite{neiman_stylistic_1995}, which explains variation in the distribution of traits as a function of their frequency distribution in the population.
-Thus, a trait is assumed to lack any selective bias and its transmission will depend on its popularity amongst the rest of individuals.
-The comparison of a given frequency distribution found in data against this unbiased transmission model is traditionally used as a null-hypothesis testing for selection.
-There exist a large number of works using this approach as the starting point to analyse patterns of cultural change in past societies~\shortcite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010,kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
-
-Unbiased transmission generates a clear pattern of power law distributions that can be replicated with a simple random copying transmission mechanism~\shortcite{bentley_random_2004}.
-Within this framework, an individual will copy the traits of a randomly chosen individual with a given probability.
+Several studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependence properties.
+These analysis often compare evidence against neutral models~\shortcite{neiman_stylistic_1995}.
+They assume that traits do not affect the fitness of the individual that acquire it; within this context its transmission is unbiased, and its success will depend on its popularity amongst the rest of individuals.
+This neutral model generates a distinctive pattern of frequency distribution of traits, identified as a power law.
+It can be replicated with a simple random copying transmission mechanism~\shortcite{bentley_random_2004}: an individual will copy the traits of a randomly chosen individual with a given probability.
 This copy can potentially introduce some errors in the acquired trait, which account for innovation processes.
@@
 This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmissio~\shortcite{heyes_social_1994,henrich_evolution_2003}.
+Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendendy to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.
 
-In particular, trade within a market system can potentially introduce a complex dynamic bias to the neutral model.
-Trasmission will be linked to the price of the different products.
-This would also affect the frequency of the product within the population, which in turn would modify its price following a co-evolutionary dynamic.
+This approach can be used as the starting point to analyse patterns of cultural change to explore frequency-dependance in archaeological contexts~\shortcite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010}.
+However, the fact that archaeology records fragmented material culture presents some challenges on the validity of the method~\shortcite{kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
-\subsection{Models including Trade}
+This work explores the impact of a crucial element on the transmission of material culture: trade.
+Networks of good exchanges are being increasingly recognised as key elements that structured ancient societies~\shortcite{temin_market_2001,remesal_epnet_2014,brughmans_connecting_2010}.
+The scenarios where this process emerge suggest a complex bias in the selection of cultural traits, which at the same time are also identified as economic products~\shortcite{bentley_specialisation_2005,macmillan_agent-based_2008}.
+Trasmission is not neutral anymore, as different prices for each product will introduce a dynamic content bias.
+This affects the frequency of the product within the population, which in turn would modifies its price following a co-evolutionary dynamic.
 
-%Hopkins 1980: structure of tax system.
-two hypothesis.
-1)taxation increased volume of trade in the empire?
-2) tax-exporting province (recently integrated province) had to export to pay tax.
-roman supported by many small taxes.
-Not sure to cite it
-
-Previous historical and archaeological studies to model trade in the ancient Mediterranean societies have focus on descriptive approaches~\shortcite{hopkins_taxes_1980,temin_market_2001,terpstra_trade_2011,temin_economy_2006,wilson_approaches_2009,scheidel_model_2007,kessler_organization_2007}.
-These works have conclude that the Roman economy was a type of market economy where a variety of small tightly connected markets had loose connections between them~\shortcite{temin_market_2001,temin_economy_2006}.
-Based on these conclusions, further works have attempt to define more exactly the characteristics of this market such, e.g.
-level of intervention of the state and its impact, or the relation-ship between local and long-distance trade~\shortcite{wilson_approaches_2009}.
-
-Few works have attempt to model the interactions between economy and cultural change in the Roman empire~\shortcite{terpstra_trade_2011,kessler_organization_2007,scheidel_model_2007}.
-An analysis based on historical documents has revealed the importance of economical and social institutions for the efficiency of trades of grains in the early Roman Empire~\shortcite{kessler_organization_2007}.
-The same type of analysis has also revealed the importance of a number of key factors (such as commercial development, population growth and geographical mobility) for the growth of income and population in the Roman Italy~\shortcite{scheidel_model_2007}.
-Finally, a micro-economic model has determined the importance of reputation and threat of expulsion from a trade network as mechanisms to maintain the overall efficiency of the trade network~\shortcite{terpstra_trade_2011}.
-These works therefore reveal the strong relation between trade and cultural change in the Roman empire.
-However a large percentage of the datasets used for these studies are based on material objects found in archaeological contexts such as pottery.
-Most of these objects are usually represented following a neutral model, but the weight of this model within a market system is not studied.
-
-An additional limitation of the previous works is the impossibility to test the conclusions reached by the authors.
-The models proposed reflects only the view of the authors on the historical and archaeological data analysed.
-A new type of model would be necessary to go beyond the interpretation, and allow the verification of the conclusions reached.
-These models should be able to generate data relative to trade which are then qualitatively compared to results of analysis of archaeological data such as amphorae or other container used to carry goods.
-By this mean, if a factor is really important in the economical network, its removal from the model will lead to data qualitatively different from the historical data.
-
-The Agent Based Models (ABM) methodology offers a way to produce this kind of model within a computer~\shortcite{lake_trends_2014}.
-An ABM is composed of a group of agents performing actions within a virtual environment.
-The environment and the behaviour of the agents, despite being an simpler than the real world, are designed to be analogous to their real-world counterpart.
-The experimenter hand designs the agents, the environment and their interaction, and observes the outcome of all interactions through time in order to compare it to the archaelogical data obtained from the real world.
-The goal of the experimenter is therefore to find a plausible set of assumptions used during the creation of the ABM to produce results close to what is observed in reality.
-
-A first example of its potential is given through a model of the trade network of tableware in the roman east~\shortcite{brughmans_roman_2014}.
-Among the parameters tested, preliminary results of this model, show that the number of links between production site has a strong influence on the results obtained.
-A second more complete example proposes a detailed model of the prehispanic Pueblo societies~\shortcite{kohler_modelling_2012}.
-This project proposes an ABM integrating numerous effects such as food consumption, production and landscape.
-The questions studied are  numerous and some works are performed on the economical system and its ties with social transmissions~\shortcite{kobti_emergence_2006,cockburn_simulating_2013}.
-However the work done in this project consider a pre-market society in a specific village which makes it difficult to reach more general conclusions, notably applicable to the Roman Empire.
-
-%kobti 2012 la meme que kobti 2006 ?
-%	pour 2006: etude de l'apparition d'inegalite
+This work explores these co-evolutionary dynamics using a theoretical Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\cite{lake_trends_2014}.
+Next section defines the model, which is based on unbiased transmission mechanisms and simple exchange dynamics.
+Next, we define different experiments to explore the dynamics of the created model.
+Finally, the concluding remarks interpret the results and discuss further possibilities of the pesented model.
 
 \section{MODEL DESCRIPTION}
-
-To explore this coevolution between trade and cultural change we have developed an ABM where the different agents trade goods with variable prices.
-
-\xrc{we can totally remove this paragraph and move the entire next subsection here:\\
-These dynamics are modelled after processes (production, cultural transmission, innovation and trade) which will be explained in further details later.
-The flexibility of the models comes from the possibility to implement these processes differently depending on the hypothesis tested.
-However, since all experiments are performed with the same four processes, the effect of the various implementations of one process can be studied easily.
-Moreover, the operating of the model revolves around the value that agents associate to products.
-Depending on the question studied, the value can reflect the interest of the agent for the good or it can be the price at which the agent evaluate this good.
-Since this vector is common to all experiments performed with this model, it is extremely useful for the comparisons of results obtained with different implementation of the key processes.}
-
-\xrc{This first paragraph should briefly explain the trade component?}
-
-\subsection{Overview of the model}
 
@@
 Within the \textit{cultural transmission} process an agent $i$ can copy the value vector ($V^j$) of an agent $j$, where $j \neq i$.
-The \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{cultrual transmission} process in that the modification is done without reference to the other agents.
+The \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{cultural transmission} process in that the modification is done without reference to the other agents.
 Finally, .
 
-This scheme achieves the two main goals listed in section~\ref{sec:intro}.
-The first goal is to be able to implement and compare various cultural transmission mechanisms as well as trade mechanisms within the same framework.
-We argue that this is possible in our framework by modifying only these four key processes i.e.
-production, trade, imitation and innovation.
-Moreover, thanks to the use of a unique $V^i$ vector, it is possible to compare the outcomes of different combinations of production, imitation and innovation mechanisms.
-The second goal is to produce a model composed of a low number of parameter.
-Our model is composed of only four processes and two vectors which is significantly less complex than previous models.
-
-\xrc{I would remove the previous paragraph, because it is implied that we want few parameters and compare mechanisms}
-
-The scheduling of the four processes (production, trade, cultural transmission and innovation) is described in algorithm~\ref{algo:complete} along with the vectors modified by each of these processes.
+The scheduling of the four processes is described in algorithm~\ref{algo:complete} along with the vectors modified by each of these processes.
 Between line 2 and 7 all agents of the population are initialised with empty quantity vectors and random values.
@@
 
-\section{DISCUSSION}
+\section{CONCLUDING REMARKS}
 
-In this paper, and thanks to the model developed, we have shown that it is the possible to implement trade mechanisms within a cultural evolutionary framework.
-In the end, it appears that the key aspects of trade are just different implementations of the key elements of cultural evolutionary framework, i.e.
+The results of this model show that the key aspects of trade are just different implementations of the key elements of cultural evolutionary framework, i.e.
 cultural transmission and innovation.
@@
 Interesting additional work could be, for example, the comparison between trade mechanisms and prestige biased cultural transmission.
-
-\section{CONCLUSION}
 
@@
 
+\xrc{I think that this section can be revised once we get the results (e.g. less future work, more interpretation of results)}
+
 \section{Acknowledgements}

### 2015-04-07 article.tex
new setup with only two model, graph modifications

@@
 
-\xrc{score is fitness? Not sure if we should use fitness here, as we are already using an evolutionary framework. Also, we could use payoff.}
 The \emph{score} $s^i$ of an agent $i$ reflects the ability of this agent to obtain the products it needs.
@@
 	\begin{center}
-		\includegraphics[width=7cm]{img/fitness.png}
+		\includegraphics[width=7cm]{img/fitness.pdf}
 	\end{center}
-	\caption{The fitness depending on price and needs}
+	\caption{The payoff depending on the estimated value and the effective needs $n(g)$ of a good.}
 	\label{fig:fit}
@@
 The figure~\ref{fig:fit} depicts the score of an agent, for different need value of one good, with regards to the quantity of the good possessed by the agent.
-We can see that even if the need for a good is small (for instance when $need(x) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need.
+We can see that even if the need for a good is small (for instance when $n(g) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need.
 This insures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.
@@
 \begin{align}
-q_g^o >= w_g^o \label{eq:constraintFirst}\\
-q_g^r <= w_g^o \\
-q_k^r >= w_k^o \label{eq:constraintLastInv}\\
-w_g^o>=(q_g^r+w_g^r)\label{eq:constraintFirstWill} \\
-w_k^o<=w_k^r \\
-w_g^o<=w_g^r
-\label{eq:constraintLast}
+q_g^o >= w_g^o,\quad q_g^r <= w_g^o,\quad q_k^r >= w_k^o \label{eq:constraintQty}\\
+w_g^o>=(q_g^r+w_g^r),\quad w_k^o<=w_k^r,\quad w_g^o<=w_g^r \label{eq:constraintWill}
 \end{align}
 
-The conditions \ref{eq:constraintFirst}-\ref{eq:constraintLastInv} insure that both agents have enough goods in their inventory to realise the trade while the conditions \ref{eq:constraintFirstWill}-\ref{eq:constraintLast} insure that the quantities of each good fit the will of both agents.
+The conditions \ref{eq:constraintQty} insure that both agents have enough goods in their inventory to realise the trade while the conditions \ref{eq:constraintWill} insure that the quantities of each good fit the will of both agents.
 
@@
 
-If such prices are reached, given the exchange rules defined in (\ref{eq:trade}) and the exchange constraints (\ref{eq:constraintFirst}) to (\ref{eq:constraintLast}) all exchanges will be optimally achieved, leading to a total score $S$ for each agent of the population :
+If such prices are reached, given the exchange rules defined in (\ref{eq:trade}) and the exchange constraints (\ref{eq:constraintQty}) and (\ref{eq:constraintWill}) all exchanges will be optimally achieved, leading to a total score $S$ for each agent of the population :
 $$ S = \sum_{i=0}^{CulturalStep}  s^i(\tilde{Q}^i) \times ngoods $$ 
@@
 \section{Experimental setup}
-In order to study the cultural transmission and the trading model two sets of implementation of the four processes of our model have been presented.
+%In order to study the cultural transmission and the trading model two sets of implementation of the four processes of our model have been presented.
 Remember that during the definition of these two sets of implementation, two cultural transmission mechanisms have been defined () along with two innovation mechanisms ().
@@
 Note that the ``neutral model" presented in section~\ref{sec:culturalTrans} corresponds to the setup A, and the trading model presented in section~\ref{sec:trade} corresponds to the setup D.
+%
+%\begin{table}[h]
+%	\centering
+%	\begin{tabular}{ll|cc}
+%				&	&\multicolumn{2}{c}{\textbf{Cultural transmission}} \\
+%		\multirow{2}[20]{*}{\rotatebox[origin=c]{90}{\textbf{Innovation}}}&  & Random & Success biased \\\hline  
+%		& \rule[-0.45cm]{0pt}{1cm} Unbounded 		&A & B \\
+%		& \rule[-0.45cm]{0pt}{1cm} Self Referenced	& C & D \\
+%	\end{tabular}
+%	\caption{Experimental Setup}
+%	\label{tab:exp}
+%\end{table}
 
-\begin{table}[h]
-	\centering
-	\begin{tabular}{ll|cc}
-				&	&\multicolumn{2}{c}{\textbf{Cultural transmission}} \\
-		\multirow{2}[20]{*}{\rotatebox[origin=c]{90}{\textbf{Innovation}}}&  & Random & Success biased \\\hline  
-		& \rule[-0.45cm]{0pt}{1cm} Unbounded 		&A & B \\
-		& \rule[-0.45cm]{0pt}{1cm} Self Referenced	& C & D \\
-	\end{tabular}
-	\caption{Experimental Setup}
-	\label{tab:exp}
-\end{table}
+For the cultural transmission setup we run two set of experiments with 250 and 500 agents in which we vary $\alpha \in \{0.004,0.016,0.064\}$.
+For each combination of parameters we did 100 runs of 10000 timestep is performed.
 
-For each of the setup 100 runs of 200000 timestep is performed.
-The parameters used are presented in table~\ref{tab:parameters}.
-Finally, remember that in our experiment one has to take in account that agents modifies their prices or exchange their price only every $culturalStep$ steps.
+For the trading model we run  again two set of experiment, one with 2 goods and 500 agents, the other with 4 goods and 800 agents.
+The length of the simulations is always 10000 timestep but this time one timestep is made of $CulturalStep$ trade action as described in the previous section~\ref{sec:trade}.
+Again for each combination 100 runs are done.
+
+The whole set of parameters used are presented in table~\ref{tab:parameters}.
+
+%Finally, remember that in our experiment one has to take in account that agents modifies their prices or exchange their price only every $culturalStep$ steps.
 Between, twos such steps, the agent exchange goods given their own prices.
@@
 
-We first analyse the result obtained in the ``neutral model" as presented in section~\ref{sec:culturalTrans} and labelled as setup A in table~\ref{tab:exp}.
+We first analyse the result obtained in the ``neutral model" as presented in section~\ref{sec:culturalTrans}.
 The figure~\ref{fig:allMutation} present the results obtained with $\mu$ varying $\in {.004,.008,.016,.064}$ and two population sizes: 250 and 500 agents.
@@
 
-In order to understand the effect of the other cultural transmission and innovation mechanisms, we study first the distribution of values obtained in the different setups.
-The distribution of values in the four setups is presented in figure~\ref{fig:4setDi}.
+In order to understand the effect of introduction of trading mechanisms we compare first the distribution of values obtained in the two models.
+The result of this comparison is in the figure~\ref{fig:2setDi}.
 
@@
 	\begin{center}
-		\includegraphics[width=7cm]{img/frequenciesABCD.pdf}
+		\includegraphics[width=6cm]{img/2SetupDistrib.pdf}
 	\end{center}
-	\caption{Frequency distribution for the 4 setup}
-	\label{fig:4setDi}
+	\caption{Frequency distribution for the neutral and the trade models}
+	\label{fig:2setDi}
 \end{figure}
@@
 
-The results studied in the previous section is reproduced here by the line labelled ``setup A''. 
+%The results studied in the previous section is reproduced here by the line labelled ``setup A''. 
 \jm{this sounds wrong what would be a valid analysis ?}
-We observe that the setup D is also following a power law.
+%We observe that the setup D is also following a power law.
 However, setups B and C are following an exponential law.
@@
 
+We can observe the action of our new analysis : the new innovation process prevents the creation of totally random new price and lead to a fewer proportion of prices that appear rarely in the population.
+
 \subsection{Values}
@@
 We now study the results obtained in more detail by investigating the ability of the population of agents to find the good price to perform exchanges between each other.
-This is done by observing the score of all agents in each of the four setups.
-The results obtained are presented in figure~\ref{tab:scoreEvol}.
+This is done by observing the score of all agents in each of the two different models.
+The results obtained are presented in figure~\ref{fig:scoreEvol}.
 
-\begin{table}[H]
+\begin{figure}[h]
 	\centering
-	\begin{tabular}{l c c}
-		& Random Transmission & Biased Transmission \\
-		Unbounded & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForA-G2N250.pdf}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForB-G2N250.pdf}} \\ Setup B} \\
-		Self-referenced & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForC-G2N250.pdf}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForD-G3N500.pdf}} \\ Setup D}
+	\begin{tabular}{ c c}
+		 Neutral Model & Trade Model \\
+		 \includegraphics[width=5cm]{img/ScoreEvolutionForRandom-G2N500.pdf}
+		 & \includegraphics[width=5cm]{img/ScoreEvolutionForTrade-G2N500.pdf}
 
 	\end{tabular}
-	\caption{Evolution of the score in the different setup for typical run of each setup.}%%
-	\label{tab:scoreEvol}
-\end{table}
+	\caption{Evolution of the score within the two different models.}%%
+	\label{fig:scoreEvol}
+\end{figure}
 
 \todo{redo the explanations nicer} 
-In the setups A and C, the score evolves randomly.
+%In the setups A and C, the score evolves randomly.
 In the two other setups however the score is increasing.
@@
 
+As expected, the neutral model scores vary randomly.
+Sometimes ``trends'' appear, where a bigger proportion of individuals adopt a better price that allow agents to reach better score (such as between \simon{adapt to last graph}), but such good score fall back as soon as another trend appears.
+In the other hand, with in the trade model, the score of all the agents increase.
+As the selection mechanism allow them to know who find better vectors of prices, they will slightly adopt prices vector that allow all of them to reach better scores.
+
 \subsection{Prices}
 
-We pursue the analysis of the economical aspect by observing the prices reached in setup D.
+We pursue the analysis of the economical aspect by observing the prices reached within the trade model.
 As explained in the section~\ref{sec:trade} we expect that the trade imitation and innovation processes will produce a convergence toward a set of price for each good that will allow agents to exchange optimally the good they produce with the other goods.
@@
 	\begin{center}
-		\includegraphics[width=7cm]{img/ClearingPriceDistanceEvolutionForD-G3N500.pdf}
+		\includegraphics[width=7cm]{img/ClearingPriceDistanceEvolutionForTrade-G2N500.pdf}
 	\end{center}
-	\caption{Evolution of the mean difference for each good of the estimated value $v_g$ and its optimal value as given by \ref{eq:optimum}. Means computed for 100 run adn 2 goods. }
+	\caption{Evolution of the mean difference for each good of the estimated value $v_g$ and its optimal value as given by \ref{eq:optimum}. Means computed for 100 run and 2 goods. }
 	\label{fig:ratioEvol}
@@
 \subsection{Suboptimal markets}
-
-Finally, a more careful analysis of the price structure reveals the presence of suboptimal markets. 
-\jm{it was written setup C, it's not setup D?}
-\jm{is it the mean in blue ?}
-In figure~\ref{fig:suboptimal} the price structure of one run of setup D is presented.
+%
+%Finally, a more careful analysis of the price structure reveals the presence of suboptimal markets. 
+%\jm{it was written setup C, it's not setup D?}
+%\jm{is it the mean in blue ?}
+%In figure~\ref{fig:suboptimal} the price structure of one run of setup D is presented.
 The x-axis represents the number of iteration, the y-axis the prices.
@@
 In blue is presented the mean of the score of the figures.
-
+%
+%%\begin{figure}[htp]
+%%	\begin{center}
+%%		\includegraphics[width=7cm]{img/evolutionGlobalScoreG4N800.pdf}
+%%	\end{center}
+%%	\caption{Evolution of global score for a run with 800 agents and 4 goods.}
+%%	\label{fig:G4N500}
+%%\end{figure}
+%%\begin{figure}[htp]
+%%	\begin{center}
+%%		\includegraphics[width=7cm]{img/evolutionToClearningPricesG4N800.pdf}
+%%	\end{center}
+%%	\caption{Evolution of prices for a run with 800 agents and 4 goods.}
+%%	\label{fig:G4N500Clearing}
+%%\end{figure}
+%
 %\begin{figure}[htp]
 %	\begin{center}
-%		\includegraphics[width=7cm]{img/evolutionGlobalScoreG4N800.pdf}
+%		\includegraphics[width=7cm]{img/scatterPlotGood1.pdf}
+%		\includegraphics[width=7cm]{img/scatterPlotGood2.pdf}
+%		\includegraphics[width=7cm]{img/scatterPlotGood3.pdf}
+%		\includegraphics[width=7cm]{img/scatterPlotGood4.pdf}
 %	\end{center}
-%	\caption{Evolution of global score for a run with 800 agents and 4 goods.}
-%	\label{fig:G4N500}
+%	\caption{Evolution of the Score for the four types of agents of a simulation with four differents good and 800 agents}
+%	\label{fig:suboptimal}
 %\end{figure}
-%\begin{figure}[htp]
-%	\begin{center}
-%		\includegraphics[width=7cm]{img/evolutionToClearningPricesG4N800.pdf}
-%	\end{center}
-%	\caption{Evolution of prices for a run with 800 agents and 4 goods.}
-%	\label{fig:G4N500Clearing}
-%\end{figure}
-
-\begin{figure}[htp]
-	\begin{center}
-		\includegraphics[width=7cm]{img/scatterPlotGood1.pdf}
-		\includegraphics[width=7cm]{img/scatterPlotGood2.pdf}
-		\includegraphics[width=7cm]{img/scatterPlotGood3.pdf}
-		\includegraphics[width=7cm]{img/scatterPlotGood4.pdf}
-	\end{center}
-	\caption{Evolution of the Score for the four types of agents of a simulation with four differents good and 800 agents}
-	\label{fig:suboptimal}
-\end{figure}
-
-\xrc{these boxplots are confusing because they are small and contain a huge amount of information.
+%
+%\xrc{these boxplots are confusing because they are small and contain a huge amount of information.
 What if we do a scatterplot with a given alpha, and on top of this a loess regression?
 It always works better to me when you have this kind of data; also, I would provide a figure for each type of score.}
-\simon{What do you mean by ``a given alpha''? does something like those new ones is better?}
-
-For the agents producing the goods 1,2 and 3 we observe a long stagnation of the mean score until timestep 750,000.
+%\simon{What do you mean by ``a given alpha''? does something like those new ones is better?}
+%
+%For the agents producing the goods 1,2 and 3 we observe a long stagnation of the mean score until timestep 750,000.
 Further investigations have revealed that during this period a few of the prices used by the agents are far from the optimal.
@@
 This situation is due to the fact that all prices are strongly linked together and until one has reach its optimum value, the other price can not evolve.
+%
 

### 2015-04-07 article.tex
remove 0.008

@@
 		N = 250	&0.004&1.53&0.03&1.54&0.02\\
-			&0.008&1.55&0.03&1.55&0.01\\
 			&0.016&1.57&0.02&1.57&0.01\\
@@
 		N= 500	&0.004&1.50&0.02&1.53&0.03\\
-			&0.008&1.52&0.02&1.57&0.01\\
 			&0.016&1.55&0.03&1.61&0.04\\

### 2015-04-07 article.tex
correct minor typo

--- 2015-04-07 article.tex
@@
 The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
-This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmissio~\shortcite{heyes_social_1994,henrich_evolution_2003}.
-Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendendy to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.
+This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission~\shortcite{heyes_social_1994,henrich_evolution_2003}.
+Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendency to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.
 

### 2015-04-08 article.tex
update ccl and abstract. check results

@@
 
-\WSCpagesetup{Montanier, Carrignon, Rubio and Zerr}
+\WSCpagesetup{Montanier, Carrignon and Rubio}
 
@@
 
-\todo{Rewrite later}
-In this article our aim is to present a model suitable to test various hypotheses on economic and cultural co-evolution during the Roman Empire.
-The ultimate goal is to address debates from history of economy such as the type of economical market found in early empires.
-Agent based modelling is a good way to understand social self-organisation resulting from a large number of interactions.
-It is used in a wide range of fields of research, from economical market mechanisms to social dynamics.
-We therefore apply this type of framework to our study.
-
-Here we present a model able it reproduces well known economical and cultural mechanism.
-Moreover this model can be envisioned to test hypothesis on those mechanisms.
-Given the appropriate match between the simulations and archaeological and historical data, the results of the model can be validated.
+This papers presents a new framework to study the co-evolution of cultural transmission and trade.
+The design aims for a trade-off between the flexibility necessary for the implementation of multiple models and the structure necessary for the comparison between the models implemented.
+To create this framework we propose an Agent-Based Model relying on agents producing, exchanging and associating values to a list of goods.
+We first present the key concepts of the framework and two examples of its implementation which allow us to show the flexibility of our framework.
+We then compare the results obtained by the two models, thus validating the structure of the framework.
+Finally, to validate our trade model we study the price structure obtained.
 
@@
 Networks of good exchanges are being increasingly recognised as key elements that structured ancient societies~\shortcite{temin_market_2001,remesal_epnet_2014,brughmans_connecting_2010}.
-The scenarios where this process emerge suggest a complex bias in the selection of cultural traits, which at the same time are also identified as economic products~\shortcite{bentley_specialisation_2005,macmillan_agent-based_2008}.
-Trasmission is not neutral anymore, as different prices for each product will introduce a dynamic content bias.
-This affects the frequency of the product within the population, which in turn would modifies its price following a co-evolutionary dynamic.
+The scenarios where this process emerge suggest a complex bias in the selection of cultural traits, which at the same time are also identified as economic goods~\shortcite{bentley_specialisation_2005,macmillan_agent-based_2008}.
+Trasmission is not neutral anymore, as different prices for each good will introduce a dynamic content bias.
+This affects the frequency of the good within the population, which in turn would modifies its price following a co-evolutionary dynamic.
 
@@
 
-The model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$. The first corresponds to the quantity of each good that the agent $i$ possesses: 
+To explore the co-evolution between trade and cultural change we have developed an ABM where the different agents produce and trade goods to which they associate variable values.
+The model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$.
+The first corresponds to the quantity of each good that the agent $i$ possesses:
 $$\forall i \in Pop, \quad Q^i = (q^i_1,\cdots,q^i_n) $$
@@
 
-The second vector reflects the estimation of the value of a product that an agent $i$ makes.
+The second vector reflects the estimation of the value of a good that an agent $i$ makes.
 $$\forall i \in Pop, \quad V^i = (v^i_1,\cdots,v^i_n) $$
@@
 Between the lines 11 and 19 is presented the part of the pseudo-code describing the instructions that will be repeated for each iteration of the simulation.
-\jm{what about saying that we just count the iterations at the ``imitation, innovation step" ?}
-\xrc{It should be justified (market is faster than cultural change?)}
 One can note that the trading process is performed at every iteration while the imitation and innovation processes are executed only every $CulturalStep$.
 The idea behind this is to perform the imitation based on a score that reflects the performance of the agent and not only one lucky or unlucky trading round.
+The timestep number used in the figures of this article refers to the number of times the \emph{cultural transmission} and \emph{innovation} processes have been called.
 
@@
 		\For{$j \in Goods$}
-			\For{$i \in \#Pop/\#Goods$} \Comment{Initialize the agent with no products and a random value vector}
+			\For{$i \in \#Pop/\#Goods$} \Comment{Initialize the agent with no goods and a random value vector}
 				\State $Q^i = (0, \cdots, 0)$
@@
 We then show that it is possible to transform our model to fit processes that are economically sound.
-To achieve these two goals, we have design for each one specific set of implementations of the four core processes (production, imitation and innovation).
+To achieve these two goals, we have design for each one a specific set of implementations of the four core processes (production, trade, cultural transmission and innovation).
+
+%These dynamics are modelled after processes (production, cultural transmission, innovation and trade) which will be explained in further details later.
+The flexibility of the models comes from the possibility to implement these processes differently depending on the hypothesis tested.
+However, since all experiments are performed with the same four processes, the effect of the various implementations of one process can be studied easily.
+Moreover, the operating of the model revolves around the value that agents associate to goods.
+Depending on the question studied, the value can reflect the interest of the agent for the good or it can be the price at which the agent evaluate this good.
+Since this vector is common to all experiments performed with this model, it is extremely useful for the comparisons of results obtained with different implementation of the key processes.
 
@@
 
-The first set of implementations is designed to reproduce a scenario of unbiased transmission, where each product is a cultural trait without intrinsic positive or negative weight \shortcite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
+The first set of implementations is designed to reproduce a scenario of unbiased transmission, where each good is a cultural trait without intrinsic positive or negative weight \shortcite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
 Under this hypothesis, the processes of \emph{production} and \emph{trade} are not relevant, and as a consequence, they do not modify the content of the quantity vectors of the agents.
@@
 More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$, where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
+We will therefore attempt to fit as good as possible the results obtained with this set of implementations to the ``power law'' distribution by modifying the $\alpha$ parameter.
 
@@
 The second set of implementations of the core processes aims at producing economical dynamics.
-We are interested in the exchange of products between agents when they can modify the prices at which they sell and buy products.
+We are interested in the exchange of goods between agents when they can modify the prices at which they sell and buy goods.
 We want to implement simple processes leading to the convergence of all prices to values acceptable by all agents, i.e.
@@
 
-The \emph{need} is a quantity of product that each agent tries to obtain. This quantity is different for each product but the need for a product is the same for all agents:
+The \emph{need} is a quantity of good that each agent tries to obtain. This quantity is different for each good but the need for a good is the same for all agents:
 $$ N = (n_1, \cdots, n_r) $$
 
-The \emph{score} $s^i$ of an agent $i$ reflects the ability of this agent to obtain the products it needs.
+The \emph{score} $s^i$ of an agent $i$ reflects the ability of this agent to obtain the goods it needs.
 It is maximum when the quantity vector of an agent is equal to its need vector and lower proportionally to the distance between the need vector and the quantity vector.
@@
 Briefly summarised, for each good that it does not produce, an agent will trade with the first parter that offer an acceptable trade, i.e.
-the agent that proposes a satisfiable ratio between the other product and the product produced by the agent.
+the agent that proposes a satisfiable ratio between the other good and the good produced by the agent.
 
-In more details, the trading phase starts by the agent looking at a first random agent producing another product. 
+In more details, the trading phase starts by the agent looking at a first random agent producing another good. 
 Let $o$ be an agent producing $g$ that proposes a trade and $r$ an agent producing $k$ that receives the proposition.
@@
 
-For the cultural transmission setup we run two set of experiments with 250 and 500 agents in which we vary $\alpha \in \{0.004,0.016,0.064\}$.
-For each combination of parameters we did 100 runs of 10000 timestep is performed.
+For the cultural transmission model we run experiments with two setups.
+The first is composed of 1 good and two population sizes: 250 and 500 agents ; the second is composed of 3 goods and 500 agents.
+For both of these setups 4 different values of $\alpha$ are studied: $\{0.004,0.016,0.064\}$.
+For each $\alpha$ we present the results obtained with 100 runs of 10000 timestep each.
 
-For the trading model we run  again two set of experiment, one with 2 goods and 500 agents, the other with 4 goods and 800 agents.
-The length of the simulations is always 10000 timestep but this time one timestep is made of $CulturalStep$ trade action as described in the previous section~\ref{sec:trade}.
-Again for each combination 100 runs are done.
+For the trading model we run also all experiments with 3 goods and 500 agents.
+Again 100 runs of 10000 timesteps are performed.
+As described in section~\ref{sec:trade}, one timestep is corresponds to the call of the \emph{cultural transmission} and \emph{innovation} processes.
 
@@
 We first analyse the result obtained in the ``neutral model" as presented in section~\ref{sec:culturalTrans}.
-The figure~\ref{fig:allMutation} present the results obtained with $\mu$ varying $\in {.004,.008,.016,.064}$ and two population sizes: 250 and 500 agents.
+Figure~\ref{fig:allMutation} presents the results obtained with $\mu$ varying $\in {.004,.008,.016,.064}$, 1 good and two population sizes: 250 and 500 agents.
 The distribution of variants obtained is shown in figure~\ref{fig:allMutation}.
@@
 
-\subsection{Distribution}
+\subsection{Distribution of variants}
 
@@
 
-%The results studied in the previous section is reproduced here by the line labelled ``setup A''. 
-\jm{this sounds wrong what would be a valid analysis ?}
-%We observe that the setup D is also following a power law.
-However, setups B and C are following an exponential law.
-We therefore observe that the innovation process has a negligeable influence on the shape distribution.
-However, the use of a biased imitation process has a major effect on the shape of the distribution.
+On this figure it appears that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis.
+In more details, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
+Additional investigation have shown us that this is due to the \emph{innovation} process used in the trade model which prevents the creation of totally random new price and lead to a fewer proportion of prices that appear rarely in the population.
 
-We can observe the action of our new analysis : the new innovation process prevents the creation of totally random new price and lead to a fewer proportion of prices that appear rarely in the population.
-
-\subsection{Values}
+\subsection{Study of scores}
 
@@
 
-\todo{redo the explanations nicer} 
 %In the setups A and C, the score evolves randomly.
@@
 Sometimes ``trends'' appear, where a bigger proportion of individuals adopt a better price that allow agents to reach better score (such as between \simon{adapt to last graph}), but such good score fall back as soon as another trend appears.
-In the other hand, with in the trade model, the score of all the agents increase.
+In the other hand, with the trade model, the score of all the agents increase.
 As the selection mechanism allow them to know who find better vectors of prices, they will slightly adopt prices vector that allow all of them to reach better scores.
-
-\subsection{Prices}
 
@@
 
-\subsection{Suboptimal markets}
+%\subsection{Suboptimal markets}
 %
@@
 
-The results of this model show that the key aspects of trade are just different implementations of the key elements of cultural evolutionary framework, i.e.
-cultural transmission and innovation.
-Moreover, we have ensure that such an implementation is valid in the sense that it leads the prices of goods to converges to the values expected under economical theories.
-This aspect which has not been studied before, opens a new line of thinking on the weight of trade mechanisms within cultural change.
-
-Within this line of thought, we have shown that the implementation of trade mechanisms as cultural transmission and innovation mechanisms leads to results departing from the neutral hypothesis largely studied to understand cultural changes.
-Interesting additional work could be, for example, the comparison between trade mechanisms and prestige biased cultural transmission.
-
 This article has proposed a framework to study both cultural change mechanisms and trade mechanisms.
@@
 
-In future works numerous, more realistic and complex dynamics can be studied in the same model.
-First the constraints on the production could be relaxed so that each agent can choose the products it wishes to produce at the current time step.
-Moreover, meterological factors can modify the quality of the production (noisy outcome of the process) thus making the process more realistic and more complex~\shortcite{bentley_specialisation_2005}.
+The successful implementation of a trade model within our framework shows that trade models can be viewed as a particular implementation of the cultural evolutionary framework.
+This aspect which has not been studied before, opens a new line of thinking on the weight of trade mechanisms within cultural change.
+Notably, we have shown that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis, which is the reference in the study of cultural changes.
+Within the trade model, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
+Interestingly, we have not find references pointing at the ability of trade mechanisms to keep a relatively large diversity in the frequency distribution.
+We suspect that this is mainly because it is not common to compare results of trade models to other cultural evolution models.
+It would therefore be interesting to compare the frequency distributions obtained by our model and the ones observed in current or past economies.
+On the side of cultural transmission, the results obtained can also be compared to the ones obtained when prestige biased cultural transmission is used.
+The idea behind this last comparison, is that trade could be interpreted as a particular prestige biased cultural transmission and therefore be fully integrated within the cultural evolutionary frameworks.
 
-The goods themselves can be of different type: ``vital'' or ``common''.
-The absence of a ``vital'' good would then lead to the death of the agent.
-Thus making the need to trade at the best price even stronger for the agent.
-The ``common'' goods on the other sides would be interesting to observe the evolution of a culture out of the necessity of survival.
-The mechanisms behind the strong use of a non-essential product can then be studied.
-Naturally in the study of these questions the consumption function would change trough time for the agent.
-
-The trading theories studied also can be extended to the \emph{Prospect Theory}~\shortcite{kahneman_prospect_1979} which proposes to study more realistic trade mechanisms taking into account the biases of humans.
-Another economical framework we envision is the Agent based Computational Economy, ACE, which is  addressing economical problems raising from the interactions of a large number of agents~\shortcite{tesfatsion_introduction_2001}.
-On top of these trading theories the influence of the network of trades by itself can be studied.
-Various networks can be envisioned ranging from fully connected to small world, and taking into account possible delays or the sudden rupture of a link.
-
-On the cultural transmission side, the vector value could be learned using any mechanism of ``social learning'' (as defined by \shortcite{lycett_cultural_2015}) known in the literature (teaching, different kind of copying mechanisms,\ldots) and/or integrate any cognitive/environmental bias that could be studied (see again \shortcite{lycett_cultural_2015} for some kind of bias that could be implemented).
-Agents could be also endowed with self-adaptation abilities implemented thanks to Reinforcement Learning or Developmental Learning.
-Another possible track to implement the self-adaptation abilities is to rely on the cognitive approaches that propose to model the complexity of the human behaviour in general representations such as BDI.
-
-\xrc{I think that this section can be revised once we get the results (e.g. less future work, more interpretation of results)}
+In future works more realistic and complex dynamics can be studied in the same model.
+First, multiple implementations of the production mechanism can be studied so as to increase the number of goods per agent and include factors such as the meteorology or the various type of goods.
+Moreover, the introduction of the distinction between ``vital'' and ``common'' goods will be useful for the creation of models studying in further details the interaction between trade and cultural transmission.
+The trading mechanism itself can be naturally implemented in different ways, each reflecting a specific theory, and thus allowing the comparison of the different theories.
+Moreover, the trade network (which in this work can be interpreted as fully connected) can be modified to study the effect of slow connections or the rupture of certain connections.
+Finally, the agent themselves could become more complex and be endowed with the ability to learn behaviours which would again produce more realistic simulations.
 
 \section{Acknowledgements}
-
-\todo{upload and put an url, complete cite mare nostrum, put nb of hours per run (or the total)}
 
@@
 R was used for figures and statistical analysis \shortcite{rdev_2012}.
+The simulations have been done in the supercomputer MareNostrum at Barcelona Supercomputing
+Center - Centro Nacional de Supercomputación (The Spanish National Supercomputing Center).
 The source code of the model is licensed under a GNU General Public License and will be available for download at publication.

### 2015-04-08 article.tex
graphs with G=3 & n=500

--- 2015-04-07 article.tex
@@
 The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
-This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission~\shortcite{heyes_social_1994,henrich_evolution_2003}.
-Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendency to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.
+This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmissio~\shortcite{heyes_social_1994,henrich_evolution_2003}.
+Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendendy to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.
 
@@
 \begin{equation}
-	 W^o=(w_g^o = v_g^o,w_k^o= \frac{v_k^o}{v_g^o}) 
+	 W^o=(w_g^o = v_g^o,w_k^o= \frac{v_k^o}{v_g^o}), \quad
 	 W^r=(w_k^r = v_k^r,w_g^r= \frac{v_g^r}{v_k^r}) 
@@
 \midrule
-Number of goods & 4 \\
-Number of agents & 800 \\
+Number of goods & 3 \\
+Number of agents & 500 \\
 Mutation probability & .004 \\
@@
 TradeThreshold & 100  \\
-TimeSteps & 200000 \\
+TimeSteps & 10000 \\
 \bottomrule
@@
 	\end{center}
-	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right)\label{fig:allMutation}}
+	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right). Each plot is the mean obtenaid for 100 runs.\label{fig:allMutation}}
 \end{figure}
@@
 	\end{center}
-	\caption{Frequency distribution for the neutral and the trade models}
+	\caption{Frequency distribution for the neutral and the trade models. Each points represent the mean for 100 runs.}
 	\label{fig:2setDi}
@@
 		 Neutral Model & Trade Model \\
-		 \includegraphics[width=5cm]{img/ScoreEvolutionForRandom-G2N500.pdf}
-		 & \includegraphics[width=5cm]{img/ScoreEvolutionForTrade-G2N500.pdf}
+		 \includegraphics[width=5cm]{img/ScoreEvolutionForRandom-G3N500.pdf}
+		 & \includegraphics[width=5cm]{img/ScoreEvolutionForTrade-G3N500.pdf}
 
 	\end{tabular}
-	\caption{Evolution of the score within the two different models.}%%
+	\caption{Evolution of the score within the two different models for two typical run with 500 agents and 3 goods evolving during 10000 timestep}%%
 	\label{fig:scoreEvol}
@@
 	\begin{center}
-		\includegraphics[width=7cm]{img/ClearingPriceDistanceEvolutionForTrade-G2N500.pdf}
+		\includegraphics[width=7cm]{img/ClearingPriceDistanceEvolutionForTrade-G3N500.pdf}
 	\end{center}
-	\caption{Evolution of the mean difference for each good of the estimated value $v_g$ and its optimal value as given by \ref{eq:optimum}. Means computed for 100 run and 2 goods. }
+	\caption{Evolution of the mean of the difference between the estimated value $v_g$ and the optimal value $\tilde{v}_g$ (as calculated with the equations~\ref{eq:optimum}) of the good $g$.
+This mean is plotted for 100 runs with 3 goods and 500 agents.}
 	\label{fig:ratioEvol}

### 2015-04-08 article.tex
slight modification

@@
 \newcommand{\added}[2]{\textcolor{#1}{#2}}
-%\renewcommand{\memo}[2]{} % uncomment in the final version
-%\renewcommand{\added}[2]{#2} % uncomment in the final version
+\renewcommand{\memo}[2]{} % uncomment in the final version
+\renewcommand{\added}[2]{#2} % uncomment in the final version
 \newcommand{\todo}[1]{\memo{red}{TODO: #1\\}}
@@
 
-\title{Modelling the co-evolution of trade and culture in the Roman market}
+\title{Modelling the Co-evolution of Trade and Culture in the Roman market}
 
@@
 
-This work explores these co-evolutionary dynamics using a theoretical Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\cite{lake_trends_2014}.
+This work explores these co-evolutionary dynamics using a theoretical Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\shortcite[3]{lake_trends_2014}.
 Next section defines the model, which is based on unbiased transmission mechanisms and simple exchange dynamics.
@@
 	\begin{tabular}{ll|llll}
-		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et al 2004}\\
+		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et. al. 2004}\\
 			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
@@
 	\end{tabular}
-	\caption{Mean \& SD are calculate on 100 run.}
+	\caption{Mean \& SD are calculate on 100 runs for our results, and 5 runs for Bentley et. al. 2004.}
 	\label{tab:mualpha}
@@
 
-\jm{Simon, do you have a comment on the table ? Like does it fit what is found in other articles ?}
+We can see in this table that our results are close to those obtained by \shortcite[3]{bentley_random_2004}.
+In the same way \shortcite[3]{mesoudi_random_2009} also find similar value of $\alpha$ for similar values of $\mu$ and for the same number of agents.
+In the other hand it is difficult to know if the slight difference between those study are statistically significant as for the two previous studies the mean of $\alpha$ are computed using only between five runs, against 100 in our case.
 
@@
 We observe that prices are indeed converging to the optimal prices which means that our innovation and imitation process are valid trade mechanisms.
-Notably, they produce results similar to the ones obtained in~\shortcite{gintis_emergence_2006}.
+Notably, they produce results similar to the ones obtained in~\shortcite[3]{gintis_emergence_2006}.
 

### 2015-04-08 article.tex
again few modif.

@@
 	\end{center}
-	\caption{The payoff depending on the estimated value and the effective needs $n(g)$ of a good.}
+	\caption{The payoff depending on the quantity owned of a given good and the effective needs $n(g)$ for this good.}
 	\label{fig:fit}
@@
 Number of agents & 500 \\
-Mutation probability & .004 \\
-Innovation probability & .001\\
+Mutation probability ($\mu$) & 0.004 \\
+Innovation range ($\beta$) & 0.005\\
 CulturalStep &  10 \\
@@
 	\end{tabular}
-	\caption{Evolution of the score within the two different models for two typical run with 500 agents and 3 goods evolving during 10000 timestep}%%
+	\caption{Evolution of the score within the two different models for two typical run with 500 agents and 3 goods evolving during 10000 timestep.}%%
 	\label{fig:scoreEvol}
@@
 	\end{center}
-	\caption{Evolution of the mean of the difference between the estimated value $v_g$ and the optimal value $\tilde{v}_g$ (as calculated with the equations~\ref{eq:optimum}) of the good $g$.
-This mean is plotted for 100 runs with 3 goods and 500 agents.}
+	\caption{Evolution of the mean of the difference between the estimated value $v^i_g$ and the optimal value $\tilde{v}^i_g$ (as calculated with the equations~\ref{eq:optimum}) for a good $g$.
+As the optimal value $\tilde{v}^i_g$ depend on which goods is produced by $i$, the mean is computed within all the agents that produce the same good.
+}
 	\label{fig:ratioEvol}
@@
 The model was created using Pandora \shortcite{rubiocampillo_2014}.
-R was used for figures and statistical analysis \shortcite{rdev_2012}.
+R was used for figures and statistical analysis \shortcite{rdev_2012} the estimation of the $\alpha$ parameters have been computed with the R package poweRlaw \cite{gillespie_fitting_2015}.
 The simulations have been done in the supercomputer MareNostrum at Barcelona Supercomputing
@@
 \end{document}
+][s[s

### 2015-04-08 article.tex
various corrections

--- 2015-04-08 article.tex
@@
 
-\title{Modelling the co-evolution of trade and culture in the Roman market}
+\title{Modelling the Co-evolution of Trade and Culture in the Roman Market}
 
@@
 
-Cultural change comprise the collection of processes that promotes or inhibits the spread of information by social interaction within a population~\shortcite[3]{boyd_origin_2005}.
-An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution~\shortcite{henrich_evolution_2003}.
+Cultural change comprises the collection of processes that promotes or inhibits the spread of information by social interaction within a population~\cite{boyd_origin_2005}.
+An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution~\cite{henrich_evolution_2003}.
 
 Several studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependence properties.
-These analysis often compare evidence against neutral models~\shortcite{neiman_stylistic_1995}.
-They assume that traits do not affect the fitness of the individual that acquire it; within this context its transmission is unbiased, and its success will depend on its popularity amongst the rest of individuals.
+These analysis often compare evidences against neutral models~\cite{neiman_stylistic_1995}.
+They assume that traits do not affect the fitness of the individual that acquires it; within this context its transmission is unbiased, and its success will depend on its popularity amongst the rest of individuals.
 This neutral model generates a distinctive pattern of frequency distribution of traits, identified as a power law.
-It can be replicated with a simple random copying transmission mechanism~\shortcite{bentley_random_2004}: an individual will copy the traits of a randomly chosen individual with a given probability.
+It can be replicated with a simple random copying transmission mechanism~\cite{bentley_random_2004}: an individual will copy the traits of a randomly chosen individual with a given probability.
 This copy can potentially introduce some errors in the acquired trait, which account for innovation processes.
 The individual will in turn continue to spread these cultural traits which will be further adopted by other individuals.
-This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission~\shortcite{heyes_social_1994,henrich_evolution_2003}.
+This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission~\cite{heyes_social_1994,henrich_evolution_2003}.
 Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendency to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.
 
-This approach can be used as the starting point to analyse patterns of cultural change to explore frequency-dependance in archaeological contexts~\shortcite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010}.
-However, the fact that archaeology records fragmented material culture presents some challenges on the validity of the method~\shortcite{kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
+This approach can be used as the starting point to analyse patterns of cultural change to explore frequency-dependance in archaeological contexts~\cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010}.
+However, the fact that archaeology records fragmented material culture presents some challenges on the validity of the method~\cite{kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
@@
 Networks of good exchanges are being increasingly recognised as key elements that structured ancient societies~\shortcite{temin_market_2001,remesal_epnet_2014,brughmans_connecting_2010}.
-The scenarios where this process emerge suggest a complex bias in the selection of cultural traits, which at the same time are also identified as economic goods~\shortcite{bentley_specialisation_2005,macmillan_agent-based_2008}.
+The scenarios where this process emerge suggest a complex bias in the selection of cultural traits, which at the same time are also identified as economic goods~\cite{bentley_specialisation_2005,macmillan_agent-based_2008}.
 Trasmission is not neutral anymore, as different prices for each good will introduce a dynamic content bias.
@@
 On top of these elements four processes are used: \emph{production}, \emph{cultural transmission}, \emph{innovation} and \emph{trade}.
-The \textit{production} process describes the creation of goods by the agent.
-Once a good is produced by an agent $i$ it is added its quantity vector ($Q^i$).
+The \emph{production} process describes the creation of goods by the agent.
+Once a good is produced by an agent $i$ it is added to its quantity vector ($Q^i$).
 The \emph{trade} process models the exchange of goods between the agents which results in a modification of the quantity vectors ($Q^i$).
 The amount of goods exchanged is computed by the agents concerned by the trade, within the \emph{trade} process, based on their value vectors ($V^i$).
-Within the \textit{cultural transmission} process an agent $i$ can copy the value vector ($V^j$) of an agent $j$, where $j \neq i$.
-The \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{cultural transmission} process in that the modification is done without reference to the other agents.
-Finally, .
+Within the \emph{cultural transmission} process an agent $i$ can copy the value vector ($V^j$) of an agent $j$, where $j \neq i$.
+Finally, the \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{cultural transmission} process in that the modification is done without reference to the other agents.
 
@@
 Between the lines 11 and 19 is presented the part of the pseudo-code describing the instructions that will be repeated for each iteration of the simulation.
-One can note that the trading process is performed at every iteration while the imitation and innovation processes are executed only every $CulturalStep$.
-The idea behind this is to perform the imitation based on a score that reflects the performance of the agent and not only one lucky or unlucky trading round.
-The timestep number used in the figures of this article refers to the number of times the \emph{cultural transmission} and \emph{innovation} processes have been called.
+One can note that the \emph{trade} process is called at each iteration while the \emph{cultural transmission} and \emph{innovation} processes are executed only every $CulturalStep$.
+The idea behind this is to perform the \emph{cultural transmission} based on a score that reflects the performance of the agent and not only one lucky or unlucky trading round.
+The timestep number used in the figures of this article refers to the number of times the \emph{cultural transmission} and \emph{innovation} processes are called.
 
@@
 In order to validate our model we first reproduce common results from the literature on cultural transmission.
-We then show that it is possible to transform our model to fit processes that are economically sound.
+We then show that it is possible to transform our model to fit processes that are economically sound, i.e.
+.
 To achieve these two goals, we have design for each one a specific set of implementations of the four core processes (production, trade, cultural transmission and innovation).
@@
 
-\subsection{Cultural Transmission}\label{sec:culturalTrans}
+\subsection{Cultural Transmission Model}\label{sec:culturalTrans}
 
-The first set of implementations is designed to reproduce a scenario of unbiased transmission, where each good is a cultural trait without intrinsic positive or negative weight \shortcite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
+The first set of implementations is designed to reproduce a scenario of unbiased transmission, where each good is a cultural trait without intrinsic positive or negative weight \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
 Under this hypothesis, the processes of \emph{production} and \emph{trade} are not relevant, and as a consequence, they do not modify the content of the quantity vectors of the agents.
 
-Unbiased transmission is implemented using ``random copy'': each agent has a low probability to pick randomly one agent among all and copy its vector of values.
-The \emph{innovation} process, termed ``unbounded'', is triggered with a low probability and draw a new random value to replace an element $v^i_j$.
-The imitation and innovation probabilities are presented with other parameters in table~\ref{tab:parameters}.
+Unbiased \emph{cultural transmission} is implemented using ``random copy'': each agent has a low probability to pick randomly one agent among all and copy its vector of values.
+The \emph{innovation} process, termed ``unbounded'', is triggered with a low probability ($\mu$) and draw a new random value to replace an element $v^i_j$.
+The probabilities to trigger \emph{cultural transmission} and \emph{innovation} are presented with other parameters in table~\ref{tab:parameters}.
 
-The neutral hypothesis states that the ``random copy'' transmission and the ``unbounded'' innovation process used under a fixed population size leads to a \emph{power law} distribution of the frequency for the different cultural variants.
+The neutral hypothesis states that the ``random copy'' transmission and the ``unbounded'' innovation process used under a fixed population size leads to a distribution of frequency of cultural variants termed \emph{power law}.
 This distribution is characterized by a small number of very frequent traits and a large number of very rare traits.
@@
 More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$, where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
-We will therefore attempt to fit as good as possible the results obtained with this set of implementations to the ``power law'' distribution by modifying the $\alpha$ parameter.
+We will therefore attempt to fit as well as possible the results obtained with this set of implementations to the ``power law'' distribution by modifying the $\alpha$ parameter.
 
@@
 
-The second set of implementations of the core processes aims at producing economical dynamics.
-We are interested in the exchange of goods between agents when they can modify the prices at which they sell and buy goods.
+The second set of implementations of the four processes of the framework aims at producing economical dynamics.
+We are interested in the exchange of goods between agents in a barter process where each agent can choose its prices of exchange.
 We want to implement simple processes leading to the convergence of all prices to values acceptable by all agents, i.e.
-we would like to observe, at the end of an experiment, all the agents using the same set of prices which allow them to trade efficiently.
+we would like to observe, at the end of an experiment, all the agents using a set of prices which allow them to trade efficiently.
 
@@
 
-The \emph{score} $s^i$ of an agent $i$ reflects the ability of this agent to obtain the goods it needs.
-It is maximum when the quantity vector of an agent is equal to its need vector and lower proportionally to the distance between the need vector and the quantity vector.
+The \emph{score} $s^i_j$ of an agent $i$ reflects the ability of this agent to obtain the quantity of good $j$ it needs.
+It is maximum when the quantity $q^i_j$ of an agent is equal to its need vector $n^i_j$ and lower proportionally to the distance between the need vector and the quantity vector.
 It is formally computed as follow for agent $i$:
@@
 \begin{equation}\label{eq:score}
-s^i = \begin{cases}
+s^i_j = \begin{cases}
  s_{max}=1 & \text{if $q^i_j = n_j$}\\
@@
 
+The complete score of an agent $i$ is termed $s^i$ and corresponds to the sum of the $s^i_j$.
 The agents will choose the agent from whom the price vector should be copied among the agents that produce the same good and have the highest score.
-In practice, a fixed proportion of the less successful agents will copy the prices of the most successful agent.
+In practice, the bottom two percent of the agents (in terms of score) will copy the prices of the top two percent.
 
@@
 Briefly summarised, for each good that it does not produce, an agent will trade with the first parter that offer an acceptable trade, i.e.
-the agent that proposes a satisfiable ratio between the other good and the good produced by the agent.
+an agent that proposes a satisfiable ratio between the other good and the good produced by the agent.
 
 In more details, the trading phase starts by the agent looking at a first random agent producing another good. 
-Let $o$ be an agent producing $g$ that proposes a trade and $r$ an agent producing $k$ that receives the proposition.
+Let $o$ be an agent producing $g$ who proposes a trade and $r$ an agent producing $k$ that receives the proposition.
 As explained earlier, each has a quantity of good $Q^o$ and $Q^r$.
@@
 
-The conditions \ref{eq:constraintQty} insure that both agents have enough goods in their inventory to realise the trade while the conditions \ref{eq:constraintWill} insure that the quantities of each good fit the will of both agents.
+The conditions \ref{eq:constraintQty} insure that both agents have enough goods in their inventory to realise the trade while the conditions \ref{eq:constraintWill} insure that the quantities of goods fit the will of both agents.
 
 If a trade is possible the two agents will exchange the agreed quantities.
-If the trade is not possible, the agent will continue to look at random partners for this good until either a good is found or $TradeThreshold$ agents have been tried.
+If the trade is not possible, the agent will continue to look at random partners for this good until either a partner is found or $TradeThreshold$ agents have been tried.
 At this point the agent will try to trade with agents producing another good.
@@
 	\scriptsize
-		\For{$j \in Goods \And j \neq produced^i $}
+		\For{$j \in Goods \And j \neq produced^o $}
 			\State $tradeAttempt = 0$
@@
 
-For the cultural transmission model we run experiments with two setups.
-The first is composed of 1 good and two population sizes: 250 and 500 agents ; the second is composed of 3 goods and 500 agents.
-For both of these setups 4 different values of $\alpha$ are studied: $\{0.004,0.016,0.064\}$.
-For each $\alpha$ we present the results obtained with 100 runs of 10000 timestep each.
+The cultural transmission model is tested through ten experimental setups.
+The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and four values of $\mu$ (0.004,0.016 and 0.064).
+The remaining four experimental setups are using 3 goods, 500 agents and the same four values of $\mu$ (0.004,0.016 and 0.064).
+For each setup we have performed 100 runs of 10000 timestep each.
 
-For the trading model we run also all experiments with 3 goods and 500 agents.
-Again 100 runs of 10000 timesteps are performed.
-As described in section~\ref{sec:trade}, one timestep is corresponds to the call of the \emph{cultural transmission} and \emph{innovation} processes.
+The trading model is tested through four experimental setups using 3 goods, 500 agents and the same four values of $\mu$ (0.004,0.016 and 0.064). Again 100 runs of 10000 timesteps are performed.
 
-The whole set of parameters used are presented in table~\ref{tab:parameters}.
+The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}.
 
@@
 Between, twos such steps, the agent exchange goods given their own prices.
-Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \shortcite{bentley_random_2004,mesoudi_random_2009}.
+Therefore we choose to run our simulation during 10000 step which correspond the 1000 time steps used by \cite{bentley_random_2004,mesoudi_random_2009}.
 
@@
 \midrule
-Number of goods & 3 \\
-Number of agents & 500 \\
-Mutation probability & .004 \\
-Innovation probability & .001\\
+Number of goods & $\{1,3\}$ \\
+Number of agents & $\{250,500\}$ \\
+Innovation probability ($\mu$) & $\{0.004,0.016,0.064\}$ \\
+Cultural transmission probability & .001\\
 CulturalStep &  10 \\
@@
 
-We first analyse the result obtained in the ``neutral model" as presented in section~\ref{sec:culturalTrans}.
-Figure~\ref{fig:allMutation} presents the results obtained with $\mu$ varying $\in {.004,.008,.016,.064}$, 1 good and two population sizes: 250 and 500 agents.
-The distribution of variants obtained is shown in figure~\ref{fig:allMutation}.
-In this graph the relative frequencies of the values obtained is analysed.
-The y-axis of the graph shows the frequencies of the variants of the vector values, the x-axis shows how many variant achieves such frequencies and the line represents the average of the frequencies obtained across all runs.
+We first analyse the result obtained in the ``cultural transmission model".
+Figure~\ref{fig:allMutation} presents the results obtained in the setups using 1 good, two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064).
+The figure represents the average (across all the runs) of the distribution of variants obtained through all experiments.
+The y-axis shows the frequencies of the variants of the vector values, the x-axis shows how many variant achieves such frequencies.
 Both axes are in a logarithmic scale.
+Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
 
-\begin{figure}[!hbp]
+\begin{figure}[h]
 	\begin{center}
@@
 
-In the figure~\ref{fig:allMutation} one can observe that the lower the mutation rate, the closer from a line the result is.
-This line corresponds to the ``power law" distribution explained in section~\ref{sec:culturalTrans} and is typical of the result obtained under the ``neutral model".
-Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
+We observe that the lower the mutation rate, the closer from a line the result is.
+This line corresponds to the ``power law" distribution explained in section~\ref{sec:culturalTrans} and is typical of the result obtained under the ``neutral hypothesis".
+Nevertheless, under all parameters tested, the value vectors exhibit power law like distribution.
+The number of agents however has no influence on the distributions obtained.
 
-Under all parameters tested the value vectors exhibit power law like distribution.
-It would then be interesting to analyse the shape of such distribution.
-In order to perform this study a linear regression is used to fit the curve obtained to a function of the form $P(v)=C/v^\alpha $.
-The mean value of the $\alpha$ parameters obtained and their standard deviation is presented in table~\ref{tab:mualpha}.
+It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.
+A linear regression is used, for each run, to fit the curve obtained to a function of the form $P(v)=C/v^\alpha $.
+The mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup) and their standard deviation is presented in table~\ref{tab:mualpha}.
+We also present side-by-side the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.
 
@@
 
-\jm{Simon, do you have a comment on the table ? Like does it fit what is found in other articles ?}
+We can see in this table that our results are close to those obtained by \cite{bentley_random_2004}.
+With a similar methodology and parameters~\cite{mesoudi_random_2009} find similar values of $\alpha$.
+However, it is difficult to know if the slight differences observed between our work and those previous studies are statistically significant as the two previous studies rely on only five runs for the computation of the mean of $\alpha$ (against 100 in our case).
 
@@
 
-In order to understand the effect of introduction of trading mechanisms we compare first the distribution of values obtained in the two models.
-The result of this comparison is in the figure~\ref{fig:2setDi}.
+In order to understand the effect of introduction of trading mechanisms we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``cultural transmission model''.
+The figure~\ref{fig:2setDi} presents the results obtained from 100 runs for each model.
+All runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.
 
@@
 In more details, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
-Additional investigation have shown us that this is due to the \emph{innovation} process used in the trade model which prevents the creation of totally random new price and lead to a fewer proportion of prices that appear rarely in the population.
+Additional investigations (not presented here) have shown that this is due to the \emph{innovation} process used in the trade model which prevents the creation of totally random new price and therefore leads to the creation of few similar prices obtaining high scores.
 
@@
 
-We now study the results obtained in more detail by investigating the ability of the population of agents to find the good price to perform exchanges between each other.
-This is done by observing the score of all agents in each of the two different models.
-The results obtained are presented in figure~\ref{fig:scoreEvol}.
+We now study the results obtained in more detail by investigating the ability of the population to find the good price to perform exchanges between each other.
+This is done first by observing the score of all agents in each of the two different models.
+The figure~\ref{fig:scoreEvol} uses again the results obtained from 100 runs for each model where all runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.
+The figure is showing, as boxplots, the score computed thanks to equation (\ref{eq:score}) for all agents of all runs.
+The y-axis shows the score computed and the x-axis shows the timesteps.
+The left plot shows the results obtained in the ``cultural transmission'' model and the right plot shows the results obtained in the ``trade'' model.
 
@@
 
-As expected, the neutral model scores vary randomly.
-Sometimes ``trends'' appear, where a bigger proportion of individuals adopt a better price that allow agents to reach better score (such as between \simon{adapt to last graph}), but such good score fall back as soon as another trend appears.
-In the other hand, with the trade model, the score of all the agents increase.
-As the selection mechanism allow them to know who find better vectors of prices, they will slightly adopt prices vector that allow all of them to reach better scores.
+As expected, the scores within the neutral model vary randomly.
+``Trends'' may appear, where a bigger proportion of individuals adopt a better price that allow agents to reach better score (such as around iteration 8000), but such good score fall back as soon as another trend appears.
+However, with the trade model, the score of all the agents increase.
+As the selection mechanism allow them to know who has found better vectors of prices, they will progressively adopt prices vector that allow all of them to reach better scores.
 
-We pursue the analysis of the economical aspect by observing the prices reached within the trade model.
-As explained in the section~\ref{sec:trade} we expect that the trade imitation and innovation processes will produce a convergence toward a set of price for each good that will allow agents to exchange optimally the good they produce with the other goods.
-To verify this assumption we analyse the prices reached.
-These are presented in figure~\ref{fig:ratioEvol} as a deviation from the optimal price.
-Record that the optimal price is the ratio between the need of the needed good and the produced good.
+The previous figure showed the capacity for the ``trade'' model to increase its score but did not analyse the exact prices used.
+As explained in the section~\ref{sec:trade} we expect that the trade \emph{cultural transmission} and \emph{innovation} processes will produce a convergence toward a set of price for each good that will allow agents to exchange optimally the good they produce with the other goods.
+To verify this assumption we analyse the prices reached during the simulations.
+These are presented in figure~\ref{fig:ratioEvol} for the 100 runs relying the experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.
+For all runs, all agents and at each iteration we compute the difference between the price used by the agent $V_g$ and the the optimal price $\tilde{V}_g$.
+Record that the optimal price for a good is the product between the need for the good and the need for the produced good.
+All the measures performed are presented as boxplots.
 
@@
 
-We observe that prices are indeed converging to the optimal prices which means that our innovation and imitation process are valid trade mechanisms.
-Notably, they produce results similar to the ones obtained in~\shortcite{gintis_emergence_2006}.
+We observe that prices are indeed converging to the optimal prices which means that the agents within the ``trade'' model are indeed improving their scores by reaching the optimal prices.
+Notably, a similar variation of prices was observed in the closely related economical model of~\cite{gintis_emergence_2006}.
+This variation of the prices to the optimum offers an additional conformation of the validity of the ``trade'' model.
 
@@
 
-The model was created using Pandora \shortcite{rubiocampillo_2014}.
-R was used for figures and statistical analysis \shortcite{rdev_2012}.
+The model was created using Pandora \cite{rubiocampillo_2014}.
+R was used for figures and statistical analysis \cite{rdev_2012}.
 The simulations have been done in the supercomputer MareNostrum at Barcelona Supercomputing

### 2015-04-08 article.tex

@@
 Innovation probability ($\mu$) & $\{0.004,0.016,0.064\}$ \\
+Innovation range ($\beta$) & 0.005\\
 Cultural transmission probability & .001\\
@@
 R was used for figures and statistical analysis \cite{rdev_2012}.
-The simulations have been done in the supercomputer MareNostrum at Barcelona Supercomputing
-Center - Centro Nacional de Supercomputación (The Spanish National Supercomputing Center).
+The estimation of the $\alpha$ parameters have been computed with the R package poweRlaw \cite{gillespie_fitting_2015}.
+The simulations have been done in the supercomputer MareNostrum at Barcelona Supercomputing Center - Centro Nacional de Supercomputación (The Spanish National Supercomputing Center).
 The source code of the model is licensed under a GNU General Public License and will be available for download at publication.

### 2015-04-08 article.tex
fix some stuff but remains the exploration of good number problem (cf mail to jm)

@@
 $$\forall i \in Pop, \quad Q^i = (q^i_1,\cdots,q^i_n) $$
-
 where $Q^i$ is the total list of possessions of agent $i$, and $q^i_j$ is the number of goods of type $j$ that agent $i$ posses.
@@
 Under this hypothesis, the processes of \emph{production} and \emph{trade} are not relevant, and as a consequence, they do not modify the content of the quantity vectors of the agents.
+%%simon: I would rather say  something like :
+%%Under this hypothesis, the processes of \emph{production} and \emph{trade} are not relevant as their results will not affect in any way the evolution of the system.
+%% but we could alos simply remove the sentence?
 
@@
 %Since this hypothesis has been verified in previous works implementing similar \emph{imitation} and \emph{innovation} mechanisms, we expect in this work the observation of a similar ``power law' distribution.
-More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$, where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
+More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$ where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
 We will therefore attempt to fit as well as possible the results obtained with this set of implementations to the ``power law'' distribution by modifying the $\alpha$ parameter.
@@
 In this set of implementations, each agent is producing only one type of good.
-The type good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
+The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
 
@@
 The \emph{score} $s^i_j$ of an agent $i$ reflects the ability of this agent to obtain the quantity of good $j$ it needs.
-It is maximum when the quantity $q^i_j$ of an agent is equal to its need vector $n^i_j$ and lower proportionally to the distance between the need vector and the quantity vector.
-It is formally computed as follow for agent $i$:
+It is maximum when the quantity $q^i_j$ that an agent $i$ own of the good $j$ is equal to the need $n_j$ for the good $j$ and lowers proportionally to the distance between the need vector and the quantity vector.
+It is formally computed as follow for agent $i$ and the good $j$:
 
@@
 During the trading phase the value associated to a good by an agent corresponds to the subjective price of the good for this agent.
-Briefly summarised, for each good that it does not produce, an agent will trade with the first parter that offer an acceptable trade, i.e.
+Briefly summarised, for each good that it does not produce, an agent will trade with the first partner that offers an acceptable trade, i.e.
 an agent that proposes a satisfiable ratio between the other good and the good produced by the agent.
@@
 
-The cultural transmission model is tested through ten experimental setups.
-The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and four values of $\mu$ (0.004,0.016 and 0.064).
+The neutral model is tested through ten experimental setups.
+The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064).
 The remaining four experimental setups are using 3 goods, 500 agents and the same four values of $\mu$ (0.004,0.016 and 0.064).
@@
 \section{RESULTS}
-\subsection{Random cultural transmission and random innovation process}
+\subsection{Neutral Model}
 
-We first analyse the result obtained in the ``cultural transmission model".
+We first analyse the result obtained in the ``neutral model".
 Figure~\ref{fig:allMutation} presents the results obtained in the setups using 1 good, two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064).
@@
 
-In order to understand the effect of introduction of trading mechanisms we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``cultural transmission model''.
+In order to understand the effect of introducing trading mechanisms, we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``cultural transmission model''.
 The figure~\ref{fig:2setDi} presents the results obtained from 100 runs for each model.
@@
 \end{figure}
-
-%\begin{table}[h]
-%	\centering
-%	\begin{tabular}{lcccc}
-%		& A & B & C & D\\
-%A & X& \includegraphics[width=5cm]{img/A-B.pdf}&\includegraphics[width=5cm]{img/A-C.pdf}&\includegraphics[width=5cm]{img/A-D.pdf}\\
-%B & X& X &\includegraphics[width=5cm]{img/B-C.pdf}&\includegraphics[width=5cm]{img/B-D.pdf}\\
-%C & X& X & X &\includegraphics[width=5cm]{img/C-D.pdf}\\
-%	\end{tabular}
-%	\caption{Experimental Setup}
-%	\label{tab:allRes}
-%\end{table}
 
@@
 These are presented in figure~\ref{fig:ratioEvol} for the 100 runs relying the experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.
-For all runs, all agents and at each iteration we compute the difference between the price used by the agent $V_g$ and the the optimal price $\tilde{V}_g$.
-Record that the optimal price for a good is the product between the need for the good and the need for the produced good.
-All the measures performed are presented as boxplots.
+For all runs, all agents and at each iteration we compute the difference between the price used by the agent $V_g$ and the optimal price $\tilde{V}_g$.
+Record that the optimal price for a good that an agent does not produce is the product between the need for this good and the need for the produced good, while the optimal price for the produced good is simply the need for it.
+All the measures performed are presented as boxplots where the results for 100 runs are condensed.
 
@@
 	\end{center}
-	\caption{Evolution of the mean of the difference between the estimated value $v^i_g$ and the optimal value $\tilde{v}^i_g$ (as calculated with the equations~\ref{eq:optimum}) for a good $g$.
-As the optimal value $\tilde{v}^i_g$ depend on which goods is produced by $i$, the mean is computed within all the agents that produce the same good.
+	\caption{Evolution of the mean of the difference between the estimated value $v^i_g$ and the optimal value $\tilde{v}^i_g$ (as calculated with the equations~\ref{eq:optimum}) for a good $g$ and an agent $i$.
+As the optimal value $\tilde{v}^i_g$ depends on which good is produced by $i$, the mean of the difference between the estimated price and the optimal one is computed between all the agents that produce the same good.
+The figure represents this mean computed at each timestep for each goods, for each groups of agents and for 100 runs in a setup with 500 agents and 3 goods.
 }
@@
 \end{document}
-][s[s

### 2015-04-08 article.tex
harmonization neutral model and trading model

@@
 We then compare the results obtained by the two models, thus validating the structure of the framework.
-Finally, to validate our trade model we study the price structure obtained.
+Finally, to validate our trading model we study the price structure obtained.
 
@@
 
-\subsection{Cultural Transmission Model}\label{sec:culturalTrans}
+\subsection{Neutral Model}\label{sec:culturalTrans}
 
@@
 \begin{figure}[h]
-	\begin{center}
-		\includegraphics[width=6cm]{img/allmuRandMaxN250.pdf}
+	\centering
+	\begin{tabular}{ c c}
+		 $N=250$ & $N=500$ \\
+		\includegraphics[width=6cm]{img/allmuRandMaxN250.pdf}&
 		\includegraphics[width=6cm]{img/allmuRandMaxN500.pdf}
-	\end{center}
+	\end{tabular}
 	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right). Each plot is the mean obtenaid for 100 runs.\label{fig:allMutation}}
@@
 
-In order to understand the effect of introducing trading mechanisms, we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``cultural transmission model''.
+In order to understand the effect of introducing trading mechanisms, we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``neutral model''.
 The figure~\ref{fig:2setDi} presents the results obtained from 100 runs for each model.
@@
 	\end{center}
-	\caption{Frequency distribution for the neutral and the trade models. Each points represent the mean for 100 runs.}
+	\caption{Frequency distribution for the neutral and the trading models. Each points represent the mean for 100 runs.}
 	\label{fig:2setDi}
@@
 In more details, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
-Additional investigations (not presented here) have shown that this is due to the \emph{innovation} process used in the trade model which prevents the creation of totally random new price and therefore leads to the creation of few similar prices obtaining high scores.
+Additional investigations (not presented here) have shown that this is due to the \emph{innovation} process used in the trading model which prevents the creation of totally random new price and therefore leads to the creation of few similar prices obtaining high scores.
 
@@
 The y-axis shows the score computed and the x-axis shows the timesteps.
-The left plot shows the results obtained in the ``cultural transmission'' model and the right plot shows the results obtained in the ``trade'' model.
+The left plot shows the results obtained in the ``cultural transmission'' model and the right plot shows the results obtained in the trading model.
 
@@
 	\begin{tabular}{ c c}
-		 Neutral Model & Trade Model \\
+		 Neutral Model & Trading Model \\
 		 \includegraphics[width=5cm]{img/ScoreEvolutionForRandom-G3N500.pdf}
@@
 ``Trends'' may appear, where a bigger proportion of individuals adopt a better price that allow agents to reach better score (such as around iteration 8000), but such good score fall back as soon as another trend appears.
-However, with the trade model, the score of all the agents increase.
+However, with the tradsing model, the score of all the agents increase.
 As the selection mechanism allow them to know who has found better vectors of prices, they will progressively adopt prices vector that allow all of them to reach better scores.
 
-The previous figure showed the capacity for the ``trade'' model to increase its score but did not analyse the exact prices used.
+The previous figure showed the capacity for the trading model to increase its score but did not analyse the exact prices used.
 As explained in the section~\ref{sec:trade} we expect that the trade \emph{cultural transmission} and \emph{innovation} processes will produce a convergence toward a set of price for each good that will allow agents to exchange optimally the good they produce with the other goods.
@@
 
-We observe that prices are indeed converging to the optimal prices which means that the agents within the ``trade'' model are indeed improving their scores by reaching the optimal prices.
+We observe that prices are indeed converging to the optimal prices which means that the agents within the trading model are indeed improving their scores by reaching the optimal prices.
 Notably, a similar variation of prices was observed in the closely related economical model of~\cite{gintis_emergence_2006}.
-This variation of the prices to the optimum offers an additional conformation of the validity of the ``trade'' model.
+This variation of the prices to the optimum offers an additional conformation of the validity of the trading model.
 
@@
 
-The successful implementation of a trade model within our framework shows that trade models can be viewed as a particular implementation of the cultural evolutionary framework.
+The successful implementation of a trading model within our framework shows that trading models can be viewed as a particular implementation of the cultural evolutionary framework.
 This aspect which has not been studied before, opens a new line of thinking on the weight of trade mechanisms within cultural change.
 Notably, we have shown that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis, which is the reference in the study of cultural changes.
-Within the trade model, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
+Within the trading model, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
 Interestingly, we have not find references pointing at the ability of trade mechanisms to keep a relatively large diversity in the frequency distribution.
-We suspect that this is mainly because it is not common to compare results of trade models to other cultural evolution models.
+We suspect that this is mainly because it is not common to compare results of trading models to other cultural evolution models.
 It would therefore be interesting to compare the frequency distributions obtained by our model and the ones observed in current or past economies.

### 2015-04-08 article.tex
on-going modifications

@@
 
-\title{Modelling the Co-evolution of Trade and Culture in the Roman Market}
+\title{Modelling the Co-evolution of Trade and Culture in Past Societies}
 
@@
 We then show that it is possible to transform our model to fit processes that are economically sound, i.e.
-.
+the model should show the convergence optimal values such as shown in~\cite{gintis_emergence_2006}.
 To achieve these two goals, we have design for each one a specific set of implementations of the four core processes (production, trade, cultural transmission and innovation).
@@
 
-The neutral model is tested through ten experimental setups.
+The neutral model is tested through seven experimental setups.
 The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064).
-The remaining four experimental setups are using 3 goods, 500 agents and the same four values of $\mu$ (0.004,0.016 and 0.064).
+The remaining experimental setup is using 3 goods, 500 agents and $\mu$ equal to 0.004.
 For each setup we have performed 100 runs of 10000 timestep each.
@@
 However, it is difficult to know if the slight differences observed between our work and those previous studies are statistically significant as the two previous studies rely on only five runs for the computation of the mean of $\alpha$ (against 100 in our case).
+
+Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods.
+The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.
 

### 2015-04-08 article.tex
replace figure 5
small fixes

@@
 We first present the key concepts of the framework and two examples of its implementation which allow us to show the flexibility of our framework.
-We then compare the results obtained by the two models, thus validating the structure of the framework.
-Finally, to validate our trading model we study the price structure obtained.
+We then compare the results obtained by the two scenarios to understand the dynamics generated by the framework.
+Finally, we study the price structure obtained to validate our trading model.
 
@@
 
-This approach can be used as the starting point to analyse patterns of cultural change to explore frequency-dependance in archaeological contexts~\cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010}.
-However, the fact that archaeology records fragmented material culture presents some challenges on the validity of the method~\cite{kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
+The archaeological record allow the researchers to identify frequency-dependance biases on cultural transmission over long-term trajectories~\cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010}.
+However, the fact that material culture recovered from archaeological contexts is noisy and fragmented presents some challenges on the validity of the method~\cite{kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
@@
 Trasmission is not neutral anymore, as different prices for each good will introduce a dynamic content bias.
-This affects the frequency of the good within the population, which in turn would modifies its price following a co-evolutionary dynamic.
+This affects the frequency of the good within the population, which in turn modifies its price following a co-evolutionary dynamic.
 
-This work explores these co-evolutionary dynamics using a theoretical Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\cite{lake_trends_2014}.
-Next section defines the model, which is based on unbiased transmission mechanisms and simple exchange dynamics.
+These dynamics are studied using an Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\cite{lake_trends_2014}.
+Next section defines the theoretical model, which is based on unbiased transmission mechanisms and simple exchange dynamics.
 Next, we define different experiments to explore the dynamics of the created model.
-Finally, the concluding remarks interpret the results and discuss further possibilities of the pesented model.
+The concluding remarks interpret the results and discuss further possibilities of the presented model.
 
@@
 
-To explore the co-evolution between trade and cultural change we have developed an ABM where the different agents produce and trade goods to which they associate variable values.
+To explore the co-evolution between trade and cultural change we have developed an ABM where the different agents produce and trade goods to which they assign variable values.
 The model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$.
-The first corresponds to the quantity of each good that the agent $i$ possesses:
+The first corresponds to the quantity of each good owned by the agent $i$:
 $$\forall i \in Pop, \quad Q^i = (q^i_1,\cdots,q^i_n) $$
-where $Q^i$ is the total list of possessions of agent $i$, and $q^i_j$ is the number of goods of type $j$ that agent $i$ posses.
+where $Q^i$ is the total list of possessions of agent $i$, and $q^i_j$ is the number of goods of type $j$ that agent $i$ possesses.
 
-The second vector reflects the estimation of the value of a good that an agent $i$ makes.
+The second vector reflects the estimation of the value of a good made by an agent $i$:
 $$\forall i \in Pop, \quad V^i = (v^i_1,\cdots,v^i_n) $$
@@
 the model should show the convergence optimal values such as shown in~\cite{gintis_emergence_2006}.
-To achieve these two goals, we have design for each one a specific set of implementations of the four core processes (production, trade, cultural transmission and innovation).
+To achieve these two goals, we have designed for each one a specific set of implementations of the four core processes (production, trade, cultural transmission and innovation).
 
@@
 
-\subsection{Neutral Model}\label{sec:culturalTrans}
+\subsection{Neutral Configuration}\label{sec:culturalTrans}
 
-The first set of implementations is designed to reproduce a scenario of unbiased transmission, where each good is a cultural trait without intrinsic positive or negative weight \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
+The first scenario is designed to reproduce unbiased transmission, where each good is a cultural trait without intrinsic positive or negative weight \cite{bentley_random_2004,bentley_specialisation_2005,mesoudi_random_2009}.
 Under this hypothesis, the processes of \emph{production} and \emph{trade} are not relevant, and as a consequence, they do not modify the content of the quantity vectors of the agents.
@@
 
-\subsection{Trading Model}\label{sec:trade}
+\subsection{Trading Biased Configuration}\label{sec:trade}
 
-The second set of implementations of the four processes of the framework aims at producing economical dynamics.
+The second scenario of the four processes of the framework aims at producing economical dynamics.
 We are interested in the exchange of goods between agents in a barter process where each agent can choose its prices of exchange.
@@
 \paragraph{Production}
-In this set of implementations, each agent is producing only one type of good.
-The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
+Each agent produces one good. The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
 
 \paragraph{Cultural transmission}
-Within this set of implementations, the cultural transmission process is not random but biased toward the agents which are the best at trading, and is therefore termed ``success bias''.
+Social learning is here biased towards the agents which are the best at trading, and is therefore termed ``success bias''.
 To achieve this bias, the cultural transmission mechanism used takes into account the value vector of the other agents and relies on two new notions: \emph{need} and \emph{score}.
@@
 It is maximum when the quantity $q^i_j$ that an agent $i$ own of the good $j$ is equal to the need $n_j$ for the good $j$ and lowers proportionally to the distance between the need vector and the quantity vector.
-It is formally computed as follow for agent $i$ and the good $j$:
+It is formally computed as follows for agent $i$ and the good $j$:
 
@@
 \end{figure}
-The figure~\ref{fig:fit} depicts the score of an agent, for different need value of one good, with regards to the quantity of the good possessed by the agent.
+Figure~\ref{fig:fit} depicts the score of an agent, for different need values of one good, with regards to the quantity of the good possessed by the agent.
 We can see that even if the need for a good is small (for instance when $n(g) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need.
@@
 The complete score of an agent $i$ is termed $s^i$ and corresponds to the sum of the $s^i_j$.
-The agents will choose the agent from whom the price vector should be copied among the agents that produce the same good and have the highest score.
-In practice, the bottom two percent of the agents (in terms of score) will copy the prices of the top two percent.
+The agents will choose the model from whom the price vector should be copied among the agents that produce the same good and have the highest score.
+In practice, the worst two percent of the agents (in terms of score) will copy the prices of the best two percent.
 
@@
 Therefore, a new and more realistic mechanism is proposed.
-The innovation process, termed ``self referenced'', is still triggered with a probability $\mu$
-but modify the previous price by adding or subtracting a small amount taken randomly from a uniform  distribution between $0 .. \beta$.
+The innovation process, coined ``self referenced'', is still triggered with probability $\mu$
+but modifies the previous price by adding or subtracting a small amount taken randomly from a uniform  distribution between $0 .. \beta$.
 
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 	\begin{center}
@@
 ``Trends'' may appear, where a bigger proportion of individuals adopt a better price that allow agents to reach better score (such as around iteration 8000), but such good score fall back as soon as another trend appears.
-However, with the tradsing model, the score of all the agents increase.
+However, with the trading model, the score of all the agents increase.
 As the selection mechanism allow them to know who has found better vectors of prices, they will progressively adopt prices vector that allow all of them to reach better scores.
@@
 
-\begin{figure}[H]
+\begin{figure}[!h]
 	\begin{center}
@@
 
-This article has proposed a framework to study both cultural change mechanisms and trade mechanisms.
+This article has proposed a framework to simultaneously study cultural change and trade dynamics.
 The development of our framework was first aimed at simplicity which is achieved by the use of two vectors (quantity and value) and four processes (production, trade, cultural transmission and innovation).

### 2015-04-08 article.tex
takes advantage of the space to make the introduction a bit easier

--- 2015-04-08 article.tex
@@
 
-This papers presents a new framework to study the co-evolution of cultural transmission and trade.
+This paper presents a new framework to study the co-evolution of cultural change and trade.
 The design aims for a trade-off between the flexibility necessary for the implementation of multiple models and the structure necessary for the comparison between the models implemented.
@@
 We then compare the results obtained by the two models, thus validating the structure of the framework.
-Finally, to validate our trading model we study the price structure obtained.
+Finally, to validate one of the implemented model, the trading model, we study the price structure obtained.
 
@@
 Cultural change comprises the collection of processes that promotes or inhibits the spread of information by social interaction within a population~\cite{boyd_origin_2005}.
-An increasing number of social scientists are using an evolutionary framework to model these dynamics, thus fostering the development of transdisciplinary efforts designed to understand cultural evolution~\cite{henrich_evolution_2003}.
+An increasing number of social scientists are using an evolutionary framework to model cultural change~\cite{henrich_evolution_2003}.
+This approach aims at fostering the development of transdisciplinary efforts designed to understand cultural change.
 
-Several studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependence properties.
-These analysis often compare evidences against neutral models~\cite{neiman_stylistic_1995}.
-They assume that traits do not affect the fitness of the individual that acquires it; within this context its transmission is unbiased, and its success will depend on its popularity amongst the rest of individuals.
+%Several studies focus on the biases that affect the transmission of cultural traits, including the relevance of intrinsic traits and frequency dependence properties.
+These analysis often compare evidences against neutral models~\cite{neiman_stylistic_1995}.They assume that traits do not affect the fitness of the individual that acquires it; within this context its transmission is unbiased, and its success will depend on its popularity amongst the rest of individuals.
 This neutral model generates a distinctive pattern of frequency distribution of traits, identified as a power law.
-It can be replicated with a simple random copying transmission mechanism~\cite{bentley_random_2004}: an individual will copy the traits of a randomly chosen individual with a given probability.
+Within the studies done in the evolutionary framework, a cultural phenomenon (such as music) is viewed as a collection of traits (such as musical genres).
+Multiple biases can explain the fact that certain of the cultural traits are more transmitted than the others.
+Among the biases studied, some can be explained by the intrinsic properties of a trait (how beneficial it is for the individual using it), while others are explained by the frequency of these traits (how popular a trait is in the culture).
+
+Multiple models can be proposed to represent cultural changes, one of them being the neutral model~\cite{neiman_stylistic_1995}.
+Within this type of model it is assumed that a trait do not bias the fitness of the individual that acquires it.
+It therefore means that no bias modifies the rate of transmission of the cultural traits, and that their success will depend only on their frequency in the population.
+Within analysis of real data, a neutral model produces a distinctive type of frequency distribution of cultural traits termed \emph{power law}.
+
+The \emph{power law} can be replicated within a virtual setup thanks to a simple random copying transmission mechanism~\cite{bentley_random_2004}: an individual will copy the traits of a randomly chosen individual with a given probability.
 This copy can potentially introduce some errors in the acquired trait, which account for innovation processes.
@@
 This approach can be used as the starting point to analyse patterns of cultural change to explore frequency-dependance in archaeological contexts~\cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010}.
-However, the fact that archaeology records fragmented material culture presents some challenges on the validity of the method~\cite{kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
+However, the fact that archaeology records cultural traits as fragmented material culture presents some challenges on the validity of the method~\cite{kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
 
@@
 This work explores these co-evolutionary dynamics using a theoretical Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\cite{lake_trends_2014}.
-Next section defines the model, which is based on unbiased transmission mechanisms and simple exchange dynamics.
-Next, we define different experiments to explore the dynamics of the created model.
-Finally, the concluding remarks interpret the results and discuss further possibilities of the pesented model.
+More precisely we propose a framework that can be implemented in multiple ways depending of the model tested.
+Next section defines the framework, which is based on the basics processes found in evolutionary models of cultural change.
+Next, we define the implementations used to explore the dynamics of the created framework.
+Finally, the concluding remarks interpret the results and discuss further possibilities of the presented framework.
 
-\section{MODEL DESCRIPTION}
+\section{FRAMEWORK DESCRIPTION}
 
-To explore the co-evolution between trade and cultural change we have developed an ABM where the different agents produce and trade goods to which they associate variable values.
+To explore the co-evolution between trade and cultural change we have developed a framework where the different agents produce and trade goods to which they associate variable values.
 The model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$.

### 2015-04-08 article.tex

--- 2015-04-08 article.tex
@@
 We first present the key concepts of the framework and two examples of its implementation which allow us to show the flexibility of our framework.
-We then compare the results obtained by the two scenarios to understand the dynamics generated by the framework.
-Finally, we study the price structure obtained to validate our trading model.
+We then compare the results obtained by the two models, thus validating the structure of the framework.
+Finally, we study the price structure obtained to validate one of the implemented model, the trading model.
 
@@
 These dynamics are studied using an Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\cite{lake_trends_2014}.
-Next section defines the theoretical model, which is based on unbiased transmission mechanisms and simple exchange dynamics.
-Next, we define different experiments to explore the dynamics of the created model.
-The concluding remarks interpret the results and discuss further possibilities of the presented model.
+More precisely we propose a framework that can be implemented in multiple ways depending of the model tested.
+Next section defines the framework, which is based on the basics processes found in evolutionary models of cultural change.
+Next, we define the implementations used to explore the dynamics of the created framework.
+Finally, the concluding remarks interpret the results and discuss further possibilities of the presented framework.
 
-\section{MODEL DESCRIPTION}
+\section{FRAMEWORK DESCRIPTION}
 
-To explore the co-evolution between trade and cultural change we have developed an ABM where the different agents produce and trade goods to which they assign variable values.
+To explore the co-evolution between trade and cultural change we have developed a framework where the different agents produce and trade goods to which they assign variable values.
 The model is composed of a population $Pop$ of $m$ agents, each defined by 2 vectors of size $n$.

### 2015-06-25 article.tex
minor modification of article forgotten
edits to intro, ccl and prepare space for new results/figure

@@
 We then compare the results obtained by the two models, thus validating the structure of the framework.
-Finally, we study the price structure obtained to validate one of the implemented model, the trading model.
+Finally, we study the price structure obtained to validate one of the implemented models, the trading model.
 
@@
 Within the studies done in the evolutionary framework, a cultural phenomenon (such as music) is viewed as a collection of traits (such as musical genres).
-Multiple biases can explain the fact that certain of the cultural traits are more transmitted than the others.
+Multiple biases can explain the fact that certain of the cultural traits are transmitted more readily than the others.
+A bias is a mechanism that favours the use of a cultural trait over an other.
 Among the biases studied, some can be explained by the intrinsic properties of a trait (how beneficial it is for the individual using it), while others are explained by the frequency of these traits (how popular a trait is in the culture).
@@
 Multiple models can be proposed to represent cultural changes, one of them being the neutral model~\cite{neiman_stylistic_1995}.
-Within this type of model it is assumed that a trait do not bias the fitness of the individual that acquires it.
+Within this type of model it is assumed that a trait does not bias the fitness of the individual that acquires it.
 It therefore means that no bias modifies the rate of transmission of the cultural traits, and that their success will depend only on their frequency in the population.
@@
 This basic model can be enriched by several additional processes both in the innovation~\shortcite{schillinger_copying_2014,sole_evolutionary_2013,ziman_technological_2003} and the transmission~\cite{heyes_social_1994,henrich_evolution_2003}.
-Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendency to copy the most common trait is is known as conformism, while the opposite is defined as anti-conformism.
+Unbiased transmission works as a baseline for identifying frequency-dependent biases: if evidence has higher tendency to copy the most common trait it is known as conformism, while the opposite is defined as anti-conformism.
 
-The archaeological record allow the researchers to identify frequency-dependance biases on cultural transmission over long-term trajectories~\cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010}.
+The archaeological record allows the researchers to identify frequency-dependence biases on cultural transmission over long-term trajectories~\cite{lipo_neutralitystyle_2001,shennan_ceramic_2001,steele_ceramic_2010}.
 However, the fact that material culture recovered from archaeological contexts is noisy and fragmented presents some challenges on the validity of the method~\cite{kandler_nonequilibrium_2013,porcic_exploring_2014,crema_approximate_2014}.
@@
 Networks of good exchanges are being increasingly recognised as key elements that structured ancient societies~\shortcite{temin_market_2001,remesal_epnet_2014,brughmans_connecting_2010}.
-The scenarios where this process emerge suggest a complex bias in the selection of cultural traits, which at the same time are also identified as economic goods~\cite{bentley_specialisation_2005,macmillan_agent-based_2008}.
+The scenarios where this process emerges suggest a complex bias in the selection of cultural traits, which at the same time are also identified as economic goods~\cite{bentley_specialisation_2005,macmillan_agent-based_2008}.
 Trasmission is not neutral anymore, as different prices for each good will introduce a dynamic content bias.
@@
 These dynamics are studied using an Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\cite{lake_trends_2014}.
-More precisely we propose a framework that can be implemented in multiple ways depending of the model tested.
-Next section defines the framework, which is based on the basics processes found in evolutionary models of cultural change.
+More precisely we propose a framework that can be implemented in multiple ways depending on the model tested.
+Next section defines the framework, which is based on the basic processes found in evolutionary models of cultural change.
 Next, we define the implementations used to explore the dynamics of the created framework.
@@
 $$\forall i \in Pop, \quad V^i = (v^i_1,\cdots,v^i_n) $$
-where $V^i$ is the total list of estimated values of agent $i$, and $v^i_j$ is the value that agent $i$ associates to the goods of type $j$.
+where $V^i$ is the total list of estimated values of agent $i$, and $v^i_j$ is the value that agent $i$ associates to one unit of a good of type $j$.
 
-On top of these elements four processes are used: \emph{production}, \emph{cultural transmission}, \emph{innovation} and \emph{trade}.
+On top of these elements five processes are used: \emph{production}, \emph{consumption} \emph{cultural transmission}, \emph{innovation} and \emph{trade}.
 The \emph{production} process describes the creation of goods by the agent.
 Once a good is produced by an agent $i$ it is added to its quantity vector ($Q^i$).
+The consumption strategy of these goods is defined in the \emph{consumption} process.
+In this article, all goods are completely consumed at each iteration for all the models tested.
 The \emph{trade} process models the exchange of goods between the agents which results in a modification of the quantity vectors ($Q^i$).
-The amount of goods exchanged is computed by the agents concerned by the trade, within the \emph{trade} process, based on their value vectors ($V^i$).
-Within the \emph{cultural transmission} process an agent $i$ can copy the value vector ($V^j$) of an agent $j$, where $j \neq i$.
+The amount of goods exchanged is computed by the agents involved in the trade, within the \emph{trade} process, based on their value vectors ($V^i$).
+Within the \emph{cultural transmission} process an agent $i$ can copy the entire value vector ($V^j$) of an agent $j$, where $j \neq i$.
 Finally, the \textit{innovation} process also modifies the value vector $V^i$ of an agent, but it differs from the \emph{cultural transmission} process in that the modification is done without reference to the other agents.
@@
 Between the lines 11 and 19 is presented the part of the pseudo-code describing the instructions that will be repeated for each iteration of the simulation.
-One can note that the \emph{trade} process is called at each iteration while the \emph{cultural transmission} and \emph{innovation} processes are executed only every $CulturalStep$.
+One can note that each of the four processes is executed synchronously by all agents.
+Moreover, the \emph{trade} process is called at each iteration while the \emph{cultural transmission} and \emph{innovation} processes are executed only every $CulturalStep$.
 The idea behind this is to perform the \emph{cultural transmission} based on a score that reflects the performance of the agent and not only one lucky or unlucky trading round.
@@
 	\State INITIALIZATION: 
-		\For{$j \in Goods$}
-			\For{$i \in \#Pop/\#Goods$} \Comment{Initialize the agent with no goods and a random value vector}
+		\For{$i \in \#Pop$} \Comment{Initialize the agent with no goods and a random value vector}
 				\State $Q^i = (0, \cdots, 0)$
 				\State $V^i = (v^i_0, \cdots, v^i_n)$ \Comment{The values of $v^i_j$ are selected randomly}
-			\EndFor
 		\EndFor
@@
 				\State $Production(Q^i)$
+			\EndFor
+			\For{$i \in Pop$}
 				\For{$j \in Pop$}
@@
 				\EndFor		
+			\EndFor
+			\For{$i \in Pop$}
+				\State $consumeGoods(Q^i)$ \Comment{All goods are consumed}
 				\If{$ (step \mod CulturalStep) = 0$}	
@@
 The neutral hypothesis states that the ``random copy'' transmission and the ``unbounded'' innovation process used under a fixed population size leads to a distribution of frequency of cultural variants termed \emph{power law}.
-This distribution is characterized by a small number of very frequent traits and a large number of very rare traits.
+This distribution is characterized by a small number of very frequent traits and a large number of rare traits.
+The main difference with similar distributions, such as exponential distribution, is that the rare traits are far from being absent of the distribution, i.e.
+the tail of the distribution is large.
 %Since this hypothesis has been verified in previous works implementing similar \emph{imitation} and \emph{innovation} mechanisms, we expect in this work the observation of a similar ``power law' distribution.
-More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$ where $v$ is the number of time a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
+More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$ where $v$ is the number of times a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
 We will therefore attempt to fit as well as possible the results obtained with this set of implementations to the ``power law'' distribution by modifying the $\alpha$ parameter.
@@
 The \emph{score} $s^i_j$ of an agent $i$ reflects the ability of this agent to obtain the quantity of good $j$ it needs.
-It is maximum when the quantity $q^i_j$ that an agent $i$ own of the good $j$ is equal to the need $n_j$ for the good $j$ and lowers proportionally to the distance between the need vector and the quantity vector.
+It is maximum when the quantity $q^i_j$ that an agent $i$ owns of the good $j$ is equal to the need $n_j$ for the good $j$ and lowers proportionally to the distance between the need vector and the quantity vector.
 It is formally computed as follows for agent $i$ and the good $j$:
@@
 We can see that even if the need for a good is small (for instance when $n(g) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need.
-This insures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.
+This ensures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.
 
@@
 In practice, the worst two percent of the agents (in terms of score) will copy the prices of the best two percent.
+This selection process is detailed in algorithm~\ref{algo:selectionCulture}.
+
+\todo{complete algo}
+\begin{algorithm}
+\caption{Copy of culture}
+\label{algo:selectionCulture}
+	\begin{algorithmic}[1]
+	\scriptsize
+	\State TO COMPLETE
+\end{algorithmic}
+\end{algorithm}
 
@@
 
-The conditions \ref{eq:constraintQty} insure that both agents have enough goods in their inventory to realise the trade while the conditions \ref{eq:constraintWill} insure that the quantities of goods fit the will of both agents.
+The conditions \ref{eq:constraintQty} ensure that both agents have enough goods in their inventory to realise the trade while the conditions \ref{eq:constraintWill} ensure that the quantities of goods fit the will of both agents.
 
@@
 \midrule
-Number of goods & $\{1,3\}$ \\
+Number of goods & $\{1,2,5\}$ \\
 Number of agents & $\{250,500\}$ \\
@@
 
+\todo{check the numbers}
 We first analyse the result obtained in the ``neutral model".
-Figure~\ref{fig:allMutation} presents the results obtained in the setups using 1 good, two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064).
+Experiments have been performed for one, two and five goods.
+Unfortunately the presentation of the results for more than one good and multiple innovation probability would require a large space to be clear.
+For this reason, the figure~\ref{fig:allMutation} presents the results obtained in the setups using 1 good, two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064).
 The figure represents the average (across all the runs) of the distribution of variants obtained through all experiments.
@@
 
-We observe that the lower the mutation rate, the closer from a line the result is.
+We observe that the lower the mutation rate, the closer to a line the result is.
 This line corresponds to the ``power law" distribution explained in section~\ref{sec:culturalTrans} and is typical of the result obtained under the ``neutral hypothesis".
@@
 
+\todo{complete the cite for the method}
+In order to verify if the distribution is in fact a power-law, a method is proposed in~\cite{}.
+Within this method a linear regression is first used, for each run, to fit the curve obtained to a function of the form $P(v)=C/v^\alpha $.
+A number of fictive data points are then generated based on this slope.
+The final step assess the validity of the regression by comparing the real distribution and the fictive distribution.
+The table ~\ref{tab:powerLawFit} summarizes the results obtained by this method on all setups used for this work.
+The first number of each cell represents the mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup).
+The second number (in parenthesis) represents the mean value of all statistical tests performed.
+
+\todo{complete table}
+\begin{table}[h]
+	\centering
+	\begin{tabular}{l|lll}
+		Innovation rate &\multicolumn{3}{c}{Number of goods}\\
+			& 1 & 2 &  5  \\\hline
+		0.004 & ??  & ??  & ?? \\
+		0.016 & ??  & ??  & ?? \\
+		0.064 & ??  & ??  & ?? \\\hline
+	\end{tabular}
+	\caption{Mean $\alpha$ and p-value for all innovation rate and number of goods studied.}
+	\label{tab:powerLawFit}
+\end{table}
+
+Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods.
+The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.
+
 It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.
-A linear regression is used, for each run, to fit the curve obtained to a function of the form $P(v)=C/v^\alpha $.
-The mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup) and their standard deviation is presented in table~\ref{tab:mualpha}.
+and their standard deviation is presented in table~\ref{tab:mualpha}.
 We also present side-by-side the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.
@@
 	\end{tabular}
-	\caption{Mean \& SD are calculate on 100 runs for our results, and 5 runs for Bentley et. al. 2004.}
+	\caption{Mean $\alpha$ \& SD are calculate on 100 runs for our results, and 5 runs for Bentley et. al. 2004.}
 	\label{tab:mualpha}
@@
 
-Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods.
-The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.
-
 \subsection{Distribution of variants}
@@
 In order to understand the effect of introducing trading mechanisms, we compare first the distribution of values obtained in the ``trading model'' against the values obtained in the ``neutral model''.
-The figure~\ref{fig:2setDi} presents the results obtained from 100 runs for each model.
+The figure~\ref{fig:2setDi}.a) presents the results obtained from 100 runs for each model.
 All runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.
 
+\todo{make the figure and comment the line}
 \begin{figure}[h]
 	\begin{center}
-		\includegraphics[width=6cm]{img/2SetupDistrib.pdf}
+		\begin{tabular}{cc}
+		\includegraphics[width=6cm]{img/2SetupDistrib.pdf} &
+%		\includegraphics[width=6cm]{img/InnovationAndNeutralDistrib.pdf}
+		\\
+		a) & b) \\
+		\end{tabular}
+
 	\end{center}
-	\caption{Frequency distribution for the neutral and the trading models. Each points represent the mean for 100 runs.}
+	\caption{Frequency distribution for: a) the neutral and the trading models. Each points represent the mean for 100 runs b) the neutral model and the composed model.}
 	\label{fig:2setDi}
@@
 
-On this figure it appears that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis.
+On figure~\ref{fig:2setDi}.a) it appears that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis.
 In more details, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
-Additional investigations (not presented here) have shown that this is due to the \emph{innovation} process used in the trading model which prevents the creation of totally random new price and therefore leads to the creation of few similar prices obtaining high scores.
+
+In order to investigate which mechanism is responsible for this deviation from the neutral model, additional investigation have been performed.
+The one presented here consisted in creating a new model composed of the cultural transmission of the ``neutral model'' and the innovation of the ``trade model''.
+This new model is termed ``composed model''.
+The figure~\ref{fig:2setDi}.b) presents the results obtained from 100 runs for the ``composed model'' and the ``neutral model''.
+All runs rely on the same experimental setup as for figure~\ref{fig:2setDi}.a).
+
+On figure~\ref{fig:2setDi}.b) it appears that the same plateau in the common prices is observed with the ``composed model'' than with the ``trade model''.
+We can therefore trace the presence of this plateau to the \emph{innovation} process used in the trading model.
+This mechanism prevents the creation of totally random new price and therefore leads to the creation of few similar prices obtaining high scores.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 	\centering
@@
 
-In future works more realistic and complex dynamics can be studied in the same model.
-First, multiple implementations of the production mechanism can be studied so as to increase the number of goods per agent and include factors such as the meteorology or the various type of goods.
+%%% proposition extention authors
+%    For example, what happens if there are two populations with distinct tastes (and separate replicators)?
+How reactive are prices to shifts in production/needs?
+(innovation will become useful to remedy the lack of genetic diversity needed to deal with shifts)
+%    If replication and imitation were to happen on a social network rather than at random, how much slower would the the correct prices emerge?
+%    Would the plateau of common prices disappear if you were to add single-crossover replication of the value vector in the cultural transmission algorithm?
+
+In future works more realistic can be studied in the same model.
+Multiple implementations of the production mechanism can be studied so as to increase the number of goods per agent and include factors such as the meteorology or the various type of goods.
 Moreover, the introduction of the distinction between ``vital'' and ``common'' goods will be useful for the creation of models studying in further details the interaction between trade and cultural transmission.
-The trading mechanism itself can be naturally implemented in different ways, each reflecting a specific theory, and thus allowing the comparison of the different theories.
-Moreover, the trade network (which in this work can be interpreted as fully connected) can be modified to study the effect of slow connections or the rupture of certain connections.
-Finally, the agent themselves could become more complex and be endowed with the ability to learn behaviours which would again produce more realistic simulations.
+
+Additionally, more complex dynamics can be looked for.
+The trading mechanism can be naturally implemented in different ways, each reflecting a specific theory, and thus allowing the comparison of the different theories.
+The cultural transmission mechanism also can be modified by including for example the a crossover between the cultural trait of multiple agents.
+The trade network (which in this work can be interpreted as fully connected) can also be modified to study the effect of slow connections or the rupture of certain connections.
+The agent themselves could become more complex and be endowed with the ability to learn behaviours which would again produce more realistic simulations.
+Moreover, various populations can be envisioned, each with their distinctive characteristics regarding cultural transmission and trade.
+
+Finally, in terms of analysis of the results, multiple factor could be taken into account.
+The rapidity of the fluctuation of prices is a good starting point for the establishment of economical studies.
+For the study of a population of agent in general, it can be interesting to analyse the number of agents active and the composition of the population.
 

### 2015-06-30 article.tex
new graph to compare different flavour of the model (with or without the trade innovation process)

@@
 		\begin{tabular}{cc}
-		\includegraphics[width=6cm]{img/2SetupDistrib.pdf} &
-%		\includegraphics[width=6cm]{img/InnovationAndNeutralDistrib.pdf}
-		\\
 		a) & b)  \\
+		\includegraphics[width=6cm]{img/2SetupDistribA.pdf} &
+		\includegraphics[width=6cm]{img/2SetupDistribB.pdf} \\
+		\includegraphics[width=6cm]{img/2SetupDistribC.pdf} &
+		\includegraphics[width=6cm]{img/2SetupDistribD.pdf} \\
+		c) & d)  \\
 		\end{tabular}
@@
 	\end{center}
-	\caption{Frequency distribution for: a) the neutral and the trading models. Each points represent the mean for 100 runs b) the neutral model and the composed model.}
+	\caption{Frequency distribution, where each points represent the mean for 100 runs, for: a) the neutral and the trading models.
+b) the neutral model and the trading model without the trading innovation process.
+c) the trading model and the random model with an innovation process similar than the one used in the trade model.
+d) the trade model and the trade model without the trading innovation process.}
 	\label{fig:2setDi}

### 2015-06-30 article.tex
reorganisation of text around the new distributions

@@
 
-\todo{make the figure and comment the line}
-\begin{figure}[h]
+\begin{figure}[!h]
 	\begin{center}
-		\begin{tabular}{cc}
-		a) & b)  \\
-		\includegraphics[width=6cm]{img/2SetupDistribA.pdf} &
-		\includegraphics[width=6cm]{img/2SetupDistribB.pdf} \\
-		\includegraphics[width=6cm]{img/2SetupDistribC.pdf} &
-		\includegraphics[width=6cm]{img/2SetupDistribD.pdf} \\
-		c) & d)  \\
+		\begin{tabular}{ccc}
+%		a) & b)  \\
+		\includegraphics[width=5.2cm]{img/2SetupDistribA.pdf} &
+		\includegraphics[width=5.2cm]{img/2SetupDistribB.pdf} &
+		\includegraphics[width=5.2cm]{img/2SetupDistribD.pdf} \\
+		a) & b) & c)  \\
 		\end{tabular}
@@
 b) the neutral model and the trading model without the trading innovation process.
-c) the trading model and the random model with an innovation process similar than the one used in the trade model.
-d) the trade model and the trade model without the trading innovation process.}
+c) the trade model and the trade model without the trading innovation process.}
 	\label{fig:2setDi}
@@
 
-In order to investigate which mechanism is responsible for this deviation from the neutral model, additional investigation have been performed.
-The one presented here consisted in creating a new model composed of the cultural transmission of the ``neutral model'' and the innovation of the ``trade model''.
-This new model is termed ``composed model''.
-The figure~\ref{fig:2setDi}.b) presents the results obtained from 100 runs for the ``composed model'' and the ``neutral model''.
-All runs rely on the same experimental setup as for figure~\ref{fig:2setDi}.a).
+In order to investigate which mechanism influences this departure from the neutral model, additional investigations have been performed.
+Here is presented the results of the analysis on the effect of the \emph{innovation} process of the trade model.
+To conduct this analysis the \emph{innovation} process of the trade model has been replaced by the \emph{innovation} process of the neutral model.
+100 runs have been performed with this model on the same experimental setup.
+The results obtained are compared to the neutral model in figure~\ref{fig:2setDi}.b) and to the trade model in figure~\ref{fig:2setDi}.c).
 
-On figure~\ref{fig:2setDi}.b) it appears that the same plateau in the common prices is observed with the ``composed model'' than with the ``trade model''.
-We can therefore trace the presence of this plateau to the \emph{innovation} process used in the trading model.
-This mechanism prevents the creation of totally random new price and therefore leads to the creation of few similar prices obtaining high scores.
+On figure~\ref{fig:2setDi}.b) it appears that the replacement of the innovation process leads to the creation of a distribution close to the one obtained with the neural model.
+On figure~\ref{fig:2setDi}.c) we observe a strong reduction in the size of the plateau and an important difference between the two distributions.
+This analysis highlights the importance of the \emph{innovation} process in the distribution of prices created by the trading model.
+This mechanism, by preventing the creation of totally random new price, leads to the creation of few similar prices obtaining high scores.
 

### 2015-06-30 article.tex
new

@@
 
-\todo{complete algo}
+\todo{Arreglar : how to say ``we choose a random number and if it's less that (or more than) the relative score we continue}
 \begin{algorithm}
-\caption{Copy of culture}
+\caption{Selection Process}
 \label{algo:selectionCulture}
@@
 	\scriptsize
-	\State TO COMPLETE
+	\State	$toGet = 0.2 \times \#Pop$
+	\For{$g \in Good$}
+		\State	$toChange = \{\}$
+                \While{$\#toChange < toGet$}
+			\State $ j = rand(Pop,g) $ 
+			\If{$P(X<ComputeScore(j))$}
+				\State $toChange = \{toChange,j\}$
+			\EndIf
+		\EndWhile
+
+                \While{$\#toChange > 0 $}
+			\State $ j = rand(toChange) $ 
+			\State $ i = rand(Pop,g) $ 
+			\If{$P(X>ComputeScore(j)>ComputeScore(i))$}
+				\State copyPrice(i,j)	
+				\State $toChange = toChange - i$
+			\EndIf
+
+		\EndWhile\
+	\EndFor
 \end{algorithmic}
@@
 \midrule
-Number of goods & $\{1,2,5\}$ \\
+Number of goods & $\{1,3,6,9\}$ \\
 Number of agents & $\{250,500\}$ \\
@@
 The figure represents the average (across all the runs) of the distribution of variants obtained through all experiments.
-The y-axis shows the frequencies of the variants of the vector values, the x-axis shows how many variant achieves such frequencies.
+The y-axis shows the frequencies of the variants of the prices used during the simulation, the x-axis shows how many variant achieves such frequencies.
 Both axes are in a logarithmic scale.
 Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
+\simon{Didn't get why there is mention of ``high frequency'' in the last sentence. I found this sentence a bit confusing }
 
@@
 
-We observe that the lower the mutation rate, the closer to a line the result is.
+We observe that the lower the mutation rate, the closer to a line the result is when plotted in to a log-log axis.
 This line corresponds to the ``power law" distribution explained in section~\ref{sec:culturalTrans} and is typical of the result obtained under the ``neutral hypothesis".
-Nevertheless, under all parameters tested, the value vectors exhibit power law like distribution.
-The number of agents however has no influence on the distributions obtained.
 
-\todo{complete the cite for the method}
-In order to verify if the distribution is in fact a power-law, a method is proposed in~\cite{}.
-Within this method a linear regression is first used, for each run, to fit the curve obtained to a function of the form $P(v)=C/v^\alpha $.
-A number of fictive data points are then generated based on this slope.
+%Nevertheless, under all parameters tested, the value vectors exhibit power law like distribution. The number of agents however has no influence on the distributions obtained.
+
+In order to verify if the distribution is in fact a power-law, we will follow the method proposed by~\cite{clauset2009powerlawdistributionsinempiricaldat} and its R implementation done by~\cite{gillespie_fitting_2015}.
+
+Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the function of power law equation $P(v)=C/v^\alpha $.
+To estimate them we use maximum likelihood estimator and Kolmogorof-Smirnov approach. This method gives use an estimated $\alpha$ parameter that one can see in the table~\ref{tab:mualpha}.
+
+In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation.
+Using again Kolmogorof-Smirnov statistic we run A number of fictive data points are then generated based on this slope.
 The final step assess the validity of the regression by comparing the real distribution and the fictive distribution.
@@
 The first number of each cell represents the mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup).
-The second number (in parenthesis) represents the mean value of all statistical tests performed.
+The second number (in parenthesis) represents the mean value of all statistical tests performed on each simulation.
 
@@
 	\centering
-	\begin{tabular}{l|lll}
-		Innovation rate &\multicolumn{3}{c}{Number of goods}\\
-			& 1 & 2 &  5  \\\hline
-		0.004 & ??  & ??  & ?? \\
-		0.016 & ??  & ??  & ?? \\
-		0.064 & ??  & ??  & ?? \\\hline
+	\begin{tabular}{l|llll}
+		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
+		      & 1   & 3   &  6 & 9  \\\hline
+		0.004 & ??  & ??  & ?? & \\
+		0.016 & ??  & ??  & ?? & \\
+		0.064 & ??  & ??  & ?? & \\\hline
 	\end{tabular}
@@
 
+\todo{Change that to say that we test for differents number of good and it doesn't change}
 Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods.
@@
 
+\todo{Change her to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
 It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.

### 2015-07-01 article.tex
Change table 2 and 3 order and add p-value of the alpha estimated

@@
 In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation.
-Using again Kolmogorof-Smirnov statistic we run A number of fictive data points are then generated based on this slope.
-The final step assess the validity of the regression by comparing the real distribution and the fictive distribution.
-The table ~\ref{tab:powerLawFit} summarizes the results obtained by this method on all setups used for this work.
-The first number of each cell represents the mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup).
+Using again Kolmogorof-Smirnov statistic a number of fictive data points are generated based on the estimated power law.
+From this bootstrapping method we can then calculate a $p$-value to reject or not the hypothesis $H_0$ that our data can indeed be generated from a power law distribution.
+
+The table~\ref{tab:mualpha} summarizes the results obtained by this method on all setups used for this work with $p$-value computed by bootstrapping 100 fictive power law on each simulation.
+The value shown in the table are the mean $p$-value computed across 100 simulations.
+We see that in almost every case the null hypothesis cannot be rejected, which mean that indeed the repartition of the price indeed follows a power law.
+
+%The first number of each cell represents the mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup).
 The second number (in parenthesis) represents the mean value of all statistical tests performed on each simulation.
 
-\todo{complete table}
-\begin{table}[h]
-	\centering
-	\begin{tabular}{l|llll}
-		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
-		      & 1   & 3   &  6 & 9  \\\hline
-		0.004 & ??  & ??  & ?? & \\
-		0.016 & ??  & ??  & ?? & \\
-		0.064 & ??  & ??  & ?? & \\\hline
-	\end{tabular}
-	\caption{Mean $\alpha$ and p-value for all innovation rate and number of goods studied.}
-	\label{tab:powerLawFit}
-\end{table}
-
-\todo{Change that to say that we test for differents number of good and it doesn't change}
-Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods.
-The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.
-
-\todo{Change her to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
+\todo{Change the transition here to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
 It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.
@@
 
+\todo{complete table with final result (here it's just false exemple)}
 \begin{table}[h]
 	\centering
-	\begin{tabular}{ll|llll}
-		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et. al. 2004}\\
-			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
-		N = 250	&0.004&1.53&0.03&1.54&0.02\\
-			&0.016&1.57&0.02&1.57&0.01\\
-			&0.064&1.66&0.01&1.67&0.01\\\hline
-		N= 500	&0.004&1.50&0.02&1.53&0.03\\
-			&0.016&1.55&0.03&1.61&0.04\\
-			&0.064&1.78&0.08&1.81&0.10\\
+	\begin{tabular}{ll|ccc}
+		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
+			&$\mu$ & $\alpha$ (sd) & $p$-value (sd) &$\alpha$ (sd)\\\hline
+		N = 250	&0.004&1.53 (0.03)&0.8 (0.05)&1.54 (0.02)\\
+			&0.016&1.57 (0.02)&0.6 (0.05)&1.57 (0.01)\\
+			&0.064&1.66 (0.01)&0.0 (0.00)&1.67 (0.01)\\\hline
+		N= 500	&0.004&1.50 (0.02)&0.6 (0.05)&1.53 (0.03)\\
+			&0.016&1.55 (0.03)&0.3 (0.05)&1.61 (0.04)\\
+			&0.064&1.78 (0.08)&0.0 (0.00)&1.81 (0.10)\\
 	\end{tabular}
@@
 However, it is difficult to know if the slight differences observed between our work and those previous studies are statistically significant as the two previous studies rely on only five runs for the computation of the mean of $\alpha$ (against 100 in our case).
+
+%\todo{Change that to say that we test for differents number of good and it doesn't change}
+%Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods.
+The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.
+
+Before introducing trading mechanism we run a series of experiment to see how react the system when agents are dealing not only with one good but with many.
+For all simulation and with all mutation rate the results are the same : when more than one good are exchange the repartition of the prices for each good taken separately are the same and this repartition is in turn the same regardless the number of good exchange.
+
+It means that if we plot the repartition of the price of every goods in a simulation with 9 goods, the 9 curves for each good will be superposed, and if we plot on the same graph the repartition for a simulation with one good, the curve of this simulation will again be superposed with the previous.
+As the graph is not meaningful, we resume this situation with the table~\ref{tab:multiGoods} where are shown the mean of estimated $\alpha$ between each good for different possible configuration.
+
+\todo{complete table with final result (here it's just false exemple)}
+\begin{table}[h]
+	\centering
+	\begin{tabular}{l|llll}
+		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
+		      & 1   & 3   &  6 & 9  \\\hline
+		0.004 &1.53 (0.03)  &1.53 (0.03)&1.53 (0.03)&1.53 (0.03) \\
+		0.016 &1.57 (0.02)  &1.57 (0.02)&1.57 (0.02)&1.57 (0.02) \\
+		0.064 &1.66 (0.01)  &1.66 (0.01)&1.66 (0.01)&1.66 (0.01) \\\hline
+	\end{tabular}
+	\caption{Mean $\alpha$ and standard deviation for all innovation rate and different  of goods.
+The $\alpha$ given here is the mean $\alpha$ among all goods taken separately and computed over 100 runs with 250 agents.}
+	\label{tab:multiGoods}
+\end{table}
 

### 2015-07-01 article.tex
Change section 4.1 organisation and add some minor review

@@
 
-On top of these elements five processes are used: \emph{production}, \emph{consumption} \emph{cultural transmission}, \emph{innovation} and \emph{trade}.
+On top of these elements five processes are used: \emph{production}, \emph{consumption}, \emph{cultural transmission}, \emph{innovation} and \emph{trade}.
 The \emph{production} process describes the creation of goods by the agent.
@@
 \paragraph{Production}
-Each agent produces one good. The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
+Each agent produces one good.
+The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
+At each time step each agent produces $n$ units of its production good, which ensure that he could theoretically trade its production good with every other goods, with the particularity that when the agent consume is own production good he will automatically reproduce some in order that it won't impact is inventory.
 
@@
 We first analyse the result obtained in the ``neutral model".
-Experiments have been performed for one, two and five goods.
-Unfortunately the presentation of the results for more than one good and multiple innovation probability would require a large space to be clear.
-For this reason, the figure~\ref{fig:allMutation} presents the results obtained in the setups using 1 good, two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064).
+Following the literature, experiments have been performed for one good.
+The figure~\ref{fig:allMutation} presents the results obtained in for two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064).
 The figure represents the average (across all the runs) of the distribution of variants obtained through all experiments.
@@
 
-In order to verify if the distribution is in fact a power-law, we will follow the method proposed by~\cite{clauset2009powerlawdistributionsinempiricaldat} and its R implementation done by~\cite{gillespie_fitting_2015}.
+In order to verify if the distribution is in fact a power-law, we follow the method proposed by~\cite{clauset2009powerlawdistributionsinempiricaldat} and the R implementation of this method done by~\cite{gillespie_fitting_2015}.
 
-Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the function of power law equation $P(v)=C/v^\alpha $.
-To estimate them we use maximum likelihood estimator and Kolmogorof-Smirnov approach. This method gives use an estimated $\alpha$ parameter that one can see in the table~\ref{tab:mualpha}.
+Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
+To estimate this the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach. It gives use an estimated $\alpha$ parameter that are summarized in the table~\ref{tab:mualpha}.
 
@@
 		0.004 &1.53 (0.03)  &1.53 (0.03)&1.53 (0.03)&1.53 (0.03) \\
-		0.016 &1.57 (0.02)  &1.57 (0.02)&1.57 (0.02)&1.57 (0.02) \\
+		0.016 &1.57 (0.02)  &1.57 (0.02)&1.56 (0.017)&1.57 (0.02) \\
 		0.064 &1.66 (0.01)  &1.66 (0.01)&1.66 (0.01)&1.66 (0.01) \\\hline
@@
 
+\simon{Remainder here : we have a problem here as it's true that the number of goods does not impact the repartition of the price when vector are randomly exchange, \emph{it is not true} when the vector are  }
+
 \subsection{Distribution of variants}
@@
 All runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.
+In all following graph  a variant is one price for one given good.
+All goods are thus studied independently.
 

### 2015-07-01 article.tex
minor

@@
 Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
-To estimate this the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach. It gives use an estimated $\alpha$ parameter that are summarized in the table~\ref{tab:mualpha}.
+To estimate this, the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach that gives use an estimated $\alpha$.
+The means of the $\alpha$ estimated for all our simulation are summarized in the table~\ref{tab:mualpha}.
 

### 2015-07-01 article.tex
argument against bentley et al

@@
 To estimate this, the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach that gives use an estimated $\alpha$.
-The means of the $\alpha$ estimated for all our simulation are summarized in the table~\ref{tab:mualpha}.
+The means of those $\alpha$ estimated for all simulations are summarized in the table~\ref{tab:mualpha}.
 
 In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation.
-Using again Kolmogorof-Smirnov statistic a number of fictive data points are generated based on the estimated power law.
-From this bootstrapping method we can then calculate a $p$-value to reject or not the hypothesis $H_0$ that our data can indeed be generated from a power law distribution.
+Using again Kolmogorof-Smirnov statistic, a number of fictive data points are generated based on the estimated power law.
+From this bootstrapping method we can then calculate a $p$-value to reject or not the hypothesis $H_0$ that indeed our data could have been generated from a power law distribution.
 
-The table~\ref{tab:mualpha} summarizes the results obtained by this method on all setups used for this work with $p$-value computed by bootstrapping 100 fictive power law on each simulation.
+The table~\ref{tab:mualpha} summarizes the results obtained by this method on all setups used for this work with $p$-value computed by bootstrapping 100 fictive power law out of each simulation.
 The value shown in the table are the mean $p$-value computed across 100 simulations.
-We see that in almost every case the null hypothesis cannot be rejected, which mean that indeed the repartition of the price indeed follows a power law.
+We see that in almost every case the null hypothesis cannot be rejected, which mean that indeed the repartition of the price follows a power law, except for $mu$ value of $0.064$, where the $p$-value of zero indicate that in those case we have to reject the null hypothesis.
 
@@
 \todo{Change the transition here to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
-It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.
-and their standard deviation is presented in table~\ref{tab:mualpha}.
-We also present side-by-side the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.
+When analysing the slope of these distributions, it is interesting to compare them to previous experiments testing the ``neutral hypothesis''.
+That's why we add int table~\ref{mualpha} the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.
 
@@
 However, it is difficult to know if the slight differences observed between our work and those previous studies are statistically significant as the two previous studies rely on only five runs for the computation of the mean of $\alpha$ (against 100 in our case).
+
+\simon{I try something there but not sure at all if it is well done}
+Nonetheless, for high value of $\mu$ \cite{bentley_random_2004} say that the distribution of variant follow a power law.
+They justify this by saying that the estimated $\alpha$ (estimated using linear regression on the log-log curve) has a high correlation coefficient.
+\cite{clauset2009powerlawdistributionsinempiricaldat} say that this method should be avoided and indeed, using bootstrapping and goodness of fit method preclude us to assume that the distribution of variant when $\mu$ is up to $0.064$ follow a power law.
 

### 2015-07-01 article.tex
fix legend and table 2
work on the writting of section 4.1

--- 2015-07-01 article.tex
@@
 
-\todo{check the numbers}
-We first analyse the result obtained in the ``neutral model".
-Following the literature, experiments have been performed for one good.
-The figure~\ref{fig:allMutation} presents the results obtained in for two population sizes (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064).
-The figure represents the average (across all the runs) of the distribution of variants obtained through all experiments.
+We first analyse the result obtained in the ``neutral model" with one good.
+The figure~\ref{fig:allMutation} presents the results obtained for two population sizes $N$	 (250 and 500 agents) and $\mu$ varying through three values (0.004,0.016,0.064).
+The figure is a log-log plot of the average (across all the runs) of the distribution of variants obtained through all experiments.
 The y-axis shows the frequencies of the variants of the prices used during the simulation, the x-axis shows how many variant achieves such frequencies.
-Both axes are in a logarithmic scale.
-Please note, that here the specific variant achieving high frequency is not studied, only the number of variants achieving such frequencies is presented.
-\simon{Didn't get why there is mention of ``high frequency'' in the last sentence. I found this sentence a bit confusing }
 
-\begin{figure}[h]
+\begin{figure}[!h]
 	\centering
@@
 
-We observe that the lower the mutation rate, the closer to a line the result is when plotted in to a log-log axis.
-This line corresponds to the ``power law" distribution explained in section~\ref{sec:culturalTrans} and is typical of the result obtained under the ``neutral hypothesis".
+We observe that the lower the mutation rate, the closer to a line the result is.
+This line corresponds to the ``power law" distribution explained in section~\ref{sec:culturalTrans}, and is typical of the result obtained under the ``neutral hypothesis".
+In order to verify if the distribution is in fact a power-law, we follow the method proposed by~\cite{clauset2009powerlawdistributionsinempiricaldat} and the R implementation proposed by~\cite{gillespie_fitting_2015}.
+Briefly, two values are returned: a) the estimation of the $\alpha$ parameter of the power law equation $P(v)=C/v^\alpha $; b) a $p$-value rejecting or not the hypothesis $H_0$ that indeed our data could have been generated from a power law distribution.
 
-%Nevertheless, under all parameters tested, the value vectors exhibit power law like distribution. The number of agents however has no influence on the distributions obtained.
+%Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
+To estimate this, the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach that gives use an estimated $\alpha$.
+The means of those $\alpha$ estimated for all simulations are summarized in the table~\ref{tab:mualpha}.
+%In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation.
+Using again Kolmogorof-Smirnov statistic, a number of fictive data points are generated based on the estimated power law.
+From this bootstrapping method we can then calculate a
 
-In order to verify if the distribution is in fact a power-law, we follow the method proposed by~\cite{clauset2009powerlawdistributionsinempiricaldat} and the R implementation of this method done by~\cite{gillespie_fitting_2015}.
-
-Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
-To estimate this the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach. It gives use an estimated $\alpha$ parameter that are summarized in the table~\ref{tab:mualpha}.
-
-In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation.
-Using again Kolmogorof-Smirnov statistic a number of fictive data points are generated based on the estimated power law.
-From this bootstrapping method we can then calculate a $p$-value to reject or not the hypothesis $H_0$ that our data can indeed be generated from a power law distribution.
-
-The table~\ref{tab:mualpha} summarizes the results obtained by this method on all setups used for this work with $p$-value computed by bootstrapping 100 fictive power law on each simulation.
-The value shown in the table are the mean $p$-value computed across 100 simulations.
-We see that in almost every case the null hypothesis cannot be rejected, which mean that indeed the repartition of the price indeed follows a power law.
-
-%The first number of each cell represents the mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup).
-The second number (in parenthesis) represents the mean value of all statistical tests performed on each simulation.
-
-\todo{Change the transition here to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
-It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.
-and their standard deviation is presented in table~\ref{tab:mualpha}.
-We also present side-by-side the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.
+The table~\ref{tab:mualpha} summarizes the results obtained on all setups.
+Each value shown in the table is the mean values of 100 simulations.
+We see that in almost every case the null hypothesis cannot be rejected, which means that indeed the repartition of the price follows a power law.
+The only exception is for $mu$ equal to $0.064$, where the $p$-value is less than $0.05$.
+In this last case the null hypothesis is rejected which means that the distribution is not a power-law.
 
 \todo{complete table with final result (here it's just false exemple)}
-\begin{table}[h]
+\begin{table}[!h]
 	\centering
@@
 
-We can see in this table that our results are close to those obtained by \cite{bentley_random_2004}.
-With a similar methodology and parameters~\cite{mesoudi_random_2009} find similar values of $\alpha$.
+For comparison purposes the results obtained by~\cite{bentley_random_2004} (which tested the ``neutral hypothesis'' with the same methodology) are added in the last column of table~\ref{tab:mualpha}.
+It appears that our results are highly similar to those obtained by~\cite{bentley_random_2004}.
+We note also that these results match the ones shown in~\cite{mesoudi_random_2009} where only one value of $\mu$ was tested ($mu = 0.008$).
 However, it is difficult to know if the slight differences observed between our work and those previous studies are statistically significant as the two previous studies rely on only five runs for the computation of the mean of $\alpha$ (against 100 in our case).
 
-%\todo{Change that to say that we test for differents number of good and it doesn't change}
-%Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods.
-The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.
+Nonetheless, for high value of $\mu$, previous works report that the distribution of variant follow a power law~\cite{bentley_random_2004}.
+This claim is justified based on the fact that the estimated $\alpha$ (estimated using linear regression on the log-log curve) has a high correlation coefficient.
+More recent works have shown that this method should be avoided~\cite{clauset2009powerlawdistributionsinempiricaldat}.
+Following these recent findings, our results preclude us to assume that the distribution of variant when $\mu$ is up to $0.064$ follow a power law .
 
-Before introducing trading mechanism we run a series of experiment to see how react the system when agents are dealing not only with one good but with many.
-For all simulation and with all mutation rate the results are the same : when more than one good are exchange the repartition of the prices for each good taken separately are the same and this repartition is in turn the same regardless the number of good exchange.
-
-It means that if we plot the repartition of the price of every goods in a simulation with 9 goods, the 9 curves for each good will be superposed, and if we plot on the same graph the repartition for a simulation with one good, the curve of this simulation will again be superposed with the previous.
-As the graph is not meaningful, we resume this situation with the table~\ref{tab:multiGoods} where are shown the mean of estimated $\alpha$ between each good for different possible configuration.
+A series of experiments are performed to see how the system reacts when multiple goods are present.
+We report in table~\ref{tab:multiGoods} the mean values of $\alpha$ and $p$-value obtained for 3 innovation rates (0.004, 0.016, 0.064) 4 number of goods (1, 3, 6, 9) and 250 agents.
 
@@
 
-\simon{Remainder here : we have a problem here as it's true that the number of goods does not impact the repartition of the price when vector are randomly exchange, \emph{it is not true} when the vector are  }
+From the results shown in table~\ref{tab:multiGoods} it appears that for each innovation rate the distribution of variants has the same properties regardless of the number of goods.
+Additional analysis (not shown here) reveals that when the repartition of the price of every goods in a simulation with 9 goods is plotted, the 9 curves are superposed.
+Moreover these 9 curves are also superposed with the distribution shown in figure~\ref{fig:allMutation} for one good.
 

### 2015-07-01 article.tex
work again on the writting of section 4.1

@@
 In order to verify if the distribution is in fact a power-law, we follow the method proposed by~\cite{clauset2009powerlawdistributionsinempiricaldat} and the R implementation proposed by~\cite{gillespie_fitting_2015}.
-Briefly, two values are returned: a) the estimation of the $\alpha$ parameter of the power law equation $P(v)=C/v^\alpha $; b) a $p$-value rejecting or not the hypothesis $H_0$ that indeed our data could have been generated from a power law distribution.
+Briefly, two values are returned: a) the estimation of the $\alpha$ parameter of the power law equation $P(v)=C/v^\alpha $; b) a $p$-value testing the null-hypothesis that our data could have been generated from a power law distribution.
 
@@
 The only exception is for $mu$ equal to $0.064$, where the $p$-value is less than $0.05$.
-In this last case the null hypothesis is rejected which means that the distribution is not a power-law.
+In this last case the null hypothesis is rejected, and we therefore assume that the distribution does not follow a power law.
 
@@
 	\centering
-	\begin{tabular}{ll|ccc}
-		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
-			&$\mu$ & $\alpha$ (sd) & $p$-value (sd) &$\alpha$ (sd)\\\hline
-		N = 250	&0.004&1.53 (0.03)&0.8 (0.05)&1.54 (0.02)\\
+	\begin{tabular}{cc|ccc}
+		\multicolumn{2}{r}{}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
+			N&$\mu$ & $\alpha$ (sd) & $p$-value (sd) &$\alpha$ (sd)\\\hline
+		250	&0.004&1.53 (0.03)&0.8 (0.05)&1.54 (0.02)\\
 			&0.016&1.57 (0.02)&0.6 (0.05)&1.57 (0.01)\\
 			&0.064&1.66 (0.01)&0.0 (0.00)&1.67 (0.01)\\\hline
-		N= 500	&0.004&1.50 (0.02)&0.6 (0.05)&1.53 (0.03)\\
+		500	&0.004&1.50 (0.02)&0.6 (0.05)&1.53 (0.03)\\
 			&0.016&1.55 (0.03)&0.3 (0.05)&1.61 (0.04)\\
@@
 For comparison purposes the results obtained by~\cite{bentley_random_2004} (which tested the ``neutral hypothesis'' with the same methodology) are added in the last column of table~\ref{tab:mualpha}.
-It appears that our results are highly similar to those obtained by~\cite{bentley_random_2004}.
-We note also that these results match the ones shown in~\cite{mesoudi_random_2009} where only one value of $\mu$ was tested ($mu = 0.008$).
+It appears that these results are highly similar to ours.
+We note also that our results match the ones presented in~\cite{mesoudi_random_2009} where only one value of $\mu$ was tested ($mu = 0.008$).
 However, it is difficult to know if the slight differences observed between our work and those previous studies are statistically significant as the two previous studies rely on only five runs for the computation of the mean of $\alpha$ (against 100 in our case).
@@
 Nonetheless, for high value of $\mu$, previous works report that the distribution of variant follow a power law~\cite{bentley_random_2004}.
-This claim is justified based on the fact that the estimated $\alpha$ (estimated using linear regression on the log-log curve) has a high correlation coefficient.
-More recent works have shown that this method should be avoided~\cite{clauset2009powerlawdistributionsinempiricaldat}.
+This claim is based on the fact that the estimated $\alpha$ (estimation based on linear regression on the log-log curve) has a high correlation coefficient.
+Recent works have shown that the use of correlation coefficient should be avoided~\cite{clauset2009powerlawdistributionsinempiricaldat}.
 Following these recent findings, our results preclude us to assume that the distribution of variant when $\mu$ is up to $0.064$ follow a power law .
 
-A series of experiments are performed to see how the system reacts when multiple goods are present.
-We report in table~\ref{tab:multiGoods} the mean values of $\alpha$ and $p$-value obtained for 3 innovation rates (0.004, 0.016, 0.064) 4 number of goods (1, 3, 6, 9) and 250 agents.
+An additional series of experiments is done to see how the system reacts when multiple goods are present.
+We report in table~\ref{tab:multiGoods} the mean values of $\alpha$ and $p$-value obtained for 3 innovation rates (0.004, 0.016, 0.064), 4 number of goods (1, 3, 6, 9), and 250 agents.
 
 \todo{complete table with final result (here it's just false exemple)}
-\begin{table}[h]
+\begin{table}[!h]
 	\centering
@@
 
-From the results shown in table~\ref{tab:multiGoods} it appears that for each innovation rate the distribution of variants has the same properties regardless of the number of goods.
-Additional analysis (not shown here) reveals that when the repartition of the price of every goods in a simulation with 9 goods is plotted, the 9 curves are superposed.
+From the results shown in table~\ref{tab:multiGoods}, it appears that for each innovation rate, the properties of the distribution of prices does not depend of the number of goods.
+Additional analysis (not shown here) reveals that when the distribution of prices of every goods in a simulation with 9 goods is plotted, the 9 curves are superposed.
 Moreover these 9 curves are also superposed with the distribution shown in figure~\ref{fig:allMutation} for one good.

### 2015-07-01 article.tex
fix algo selection process
finalise the algorithm and remove a figure to gain space

@@
 
-\begin{figure}[htp]
-	\begin{center}
-		\includegraphics[width=7cm]{img/fitness.pdf}
-	\end{center}
-	\caption{The payoff depending on the quantity owned of a given good and the effective needs $n(g)$ for this good.}
-	\label{fig:fit}
-\end{figure}
-Figure~\ref{fig:fit} depicts the score of an agent, for different need values of one good, with regards to the quantity of the good possessed by the agent.
+%\begin{figure}[htp]
+%	\begin{center}
+%		\includegraphics[width=7cm]{img/fitness.pdf}
+%	\end{center}
+%	\caption{The payoff depending on the quantity owned of a given good and the effective needs $n(g)$ for this good.}
+%	\label{fig:fit}
+%\end{figure}
+%Figure~\ref{fig:fit} depicts the score of an agent, for different need values of one good, with regards to the quantity of the good possessed by the agent.
 We can see that even if the need for a good is small (for instance when $n(g) = 0.01$) an agent can have a high score as soon as it manages to get a quantity close to the need.
@@
 
-\todo{Arreglar : how to say ``we choose a random number and if it's less that (or more than) the relative score we continue}
 \begin{algorithm}
@@
 	\scriptsize
-	\State	$toGet = 0.2 \times \#Pop$
+	\State	$ToGet = 0.2 \times \#Pop$
 	\For{$g \in Good$}
-		\State	$toChange = \{\}$
-                \While{$\#toChange < toGet$}
-			\State $ j = rand(Pop,g) $ 
-			\If{$P(X<ComputeScore(j))$}
-				\State $toChange = \{toChange,j\}$
+		\State	$ToReplace = \{\}$
+                \While{$\#ToReplace < ToGet$} 
+			\State $ j = SelectRand(Pop,g) $ \Comment{Select randomly an agent $j$ among the agents producing $g$}
+			\State $X \sim U([0,1])$ \Comment{Draw a random number from the uniform distribution between 0 and 1}
+			\If{$X>ComputeScore(j)$} \Comment{Select preferably the agents with the lowest scores}
+				\State $ToReplace = \{ToReplace,j\}$
 			\EndIf
@@
 
-                \While{$\#toChange > 0 $}
-			\State $ j = rand(toChange) $ 
-			\State $ i = rand(Pop,g) $ 
-			\If{$P(X>ComputeScore(j)>ComputeScore(i))$}
-				\State copyPrice(i,j)	
-				\State $toChange = toChange - i$
+                \While{$\#ToReplace > 0 $}
+			\State $ j = SelectRand(ToReplace) $ 
+			\State $ i = SelectRand(Pop,g) $  \Comment{Select randomly an agent $i$ among the agents producing $g$}
+			\State $X \sim U([0,1])$ 
+			\If{$ (X<ComputeScore(i))$} \Comment{Select preferably an agent $i$ with a high score}
+				\If {$ (ComputeScore(i)>ComputeScore(j))$} \Comment{Verify that agent $i$ has a higher score than agent $j$}
+					\State $CopyPrice(i,j)$
+					\State $ToReplace = ToReplace - i$
+				\EndIf
 			\EndIf

### 2015-07-01 article.tex
final modifications ongoing

@@
 \newcommand{\added}[2]{\textcolor{#1}{#2}}
-\renewcommand{\memo}[2]{} % uncomment in the final version
-\renewcommand{\added}[2]{#2} % uncomment in the final version
+%\renewcommand{\memo}[2]{} % uncomment in the final version
+%\renewcommand{\added}[2]{#2} % uncomment in the final version
 \newcommand{\todo}[1]{\memo{red}{TODO: #1\\}}
@@
 
-\WSCpagesetup{Montanier, Carrignon and Rubio}
+\WSCpagesetup{Carrignon, Montanier, and Rubio}
 
@@
 \centering
+Simon Carrignon\\ 
 Jean-Marc Montanier\\
-Simon Carrignon\\ 
 Xavier Rubio-Campillo\\
@@
 We then compare the results obtained by the two models, thus validating the structure of the framework.
-Finally, we study the price structure obtained to validate one of the implemented models, the trading model.
+Finally, we validate the implementation of a trading model by studying the price structure it produces.
 
@@
 Within the studies done in the evolutionary framework, a cultural phenomenon (such as music) is viewed as a collection of traits (such as musical genres).
-Multiple biases can explain the fact that certain of the cultural traits are transmitted more readily than the others.
-A bias is a mechanism that favours the use of a cultural trait over an other.
+Multiple biases (mechanism favouring the use of a cultural trait over an other) can explain the fact that certain of the cultural traits are transmitted more readily than the others.
 Among the biases studied, some can be explained by the intrinsic properties of a trait (how beneficial it is for the individual using it), while others are explained by the frequency of these traits (how popular a trait is in the culture).
@@
 Within analysis of real data, a neutral model produces a distinctive type of frequency distribution of cultural traits termed \emph{power law}.
+\todo{find where this is found in economical studies}
 
@@
 Between line 2 and 7 all agents of the population are initialised with empty quantity vectors and random values.
-Between the lines 11 and 19 is presented the part of the pseudo-code describing the instructions that will be repeated for each iteration of the simulation.
+The code used to update the status of each agent at each iteration is presented between the lines 8 and 22.
 One can note that each of the four processes is executed synchronously by all agents.
@@
 %Since this hypothesis has been verified in previous works implementing similar \emph{imitation} and \emph{innovation} mechanisms, we expect in this work the observation of a similar ``power law' distribution.
-More formally, this distribution is formalised as : $$P(v)=C/v^\alpha $$ where $v$ is the number of times a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
+This distribution is formalised as : $$P(v)=C/v^\alpha $$ where $v$ is the number of times a variant has been repeated, $P(v)$ the probability to find that variant, $C$ a constant, $\alpha$ a variable describing the slope of the curve obtained.
 We will therefore attempt to fit as well as possible the results obtained with this set of implementations to the ``power law'' distribution by modifying the $\alpha$ parameter.
@@
 
-The second scenario of the four processes of the framework aims at producing economical dynamics.
-We are interested in the exchange of goods between agents in a barter process where each agent can choose its prices of exchange.
+In the second scenario, we are interested in the exchange of goods between agents in a barter process where each agent can choose its prices of exchange.
 We want to implement simple processes leading to the convergence of all prices to values acceptable by all agents, i.e.
@@
 \paragraph{Production}
+\todo{what is some, what is n}
 Each agent produces one good.
 The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
-At each time step each agent produces $n$ units of its production good, which ensure that he could theoretically trade its production good with every other goods, with the particularity that when the agent consume is own production good he will automatically reproduce some in order that it won't impact is inventory.
+At each time step each agent produces $n$ units of its production good, which ensure that he could theoretically trade its production good with every other goods.
+When an agent consumes its own production good he will automatically reproduce some, so that the consumption does not impact its inventory.
 

### 2015-07-01 article.tex
.

@@
 The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
-At each time step each agent produces $n$ units of its production good, which ensure that he could theoretically trade its production good with every other goods.
-When an agent consumes its own production good he will automatically reproduce some, so that the consumption does not impact its inventory.
+At each time step each agent produces $n$ units of its production good, which ensure that it own theoretically enough of it to trade it with every other goods.
+Moreover, when an agent consumes its own production good, it doesn't not impact its inventory, meaning that he can produced for free the quantity he consume for itself.
 
@@
 
-\paragraph{Innovation} In a trading environment it seems unlikely that a price will change radically to a very different value.
+\paragraph{Innovation}
+
+In a trading environment it seems unlikely that a price will change radically to a very different value.
 Therefore, a new and more realistic mechanism is proposed.

### 2015-07-01 article.tex
edits on the paper. Fit in 12 pages if todo are removed. Some little todo and questions are yet to be addressed

@@
 The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
-At each time step each agent produces $n$ units of its production good, which ensure that it own theoretically enough of it to trade it with every other goods.
-Moreover, when an agent consumes its own production good, it doesn't not impact its inventory, meaning that he can produced for free the quantity he consume for itself.
+At each time step, each agent, produces $n$ units of its production good, which ensures that enough is owned to be traded for other goods.
+Moreover, when an agent consumes its own production good, it does not impact its inventory.
 
@@
 This function ensures that each good has the same weight in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
-
 %\begin{figure}[htp]
@@
 This ensures that an agent needs to have for each of the good a quantity equal to the need and that no agent could reach a better score just by getting the right quantity for a good with a high need.
-
 The complete score of an agent $i$ is termed $s^i$ and corresponds to the sum of the $s^i_j$.
@@
 
-The neutral model is tested through seven experimental setups.
+The neutral model is tested through 15 experimental setups.
 The first six experimental setups are using 1 good, two population sizes (250 and 500 agents) and three values of $\mu$ (0.004,0.016 and 0.064).
-The remaining experimental setup is using 3 goods, 500 agents and $\mu$ equal to 0.004.
+The remaining experimental setups are using 500 agents, 3 number of goods (3,6 and 9) and three values of $\mu$ (0.004,0.016 and 0.064).
 For each setup we have performed 100 runs of 10000 timestep each.
@@
 We see that in almost every case the null hypothesis cannot be rejected, which means that indeed the repartition of the price follows a power law.
-The only exception is for $mu$ equal to $0.064$, where the $p$-value is less than $0.05$.
+The only exception is for $\mu$ equal to $0.064$, where the $p$-value is less than $0.05$.
 In this last case the null hypothesis is rejected, and we therefore assume that the distribution does not follow a power law.
@@
 It appears that these results are highly similar to ours.
-We note also that our results match the ones presented in~\cite{mesoudi_random_2009} where only one value of $\mu$ was tested ($mu = 0.008$).
+We note also that our results match the ones presented in~\cite{mesoudi_random_2009} where only one value of $\mu$ was tested ($\mu = 0.008$).
 However, it is difficult to know if the slight differences observed between our work and those previous studies are statistically significant as the two previous studies rely on only five runs for the computation of the mean of $\alpha$ (against 100 in our case).
@@
 
-An additional series of experiments is done to see how the system reacts when multiple goods are present.
-We report in table~\ref{tab:multiGoods} the mean values of $\alpha$ and $p$-value obtained for 3 innovation rates (0.004, 0.016, 0.064), 4 number of goods (1, 3, 6, 9), and 250 agents.
-
-\todo{complete table with final result (here it's just false exemple)}
-\begin{table}[!h]
-	\centering
-	\begin{tabular}{l|llll}
-		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
-		      & 1   & 3   &  6 & 9  \\\hline
-		0.004 &1.53 (0.03)  &1.53 (0.03)&1.53 (0.03)&1.53 (0.03) \\
-		0.016 &1.57 (0.02)  &1.57 (0.02)&1.56 (0.017)&1.57 (0.02) \\
-		0.064 &1.66 (0.01)  &1.66 (0.01)&1.66 (0.01)&1.66 (0.01) \\\hline
-	\end{tabular}
-	\caption{Mean $\alpha$ and standard deviation for all innovation rate and different  of goods.
+An additional series of experiments is done to analyse how the system reacts when multiple goods are present.
+The mean values of $\alpha$ and $p$-value have been analysed for 3 innovation rates (0.004, 0.016, 0.064), 4 number of goods (1, 3, 6, 9), and 250 agents.
+However, due to the simplicity of the results and the space restriction we only report the analysis of the results here.
+%\todo{complete table with final result (here it's just false exemple)}
+%\begin{table}[!h]
+%	\centering
+%	\begin{tabular}{l|llll}
+%		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
+%		      & 1   & 3   &  6 & 9  \\\hline
+%		0.004 &1.53 (0.03)  &1.53 (0.03)&1.53 (0.03)&1.53 (0.03) \\
+%		0.016 &1.57 (0.02)  &1.57 (0.02)&1.56 (0.017)&1.57 (0.02) \\
+%		0.064 &1.66 (0.01)  &1.66 (0.01)&1.66 (0.01)&1.66 (0.01) \\\hline
+%	\end{tabular}
+%	\caption{Mean $\alpha$ and standard deviation for all innovation rate and different  of goods.
 The $\alpha$ given here is the mean $\alpha$ among all goods taken separately and computed over 100 runs with 250 agents.}
-	\label{tab:multiGoods}
-\end{table}
-
-From the results shown in table~\ref{tab:multiGoods}, it appears that for each innovation rate, the properties of the distribution of prices does not depend of the number of goods.
-Additional analysis (not shown here) reveals that when the distribution of prices of every goods in a simulation with 9 goods is plotted, the 9 curves are superposed.
-Moreover these 9 curves are also superposed with the distribution shown in figure~\ref{fig:allMutation} for one good.
+%	\label{tab:multiGoods}
+%\end{table}
+Visual analysis reveals that independently of the number of goods, the distributions obtained are exactly the same.
+Therefore it is no surprise that, for each innovation rate, the properties of the distribution of prices does not depend of the number of goods.
 
@@
 For all runs, all agents and at each iteration we compute the difference between the price used by the agent $V_g$ and the optimal price $\tilde{V}_g$.
-Record that the optimal price for a good that an agent does not produce is the product between the need for this good and the need for the produced good, while the optimal price for the produced good is simply the need for it.
+Record that the optimal price for a good is given in equation~\ref{eq:optimum}.
 All the measures performed are presented as boxplots where the results for 100 runs are condensed.
@@
 
-In future works more realistic can be studied in the same model.
+In future works more realistic scenarios can be studied in the same framework.
 Multiple implementations of the production mechanism can be studied so as to increase the number of goods per agent and include factors such as the meteorology or the various type of goods.
@@
 Additionally, more complex dynamics can be looked for.
-The trading mechanism can be naturally implemented in different ways, each reflecting a specific theory, and thus allowing the comparison of the different theories.
+The trading mechanism can be naturally implemented in different ways, each reflecting a specific theory, and thus allowing their comparisons.
 The cultural transmission mechanism also can be modified by including for example the a crossover between the cultural trait of multiple agents.

### 2015-07-02 article.tex
result p-value for N=250
small edits to the text

@@
 \paragraph{Production}
-\todo{what is some, what is n}
+
 Each agent produces one good.
 The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
-At each time step, each agent, produces $n$ units of its production good, which ensures that enough is owned to be traded for other goods.
+At each time step, each agent, produces a number of units (of its production good) equal to the number of goods, which ensures that enough is owned to be traded for other goods.
 Moreover, when an agent consumes its own production good, it does not impact its inventory.
@@
 For each setup we have performed 100 runs of 10000 timestep each.
-
-The trading model is tested through four experimental setups using 3 goods, 500 agents and the same four values of $\mu$ (0.004,0.016 and 0.064). Again 100 runs of 10000 timesteps are performed.
-
+The trading model is tested on an experimental setups using 3 goods, 500 agents and $\mu$ equal to 0.004.
+Again 100 runs of 10000 timesteps are performed.
 The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}.
@@
 In all following graph  a variant is one price for one given good.
-All goods are thus studied independently.
+The distributions are first computed for each good independently and then averaged together.
 

### 2015-07-02 article.tex
pr-value

@@
 The figure is a log-log plot of the average (across all the runs) of the distribution of variants obtained through all experiments.
-The y-axis shows the frequencies of the variants of the prices used during the simulation, the x-axis shows how many variant achieves such frequencies.
+The y-axis shows the proportions of the variants of the prices used during the simulation, the x-axis shows how many variant achieves such proportions.
 
@@
 	\end{tabular}
-	\caption{Distribution of frequencies depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right). Each plot is the mean obtenaid for 100 runs.\label{fig:allMutation}}
+	\caption{Distribution of proportions depending on the $\mu$ parameter with 250 agents (left) and 500 agents (right). Each plot is the mean obtenaid for 100 runs.\label{fig:allMutation}}
 \end{figure}
@@
 		\multicolumn{2}{r}{}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
-			N&$\mu$ & $\alpha$ (sd) & $p$-value (sd) &$\alpha$ (sd)\\\hline
-		250	&0.004&1.53 (0.03)&0.8 (0.05)&1.54 (0.02)\\
-			&0.016&1.57 (0.02)&0.6 (0.05)&1.57 (0.01)\\
-			&0.064&1.66 (0.01)&0.0 (0.00)&1.67 (0.01)\\\hline
+			N&$\mu$ & $\alpha$ (sd) & $p$-value (sd - pr) &$\alpha$ (sd)\\\hline
+		250	&0.004&1.53 (0.03)&0.58 (0.24 - .01)&1.54 (0.02)\\
+			&0.016&1.57 (0.02)&0.35 (0.26 - .05)&1.57 (0.01)\\
+			&0.064&1.66 (0.01)&0.0 (0.00 - 1)&1.67 (0.01)\\\hline
 		500	&0.004&1.50 (0.02)&0.6 (0.05)&1.53 (0.03)\\
@@
 	\end{tabular}
-	\caption{Mean $\alpha$ \& SD are calculate on 100 runs for our results, and 5 runs for Bentley et. al. 2004.}
+	\caption{Mean $\alpha$ \& sd are calculate on 100 runs for our results, and 5 runs for Bentley et.
+al.
+2004, pr is the percent of run for which the $p$-value<0.05 (we reject the hypothese that the distribution follow a power law).}
 	\label{tab:mualpha}
@@
 	\end{center}
-	\caption{Frequency distribution, where each points represent the mean for 100 runs, for: a) the neutral and the trading models.
+	\caption{Proportions distribution, where each points represent the mean for 100 runs, for: a) the neutral and the trading models.
 b) the neutral model and the trading model without the trading innovation process.
@@
 On figure~\ref{fig:2setDi}.a) it appears that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis.
-In more details, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
+In more details, the proportion distribution has a plateau of common prices (a number of prices share similar and high proportion), which shows that, when trade is taken into account, the most common variants are more diverse.
 
@@
 Notably, we have shown that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis, which is the reference in the study of cultural changes.
-Within the trading model, the frequency distribution has a plateau of common prices (a number of prices share similar and high frequency), which shows that, when trade is taken into account, the most common variants are more diverse.
+Within the trading model, the frequency distribution has a plateau of common prices (a number of prices share similar and high proportion), which shows that, when trade is taken into account, the most common variants are more diverse.
 Interestingly, we have not find references pointing at the ability of trade mechanisms to keep a relatively large diversity in the frequency distribution.

### 2015-07-02 article.tex
detail corrections

--- 2015-07-02 article.tex
@@
 Within analysis of real data, a neutral model produces a distinctive type of frequency distribution of cultural traits termed \emph{power law}.
-\todo{find where this is found in economical studies}
 
@@
 Next, we define the implementations used to explore the dynamics of the created framework.
-Finally, the concluding remarks interpret the results and discuss further possibilities of the presented framework.
+In the following section we analyse the results obtained with these two implementations.
+Finally, the concluding remarks discuss further possibilities of the presented framework.
 
@@
 Once a good is produced by an agent $i$ it is added to its quantity vector ($Q^i$).
-The consumption strategy of these goods is defined in the \emph{consumption} process.
+The consumption strategy of these goods is defined in the \emph{consumption} process which decreases the number of goods in the vector ($Q^i$).
 In this article, all goods are completely consumed at each iteration for all the models tested.
@@
 
-The scheduling of the four processes is described in algorithm~\ref{algo:complete} along with the vectors modified by each of these processes.
-Between line 2 and 7 all agents of the population are initialised with empty quantity vectors and random values.
+The scheduling of the five processes is described in algorithm~\ref{algo:complete} along with the vectors modified by each of these processes.
+On lines 3 and 4 all agents of the population are initialised with empty quantity vectors and random values.
 The code used to update the status of each agent at each iteration is presented between the lines 8 and 22.
-One can note that each of the four processes is executed synchronously by all agents.
+One can note that each of the five processes is executed synchronously by all agents.
 Moreover, the \emph{trade} process is called at each iteration while the \emph{cultural transmission} and \emph{innovation} processes are executed only every $CulturalStep$.
@@
 			\For{$i \in Pop$}
-				\State $consumeGoods(Q^i)$ \Comment{All goods are consumed}
+				\State $ConsumeGoods(Q^i)$ \Comment{All goods are consumed}
 				\If{$ (step \mod CulturalStep) = 0$}	
@@
 the model should show the convergence optimal values such as shown in~\cite{gintis_emergence_2006}.
-To achieve these two goals, we have designed for each one a specific set of implementations of the four core processes (production, trade, cultural transmission and innovation).
+To achieve these two goals, we have designed for each one a specific set of implementations of the five core processes (production, consumption, trade, cultural transmission and innovation).
 
@@
 
-\section{Experimental setup}
+\subsection{Experimental setups}
 %In order to study the cultural transmission and the trading model two sets of implementation of the four processes of our model have been presented.
@@
 		\multicolumn{2}{r}{}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
-			N&$\mu$ & $\alpha$ (sd) & $p$-value (sd) &$\alpha$ (sd)\\\hline
-		250	&0.004&1.53 (0.03)&0.8 (0.05)&1.54 (0.02)\\
-			&0.016&1.57 (0.02)&0.6 (0.05)&1.57 (0.01)\\
-			&0.064&1.66 (0.01)&0.0 (0.00)&1.67 (0.01)\\\hline
+			N&$\mu$ & $\alpha$ (sd) & $p$-value (sd) - r &$\alpha$ (sd)\\\hline
+		250	&0.004&1.53 (0.03)&0.58 (0.24) - 0 &1.54 (0.02)\\
+			&0.016&1.57 (0.02)&0.35 (0.26) - 3 &1.57 (0.01)\\
+			&0.064&1.66 (0.01)&0.0 (0.00) - 1 &1.67 (0.01)\\\hline
 		500	&0.004&1.50 (0.02)&0.6 (0.05)&1.53 (0.03)\\
@@
 This article has proposed a framework to simultaneously study cultural change and trade dynamics.
-The development of our framework was first aimed at simplicity which is achieved by the use of two vectors (quantity and value) and four processes (production, trade, cultural transmission and innovation).
+The development of our framework was first aimed at simplicity which is achieved by the use of two vectors (quantity and value) and five processes (production, consumption, trade, cultural transmission and innovation).
 The second aim of the work conducted was to obtain a flexible framework which is possible since each of the processes can be implemented accordingly to the question studied.

### 2015-07-02 article.tex
new proof read of the article. miss a link to implmentation, and new results of simon

@@
 
-\paragraph{Production}
-
-Each agent produces one good.
-The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation and is referred as $produced^i$.
+\paragraph{Production} Each agent produces one good.
+The type of good produced by an agent $i$ is assigned to it at the beginning of the simulation, does not change through the simulation, and is referred to as $produced^i$.
 At each time step, each agent, produces a number of units (of its production good) equal to the number of goods, which ensures that enough is owned to be traded for other goods.
@@
 
-This function ensures that each good has the same weight in the final score (i.e.: managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent).
+This function ensures that each good has the same weight in the final score, i.e. managing to get only the right amount of a good with a high ``need'' value will not give a better score to the agent.
 %\begin{figure}[htp]
@@
 The complete score of an agent $i$ is termed $s^i$ and corresponds to the sum of the $s^i_j$.
-The agents will choose the model from whom the price vector should be copied among the agents that produce the same good and have the highest score.
+An agent will choose from whom the price vector should be copied among the agents that produce the same good and have the highest score.
 In practice, the worst two percent of the agents (in terms of score) will copy the prices of the best two percent.
@@
 
-If a trade is possible the two agents will exchange the agreed quantities.
+If a trade is possible, the two agents will exchange the agreed quantities.
 If the trade is not possible, the agent will continue to look at random partners for this good until either a partner is found or $TradeThreshold$ agents have been tried.
@@
 
-\paragraph{Innovation}
-
-In a trading environment it seems unlikely that a price will change radically to a very different value.
+\paragraph{Innovation} In a trading environment it seems unlikely that a price will change radically to a very different value.
 Therefore, a new and more realistic mechanism is proposed.
@@
 
-\paragraph{Expected outcome}
-
-Based on the set of implementations presented and given the equations (\ref{eq:score}) and (\ref{eq:trade}), it is expected that the prices will converge to value allowing each agent to obtain quantities of resources exactly equivalent to the needs.
+\paragraph{Expected outcome} Based on the set of implementations presented and given the equations (\ref{eq:score}) and (\ref{eq:trade}), it is expected that the prices will converge to value allowing each agent to obtain quantities of resources exactly equivalent to the needs.
 The best possible price of all good satisfies the equations :
@@
 The remaining experimental setups are using 500 agents, 3 number of goods (3,6 and 9) and three values of $\mu$ (0.004,0.016 and 0.064).
-For each setup we have performed 100 runs of 10000 timestep each.
+For each setup, we have performed 100 runs of 10000 timestep each.
 The trading model is tested on an experimental setups using 3 goods, 500 agents and $\mu$ equal to 0.004.
@@
 		\multicolumn{2}{r}{}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
-			N&$\mu$ & $\alpha$ (sd) & $p$-value (sd - pr) &$\alpha$ (sd)\\\hline
+			N&$\mu$ & $\alpha$ ($sd$) & $p$-value ($sd$ - $pr$) &$\alpha$ ($sd$)\\\hline
 		250	&0.004&1.53 (0.03)&0.58 (0.24 - .01)&1.54 (0.02)\\
@@
 	\end{tabular}
-	\caption{Mean $\alpha$ \& sd are calculate on 100 runs for our results, and 5 runs for Bentley et.
+	\caption{Mean $\alpha$ \& $sd$ are calculated on 100 runs for our results, and 5 runs for Bentley et.
 al.
-2004, pr is the percent of run for which the $p$-value<0.05 (we reject the hypothese that the distribution follow a power law).}
+2004.
+$pr$ is the percentage of run for which the $p$-value is less than 0.05, i.e.
+the percentage of runs for which we rejected the null-hypotheses stating that the distribution follow a power law.}
 	\label{tab:mualpha}
@@
 
-Nonetheless, for high value of $\mu$, previous works report that the distribution of variant follow a power law~\cite{bentley_random_2004}.
+Nonetheless, for high values of $\mu$, previous works report that the distribution of variant follow a power law~\cite{bentley_random_2004}.
 This claim is based on the fact that the estimated $\alpha$ (estimation based on linear regression on the log-log curve) has a high correlation coefficient.
@@
 Visual analysis reveals that independently of the number of goods, the distributions obtained are exactly the same.
-Therefore it is no surprise that, for each innovation rate, the properties of the distribution of prices does not depend of the number of goods.
+Therefore it is no surprise that, for each innovation rate, the properties of the distribution of prices does not depend on the number of goods.
 
@@
 All runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.
-In all following graph  a variant is one price for one given good.
+In all following graph  a variant is one price of one given good.
 The distributions are first computed for each good independently and then averaged together.
@@
 On figure~\ref{fig:2setDi}.a) it appears that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis.
-In more details, the proportion distribution has a plateau of common prices (a number of prices share similar and high proportion), which shows that, when trade is taken into account, the most common variants are more diverse.
+In more details, the proportion distribution has a plateau of common prices (a number of prices share similar and high proportions), which shows that, when trade is taken into account, the most common variants are more diverse.
 
@@
 On figure~\ref{fig:2setDi}.c) we observe a strong reduction in the size of the plateau and an important difference between the two distributions.
-This analysis highlights the importance of the \emph{innovation} process in the distribution of prices created by the trading model.
-This mechanism, by preventing the creation of totally random new price, leads to the creation of few similar prices obtaining high scores.
+This analysis highlights the importance of the \emph{innovation} process of the trading model in the distribution of prices.
+This mechanism, by preventing the creation of totally random new price, promotes the creation of few similar prices.
 
@@
 The y-axis shows the score computed and the x-axis shows the timesteps.
-The left plot shows the results obtained in the ``cultural transmission'' model and the right plot shows the results obtained in the trading model.
+The left plot shows the results obtained in the ``neutral model'' and the right plot shows the results obtained in the ``trading model''.
 
@@
 These are presented in figure~\ref{fig:ratioEvol} for the 100 runs relying the experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.
-For all runs, all agents and at each iteration we compute the difference between the price used by the agent $V_g$ and the optimal price $\tilde{V}_g$.
-Record that the optimal price for a good is given in equation~\ref{eq:optimum}.
-All the measures performed are presented as boxplots where the results for 100 runs are condensed.
+For all runs, all agents and at each iteration we compute the difference between the price used by the agent $V_g$ and the optimal price $\tilde{V}_g$ (given by equation~\ref{eq:optimum}).
+The measures performed are presented as boxplots condensing the results for 100 runs.
 
@@
 	\end{center}
-	\caption{Evolution of the mean of the difference between the estimated value $v^i_g$ and the optimal value $\tilde{v}^i_g$ (as calculated with the equations~\ref{eq:optimum}) for a good $g$ and an agent $i$.
+	\caption{Evolution of the mean of the difference between the estimated value $v^i_g$ and the optimal value $\tilde{v}^i_g$ (calculated with equation~\ref{eq:optimum}) for a good $g$ and an agent $i$.
 As the optimal value $\tilde{v}^i_g$ depends on which good is produced by $i$, the mean of the difference between the estimated price and the optimal one is computed between all the agents that produce the same good.
@@
 The trading mechanism can be naturally implemented in different ways, each reflecting a specific theory, and thus allowing their comparisons.
-The cultural transmission mechanism also can be modified by including for example the a crossover between the cultural trait of multiple agents.
+The cultural transmission mechanism also can be modified by including for example a crossover between the cultural trait of multiple agents.
 The trade network (which in this work can be interpreted as fully connected) can also be modified to study the effect of slow connections or the rupture of certain connections.

### 2015-07-02 article.tex
polish color of refs, add link to upload of text

@@
  \usepackage{multirow}
+  \usepackage[a4paper,pagebackref,hyperindex=true]{hyperref}
+\usepackage{color}
+\definecolor{linkcol}{rgb}{0,0,0.4} 
+\definecolor{citecol}{rgb}{0.5,0,0} 
+\definecolor{pylabgreen}{RGB}{0,128,0}
+\definecolor{pylabpink}{RGB}{255,192,203}
+\definecolor{pylabblue}{RGB}{36,36,255}
+\definecolor{pylabgrey}{RGB}{128,128,128}
+\hypersetup
+{
+bookmarksopen=false,
+pdftitle=Modelling the Co-evolution of Trade and Culture in Past Societies,
+pdfauthor="Carrignon Montanier Rubio-Campillo", %auteur du document
+pdfsubject="", %sujet du document
+%pdftoolbar=false, %barre d'outils non visible
+pdfmenubar=true, %barre de menu visible
+pdfhighlight=/O, %effet d'un clic sur un lien hypertexte
+colorlinks=true, %couleurs sur les liens hypertextes
+pdfpagemode=None, %aucun mode de page
+pdfpagelayout=SinglePage, %ouverture en simple page
+pdffitwindow=true, %pages ouvertes entierement dans toute la fenetre
+linkcolor=linkcol, %couleur des liens hypertextes internes
+citecolor=citecol, %couleur des liens pour les citations
+urlcolor=linkcol %couleur des liens pour les url
+}
 
@@
 
-\WSCpagesetup{Carrignon, Montanier, and Rubio}
+\WSCpagesetup{Carrignon, Montanier, and Rubio-Campillo}
 
@@
 The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}.
+The experiments are available online\footnote{\href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}} for the Pandora simulator~\cite{rubiocampillo_2014}.
 
@@
 The simulations have been done in the supercomputer MareNostrum at Barcelona Supercomputing Center - Centro Nacional de Supercomputación (The Spanish National Supercomputing Center).
-The source code of the model is licensed under a GNU General Public License and will be available for download at publication.
+The source code of the model is licensed under a GNU General Public License.
 

### 2015-07-02 article.tex
again minor corrections to the text

@@
 To create this framework we propose an Agent-Based Model relying on agents producing, exchanging and associating values to a list of goods.
-We first present the key concepts of the framework and two examples of its implementation which allow us to show the flexibility of our framework.
-We then compare the results obtained by the two models, thus validating the structure of the framework.
+We present the key concepts of the framework and two examples of its implementation which allow us to show the flexibility of our framework.
+Moreover, we compare the results obtained by the two models, thus validating the structure of the framework.
 Finally, we validate the implementation of a trading model by studying the price structure it produces.
@@
 
-We now study the results obtained in more detail by investigating the ability of the population to find the good price to perform exchanges between each other.
-This is done first by observing the score of all agents in each of the two different models.
+The results obtained with the trade model are studied in more detail by investigating the ability of the population to find the price most suited for exchanges.
+This is done by first measuring the score of all agents in each of the two different models.
 The figure~\ref{fig:scoreEvol} uses again the results obtained from 100 runs for each model where all runs rely on the same experimental setup using 3 goods, 500 agents and $\mu$ equal to 0.004.

### 2015-07-02 article.tex
p-value and pr-value for 500 agents and selection percent correction

--- 2015-07-02 article.tex
@@
 An agent will choose from whom the price vector should be copied among the agents that produce the same good and have the highest score.
-In practice, the worst two percent of the agents (in terms of score) will copy the prices of the best two percent.
+In practice, the worst (in terms of score) 20 percent of the agents producing the same good will copy the prices of the best twenty percent producing the same good.
 This selection process is detailed in algorithm~\ref{algo:selectionCulture}.
@@
 	\scriptsize
-	\State	$ToGet = 0.2 \times \#Pop$
+	\State	$ToGet = 0.2 \times \frac{\#Pop}{\#Good}$
 	\For{$g \in Good$}
@@
 		250	&0.004&1.53 (0.03)&0.58 (0.24 - .01)&1.54 (0.02)\\
-			&0.016&1.57 (0.02)&0.35 (0.26 - .05)&1.57 (0.01)\\
+			&0.016&1.57 (0.02)&0.35 (0.28 - .05)&1.57 (0.01)\\
 			&0.064&1.66 (0.01)&0.0 (0.00 - 1)&1.67 (0.01)\\\hline
-		500	&0.004&1.50 (0.02)&0.6 (0.05)&1.53 (0.03)\\
-			&0.016&1.55 (0.03)&0.3 (0.05)&1.61 (0.04)\\
-			&0.064&1.78 (0.08)&0.0 (0.00)&1.81 (0.10)\\
+		500	&0.004&1.50 (0.02)&0.59 (0.28 - .02 )&1.53 (0.03)\\
+			&0.016&1.55 (0.03)&0.15 (0.17 - .10 )&1.61 (0.04)\\
+			&0.064&1.78 (0.08)&0.0 (0.00 - 1)&1.81 (0.10)\\
 	\end{tabular}
@@
 	\end{center}
-	\caption{Proportions distribution, where each points represent the mean for 100 runs, for: a) the neutral and the trading models.
+	\caption{Frequencies distribution, where each points represent the mean for 100 runs, for: a) the neutral and the trading models.
 b) the neutral model and the trading model without the trading innovation process.
@@
 On figure~\ref{fig:2setDi}.a) it appears that the implementation of trade mechanisms leads to a distribution of prices departing from the neutral hypothesis.
-In more details, the proportion distribution has a plateau of common prices (a number of prices share similar and high proportions), which shows that, when trade is taken into account, the most common variants are more diverse.
+In more details, the frequencies distribution has a plateau of common prices (a number of prices share similar and high proportions), which shows that, when trade is taken into account, the most common variants are more diverse.
 

### 2015-07-20 article.tex
revision etape 3 miss Xavi Bio and Bigger Legend

@@
  \usepackage{multirow}
-  \usepackage[a4paper,pagebackref,hyperindex=true]{hyperref}
+  %\usepackage[a4paper,pagebackref,hyperindex=true]{hyperref}
 \usepackage{color}
@@
 \definecolor{pylabgrey}{RGB}{128,128,128}
-\hypersetup
-{
-bookmarksopen=false,
-pdftitle=Modelling the Co-evolution of Trade and Culture in Past Societies,
-pdfauthor="Carrignon Montanier Rubio-Campillo", %auteur du document
-pdfsubject="", %sujet du document
-%pdftoolbar=false, %barre d'outils non visible
-pdfmenubar=true, %barre de menu visible
-pdfhighlight=/O, %effet d'un clic sur un lien hypertexte
-colorlinks=true, %couleurs sur les liens hypertextes
-pdfpagemode=None, %aucun mode de page
-pdfpagelayout=SinglePage, %ouverture en simple page
-pdffitwindow=true, %pages ouvertes entierement dans toute la fenetre
-linkcolor=linkcol, %couleur des liens hypertextes internes
-citecolor=citecol, %couleur des liens pour les citations
-urlcolor=linkcol %couleur des liens pour les url
-}
+
+%\hypersetup
+%{
+%bookmarksopen=false,
+%pdftitle=Modelling the Co-evolution of Trade and Culture in Past Societies,
+%pdfauthor="Carrignon Montanier Rubio-Campillo", %auteur du document
+%pdfsubject="", %sujet du document
+%%pdftoolbar=false, %barre d'outils non visible
+%pdfmenubar=true, %barre de menu visible
+%colorlinks=true, %couleurs sur les liens hypertextes
+%pdfpagemode=None, %aucun mode de page
+%pdfpagelayout=SinglePage, %ouverture en simple page
+%pdffitwindow=true, %pages ouvertes entierement dans toute la fenetre
+%linkcolor=black, %couleur des liens hypertextes internes
+%citecolor=black, %couleur des liens pour les citations
+%urlcolor=linkcol %couleur des liens pour les url
+%}
 
@@
 \usepackage{xcolor}
+
 \usepackage{cite}
@@
 
+\usepackage[pdftex,colorlinks=true,urlcolor=blue,citecolor=black,
+anchorcolor=black,linkcolor=black,pdftitle=Modelling the Co-evolution of Trade and Culture in Past Societies,pdfauthor="Carrignon Montanier Rubio-Campillo"]{hyperref}
+
 \begin{document}
@@
 
-\title{Modelling the Co-evolution of Trade and Culture in Past Societies}
+\title{MODELLING THE CO-EVOLUTION OF TRADE AND CULTURE IN PAST SOCIETIES}
 
-\maketitle
-
-\begin{figure*}[htb]
-{
-\centering
-Simon Carrignon\\ 
+\author{Simon Carrignon\\ 
 	Jean-Marc Montanier\\
-Xavier Rubio-Campillo\\
-\vspace{12pt}
+	Xavier Rubio-Campillo\\[12pt]
 	Barcelona Supercomputing Center\\
 	Carrer de Jordi Girona, 29, \\
-08034 Barcelona, Spain\\
+	Barcelona, 08034, SPAIN
 }
-\end{figure*}
+\maketitle
 
@@
 The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}.
-The experiments are available online\footnote{\href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}} for the Pandora simulator~\cite{rubiocampillo_2014}.
+The experiments are \href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{available online} \cite{github_2015} for the Pandora simulator~\cite{rubiocampillo_2014}.
 
@@
 \begin{table}
+\caption{Table of parameters}\label{tab:parameters}
+	\scriptsize
 \begin{center}
@@
 \end{tabular}
-\caption{Table of parameters}\label{tab:parameters}
 \end{center}
@@
 \begin{table}[!h]
+	\caption{Mean $\alpha$ \& $sd$ are calculated on 100 runs for our results, and 5 runs for Bentley et.
+al.
+2004.
+$pr$ is the percentage of run for which the $p$-value is less than 0.05, i.e.
+the percentage of runs for which we rejected the null-hypotheses stating that the distribution follow a power law.}
 	\centering
+	\scriptsize
 	\begin{tabular}{cc|ccc}
@@
 	\end{tabular}
-	\caption{Mean $\alpha$ \& $sd$ are calculated on 100 runs for our results, and 5 runs for Bentley et.
-al.
-2004.
-$pr$ is the percentage of run for which the $p$-value is less than 0.05, i.e.
-the percentage of runs for which we rejected the null-hypotheses stating that the distribution follow a power law.}
 	\label{tab:mualpha}
@@
 
-\section{Acknowledgements}
+\section*{ACKNOWLEDGEMENTS}
 
@@
 \bibliography{wsc.bib}
+
+\section*{AUTHOR BIOGRAPHIES}
+\noindent {\bf SIMON CARRIGNON} is a PhD student at the Pompeu Fabra University.
+He holds a M.S.
+in in Cognitive Sciences and a M.A.
+in History and Philosophy of Science.
+His work focus on the use of computer modeling and evolutionary method to study Complex Systems.
+His email address is \email{simon.carrignon@bsc.es}.
+
+\noindent {\bf JEAN-MARC MONTANIER} has obtained his engineering title in the domain of embedded computing.
+Since then, he has complete a Ph.D.
+in collective robotics at Universit\'e Paris-Sud XI.
+The topic of this Ph.D.
+was focused on the adaptation of a swarm of robots to unknown environments.
+His latest work in this area has addressed the learning of cooperative strategies, as well as the division of labour.
+He is now working in a new domain which proposes to apply Agent-Based Models to study economical and cultural evolution.
+His email address is \email{jeanmarc.montanier@bsc.es}.
+
+\noindent {\bf XAVIER RUBIO-CAMPILLO}
+
 \end{document}

### 2015-07-20 article.tex
revision etape 3 all bio miss Bigger Legend

@@
 \section*{AUTHOR BIOGRAPHIES}
-\noindent {\bf SIMON CARRIGNON} is a PhD student at the Pompeu Fabra University.
+\noindent {\bf SIMON CARRIGNON} is a PhD student in Computer Applications in Science and Engineering, Barcelona Supercomputing Center.
 He holds a M.S.
-in in Cognitive Sciences and a M.A.
+in Cognitive Sciences and a M.A.
 in History and Philosophy of Science.
-His work focus on the use of computer modeling and evolutionary method to study Complex Systems.
+His works focused on the use of computer modeling and evolutionary method to study Complex Systems, ranging from Evolutionary Biology to Human and Cultural Dynamics.
 His email address is \email{simon.carrignon@bsc.es}.
 
-\noindent {\bf JEAN-MARC MONTANIER} has obtained his engineering title in the domain of embedded computing.
-Since then, he has complete a Ph.D.
-in collective robotics at Universit\'e Paris-Sud XI.
-The topic of this Ph.D.
-was focused on the adaptation of a swarm of robots to unknown environments.
-His latest work in this area has addressed the learning of cooperative strategies, as well as the division of labour.
-He is now working in a new domain which proposes to apply Agent-Based Models to study economical and cultural evolution.
-His email address is \email{jeanmarc.montanier@bsc.es}.
+\noindent {\bf JEAN-MARC MONTANIER} is Researcher in Computer Applications in Science and Engineering, Barcelona Supercomputing Center.
+He has obtained his engineering title in the domain of embedded computing and holds a Ph.D.
+in collective robotics.
+His topics of interest focused on Agent-Based Modeling, swarm adaptation, learning of cooperative strategies, division of labour and more recently study of economical and cultural evolution.
+His email address is \email{jean.montanier@bsc.es}.
 
-\noindent {\bf XAVIER RUBIO-CAMPILLO}
+\noindent {\bf XAVIER RUBIO-CAMPILLO} is Researcher in Computer Applications in Science and Engineering, Barcelona Supercomputing Center.
+He has a transdisciplinary training of Computer Science (BSc) and Humanities (PhD) with a strong emphasis on the study of past societies using historical and archaeological contexts.
+His main research line is the application of formal models to explore the processes of cultural evolution in past societies.
+His email address is \email{xavier.rubio@bsc.es}.
 

### 2015-07-22 article.tex
version sumbimett

@@
 The \emph{innovation} process, termed ``unbounded'', is triggered with a low probability ($\mu$) and draw a new random value to replace an element $v^i_j$.
-The probabilities to trigger \emph{cultural transmission} and \emph{innovation} are presented with other parameters in table~\ref{tab:parameters}.
+%The probabilities to trigger \emph{cultural transmission} and \emph{innovation} are presented with other parameters in table~\ref{tab:parameters}.
 
@@
 Again 100 runs of 10000 timesteps are performed.
-The complete set of parameters tested on both models is presented in table~\ref{tab:parameters}.
-The experiments are \href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{available online} \cite{github_2015} for the Pandora simulator~\cite{rubiocampillo_2014}.
+The experiments, as well as the parameters used to run those experiments, are \href{https://github.com/montanier/CMR-WSC-CoEvolutionTradeCulture}{available online} \cite{github_2015} for the Pandora simulator~\cite{rubiocampillo_2014}.
 
@@
 
-\begin{table}
-\caption{Table of parameters}\label{tab:parameters}
-	\scriptsize
-\begin{center}
-\begin{tabular}{@{}ll@{}}
-\toprule
-Parameter & Value \\
-\midrule
-Number of goods & $\{1,3,6,9\}$ \\
-Number of agents & $\{250,500\}$ \\
-Innovation probability ($\mu$) & $\{0.004,0.016,0.064\}$ \\
-Innovation range ($\beta$) & 0.005\\
-Cultural transmission probability & .001\\
-CulturalStep &  10 \\
-TradeThreshold & 100  \\
-TimeSteps & 10000 \\
-\bottomrule
-\end{tabular}
-\end{center}
-\end{table}
+%\begin{table}
+%\caption{Table of parameters}\label{tab:parameters}
+%	\scriptsize
+%\begin{center}
+%\begin{tabular}{@{}ll@{}}
+%\toprule
+%Parameter & Value \\
+%\midrule
+%Number of goods & $\{1,3,6,9\}$ \\
+%Number of agents & $\{250,500\}$ \\
+%Innovation probability ($\mu$) & $\{0.004,0.016,0.064\}$ \\
+%Innovation range ($\beta$) & 0.005\\
+%Cultural transmission probability & .001\\
+%CulturalStep &  10 \\
+%TradeThreshold & 100  \\
+%TimeSteps & 10000 \\
+%\bottomrule
+%\end{tabular}
+%\end{center}
+%\end{table}
 
@@
 His works focused on the use of computer modeling and evolutionary method to study Complex Systems, ranging from Evolutionary Biology to Human and Cultural Dynamics.
-His email address is \email{simon.carrignon@bsc.es}.
+His email address is \email{simon.carrignon@bsc.es}.\\
 
@@
 His topics of interest focused on Agent-Based Modeling, swarm adaptation, learning of cooperative strategies, division of labour and more recently study of economical and cultural evolution.
-His email address is \email{jean.montanier@bsc.es}.
+His email address is \email{jean.montanier@bsc.es}.\\
 
@@
 His main research line is the application of formal models to explore the processes of cultural evolution in past societies.
-His email address is \email{xavier.rubio@bsc.es}.
+His email address is \email{xavier.rubio@bsc.es}.\\
 
